### 2018-10-02 paper/boneyard.tex
added paper from Overleaf and also added CDL-bibliography as submodule

, the gross \textit{structural} aspects of our brain are essentailly static over the timescales of typical experiments (on the order of

Current human brain recording techniques are fraught with compromise.
Commonly used approaches include functional magnetic resonance imaging
(fMRI), scalp electroencephalography (EEG), and magnetoencephalography
(MEG).  For each of these techniques, neuroscientists
and electrophysiologists must choose to optimize spatial resolution
at the cost of temporal resolution (e.g.\ as in fMRI) or temporal
resolution at the cost of spatial resolution (e.g.\ as in EEG
and MEG).  A less widely used approach (due to requiring work with
neurosurgical patients) is to record from electrodes implanted
directly onto the cortical surface (electrocorticography; ECoG) or
into deep brain structures (intracranial EEG; iEEG).  However, these
intracranial approaches also require compromise: the high temporal and
spatial resolutions of intracranial recordings come at the cost of
substantially reduced brain coverage, since safety considerations
limit the number of electrodes one may implant in a given patient's
brain.  Further, the locations of implanted electrodes are determined by clinical,
rather than research, needs.

%Beamforming: huge advance for scalp recordings, but the inverse
%problem is fundamentally ambiguous.  This limits the precision with
%which one can measure activity from deep brain structures.
An increasingly popular approach is to improve the effective spatial resolution
of MEG or scalp EEG data by using a geometric approach called
\textit{beamforming} to solve the biomagnetic or bioelectrical inverse
problem~\cite{Sarv87}.  This approach entails using detailed brain
conductance models (often informed by high spatial resolution
anatomical MRI images) along with the known sensor placements
(localized precisely in 3D space) to reconstruct brain signals
originating from theoretical point sources deep in the brain (and far
from the sensors).  Traditional beamforming approaches must overcome
two obstacles.  First, the inverse problem beamforming seeks to solve
has infinitely many solutions.  Researchers have made traction towards
constraining the solution space by assuming that signal-generating
sources are localized on a regularly spaced grid spanning the brain
and that individual sources are small relative to their distances to
the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
some ways much more serious, obstacle is that the magnetic fields
produced by external (noise) sources are substantially stronger than
those produced by the neuronal changes being sought (i.e.\ at deep structures, as measured by sensors at the scalp).  This means that
obtaining adequate signal quality often requires averaging the measured
responses over tens to hundreds of responses or trials (e.g. see
review by~\cite{HillEtal05}).

Another approach to obtaining high spatial and temporal resolution
neural data has been to collect fMRI and EEG data simultaneously.
Simultaneous fMRI-EEG has the potential to balance the high spatial
resolution of fMRI with the high temporal resolution of scalp EEG,
thereby, in theory, providing the best of both worlds.  In practice,
however, the signal quality of both recordings suffers substantially
when the two techniques are applied simultaneously (e.g. see review
by~\cite{HustEtal12}).  In addition, the experimental designs that are
ideally suited to each technique individually are somewhat at odds.
For example, fMRI experiments typically lock stimulus presentation
events to the regularly spaced image acquisition time (TR), which
maximizes the number of post-stimulus samples.  By contrast, EEG
experiments typically employ jittered stimulus presentation times to
maximize the experimentalist's ability to distinguish electrical brain
activity from external noise sources such as from 60 Hz alternating
current power sources.

%Direct intracranial recordings are the gold standard method for
%measuring activity from deep brain structures in both humans and
%animals.
%However, one can only implant a limited number of electrodes in a
%given person's brain.  This begs the question: what can we infer
%about the activity exhibited by the rest of that person's brain,
%given what we learn from recordings taken from \textit{other people's
%brains}?
The current ``gold standard'' for precisely localizing signals and
sampling at high temporal resolution is to take (ECoG or iEEG)
recordings from implanted electrodes (but from a limited set of
locations in any given brain).  This begs the following question: what
can we infer about the activity exhibited by the rest of a person's
brain, given what we learn from the limited intracranial recordings we
have from their brain and additional recordings taken from
\textit{other} people's brains?  Here we develop an approach, based on
Gaussian process regression~\cite{Rasm06}, that uses data from
multiple people to estimate activity at arbitrary
locations in each person's brain (i.e., independent of their electrode
placements).  We test this \textit{Super EEG} approach using two large
datasets of intracranial recordings collected as neurosurgical patients
studied and recalled random word lists~\cite{SedeEtal03, SedeEtal07a,
  SedeEtal07b, MannEtal11, MannEtal12}.  We show that the Super EEG
algorithm recovers signals well from electrodes that were held out of
the training dataset.  We replicate this finding using a second dataset, which contains data from two experiments for each patient, allowing us to also probe the task-specific contributions to reconstruction accuracy.  Additionally, we examine the factors that influence how
accurately activity may be estimated (recovered), which may have important
implications for electrode design and for electrode placement in
neurosurgical applications.

Further, if some aspects of our connectomes are static, can we use them to fill in ``missing'' data?  In other words, given recordings from a subset of brain locations, how reliably can activity patterns from the rest of the brain be inferred using an estimated static connectome?  And to what extent can those

Human \textit{Super EEG}\footnote{The term ``Super EEG'' was
coined by Robert J. Sawyer in his popular science fiction novel
\textit{The Terminal Experiment}~\cite{Sawy95}} entails
measuring ongoing activity from every cell in a living human brain
at millisecond-scale temporal resolutions.  Although direct
cell-by-cell Super EEG recordings are impossible using existing
methods, here we present a technique for \textit{inferring} neural
activity at millimeter-scale spatial resolutions and millisecond-scale temporal resolutions by fitting a model to existing human intracranial electrophysiological recordings.  Our approach, based
on Gaussian process regression, relies on two assumptions.  First,
we assume that some of the correlational structure of people's
brain activity is similar across individuals.  Second, we resolve
ambiguities in the data by assuming that neural activity from
nearby sources will tend to be similar, all else being equal.  One
can then ask, for an arbitrary individual's brain: given what we
know about the correlational structure of \textother people's brains,
and given the recordings we made from electrodes implanted in this
person's brain, how would those recordings most likely have looked
at \textit{other} locations throughout this person's brain?  Our work examines a deep neuroscientific question: given recordings for one set of locations from a given person, how much can we infer about activity patterns throughout the rest of the same person's brain as those recordings were taken?

The above finding that activity at densely sampled brain areas can be
(slightly) better reconstructed than at sparsely sampled brain areas
could have important implications for patient surgeries.  For example,
when implanting electrodes into new patients, perhaps those electrodes
should target regions

we hypothesized might influence the quality of the
data reconstructions is the

Whereas the above analyses show that the Super EEG algorithm may be
used to estimate time-varying LFPs throught the brain using data from a small
number of implanted electrodes,

Having established that data within and across patients may be used to
accurately estimate neural recordings from unsampled locations, we
next wondered whether certain electrode placements might be especially
informative to these estimates.

We also carried out an analogous analysis
across patients by comparing the average correlation coefficients from
each patient obtained using Super EEG versus using the nearest
neighbor's voltages ($t(XXX) = XXX, p = XXX$).

%average correlation by nearest within-subject and across-subject electrode
%distance

%average correlation by holding out electrodes at various distances
%within subject (include none and all).  note that the all case can
%only be included for the covariance estimation; for the final
%reconstruction step that datapoint should be separate (on the plot)
%and should indicate reconstruction correlation using just the
%furthest-away electrode.

%map showing how informative each location is: if you include
% electrodes within a searchlight surrounding the location vs. don't
% include them, how substantially do the average reconstruction
% correlations change?  use k-means clustering to find sets of
% electrodes whose correlation change profiles group together, and
% pick the electrode with the highest correlation difference within
% each set.  (show maps of each correlation profile.)  show the
% average reconstruction correlation as a function of the numbers of
% electrodes near these regions.  this can be used to suggest
% electrode placements for the best accuracy.

%maybe there's a dataset I could use that includes single neuron
%recordings?  I could use broadband LFPs to predict firing rates.

%The preceding analyses elucidate how the quality of the Super EEG
%algorithm's estimates varies with spatial location, and how the
%predictive power of the recordings vary with spatial location.  In
%addition to the spatial properties of the electrodes, the temporal
%resolutions of the recordings can vary substantially from patient to
%patient (e.g. according to the sampling rate of each hospital's
%clinical recording hardware).  In the above analyses, each patients'
%data were reconstructed at the sampling rates of their original
%recordings.  However, these across-patient differences in sampling
%rates could affect the degrees to which different features of the
%underlying neural activity were reflected in the recordings.  For
%example, high frequency oscillations could not be measured in low
%temporal resolution recordings, whereas they may be measured using
%high temporal resolution recordings.  In turn, this could affect the
%estimates of how different brain structures were interacting, such
%that the estimates contributed by some patients' data would be driven
%by high frequency activity that was not present in other patients'
%data due to differences in sampling rates.

% To evaluate the quality of the reconstruction of a given
% electrode from a given patient $s$, we computed the average Pearson's
% correlation (across recording sessions) between the Super
% EEG-reconstructed voltage trace, $\hat{Y}_{s,k}$, and the observed
% voltage trace, $Y_{s,k}$ at that location (specifically, the corresponding
% columns of those matrices).  (Note that here $k$ denotes the recording
% session number.)  In other words, we computed $\hat{Y}_{s,k,\beta}$
% using Equations~\ref{eqn:Kba}, \ref{eqn:Kaa}, and
% \ref{eqn:reconstruction}, but we treated the to-be-reconstructed
% electrode location $i$ as a member of $\beta$ (the unobserved set of
% recording locations) rather than as a member of $\alpha$ (the observed
% set of recording locations).

We present a method for inferring local field potentials throughout the brain from recordings at a limited number sites.

Methods overview. Electrode
      locations.  Each dot reflects the location of a single
    electrode in the dataset.  One patient's electrode locations are
    highlighted in red and the to-be-reconstructed recording location
    is highlighted in blue. \textbf{B. Radial basis function (RBF).}
    Each electrode contributed by the patient (red) weights on the
    full set of locations under consideration (all dots in panel A,
    defined as $\bar{R}$ in the text).  The weights fall off with
    positional distance (in MNI space) according to an RBF.
    \textbf{C. Per-patient correlation matrices.}  After computing the
    pairwise correlations between the recordings from each patient's
    electrodes, we use RBF-weighted averages to estimate correlations
    between all locations in $\bar{R}$.  We obtain an estimated
    full-brain correlation matrix using each patient's
    data. \textbf{D.  Combined correlation matrix.}  We estimate a
    single full-brain correlation matrix by averaging 
    the patient-specific correlation matrices.  \textbf{E.
      Reconstructing ``missing'' activity.}  Given the observed
    activity from the patient's electrodes and the estimated
    correlation matrix (Panel D), we can compute a maximum likelihood
    estimate of the voltage trace at any location in $\bar{R}$.  An
    example reconstruction (at the blue dot in Panel A) is shown in
    gray.

% Across all electrodes, from all patients, the correlations between
% observed and estimated activity were reliably greater than 0
% (Fig.~\ref{fig:corrmap}B; $t(4148) = 107, p < 10^{-10}$; $t$-test on
% the distribution of $z$-transformed correlation
% coefficients). Furthermore, across patients the average correlations
% between observed and estimated activity were also reliably greater
% than 0 $(t(66) = 23.3, p < 10^{-10}$; $t$-test on the distribution of
% averaged $z$-transformed correlation coefficients for each patient).
% Overall, these analyses suggest that data from held-out electrodes may
% be reliably estimated using Super EEG.

% %%% should the remaining equations be in this section or in the methods?
% Finally, we wished to infer activity at all locations in the standard MNI152 brain. First, we calculate the location similarity $\theta$ between each voxel location in the standard MNI152 brain $i$ and every location $j \in \bar{R}$. With this similarity value, we can create a map in MNI space by interpolating a correlation value $\hat{\rho}$ at every voxel $i$ using the corresponding correlation value $\rho$ at each location in $\bar{R}$ with the following equations:

% \begin{align}
% \hat{\rho}(i) &= \mathrm{r}\left\{\frac{\sum_{j=1}^{|\bar{R}|}\theta(i,j)\cdot\mathrm{z}(\rho(i))}{\sum_{j=1}^{|\bar{R}|}\theta(i,j)} \right\}, \mathrm{where}\\
% \theta(i,j) &= \mathrm{exp} \left\{-||i-j||^2\right\}.\\
% \end{align}

% As mentioned above, the reconstruction procedure for $\hat{Y}_i$ cannot account
% for across-electrode impedance differences, so the estimates will be
% off by a constant scaling factor.

% % already mention this above...

% the next section addresses 'patient 1' and 'electrode 1'... keep this way of describing??

% We also used a permutation-based procedure to assess which
% correlations were both positive and statistically reliable (see
% \textit{Supplemental Methods}).

One potential application of the Super EEG algorithm is localizing
seizures.  For example, whereas examining recordings from implanted
electrodes can yield insights into which electrode is closest to where
the seizure was kindled, the Super EEG algorithm could provide a full 3D
map of activity throughout the brain at each moment in time as the
seizure evolves.  However, reconstruction quality

, which we hypothesized might be
related to how

More generally, we can ask about the quality of this type of
reconstruction across all electrodes and patients in the dataset.
Figure~\ref{fig:corrmap}A displays the correlation between the
observed and estimated LFPs as a function of electrode location (i.e.,
holding out each electrode in turn, and comparing the estimated versus
observed data for the held-out electrode).  The map
reveals that the reconstruction quality varies somewhat with the spatial
location being considered.  Specifically, activity at locations that
receive dense electrode coverage within and across patients
(e.g. medial temporal lobe) is estimated more accurately than activity
at sparsely sampled locations (Fig.~\ref{fig:density}B).

### 2018-10-02 paper/main.tex
added paper from Overleaf and also added CDL-bibliography as submodule

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

%\usepackage{scicite}
\usepackage[numbers, square, sort, compress]{natbib}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left]{lineno}
\linenumbers
% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm

% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}

% Include your paper's title here

\title{Towards human Super EEG}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{Lucy L. W. Owen$^{1}$, Andrew C. Heusser$^{1}$, and Jeremy R. Manning$^{1\ast}$\\
\\
\normalsize{$^{1}$Department of Psychological and Brain Sciences,
  Dartmouth College,}\\
\normalsize{Hanover, NH 03755, USA}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle

\begin{abstract}
A growing body of literature over the past several decades reports that the dynamic correlational structure of functional neuroimaging data may be used to predict which moment of movie or story an individual is experiencing, identify which person's brain a recording came from, and identify the task a person is performing.  However, our structural (anatomical) connectome is roughly static for the duration of typical neuroimaging experiments.  How might these notions of dynamic functional connectomes versus static structural connectomes be reconciled?  We use two human electrocorticographic (ECoG) datasets to ask: to what extent can we use a static connectome model (trained using within versus across subject data, and within versus across task data) to explain dynamic full-brain activity patterns?  Given a fixed connectome model, and given recordings from a subset of brain locations, we test how reliably can one infer activity patterns throughout the rest of the brain.  Our model-based approach, termed \textit{SuperEEG}\footnote{The term ``Super EEG'' was
coined by Robert J. Sawyer in his popular science fiction novel
\textit{The Terminal Experiment}~\cite{Sawy95}}, is in itself useful for inferring full-brain activity patterns (at millimeter-scale spatial resolutions and millisecond-scale temporal resolutions) from ECoG recordings from a limited set of brain locations.  For both datasets, we found that full-brain activity patterns can be best explained using connectomes from \textit{other} people who performed a shared task.\\

\small{\textbf{Keywords: Electrocorticography (ECoG), intracranial electroencephalography (iEEG),
local field potential (LFP), epilepsy, maximum likelihood estimation, Gaussian process regression}}
\end{abstract}

Are our brain's networks static or dynamic?  And to what extent are the network properties of our brains stable across people and tasks?  One body of work suggests that our brain's \textit{functional} networks are dynamic~\citep[e.g., ][]{MannEtal18}, person-specific~\citep[e.g., ][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the gross anatomical structure of our brains changes meaningfully over the course of years as our brains develop, on the timescales of typical neuroimaging experiments (i.e., hours to days) our anatomical networks are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many aspects of brain anatomy, including white matter structure, is largely preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}  There are several possible means of reconciling this apparent contradiction between dynamic person- and task-specific functional networks versus stable anatomical networks.  For example, relatively small magnitude anatomical differences across people may be reflected in reliable functional connectivity differences.  Along these lines, one recent study found that diffusion tensor imaging (DTI) structural data is similar across people, but may be used to predict person-specific resting state functional connectivity data~\citep{BeckEtal18}.  Another (potentially complementary) possibility is that our functional networks are constrained by anatomy, but nevertheless exhibit rapid task-dependent changes~\citep[e.g., ][]{SporBetz16}.

Here we take a model-based approach to studying whether high spatiotemporal resolution activity patterns throughout the human brain may be explained by a static connectome model that is shared across people and tasks.  Specifically, we trained a model to take in recordings from a subset of brain locations, and then predict activity patterns during the same interval, but at \textit{other} locations that were held out from the model.  Our model, based
on Gaussian process regression, relies on three assumptions (each of which we test).  First, we assume that functional correlations are stable over time and across tasks.  Second, we assume that some of the correlational structure of people's brain activity is similar across individuals.  Third, we resolve
ambiguities in the data by assuming that neural activity from
nearby sources will tend to be similar, all else being equal.  After fitting the model to an ECoG dataset, one
can then ask (for a held-out individual's brain): given what we
know about the correlational structure of \textit{other} people's brains,
and given the recordings we made from electrodes implanted in this
person's brain, how would those recordings most likely have looked
at \textit{other} locations throughout this person's brain?  We named our general approach \textit{SuperEEG} because the trained model provides a means of inferring full-brain activity patterns at high spatiotemporal resolutions, using ECoG recordings taken from a limited set of brain locations.

We tested the SuperEEG approach using two large ECoG datasets. Dataset 1 comprises multi-hour recordings from 6876 electrodes taken across several recording sessions as 88 neurosurgical patients studied random word lists periodically throughout their day~\cite{SedeEtal03, SedeEtal07a,
  SedeEtal07b, MannEtal11, MannEtal12}.  Dataset 2 comprises recordings from XXX electrodes taken as XXX patients performed a series of two memory tasks~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  In both datasets, 
  we compared the predictions made using models trained across people to predictions made using within-person data.  We found that models that incorporate data from other patients yield far more reliable predictions about an individual patient's brain activity patterns than models trained solely on that individual's data.  This indicates that at least some functional correlations are common across people.  We also used Dataset 2 to compare predictions made using data from within task, across task, or combining within and across task data.  We found that all three approaches yielded reliable predictions, but the within task predictions were the most accurate.  This indicates that some aspects of our functional connectomes are common across tasks, whereas other aspects are task-specific.  Finally, all of the models we trained (within and across patients and tasks) assumed a static connectome and yielded above-chance accuracy.  This indicates that despite moment-by-moment fluctuations in the functional connectome, at least some aspects of our connectome appear to be stable over the course of several hours.

\section*{Approach}
The SuperEEG approach to inferring high temporal resolution full-brain activity patterns is outlined and summarized in
Figure~\ref{fig:methods}. We describe (in this section) and evaluate
(in \textit{Results}) our approach using a two large previously collected
dataset comprising multi-session intracranial recordings.  The first dataset was taken from
6876 electrodes implanted in the brains of 88 epilepsy
patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
  MannEtal12}.  We first applied a fourth order Butterworth notch filter to remove
60 Hz ($\pm$ .5 Hz) line noise.  We then excluded any electrodes that
showed putative epileptiform activity.  Specifically, we excluded from
further analysis any electrode that exhibited an average kurtosis of
10 or greater across all of that patient's recording sessions.  We
also excluded any patients with fewer than 2 electrodes that passed
this criteria, as the Super EEG algorithm requires measuring
correlations between 2 or more electrodes from each patient.
Altogether this yielded clean recordings from 4168 electrodes
implanted throughout the brains of 67 patients (Fig.~\ref{fig:methods}A). For the purposes of comparing task-specific contributions to reconstruction accuracy, we limited our analyses in the second dataset to patients that participated in two free recall experiments.  Applying the same kurtosis thresholding yielded clean recordings from 24 patients and 2975 electrodes for the second dataset. Each individual patient contributes
electrodes from a limited set of brain locations, which we localized
in a common space (MNI152); an example patient's 54 electrodes that
passed the predefined kurtosis test are highlighted in black and red.

The recording from a given electrode is maximally informative about
the activity of the neural tissue immediately surrounding its
recording surface.  However, brain regions that are distant from the
recording surface of the electrode also contribute to the recording,
albeit (often) to a much lesser extent.  One mechanism underlying these
contributions is volume conduction.  The precise rate of falloff due
to volume conduction (i.e. how much a small volume of brain tissue at
location $x$ contributes to the recording from an electrode at
location $\eta$) depends on the size of the recording surface, the
electrode's impedance, and the conductance profile of the volume of
brain between $x$ and $\eta$.  As an approximation of this intuition,
we place a Gaussian radial basis function (RBF) at the location $\eta$
of each electrode's recording surface (Fig.~\ref{fig:methods}B).  We
use the values of the RBF at any brain location $x$ as a rough
estimate of how much structures around $x$ contributed to the
recording from location $\eta$:

\begin{align}
  \mathrm{rbf}(x|\eta,\lambda) & =
  \mathrm{exp}\left\{ -\frac{||x - \eta||^2}{\lambda} \right\},\label{eqn:rbf}
\end{align}
where the width variable $\lambda$ is a parameter of the algorithm
(which may in principle be set according to location-specific tissue
conductance profiles) that governs the level of spatial smoothing.  In
choosing $\lambda$ for the analyses presented here, we sought to
maximize spatial resolution (which implies a small value of $\lambda$)
while also maximizing the algorithm's ability to generalize to any
location throughout the brain, including those without dense electrode
coverage (which implies a large value of $\lambda$). Using our prior
work as a guide~\cite{MannEtal14b}, we set $\lambda = 20$, although
this could in theory be optimized, e.g. using cross validation.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods}
  \caption{\textbf{Methods overview.}  \textbf{A.  Electrode
      locations.}  Each dot reflects the location of a single
    electrode in dataset 1, colored according to 7 factor labels (see Panel D for details). One patient's electrode locations are
    highlighted in black and the to-be-reconstructed recording location
    is highlighted in red. \textbf{B. Radial basis function (RBF).}
    Each electrode contributed by the patient (black) weights on the
    full set of locations under consideration (all dots in Panel A,
    defined as $\bar{R}$ in the text).  The weights fall off with
    positional distance (in MNI space) according to an RBF.
    \textbf{C. Per-patient correlation matrices.}  After computing the
    pairwise correlations between the recordings from each patient's
    electrodes, we use RBF-weighted averages to estimate correlations
    between all locations in $\bar{R}$.  We obtain an estimated
    full-brain correlation matrix using each patient's
    data. \textbf{D.  Combined correlation matrix.}  We estimate a
    single full-brain correlation matrix by averaging 
    the patient-specific correlation matrices.  We sort the resulting correlation matrix based on 7 factor labels obtained from k-means clustering~\cite{YeoEtal11}). \textbf{E.
      Reconstructing activity throughout the brain.}  Given the observed
    activity from the patient's electrodes and the estimated
    correlation matrix (Panel D), we can compute a maximum likelihood
    estimate of the voltage trace at any location in $\bar{R}$.  An
    example reconstruction (at the red dot in Panel A) is shown in
    red, and the actual recording at that location is highlighted above in blue.}
  \label{fig:methods}
\end{figure}

A second mechanism whereby a given region $x$ can contribute to the
recording at $\eta$ is through anatomical connections between
structures near $x$ and $\eta$.  We use spatial correlations in the
data to estimate these anatomical connections.  Let $\bar{R}$ be the
set of locations at which we wish to estimate local field potentials,
and let $R_{s}$ be set of locations at which we observe local field
potentials from patient $s$ (excluding the electrodes that did not
pass the kurtosis test described above). In the analyses below we
define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate the expected
inter-electrode correlation matrix for patient $s$, where
$C_{s,k}(i,j)$ is the correlation between the time series of voltages
for electrodes $i$ and $j$ from subject $s$ during session $k$, using:

\begin{align}
  \bar{C}_{s} &=
  \mathrm{r}(\frac{1}{n}(\sum_{k=1}^{n}\mathrm{z}(C_{s,k}))),\label{eqn:inter_corr}~\mathrm{where}\\
\mathrm{z}(r) &= \frac{\log(1+r) - \log(1 - r)}{2}~\mathrm{is~the~Fisher}~z \mathrm{-transformation~and}\label{eqn:fishersz}\\
\mathrm{z}^{-1}(z) = \mathrm{r}(z) &= \frac{\exp(2z) - 1}{\exp(2z) + 1}\mathrm{~is~its~inverse}.\label{eqn:invfishersz}
\end{align}
Next, we use Equation~\ref{eqn:rbf} to construct a number of
to-be-estimated locations by number of patient electrode locations
weight matrix, $W$.  Specifically, $W$ approximates how informative the
recordings at each location in $R_s$ are in reconstructing activity at
each location in $\bar{R}$, where the contributions fall off with an RBF according to
the distances between the corresponding locations:

\begin{align}
W(i, j) = \mathrm{rbf}(i|j,\lambda)\label{eqn:weight_matrix}.
\end{align}

Given this weight matrix, $W$,
and the observed inter-electrode correlation matrix for patient $s$,
$\bar{C}_{s}$, we can estimate the correlation matrix for all locations in
$\bar{R}$ (Fig.~\ref{fig:methods}C) using:

\begin{align}
\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\bar{C}_{s}(i,j))}\label{eqn:correlation_matrix_num}\\
 \hat{D}_{s}(x,y) & = \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j). \label{eqn:correlation_matrix_den}
\end{align}
Intuitively, we construct an estimated correlation matrix from each
individual patient's data (Fig.~\ref{fig:methods}C) using
Equations~\ref{eqn:correlation_matrix_num} \& \ref{eqn:correlation_matrix_den}, then we sum across these estimates for $S$ patients and divide (see Equations~\ref{eqn:correlation_matrix}) to obtain the expected correlation
matrix, $\hat{K}$ (Fig.~\ref{fig:methods}D):

\begin{align}
 \hat{K} = \mathrm{r} \left (  \frac{\sum  \hat{N}_{s}}{\sum \hat{D}_{s}}\right ).\label{eqn:correlation_matrix}
\end{align}
Now we can use the following intuition: given (i) the observed
responses from a limited set of locations in $R_{s}$ ($Y_{s}$) and
(ii) how each location's responses relate to all other responses
($\hat{K}$), we can estimate the LFP data from patient
$s$, for any arbitrary location in $\bar{R}$
(Fig.~\ref{fig:methods}E).

Let $\alpha$ be the set of indices of patient $s$'s electrode locations in
$\bar{R}$, and let $\beta$ be the set of indices of all other
locations in $\bar{R}$. In other words, $\beta$ reflects the locations
in $\bar{R}$ where we did not observe a recording for patient $s$
(these are the recording locations we will want to fill in using Super EEG).
We can sub-divide $\hat{K}$ as follows:

\begin{align}
\hat{K}_{\beta,\alpha} &= \hat{K}(\beta,\alpha),~\mathrm{and}\label{eqn:Kba}\\
\hat{K}_{\alpha,\alpha} &= \hat{K}(\alpha,\alpha)\label{eqn:Kaa}.
\end{align}
Here $\hat{K}_{\beta, \alpha}$ stores the correlations between the
``unknown'' activity at the locations in $\beta$ and the observed
activity at the locations in $\alpha$, and $\hat{K}_{\alpha, \alpha}$
stores the correlations between the observed recordings (at the
locations in $\alpha$).

Let $Y_{s,k,\alpha}$ be the number-of-timepoints
($T$) by length($\alpha$) matrix of (observed) voltages from the electrodes in $\alpha$ during session $k$ from patient $s$. Then we can estimate the voltage from patient $s$'s $k^{th}$ session at the locations in $\beta$ using~\cite{Rasm06}:

\begin{align}
Y_{s,k,\beta} &= ((\hat{K}_{\beta,\alpha}\cdot\hat{K}_{\alpha,\alpha}^{-1})\cdot Y_{s,k,\alpha}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
\end{align}
This equation is the foundation of the Super EEG algorithm.  Whereas
we observe the recordings only at the locations in $\alpha$,
Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
at all locations in $\beta$, which we can define \textit{a priori} to
include any locations we wish, throughout the brain.  This yields estimates of
the time-varying voltages at \textit{every} location in $\bar{R}$.

We designed our approach to be agnostic to electrode impedances, as
electrodes that do not exist do not have impedances.  Therefore our
algorithm recovers voltages in standard deviation ($z$-scored) units
rather than attempting to recover absolute voltages. (This property
reflects the fact that $\hat{K}_{\beta, \alpha}$ and
$\hat{K}_{\alpha, \alpha}$ are correlation matrices rather than
covariance matrices.)  Also, note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
matrix, which can become computationally intractable when $T$ is very
large (e.g.\ for the patient highlighted in Fig.~\ref{fig:recon}, $T = 20458799$). However, we may approximate $Y_{s,k,\beta}$ in a piecewise
manner by filling in $Y_{s,k,\beta}$ in blocks of size $b$ samples
(using the corresponding samples from $Y_{s, k, \alpha}$).  In our
computations we set $b = 25000$.

The Super EEG algorithm described above and in
Figure~\ref{fig:methods} allows us to estimate (up to a constant
scaling factor) LFPs for each patient at all arbitrarily chosen
locations in the set $\bar{R}$, \textit{even if we did not record that
  patient's brain at all of those locations}.

\section*{Results}
To test the accuracy with which the Super EEG algorithm reconstructs activity throughout the brain, we held out each electrode from the full
dataset in turn and treated it as unobserved. We then asked: how
closely did each of the Super EEG-reconstructed LFPs match the
observed data?  We sought to evaluate both the overall reconstruction
accuracy as well as how reconstruction accuracy varied as a function
of implantation location.

We first examined raw LFP traces and their associated Super
EEG-derived reconstructions.  Figure~\ref{fig:recon}A displays the
LFP from the red electrode in Figure~\ref{fig:methods}A, and its
associated reconstruction, during a 5~s time window during one of the
patient's 6 recording sessions.  Figure~\ref{fig:recon}B displays a 2D
histogram of the observed versus reconstructed voltages for every
sample across 14.2 total hours of recordings from that patient (correlation:
$r = 0.91, p < 10\textsuperscript{-10}$).  Although the Super EEG
algorithm recovered the recordings from this electrode well, we sought to
quantify the algorithm's performance across the full dataset.

%sample trace & reconstruction, several frames of activity snapshot?
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/recon}
  \caption{\textbf{Observed and reconstructed LFP from a single
      electrode.} \textbf{A. Example LFP.}  A 2~s recording from the blue
    electrode in Figure~\ref{fig:methods}A is displayed in red, and
    the reconstructed LFP during the same time window is shown in
   black.  All voltages are plotted in standard deviation units.
    \textbf{B. Observed versus reconstructed voltages over 14.2~hours.}
    The 2D histogram reflects the relation between distributions of
    observed versus reconstructed voltages from one patient, across the
    14.2 hours of recorded data collected in 6 recording sessions.  The
    correlation reported in the panel is between the observed and reconstructed
    voltages.}
  \label{fig:recon}
\end{figure}

Holding out each electrode from each patient in turn, we computed the
average correlation (across recording sessions) between the Super
EEG-reconstructed voltage traces and the observed voltage traces from
that electrode.  For each reconstruction, we estimated the full-brain
correlation matrix using every \textit{other} patient's data
(i.e. every patient except the one who contributed the
to-be-reconstructed electrode data).  In our analyses, we then
substituted the average correlation matrix computed after excluding
patient $s$'s data for $\hat{K}$ in Equations~\ref{eqn:Kba} and
\ref{eqn:Kaa}.  This step ensured that the data we were reconstructing
could not also be used to estimate the between-location correlations
that drove the reconstructions via Equation~\ref{eqn:reconstruction}
(otherwise the analysis would be circular).

We obtained a single correlation coefficient for each electrode
location in $\bar{R}$, reflecting how well the Super EEG algorithm was
able to recover the recording at that location by incorporating data across patients (Across shown in black, see Fig.~\ref{fig:corrmap}A). We also reconstructed activity for each electrode using a model trained on the remaining electrodes from only that patient, to account for reconstruction accuracy attributed to volume conductance alone (Within shown in gray, see Fig.~\ref{fig:corrmap}A). For the first dataset, we compared these two distributions of correlation coefficients (paired $t$-test
between $z$-transformed mean correlation coefficients by patient:
$t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated this analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with similar results (paired $t$-test
between $z$-transformed mean correlation coefficients by patient: $t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially conservative
test, given that the Super EEG reconstructions exclude (from the
correlation matrix estimates) all data from the patient whose data is
being reconstructed.  Furthermore, we also replicated this finding for each independent experiment within dataset 2 (Fig. S3 (paired $t$-test
between $z$-transformed mean correlation coefficients by patient for experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).  That the Super EEG-derived correlations were reliably
stronger than these correlations obtained using a volume conductance null model is exciting
for two reasons.  First, it implies that distant electrodes provide
additional predictive power to the data reconstructions beyond the
information contained in nearby electrodes.  Second, it implies that
the spatial correlations driving the Super EEG algorithm are, to some
extent, shared across people.

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction quality.}  \textbf{A. \& C.  Distributions
      of correlation coefficients.}  Across all electrodes from all
    patients in the labeled dataset, the panel displays the distribution of correlations between the observed and reconstructed LFP data using models trained on data from all other patients (Across, in black) and all other electrodes from the same patient (Within, in gray). 
    \textbf{B. \& D. Correlation maps.}  The glass brain maps display the
    average correlation between the observed LFP data and the across-subjects model reconstructed data by location, for each labeled experiment.}
  \label{fig:corrmap}
\end{figure}

We were interested in the task specific contributions to the reconstruction accuracy.  Each patient in the the second dataset participated in two free recall experiments.  We ran similar analyses for both experiments and found that activity was best reconstructed when limiting the training data to within task, as opposed to across task or incorporating data from both tasks (Fig. S1 (mean reconstruction accuracy incorporating data within task: 0.55, across task: 0.37, all tasks: .50)). Although reconstruction accuracy in the across task analysis was still better than the volume conductance model alone (paired $t$-test
between $z$-transformed mean correlation coefficients by patient: $t(47) = 5.65, p < 10\textsuperscript{-5}$), these results suggests that having a common tasks for patients may yield better reconstruction accuracy.

We also wondered whether reconstruction quality (measured as the
correlation between the observed and reconstructed data) varied with
the electrode locations (Fig.~\ref{fig:corrmap}B \& D). In general, reconstruction quality remained high throughout the brain. Although reconstruction accuracy appeared high in the medial temporal lobe, which is a common epileptic focus (and therefore a common target for electrode implantation), we observed a weak but statistically reliable negative correlation between reconstruction quality and electrode density (defined as the proportion of electrodes within 20 MNI units for each location; dataset 1: $r = -0.07, p < 10^{-5}$, dataset 2: $r = -0.16, p < 10^{-10}$). This provides some evidence that our reconstruction accuracy results cannot be driven only by volume conductance.  Qualitatively, it appeared that the distribution of electrodes was similar across the datasets, suggesting potential commonalities of target locations across patients and similarities in surgical decisions. Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A & B); $r = 0.57, p < 10^{-10}$).

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/density}
  \caption{\textbf{Sampling density and reconstruction quality.}
    \textbf{A. \& B. } The glass brain maps show sampling density by voxel location for dataset 1 and dataset 2. \textbf{C.}
      Correlation of sampling density by voxel location for dataset 1 vs. dataset 2.}
  \label{fig:density}
\end{figure}

In addition to exploring how reconstruction quality varies with
location, we also wondered whether there might be effects of electrode
placements on reconstruction quality.  For example, are there
particular implantation locations that yield especially high
reconstruction accuracies at other locations throughout the brain? To gain insights into this questions, we computed the average reconstruction correlation for each patient, then computed the average patient reconstruction correlation for any patients who had electrodes within a 20 MNI unit diameter sphere centered on each voxel location. The resulting maps highlight the locations of implanted electrodes from patients whose
reconstructions were especially accurate  (Fig.~\ref{fig:informap}A & B). We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations in dark red might therefore be good candidate
implantation targets for neurosurgeons and neurologists who wish to
use Super EEG to reconstruct full-brain electrophysiological signals.
The above findings, that one can infer brain activity throughout a person's brain 
using recordings from a limited number of locations from that person's brain in conjunction with recordings from other people's brains, have deep
implications for the structure of brain data.  The first implication
is that the correlational structure of different people's brain data
is largely preserved across individuals. Despite recent evidence that different people have stable but reliably different resting state connectome~\cite{FinnEtal15}, our results suggest that the correlational structure of different people's brain data is preserved enough across individuals to provide meaningful information.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.} \textbf{A. \& B. } The glass
    brain maps displays the average reconstruction correlations (by patient, across
    all electrodes) for patients with electrodes within a 20 MNI unit diameter sphere centered on
    each location for dataset 1 and dataset 2. \textbf{C.} Correlation between z-transformed correlations by voxel for dataset 1 vs. dataset 2.}
  \label{fig:informap}
\end{figure}

\section*{Discussion}
%DISCUSSION POINTS
%recap main approach
Super EEG infers full-brain activity patterns by leveraging
correlations in those patterns of brain activity within and across people.  Although
the approach may, in principle, be used to infer brain activity
\textit{anywhere} in the brain, the inferences perform slightly better for
regions with dense electrode sampling across patients.  (Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
are included in the inference procedure, this suggests that reconstruction accuracy should improve.

%why does it work?  redundancy of brain
A fundamental assumption of the Super EEG algorithm is that the data
covariance matrix is stable over time and across people.  This is a
useful simplification.  However, a growing body of evidence from the
fMRI community suggests that the data covariance matrix changes in
meaningful ways over time (for example, the data covariance matrix
changes from moment-to-moment during story listening, serving as a
unique ``fingerprint'' for each moment of the story; further, these
task-driven timepoint-specific covariance fingerprints appear to be
largely preserved across people~\cite{SimoEtal16, MannEtal17}).  These
findings indicate that the full-brain covariance matrix is not stable
over time.  Other recent work has shown that people's resting state
connectivity matrices may be used to uniquely identify individuals and
predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
that the full-brain covariance matrix is not stable across people.  If
the fundamental stability assumptions that Super EEG relies on are
violated, how can the Super EEG algorithm still accurately recover LFP
data?  It is important to recognize that the fact that variability
(over time or across people) is predictive (e.g.\ of cognitive states
during story listening or fluid intelligence scores) does not
necessarily mean that this variability is large in magnitude.  Rather,
we have long known that brain structure is tightly preserved across
individuals (and over time, at least on the timescale of typical
clinical and experimental recording sessions), and any functional
changes must occur within the framework of the underlying structural
anatomy.  Nevertheless, one could imagine future improvements to the
Super EEG approach that leverage resting state fMRI or structural data
[e.g. diffusion tensor imaging (DTI)] to estimate Bayesian priors over
the correlation matrices inferred, in the current framing, using only
ECoG data.  Further, relaxing the assumption that the covariance
matrix is stable (over time and/or across people), and/or
incorporating more detailed brain conductance models (e.g.\ informed
by structural MRI scans) may improve the predictive performance of the
approach.

%This technique relies on recordings from many patients performing the
%same basic cognitive task.  To what extent do these findings
%generalize across studies?  For example, could one combine recordings
%from several studies to improve our ability to reconstruct neural
%activity?
One potential limitation of the Super EEG approach is that the above
assumption of covariance stability across people may be violated even
more if different patients are performing different cognitive tasks.
To understand of the extent to which the current findings generalize across
cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks. Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
matrix.  Or, using a more sophisticated approach, one could create a
hierarchical model whereby each task-specific covariance matrix was
modeled as a perturbation of a ``global'' task-unspecific covariance
matrix (which could in turn be informed by fMRI or DTI data).
% Alternatively, if the covariance matrix is stable across tasks, this would
% suggest that recordings from multiple studies could be combined to
% improve the overall reconstruction accuracy.

A second potential limitation of the Super EEG approach is that it
does not provide a natural means of estimating the precise timing of
single-neuron action potentials.  Prior work has shown that gamma band
and broadband activity in the LFP may be used to estimate the firing
rates of neurons that underly the population contributing to the
LFP~\cite{MannEtal09}.  Because Super EEG reconstructs LFPs throughout
the brain, one could in principle use gamma or broadband power in the
reconstructed signals to estimate the corresponding firing rates
(though not the timings of individual action potentials).

Beyond providing a means of estimating ongoing activity throughout the
brain using already implanted electrodes, our work also has
implications for where to place the electrodes in the first place.
Electrodes are typically implanted to maximize coverage of suspected
epileptogenic tissue.  However, our findings suggest that this approach
could be further optimized.  Specifically, one could leverage not only
the non-invasive recordings taken during an initial monitoring period
(as is currently done), but also recordings collected from other
patients.  We could then ask: given everything we know about the other
patients and from the scalp recordings of this new patient, where
should we place a fixed number of electrodes to maximize our ability
to map seizure foci?  As shown in Figure~\ref{fig:informap}, recordings
from different locations are differently informative in terms of
reconstructing the spatiotemporal patterns throughout the brain.
This property might be leveraged in decisions about where to
surgically implant electrodes in future patients.

\section*{Concluding remarks}
Over the past several decades, neuroscientists have begun to leverage
the strikingly profound mathematical structure underlying the brain's
complexity to infer how our brains carry out computations to support
our thoughts, actions, and physiological processes.  Whereas
traditional beamforming techniques rely on geometric
source-localization of signals measured at the scalp, here we propose
an alternative approach that leverages the rich correlational
structure of a large dataset of human intracranial recordings.  In
doing so, we are one step closer to observing, and perhaps
someday understanding, the full spatiotemporal structure of human
neural activity.

\section*{Code availability}
We have released an open-source SuperEEG Python toolbox.  All of the code used in this manuscript is on GitHub, and the code may be shared using a GitHub account accessible to the reviewers upon request.

\section*{Data availability}
The dataset analyzed in this study was generously shared by Michael J. Kahana.  A portion of the dataset may be downloaded \href{http://memory.psych.upenn.edu/Request_EEG_access?paper=SedeEtal03}{\underline{here}}.
\section*{Acknowledgements}
We are grateful for useful discussions with Luke J. Chang and Matthijs van der Meer.  We are also grateful to Michael J. Kahana for generously sharing
the ECoG dataset we analyzed in our paper, which was collected under
NIMH grant MH55687 to MJK.  Our work was also supported in part by NSF EPSCoR Award Number 1632738.  The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
\section*{Author Contributions}
J.R.M conceived and initiated the project. L.L.W.O. and A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the manuscript.

\section*{Author Information}
Reprints and permissions information is available at www.nature.com/reprints.  The authors declare no competing financial interests.  Readers are welcome to comment on the online version of the paper.  Publisher's note: Springer Nature remains neutral with regard to jurisdictional claims in published maps and institutional affiliations.  Correspondence and requests for materials should be addressed to J.R.M.  (jeremy.r.manning@dartmouth.edu).

\bibliography{memlab}
\bibliographystyle{Science}

\clearpage

\end{document}

### 2018-10-02 paper/supporting_information.tex
added paper from Overleaf and also added CDL-bibliography as submodule

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{geometry}
\usepackage{natbib}
\usepackage{pxfonts}
\usepackage{graphicx}
\usepackage{newfloat}
\usepackage{setspace}
%\doublespacing

\newcommand{\argmax}{\mathop{\mathrm{argmax}}\limits}

\title{\textit{Supporting Information for}: Towards human Super EEG?}
\author{Lucy L. W. Owen, Andrew C. Heusser, and Jeremy R. Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}

\bibliographystyle{apa}

\begin{document}
\maketitle

\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\section*{Overview}
This document provides additional details about the methods we used in the main text.  We also include some additional analyses referenced in the main text.

\begin{figure}[p!]
\centering
\includegraphics[width=0.75\textwidth]{figs/supplemental_1}
\caption{\small \textbf{Reconstruction quality for datasets 1 and 2.} \textbf{A. Distributions
      of correlation coefficients.}  Although patients in dataset 1 all participated in the same experiment, we did not limit our analyses to task specific data.  Instead we incorporated data from their entire recording session (sometimes up to 14 hours of data) and classify this as training our model on across experiment information. The split violin plot shows the distributions of reconstruction accuracy using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray). \textbf{B.  Distributions of correlation coefficients.} Since all patients participated in two experiments in dataset 2, we limit our analyses to task specific data.  The violin plots compare distributions of reconstruction accuracy using data from the same task (Within Experiment), the other task (Across Experiment), and from both tasks (All Experiment), using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray).}
\label{fig:supplemental_1}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_2}
\caption{\small \textbf{Reconstruction quality for experiments 1 and 2.} \textbf{A. Distributions
      of correlation coefficients.} For experiment 1, the split violin plots compare distributions of reconstruction accuracy using data from just experiment 1 (Within Experiment), just experiment 2 (Across Experiment), and from both experiments (All Experiment), using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray). \textbf{B.  Distributions
      of correlation coefficients.} For experiment 2, the split violin plots compare distributions of reconstruction accuracy using data from just experiment 2 (Within Experiment), just experiment 1 (Across Experiment), and from both experiments (All Experiment), using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray). }
\label{fig:supplemental_2}
\end{figure}

\begin{figure}[p!]
\centering
\includegraphics[width=\textwidth]{figs/supplemental_3}
\caption{\small \textbf{Reconstruction quality for each experiment.} \textbf{A. \& C.  Distributions
      of correlation coefficients.}  Across all electrodes from all
    patients in the labeled experiment from dataset 2, the panel displays the distribution of correlations between the observed and reconstructed LFP data using models trained on data from all other patients (Across, in black) and all other electrodes from the same patient (Within, in gray). 
    \textbf{B. \& D. Correlation maps.}  The glass brain maps display the
    average correlation between the observed LFP data and the across-subjects model reconstructed data by location, for each labeled experiment.}
\label{fig:supplemental_3}
\end{figure}

% \newpage
% \renewcommand{\refname}{Supplemental references}
% \bibliography{memlab}

\end{document}

### 2018-10-02 paper/main.tex
minor paper organization stuff

@@
 \author
-{Lucy L. W. Owen$^{1}$, Andrew C. Heusser$^{1}$, and Jeremy R. Manning$^{1\ast}$\\
-\\
-\normalsize{$^{1}$Department of Psychological and Brain Sciences,
-  Dartmouth College,}\\
-\normalsize{Hanover, NH 03755, USA}
-}
+{Lucy L. W. Owen$^{1}$, Andrew C. Heusser$^{1, 2}$, and Jeremy R. Manning$^{1\ast}$\\\\
+$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
+Hanover, NH 03755, USA\\
+$^{2}$Akili Interactive,\\
+Boston, MA 02110, USA}
 
@@
 Qualitatively, it appeared that the distribution of electrodes was similar across the datasets, suggesting potential commonalities of target locations across patients and similarities in surgical decisions.
-Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A & B); $r = 0.57, p < 10^{-10}$).
+Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A, B); $r = 0.57, p < 10^{-10}$).
 
@@
 The resulting maps highlight the locations of implanted electrodes from patients whose
-reconstructions were especially accurate  (Fig.~\ref{fig:informap}A & B).
+reconstructions were especially accurate  (Fig.~\ref{fig:informap}A and B).
 We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).
@@
 
-\bibliography{memlab}
+\bibliography{CDL-bibliography/memlab.bib}
 \bibliographystyle{Science}

### 2018-10-03 paper/boneyard.tex
checking in more changes (reverted and revamped intro, now getting into approach)

@@
+\section*{Introduction}
+Current human brain recording techniques are fraught with compromise.
+Commonly used approaches include functional magnetic resonance imaging
+(fMRI), scalp electroencephalography (EEG), and magnetoencephalography
+(MEG).  For each of these techniques, neuroscientists
+and electrophysiologists must choose to optimize spatial resolution
+at the cost of temporal resolution (e.g.\ as in fMRI) or temporal
+resolution at the cost of spatial resolution (e.g.\ as in EEG
+and MEG).  A less widely used approach (due to requiring work with
+neurosurgical patients) is to record from electrodes implanted
+directly onto the cortical surface (electrocorticography; ECoG) or
+into deep brain structures (intracranial EEG; iEEG).  However, these
+intracranial approaches also require compromise: the high temporal and
+spatial resolutions of intracranial recordings comes at the cost of
+substantially reduced brain coverage, since safety considerations
+limit the number of electrodes one may implant in a given patient's
+brain.  Further, the locations of implanted electrodes are determined by clinical,
+rather than research, needs.
+
+%Beamforming: huge advance for scalp recordings, but the inverse
+%problem is fundamentally ambiguous.  This limits the precision with
+%which one can measure activity from deep brain structures.
+An increasingly popular approach is to improve the effective spatial resolution
+of MEG or scalp EEG data by using a geometric approach called
+\textit{beamforming} to solve the biomagnetic or bioelectrical inverse
+problem~\cite{Sarv87}.  This approach entails using detailed brain
+conductance models (often informed by high spatial resolution
+anatomical MRI images) along with the known sensor placements
+(localized precisely in 3D space) to reconstruct brain signals
+originating from theoretical point sources deep in the brain (and far
+from the sensors).  Traditional beamforming approaches must overcome
+two obstacles.  First, the inverse problem beamforming seeks to solve
+has infinitely many solutions.  Researchers have made traction towards
+constraining the solution space by assuming that signal-generating
+sources are localized on a regularly spaced grid spanning the brain
+and that individual sources are small relative to their distances to
+the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
+some ways much more serious, obstacle is that the magnetic fields
+produced by external (noise) sources are substantially stronger than
+those produced by the neuronal changes being sought (i.e.\ at deep structures, as measured by sensors at the scalp).  This means that
+obtaining adequate signal quality often requires averaging the measured
+responses over tens to hundreds of responses or trials (e.g. see
+review by~\cite{HillEtal05}).
+
+Another approach to obtaining high spatial and temporal resolution
+neural data has been to collect fMRI and EEG data simultaneously.
+Simultaneous fMRI-EEG has the potential to balance the high spatial
+resolution of fMRI with the high temporal resolution of scalp EEG,
+thereby, in theory, providing the best of both worlds.  In practice,
+however, the signal quality of both recordings suffers substantially
+when the two techniques are applied simultaneously (e.g. see review
+by~\cite{HustEtal12}).  In addition, the experimental designs that are
+ideally suited to each technique individually are somewhat at odds.
+For example, fMRI experiments typically lock stimulus presentation
+events to the regularly spaced image acquisition time (TR), which
+maximizes the number of post-stimulus samples.  By contrast, EEG
+experiments typically employ jittered stimulus presentation times to
+maximize the experimentalist's ability to distinguish electrical brain
+activity from external noise sources such as from 60 Hz alternating
+current power sources.
+
+%Direct intracranial recordings are the gold standard method for
+%measuring activity from deep brain structures in both humans and
+%animals.
+%However, one can only implant a limited number of electrodes in a
+%given person's brain.  This begs the question: what can we infer
+%about the activity exhibited by the rest of that person's brain,
+%given what we learn from recordings taken from \textit{other people's
+%brains}?
+The current ``gold standard'' for precisely localizing signals and
+sampling at high temporal resolution is to take (ECoG or iEEG)
+recordings from implanted electrodes (but from a limited set of
+locations in any given brain).  This begs the following question: what
+can we infer about the activity exhibited by the rest of a person's
+brain, given what we learn from the limited intracranial recordings we
+have from their brain and additional recordings taken from
+\textit{other} people's brains?  Here we develop an approach, based on
+Gaussian process regression~\cite{Rasm06}, that uses data from
+multiple people to estimate activity at arbitrary
+locations in each person's brain (i.e., independent of their electrode
+placements).  We test this \textit{Super EEG} approach using a large
+dataset of intracranial recordings collected as neurosurgical patients
+studied and recalled random word lists~\cite{SedeEtal03, SedeEtal07a,
+  SedeEtal07b, MannEtal11, MannEtal12}.  We show that the Super EEG
+algorithm recovers signals well from electrodes that were held out of
+the training dataset.  We also examine the factors that influence how
+accurately activity may be estimated (recovered), which may have important
+implications for electrode design and for electrode placement in
+neurosurgical applications.
+
+%%%%%
+
+  The correlational structure of functional neuroimaging data may be
+  used to predict which moment of movie or story an individual is
+  experiencing, identify which person's brain a recording came from,
+  and identify the task a person is performing.  In contrast, our
+  structural (anatomical) connectome is static for the duration of
+  typical neuroimaging experiments, is task invariant, and is similar
+  across people.  How might these seemingly opposing features of
+  functional connectomes versus static structural connectomes be
+  reconciled?  We developed a static task- and person-invariant
+  connectome model, and explored the extent to which the model could
+  explain dynamic full-brain activity patterns.  We trained the model
+  using ECoG recordings from two large datasets, and we tested its
+  ability to predict held-out data.  We found that neural activity
+  patterns are best explained by a connectome that is common across
+  individuals, but changes across tasks.
+
+Are our brain's networks static or dynamic?
+And to what extent are the network properties of our brains stable across people and tasks?
+One body of work suggests that our brain's \textit{functional} networks are dynamic~\citep[e.g., ][]{MannEtal18}, person-specific~\citep[e.g., ][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.
+In contrast, although the gross anatomical structure of our brains changes meaningfully over the course of years as our brains develop, on the timescales of typical neuroimaging experiments (i.e., hours to days) our anatomical networks are largely stable~\citep[e.g., ][]{CaseEtal00}.
+Further, many aspects of brain anatomy, including white matter structure, is largely preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}  There are several possible means of reconciling this apparent inconsistency between dynamic person- and task-specific functional networks versus stable anatomical networks.
+For example, relatively small magnitude anatomical differences across people may be reflected in reliable functional connectivity differences.
+Along these lines, one recent study found that diffusion tensor imaging (DTI) structural data is similar across people, but may be used to predict person-specific resting state functional connectivity data~\citep{BeckEtal18}.
+Another (potentially complementary) possibility is that our functional networks are constrained by anatomy, but nevertheless exhibit rapid task-dependent changes~\citep[e.g., ][]{SporBetz16}.
+
+Here we take a model-based approach to studying whether high
+spatiotemporal resolution activity patterns throughout the human brain
+may be explained by a static connectome model that is shared across
+people and tasks.  Specifically, we trained a model to take in
+recordings from a subset of brain locations, and then predicted
+activity patterns during the same interval, but at \textit{other}
+locations that were held out from the model.  Our model, based on
+Gaussian process regression, relies on three assumptions (each of
+which we test).  First, we assume that functional correlations are
+stable over time and across tasks.  Second, we assume that some of the
+correlational structure of people's brain activity is similar across
+individuals.  Third, we resolve ambiguities in the data by assuming
+that neural activity from nearby sources will tend to be similar, all
+else being equal.  After fitting the model to an ECoG dataset, one can
+then ask (for a held-out individual's brain): given what we know about
+the correlational structure of \textit{other} people's brains, and
+given the recordings we made from electrodes implanted in this
+person's brain, how would those recordings most likely have looked at
+\textit{other} locations throughout this person's brain?  We named our
+general approach \textit{SuperEEG} because the trained model provides
+a means of inferring full-brain activity patterns at high
+spatiotemporal resolutions, using ECoG recordings taken from a limited
+set of brain locations.
+
+We tested the SuperEEG approach using two large ECoG datasets.
+Dataset 1 comprises multi-hour recordings from 6876 electrodes taken across several recording sessions as 88 neurosurgical patients studied random word lists periodically throughout their day~\cite{SedeEtal03, SedeEtal07a,
+  SedeEtal07b, MannEtal11, MannEtal12}.
+Dataset 2 comprises recordings from XXX electrodes taken as XXX patients performed a series of two memory tasks~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.
+In both datasets,
+  we compared the predictions made using models trained across people to predictions made using within-person data.
+We found that models that incorporate data from other patients yield far more reliable predictions about an individual patient's brain activity patterns than models trained solely on that individual's data.
+This indicates that at least some functional correlations are common across people.
+We also used Dataset 2 to compare predictions made using data from within task, across task, or combining within and across task data.
+We found that all three approaches yielded reliable predictions, but the within task predictions were the most accurate.
+This indicates that some aspects of our functional connectomes are common across tasks, whereas other aspects are task-specific.
+Finally, all of the models we trained (within and across patients and tasks) assumed a static connectome and yielded above-chance accuracy.
+This indicates that despite moment-by-moment fluctuations in the functional connectome, at least some aspects of our connectome appear to be stable over the course of several hours.
+
+%%%%%
+
 , the gross \textit{structural} aspects of our brain are essentailly static over the timescales of typical experiments (on the order of

### 2018-10-03 paper/main.tex
backing up current progress (made it through abstract + intro)
checking in more changes (reverted and revamped intro, now getting into approach)

@@
 
-\documentclass[12pt]{article}
+\documentclass[11pt]{article}
 
@@
 
-\title{Towards human Super EEG}
+\title{Towards human SuperEEG}
 
@@
 \begin{abstract}
-A growing body of literature over the past several decades reports that the dynamic correlational structure of functional neuroimaging data may be used to predict which moment of movie or story an individual is experiencing, identify which person's brain a recording came from, and identify the task a person is performing.
-However, our structural (anatomical) connectome is roughly static for the duration of typical neuroimaging experiments.
-How might these notions of dynamic functional connectomes versus static structural connectomes be reconciled?
-We use two human electrocorticographic (ECoG) datasets to ask: to what extent can we use a static connectome model (trained using within versus across subject data, and within versus across task data) to explain dynamic full-brain activity patterns?
-Given a fixed connectome model, and given recordings from a subset of brain locations, we test how reliably can one infer activity patterns throughout the rest of the brain.
-Our model-based approach, termed \textit{SuperEEG}\footnote{The term ``Super EEG'' was
-coined by Robert J. Sawyer in his popular science fiction novel
-\textit{The Terminal Experiment}~\cite{Sawy95}}, is in itself useful for inferring full-brain activity patterns (at millimeter-scale spatial resolutions and millisecond-scale temporal resolutions) from ECoG recordings from a limited set of brain locations.
-For both datasets, we found that full-brain activity patterns can be best explained using connectomes from \textit{other} people who performed a shared task.\\
-
-\small{\textbf{Keywords: Electrocorticography (ECoG), intracranial electroencephalography (iEEG),
-local field potential (LFP), epilepsy, maximum likelihood estimation, Gaussian process regression}}
+  Human \textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by
+    Robert J. Sawyer in his popular science fiction novel \textit{The
+      Terminal Experiment}~\cite{Sawy95}} entails measuring ongoing
+  neural activity with perfect precision and at arbitrarily high
+  spatiotemporal resolution.  Although true SuperEEG is impossible
+  using existing methods, here we present a model-based method for
+  \textit{inferring} neural activity at millimeter-scale spatial
+  resolutions and millisecond-scale temporal resolutions using
+  standard human intracranial recordings.  Our approach assumes that
+  different people's brains exhibit similar spatial correlations, and
+  that (all else being equal) neural activity at nearby locations will
+  tend to be similar.  One can then ask, for an arbitrary individual's
+  brain: given recordings from a limited set of locations in that
+  individual's brain, along with the observed spatial correlations in
+  other people's recordings, what would recordings most likely have
+  looked like at \textit{other} locations in that individual's brain?
+%\\
+%\small{\textbf{Keywords: Electrocorticography (ECoG), intracranial electroencephalography (iEEG),
+%local field potential (LFP), epilepsy, maximum likelihood estimation, Gaussian process regression}}
 \end{abstract}
 
-Are our brain's networks static or dynamic?
-And to what extent are the network properties of our brains stable across people and tasks?
-One body of work suggests that our brain's \textit{functional} networks are dynamic~\citep[e.g., ][]{MannEtal18}, person-specific~\citep[e.g., ][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.
-In contrast, although the gross anatomical structure of our brains changes meaningfully over the course of years as our brains develop, on the timescales of typical neuroimaging experiments (i.e., hours to days) our anatomical networks are largely stable~\citep[e.g., ][]{CaseEtal00}.
-Further, many aspects of brain anatomy, including white matter structure, is largely preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}  There are several possible means of reconciling this apparent contradiction between dynamic person- and task-specific functional networks versus stable anatomical networks.
-For example, relatively small magnitude anatomical differences across people may be reflected in reliable functional connectivity differences.
-Along these lines, one recent study found that diffusion tensor imaging (DTI) structural data is similar across people, but may be used to predict person-specific resting state functional connectivity data~\citep{BeckEtal18}.
-Another (potentially complementary) possibility is that our functional networks are constrained by anatomy, but nevertheless exhibit rapid task-dependent changes~\citep[e.g., ][]{SporBetz16}.
+\section*{Introduction}
+Modern human brain recording techniques are fraught with
+compromise~\citep{SejnEtal14}.  Commonly used approaches include
+functional magnetic resonance imaging (fMRI), scalp
+electroencephalography (EEG), and magnetoencephalography (MEG).  For
+each of these techniques, neuroscientists and electrophysiologists
+must choose to optimize spatial resolution at the cost of temporal
+resolution (e.g.\ as in fMRI) or temporal resolution at the cost of
+spatial resolution (e.g.\ as in EEG and MEG).  A less widely used
+approach (due to requiring work with neurosurgical patients) is to
+record from electrodes implanted directly onto the cortical surface
+(electrocorticography; ECoG) or into deep brain structures
+(intracranial EEG; iEEG).  However, these intracranial approaches also
+require compromise: the high temporal and spatial resolutions of
+intracranial recordings comes at the cost of substantially reduced
+brain coverage, since safety considerations limit the number of
+electrodes one may implant in a given patient's brain.  Further, the
+locations of implanted electrodes are determined by clinical, rather
+than research, needs.
 
-Here we take a model-based approach to studying whether high spatiotemporal resolution activity patterns throughout the human brain may be explained by a static connectome model that is shared across people and tasks.
-Specifically, we trained a model to take in recordings from a subset of brain locations, and then predict activity patterns during the same interval, but at \textit{other} locations that were held out from the model.
-Our model, based
-on Gaussian process regression, relies on three assumptions (each of which we test).
-First, we assume that functional correlations are stable over time and across tasks.
-Second, we assume that some of the correlational structure of people's brain activity is similar across individuals.
-Third, we resolve
-ambiguities in the data by assuming that neural activity from
-nearby sources will tend to be similar, all else being equal.  After fitting the model to an ECoG dataset, one
-can then ask (for a held-out individual's brain): given what we
-know about the correlational structure of \textit{other} people's brains,
-and given the recordings we made from electrodes implanted in this
-person's brain, how would those recordings most likely have looked
-at \textit{other} locations throughout this person's brain?
-We named our general approach \textit{SuperEEG} because the trained model provides a means of inferring full-brain activity patterns at high spatiotemporal resolutions, using ECoG recordings taken from a limited set of brain locations.
+%Beamforming: huge advance for scalp recordings, but the inverse
+%problem is fundamentally ambiguous.  This limits the precision with
+%which one can measure activity from deep brain structures.
+An increasingly popular approach is to improve the effective spatial
+resolution of MEG or scalp EEG data by using a geometric approach
+called \textit{beamforming} to solve the biomagnetic or bioelectrical
+inverse problem~\cite{Sarv87}.  This approach entails using detailed
+brain conductance models (often informed by high spatial resolution
+anatomical MRI images) along with the known sensor placements
+(localized precisely in 3D space) to reconstruct brain signals
+originating from theoretical point sources deep in the brain (and far
+from the sensors).  Traditional beamforming approaches must overcome
+two obstacles.  First, the inverse problem beamforming seeks to solve
+has infinitely many solutions.  Researchers have made traction towards
+constraining the solution space by assuming that signal-generating
+sources are localized on a regularly spaced grid spanning the brain
+and that individual sources are small relative to their distances to
+the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
+some ways much more serious, obstacle is that the magnetic fields
+produced by external (noise) sources are substantially stronger than
+those produced by the neuronal changes being sought (i.e.\ at deep
+structures, as measured by sensors at the scalp).  This means that
+obtaining adequate signal quality often requires averaging the
+measured responses over tens to hundreds of responses or trials
+(e.g. see review by~\cite{HillEtal05}).
 
-We tested the SuperEEG approach using two large ECoG datasets.
-Dataset 1 comprises multi-hour recordings from 6876 electrodes taken across several recording sessions as 88 neurosurgical patients studied random word lists periodically throughout their day~\cite{SedeEtal03, SedeEtal07a,
-  SedeEtal07b, MannEtal11, MannEtal12}.
-Dataset 2 comprises recordings from XXX electrodes taken as XXX patients performed a series of two memory tasks~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.
-In both datasets,
-  we compared the predictions made using models trained across people to predictions made using within-person data.
-We found that models that incorporate data from other patients yield far more reliable predictions about an individual patient's brain activity patterns than models trained solely on that individual's data.
-This indicates that at least some functional correlations are common across people.
-We also used Dataset 2 to compare predictions made using data from within task, across task, or combining within and across task data.
-We found that all three approaches yielded reliable predictions, but the within task predictions were the most accurate.
-This indicates that some aspects of our functional connectomes are common across tasks, whereas other aspects are task-specific.
-Finally, all of the models we trained (within and across patients and tasks) assumed a static connectome and yielded above-chance accuracy.
-This indicates that despite moment-by-moment fluctuations in the functional connectome, at least some aspects of our connectome appear to be stable over the course of several hours.
+Another approach to obtaining high spatial and temporal resolution
+neural data has been to collect fMRI and EEG data simultaneously.
+Simultaneous fMRI-EEG has the potential to balance the high spatial
+resolution of fMRI with the high temporal resolution of scalp EEG,
+thereby, in theory, providing the best of both worlds.  In practice,
+however, the signal quality of both recordings suffers substantially
+when the two techniques are applied simultaneously (e.g. see review
+by~\cite{HustEtal12}).  In addition, the experimental designs that are
+ideally suited to each technique individually are somewhat at odds.
+For example, fMRI experiments typically lock stimulus presentation
+events to the regularly spaced image acquisition time (TR), which
+maximizes the number of post-stimulus samples.  By contrast, EEG
+experiments typically employ jittered stimulus presentation times to
+maximize the experimentalist's ability to distinguish electrical brain
+activity from external noise sources such as from 60 Hz alternating
+current power sources.
+
+%Direct intracranial recordings are the gold standard method for
+%measuring activity from deep brain structures in both humans and
+%animals.
+%However, one can only implant a limited number of electrodes in a
+%given person's brain.  This begs the question: what can we infer
+%about the activity exhibited by the rest of that person's brain,
+%given what we learn from recordings taken from \textit{other people's
+%brains}?
+The current ``gold standard'' for precisely localizing signals and
+sampling at high temporal resolution is to take (ECoG or iEEG)
+recordings from implanted electrodes (but from a limited set of
+locations in any given brain).  This begs the following question: what
+can we infer about the activity exhibited by the rest of a person's
+brain, given what we learn from the limited intracranial recordings we
+have from their brain and additional recordings taken from
+\textit{other} people's brains?  Here we develop an approach, which we
+call \textit{SuperEEG}, based on Gaussian process
+regression~\cite{Rasm06}.  SuperEEG entails using data from multiple
+people to estimate activity patterns at arbitrary locations in each
+person's brain (i.e., independent of their electrode placements).  We
+test SuperEEG approach using two large datasets of intracranial
+recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
+  MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
+  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  We show
+that the SuperEEG algorithm recovers signals well from electrodes that
+were held out of the training dataset.  We also examine the factors
+that influence how accurately activity may be estimated (recovered),
+which may have important implications for electrode design and
+placement in neurosurgical applications.
 
 \section*{Approach}
-The SuperEEG approach to inferring high temporal resolution full-brain activity patterns is outlined and summarized in
+The SuperEEG approach to inferring high temporal resolution full-brain
+activity patterns is outlined and summarized in
 Figure~\ref{fig:methods}. We describe (in this section) and evaluate
-(in \textit{Results}) our approach using a two large previously collected
-dataset comprising multi-session intracranial recordings.  The first dataset was taken from
-6876 electrodes implanted in the brains of 88 epilepsy
+(in \textit{Results}) our approach using a two large previously
+collected dataset comprising multi-session intracranial recordings.
+Dataset 1 comprises multi-session recordings taken from 6876
+electrodes implanted in the brains of 88 epilepsy
 patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  We first applied a fourth order Butterworth notch filter to remove
-60 Hz ($\pm$ .5 Hz) line noise.  We then excluded any electrodes that
-showed putative epileptiform activity.  Specifically, we excluded from
-further analysis any electrode that exhibited an average kurtosis of
-10 or greater across all of that patient's recording sessions.  We
-also excluded any patients with fewer than 2 electrodes that passed
-this criteria, as the Super EEG algorithm requires measuring
-correlations between 2 or more electrodes from each patient.
-Altogether this yielded clean recordings from 4168 electrodes
-implanted throughout the brains of 67 patients (Fig.~\ref{fig:methods}A).
-For the purposes of comparing task-specific contributions to reconstruction accuracy, we limited our analyses in the second dataset to patients that participated in two free recall experiments.
-Applying the same kurtosis thresholding yielded clean recordings from 24 patients and 2975 electrodes for the second dataset.
-Each individual patient contributes
-electrodes from a limited set of brain locations, which we localized
-in a common space (MNI152); an example patient's 54 electrodes that
-passed the predefined kurtosis test are highlighted in black and red.
+  MannEtal12}.  Each recording session lasted from XXX--XXX hours, and
+includes data recorded roughly from when the patients woke up each
+morning, to before they went to sleep at the end of each day.  In
+addition to typical bed-ridden hospital patient activities (e.g.,
+lying in bed, reading, watching television, using personal electronic
+devices, listening to music, visiting with family and friends, etc.),
+the patients also performed a variety of experimental cognitive tasks
+throughout their day (primarily list-learning memory tasks).  For the
+purposes of the Dataset 1 analyses presented here, we aggregated all
+data across each recording session, ignoring the particular activities
+or tasks the patients were performing at any given moment.  We used
+Dataset 1 to develop and debug our main SuperEEG approach, and to
+examine the extent to which SuperEEG might be able to generate
+task-general predictions.  Dataset 2 comprised multi-session
+recordings from XXX electrodes implanted in the brains of XXX epilepsy
+patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
+  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Whereas
+Dataset 1 included recordings taken during a wide variety of
+behaviors, Dataset 2 included recordings taken as each patient
+performed each of two memory tasks: a random word list free recall
+task and a categorized word list free recall task.  We used Dataset 2
+to further examine the ability of SuperEEG to generalize its
+predictions within versus across tasks.
+
+\textbf{JRM STOPPED HERE}
+
+The first dataset was taken from 6876 electrodes implanted in the
+brains of 88 epilepsy patients~\cite{SedeEtal03, SedeEtal07a,
+  SedeEtal07b, MannEtal11, MannEtal12}.  We first applied a fourth
+order Butterworth notch filter to remove 60 Hz ($\pm$ .5 Hz) line
+noise.  We then excluded any electrodes that showed putative
+epileptiform activity.  Specifically, we excluded from further
+analysis any electrode that exhibited an average kurtosis of 10 or
+greater across all of that patient's recording sessions.  We also
+excluded any patients with fewer than 2 electrodes that passed this
+criteria, as the SuperEEG algorithm requires measuring correlations
+between 2 or more electrodes from each patient.  Altogether this
+yielded clean recordings from 4168 electrodes implanted throughout the
+brains of 67 patients (Fig.~\ref{fig:methods}A). For the purposes of
+comparing task-specific contributions to reconstruction accuracy, we
+limited our analyses in the second dataset to patients that
+participated in two free recall experiments.  Applying the same
+kurtosis thresholding yielded clean recordings from 24 patients and
+2975 electrodes for the second dataset. Each individual patient
+contributes electrodes from a limited set of brain locations, which we
+localized in a common space (MNI152); an example patient's 54
+electrodes that passed the predefined kurtosis test are highlighted in
+black and red.
 
@@
 in $\bar{R}$ where we did not observe a recording for patient $s$
-(these are the recording locations we will want to fill in using Super EEG).
+(these are the recording locations we will want to fill in using SuperEEG).
 We can sub-divide $\hat{K}$ as follows:
@@
 \end{align}
-This equation is the foundation of the Super EEG algorithm.  Whereas
+This equation is the foundation of the SuperEEG algorithm.  Whereas
 we observe the recordings only at the locations in $\alpha$,
@@
 
-The Super EEG algorithm described above and in
+The SuperEEG algorithm described above and in
 Figure~\ref{fig:methods} allows us to estimate (up to a constant
@@
 \section*{Results}
-To test the accuracy with which the Super EEG algorithm reconstructs activity throughout the brain, we held out each electrode from the full
+To test the accuracy with which the SuperEEG algorithm reconstructs activity throughout the brain, we held out each electrode from the full
 dataset in turn and treated it as unobserved. We then asked: how
-closely did each of the Super EEG-reconstructed LFPs match the
+closely did each of the SuperEEG-reconstructed LFPs match the
 observed data?  We sought to evaluate both the overall reconstruction
@@
 sample across 14.2 total hours of recordings from that patient (correlation:
-$r = 0.91, p < 10\textsuperscript{-10}$).  Although the Super EEG
+$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
 algorithm recovered the recordings from this electrode well, we sought to
@@
 We obtained a single correlation coefficient for each electrode
-location in $\bar{R}$, reflecting how well the Super EEG algorithm was
+location in $\bar{R}$, reflecting how well the SuperEEG algorithm was
 able to recover the recording at that location by incorporating data across patients (Across shown in black, see Fig.~\ref{fig:corrmap}A).
@@
 between $z$-transformed mean correlation coefficients by patient: $t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially conservative
-test, given that the Super EEG reconstructions exclude (from the
+test, given that the SuperEEG reconstructions exclude (from the
 correlation matrix estimates) all data from the patient whose data is
@@
 between $z$-transformed mean correlation coefficients by patient for experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).
-That the Super EEG-derived correlations were reliably
+That the SuperEEG-derived correlations were reliably
 stronger than these correlations obtained using a volume conductance null model is exciting
@@
 information contained in nearby electrodes.  Second, it implies that
-the spatial correlations driving the Super EEG algorithm are, to some
+the spatial correlations driving the SuperEEG algorithm are, to some
 extent, shared across people.
@@
 implantation targets for neurosurgeons and neurologists who wish to
-use Super EEG to reconstruct full-brain electrophysiological signals.
+use SuperEEG to reconstruct full-brain electrophysiological signals.
 The above findings, that one can infer brain activity throughout a person's brain 
@@
 %recap main approach
-Super EEG infers full-brain activity patterns by leveraging
+SuperEEG infers full-brain activity patterns by leveraging
 correlations in those patterns of brain activity within and across people.  Although
@@
 %why does it work?  redundancy of brain
-A fundamental assumption of the Super EEG algorithm is that the data
+A fundamental assumption of the SuperEEG algorithm is that the data
 covariance matrix is stable over time and across people.  This is a
@@
 that the full-brain covariance matrix is not stable across people.  If
-the fundamental stability assumptions that Super EEG relies on are
-violated, how can the Super EEG algorithm still accurately recover LFP
+the fundamental stability assumptions that SuperEEG relies on are
+violated, how can the SuperEEG algorithm still accurately recover LFP
 data?  It is important to recognize that the fact that variability
@@
 anatomy.  Nevertheless, one could imagine future improvements to the
-Super EEG approach that leverage resting state fMRI or structural data
+SuperEEG approach that leverage resting state fMRI or structural data
 [e.g. diffusion tensor imaging (DTI)] to estimate Bayesian priors over
@@
 %activity?
-One potential limitation of the Super EEG approach is that the above
+One potential limitation of the SuperEEG approach is that the above
 assumption of covariance stability across people may be violated even
@@
 
-A second potential limitation of the Super EEG approach is that it
+A second potential limitation of the SuperEEG approach is that it
 does not provide a natural means of estimating the precise timing of
@@
 rates of neurons that underly the population contributing to the
-LFP~\cite{MannEtal09}.  Because Super EEG reconstructs LFPs throughout
+LFP~\cite{MannEtal09}.  Because SuperEEG reconstructs LFPs throughout
 the brain, one could in principle use gamma or broadband power in the

### 2018-10-04 paper_figs/code/plot.py
updated supplemental figures

@@ -552,11 +552,12 @@ def plot_2d_corr_hist(df, outfile=None):
 
 ######### Supplemental ###########
 
+
 def plot_split_violin(df, legend=True, yticks=True, outfile=None):
     fig = plt.gcf()
-    fig.set_size_inches(10.5, 10.5)
+    fig.set_size_inches(12.5, 10.5)
     plt.ylim(-1.2,2.0)
-    ax = sns.violinplot(x="Experiment", y="Correlation", hue="Subject", order=[ "a", "w", "all"], ylim=[-1,1], data=df, palette="gray", split=True)
+    ax = sns.violinplot(x="Experiment", y="Correlation", hue="Subject", order=["w", "a", "all"], ylim=[-1,1], data=df, palette="gray", split=True)
     if legend:
         handles, labels = fig.get_axes()[0].get_legend_handles_labels()
         fig.get_axes()[0].legend(handles, ['Across', 'Within'], loc='lower right', fontsize=30)
@@ -566,12 +567,31 @@ def plot_split_violin(df, legend=True, yticks=True, outfile=None):
     ax.tick_params(axis='y', which='both', length=0, labelsize=18)
     ax.set_xticklabels(['Within', 'Across','All'])
     ax.set_xlabel('Experiment', fontsize=30)
+
+    yposlist_df = df.groupby(['Experiment', 'Subject'])['Correlation'].mean()
+    yposlist = yposlist_df.reindex(["w", "a", "all"], level='Experiment').tolist()
+    xposlist = range(3)
+
+    c = 0
+    for i in range(len(yposlist)):
+
+        if (i%2) == 0:
+            ax.text(c-.12, yposlist[i], np.round(yposlist[i],2), fontsize=14, color='white')
+        else:
+            ax.text(c+.02, yposlist[i], np.round(yposlist[i],2) , fontsize=14, color='white')
+            c +=1
+
     ### first two significance lines:
-    ylim = 1
+    ylim = 1.2
     for l in range(3):
-        ylim += .2
+        plt.plot([l-.05, l+.05], [1.15, 1.15], marker = '|', mew=2, markersize=10, color='k', linewidth=2)
+        ax.plot(l, 1.15 + .05, marker = '*', markersize=10, color='k')
+
+        ylim += .15
         for i in range(2):
-            ylim += i/10
+            ylim += i/14
+
+
             if l==2:
                 m1, n1 = [l, l-l], [ylim, ylim]
                 a1 = (l + (l-l)) /2
[…]

### 2018-10-04 paper_figs/code/plot.py
new supplemental figures

@@ -28,8 +28,12 @@ def r2z(r):
 
 def z2r(z):
     r = np.divide((np.exp(2*z) - 1), (np.exp(2*z) + 1))
-    r[np.isnan(r)] = 0
-    r[np.isinf(r)] = np.sign(r)[np.isinf(r)]
+    try:
+        r[np.isnan(r)] = 0
+        r[np.isinf(r)] = np.sign(r)[np.isinf(r)]
+    except:
+        pass
+
     return r
 
 def compile_df_locs(df_column):
@@ -51,12 +55,12 @@ def compile_df_locs(df_column):
 
 ############## Methods ##########################
 
-def plot_hist(dataframe, title=None, outfile=None):
+def plot_hist(dataframe, X='Correlation', title=None, outfile=None):
     fig = plt.gcf()
     fig.set_size_inches(18.5, 10.5)
     sns.set_style("white")
     df_corrs = pd.DataFrame()
-    df_corrs['Correlations'] = dataframe['Correlation'].values
+    df_corrs[X] = dataframe[X].values
     n_count = len(df_corrs)
     bin_values = np.arange(start=-1, stop=1, step=.025)
     ax = sns.distplot(df_corrs, hist=True, kde=True,
@@ -67,7 +71,7 @@ def plot_hist(dataframe, title=None, outfile=None):
     vals = ax.get_yticks()
     ax.set_yticklabels([np.round(x/n_count,5) for x in vals])
     ax.set_ylabel('Proportion of electrodes', fontsize=21)
-    ax.set_xlabel('Correlation', fontsize=21)
+    ax.set_xlabel(X, fontsize=21)
     ax.set_xlim(-1, 1)
     ax.set_frame_on(False)
     ax.tick_params(axis='x', labelsize=18)
@@ -77,7 +81,7 @@ def plot_hist(dataframe, title=None, outfile=None):
     bottom, height = .75, .5
     plt.tight_layout()
 
-    ax.text(left, bottom, 'mean = '+ str(np.round(dataframe['Correlation'].mean(),3)),
+    ax.text(left, bottom, 'mean = '+ str(np.round(dataframe[X].mean(),3)),
             horizontalalignment='left',
             verticalalignment='top',
             transform=ax.transAxes, fontsize=18)
@@ -626,22 +630,70 @@ def plot_split_violin(df, legend=True, yticks=True, outfile=None):
     if outfile:
         plt.savefig(outfile)
 
-########### Dont need ####################
 
[…]

### 2018-10-04 paper/main.tex

@@
   other people's recordings, what would recordings most likely have
-  looked like at \textit{other} locations in that individual's brain?
-%\\
-%\small{\textbf{Keywords: Electrocorticography (ECoG), intracranial electroencephalography (iEEG),
-%local field potential (LFP), epilepsy, maximum likelihood estimation, Gaussian process regression}}
+  looked like at \textit{other} locations in that individual's
+  brain?\\\\
+  \footnotesize{\textbf{Keywords: Electrocorticography (ECoG),
+      intracranial electroencephalography (iEEG), local field
+      potential (LFP), epilepsy, maximum likelihood estimation,
+      Gaussian process regression}}
 \end{abstract}
@@
 must choose to optimize spatial resolution at the cost of temporal
-resolution (e.g.\ as in fMRI) or temporal resolution at the cost of
-spatial resolution (e.g.\ as in EEG and MEG).  A less widely used
+resolution (e.g., as in fMRI) or temporal resolution at the cost of
+spatial resolution (e.g., as in EEG and MEG).  A less widely used
 approach (due to requiring work with neurosurgical patients) is to
@@
 
-%Beamforming: huge advance for scalp recordings, but the inverse
-%problem is fundamentally ambiguous.  This limits the precision with
-%which one can measure activity from deep brain structures.
 An increasingly popular approach is to improve the effective spatial
@@
 produced by external (noise) sources are substantially stronger than
-those produced by the neuronal changes being sought (i.e.\ at deep
+those produced by the neuronal changes being sought (i.e., at deep
 structures, as measured by sensors at the scalp).  This means that
@@
 measured responses over tens to hundreds of responses or trials
-(e.g. see review by~\cite{HillEtal05}).
+(e.g., see review by~\cite{HillEtal05}).
 
@@
 however, the signal quality of both recordings suffers substantially
-when the two techniques are applied simultaneously (e.g. see review
+when the two techniques are applied simultaneously (e.g., see review
 by~\cite{HustEtal12}).  In addition, the experimental designs that are
@@
 
-%Direct intracranial recordings are the gold standard method for
-%measuring activity from deep brain structures in both humans and
-%animals.
-%However, one can only implant a limited number of electrodes in a
-%given person's brain.  This begs the question: what can we infer
-%about the activity exhibited by the rest of that person's brain,
-%given what we learn from recordings taken from \textit{other people's
-%brains}?
 The current ``gold standard'' for precisely localizing signals and
@@
 
-\textbf{JRM STOPPED HERE}
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/methods}
+  \caption{\textbf{Methods overview.}  \textbf{A.  Electrode
+      locations.}  Each dot reflects the location of a single
+    electrode in dataset 1, colored according to 7 factor labels (see
+    Panel D for details). One patient's electrode locations are
+    highlighted in black and the to-be-reconstructed recording
+    location is highlighted in red. \textbf{B. Radial basis function
+      (RBF).}  Each electrode contributed by the patient (black)
+    weights on the full set of locations under consideration (all dots
+    in Panel A, defined as $\bar{R}$ in the text).  The weights fall
+    off with positional distance (in MNI space) according to an RBF.
+    \textbf{C. Per-patient correlation matrices.}  After computing the
+    pairwise correlations between the recordings from each patient's
+    electrodes, we use RBF-weighted averages to estimate correlations
+    between all locations in $\bar{R}$.  We obtain an estimated
+    full-brain correlation matrix using each patient's
+    data. \textbf{D.  Combined correlation matrix.}  We estimate a
+    single full-brain correlation matrix by averaging the
+    patient-specific correlation matrices.  We sort the resulting
+    correlation matrix based on 7 factor labels obtained from k-means
+    clustering~\cite{YeoEtal11}). \textbf{E.  Reconstructing activity
+      throughout the brain.}  Given the observed activity from the
+    patient's electrodes and the estimated correlation matrix (Panel
+    D), we can compute a maximum likelihood estimate of the voltage
+    trace at any location in $\bar{R}$.  An example reconstruction (at
+    the red dot in Panel A) is shown in red, and the actual recording
+    at that location is highlighted above in blue.}
+  \label{fig:methods}
+\end{figure}
 
-The first dataset was taken from 6876 electrodes implanted in the
-brains of 88 epilepsy patients~\cite{SedeEtal03, SedeEtal07a,
-  SedeEtal07b, MannEtal11, MannEtal12}.  We first applied a fourth
-order Butterworth notch filter to remove 60 Hz ($\pm$ .5 Hz) line
-noise.  We then excluded any electrodes that showed putative
-epileptiform activity.  Specifically, we excluded from further
-analysis any electrode that exhibited an average kurtosis of 10 or
-greater across all of that patient's recording sessions.  We also
-excluded any patients with fewer than 2 electrodes that passed this
-criteria, as the SuperEEG algorithm requires measuring correlations
-between 2 or more electrodes from each patient.  Altogether this
-yielded clean recordings from 4168 electrodes implanted throughout the
-brains of 67 patients (Fig.~\ref{fig:methods}A). For the purposes of
-comparing task-specific contributions to reconstruction accuracy, we
-limited our analyses in the second dataset to patients that
-participated in two free recall experiments.  Applying the same
-kurtosis thresholding yielded clean recordings from 24 patients and
-2975 electrodes for the second dataset. Each individual patient
-contributes electrodes from a limited set of brain locations, which we
-localized in a common space (MNI152); an example patient's 54
-electrodes that passed the predefined kurtosis test are highlighted in
-black and red.
+We first applied fourth order Butterworth notch filter to remove 60 Hz
+($\pm$ .5 Hz) line noise from every recording (from every electrode).
+We then excluded any electrodes that showed putative epileptiform
+activity.  Specifically, we excluded from further analysis any
+electrode that exhibited an average kurtosis of 10 or greater across
+all of that patient's recording sessions.  We also excluded any
+patients with fewer than 2 electrodes that passed this criteria, as
+the SuperEEG algorithm requires measuring correlations between 2 or
+more electrodes from each patient.  For Dataset 1, this yielded clean
+recordings from 4168 electrodes implanted throughout the brains of 67
+patients (Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
+recordings from 2975 electrodes from 24 patients.  Each individual
+patient contributes electrodes from a limited set of brain locations,
+which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
+example Dataset 1 patient's 54 electrodes that passed the predefined
+kurtosis test are highlighted in black and red.
 
@@
 recording surface of the electrode also contribute to the recording,
-albeit (often) to a much lesser extent.  One mechanism underlying these
-contributions is volume conduction.  The precise rate of falloff due
-to volume conduction (i.e. how much a small volume of brain tissue at
-location $x$ contributes to the recording from an electrode at
-location $\eta$) depends on the size of the recording surface, the
-electrode's impedance, and the conductance profile of the volume of
-brain between $x$ and $\eta$.  As an approximation of this intuition,
-we place a Gaussian radial basis function (RBF) at the location $\eta$
-of each electrode's recording surface (Fig.~\ref{fig:methods}B).  We
-use the values of the RBF at any brain location $x$ as a rough
-estimate of how much structures around $x$ contributed to the
-recording from location $\eta$:
-
+albeit (ceteris paribus) to a much lesser extent.  One mechanism
+underlying these contributions is volume conduction.  The precise rate
+of falloff due to volume conduction (i.e., how much a small volume of
+brain tissue at location $x$ contributes to the recording from an
+electrode at location $\eta$) depends on the size of the recording
+surface, the electrode's impedance, and the conductance profile of the
+volume of brain between $x$ and $\eta$.  As an approximation of this
+intuition, we place a Gaussian radial basis function (RBF) at the
+location $\eta$ of each electrode's recording surface
+(Fig.~\ref{fig:methods}B).  We use the values of the RBF at any brain
+location $x$ as a rough estimate of how much structures around $x$
+contributed to the recording from location $\eta$:
 \begin{align}
@@
 coverage (which implies a large value of $\lambda$). Using our prior
-work as a guide~\cite{MannEtal14b}, we set $\lambda = 20$, although
-this could in theory be optimized, e.g. using cross validation.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/methods}
-  \caption{\textbf{Methods overview.}  \textbf{A.  Electrode
-      locations.}  Each dot reflects the location of a single
-    electrode in dataset 1, colored according to 7 factor labels (see Panel D for details). One patient's electrode locations are
-    highlighted in black and the to-be-reconstructed recording location
-    is highlighted in red. \textbf{B. Radial basis function (RBF).}
-    Each electrode contributed by the patient (black) weights on the
-    full set of locations under consideration (all dots in Panel A,
-    defined as $\bar{R}$ in the text).  The weights fall off with
-    positional distance (in MNI space) according to an RBF.
-    \textbf{C. Per-patient correlation matrices.}  After computing the
-    pairwise correlations between the recordings from each patient's
-    electrodes, we use RBF-weighted averages to estimate correlations
-    between all locations in $\bar{R}$.  We obtain an estimated
-    full-brain correlation matrix using each patient's
-    data. \textbf{D.  Combined correlation matrix.}  We estimate a
-    single full-brain correlation matrix by averaging 
-    the patient-specific correlation matrices.  We sort the resulting correlation matrix based on 7 factor labels obtained from k-means clustering~\cite{YeoEtal11}). \textbf{E.
-      Reconstructing activity throughout the brain.}  Given the observed
-    activity from the patient's electrodes and the estimated
-    correlation matrix (Panel D), we can compute a maximum likelihood
-    estimate of the voltage trace at any location in $\bar{R}$.  An
-    example reconstruction (at the red dot in Panel A) is shown in
-    red, and the actual recording at that location is highlighted above in blue.}
-  \label{fig:methods}
-\end{figure}
+work as a guide~\citep{MannEtal14b, MannEtal18}, we set $\lambda = 20$,
+although this could in theory be optimized, e.g., using cross
+validation or a formal model~\citep[e.g.,][]{MannEtal18}.
 
@@
 structures near $x$ and $\eta$.  We use spatial correlations in the
-data to estimate these anatomical connections.  Let $\bar{R}$ be the
-set of locations at which we wish to estimate local field potentials,
-and let $R_{s}$ be set of locations at which we observe local field
-potentials from patient $s$ (excluding the electrodes that did not
-pass the kurtosis test described above). In the analyses below we
-define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate the expected
-inter-electrode correlation matrix for patient $s$, where
-$C_{s,k}(i,j)$ is the correlation between the time series of voltages
-for electrodes $i$ and $j$ from subject $s$ during session $k$, using:
+data to estimate these anatomical connections~\citep{BeckEtal18}.  Let
+$\bar{R}$ be the set of locations at which we wish to estimate local
+field potentials, and let $R_{s}$ be set of locations at which we
+observe local field potentials from patient $s$ (excluding the
+electrodes that did not pass the kurtosis test described above). In
+the analyses below we define $\bar{R} = \cup_{s=1}^S R_s$.  We can
+calculate the expected inter-electrode correlation matrix for patient
+$s$, where $C_{s,k}(i,j)$ is the correlation between the time series
+of voltages for electrodes $i$ and $j$ from subject $s$ during session
+$k$, using:
 
@@
 to-be-estimated locations by number of patient electrode locations
-weight matrix, $W$.  Specifically, $W$ approximates how informative the
+weight matrix, $W_s$.  Specifically, $W_s$ approximates how informative the
 recordings at each location in $R_s$ are in reconstructing activity at
@@
 \begin{align}
-W(i, j) = \mathrm{rbf}(i|j,\lambda)\label{eqn:weight_matrix}.
+W_s(i, j) = \mathrm{rbf}(i|j,\lambda)\label{eqn:weight_matrix}.
 \end{align}
 
-Given this weight matrix, $W$,
+Given this weight matrix, $W_s$,
 and the observed inter-electrode correlation matrix for patient $s$,
 $\bar{C}_{s}$, we can estimate the correlation matrix for all locations in
-$\bar{R}$ (Fig.~\ref{fig:methods}C) using:
+$\bar{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:
 
 \begin{align}
-\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\bar{C}_{s}(i,j))}\label{eqn:correlation_matrix_num}\\
- \hat{D}_{s}(x,y) & = \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j). \label{eqn:correlation_matrix_den}
+\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\bar{C}_{s}(i,j))}\label{eqn:subj_corrmat_num}\\
+ \hat{D}_{s}(x,y) & = \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i)
+                    \cdot W(y,j). \label{eqn:subj_corrmat_den}\\
+ \hat{C}_s &= \mathrm{r}\left( \frac{\hat{N}_{s}}{\hat{D}_{s}} \right)
+             \label{eqn:subj_corrmat}.
 \end{align}
-Intuitively, we construct an estimated correlation matrix from each
-individual patient's data (Fig.~\ref{fig:methods}C) using
-Equations~\ref{eqn:correlation_matrix_num} \& \ref{eqn:correlation_matrix_den}, then we sum across these estimates for $S$ patients and divide (see Equations~\ref{eqn:correlation_matrix}) to obtain the expected correlation
-matrix, $\hat{K}$ (Fig.~\ref{fig:methods}D):
+After estimating the numerator ($\hat{N}_{s}$) and denominator
+($\hat{D}_{s}$) placeholders for each $\hat{C}_{s}$, we aggregate these
+estimates across patients to obtain a single expected full-brain
+correlation matrix ($\hat{K}$; Fig.~\ref{fig:methods}D):
+\begin{align}
+ \hat{K} = \mathrm{r} \left(  \frac{\sum  \hat{N}_{s}}{\sum \hat{D}_{s}}\right).\label{eqn:correlation_matrix}
+\end{align}
+Intuitively, the numerators capture the general structures of the
+patient-specific estimates of full-brain correlations, and the
+denominators account for which locations were near the implanted
+electrodes in each patient.  To obtain $\hat{K}$, we compute a
+weighted average across the estimated patient-specific full-brain
+correlation matrices, where patients with observed electrodes near a
+particular set of locations in $\hat{K}$ contribute more to the
+estimate.
 
-\begin{align}
- \hat{K} = \mathrm{r} \left (  \frac{\sum  \hat{N}_{s}}{\sum \hat{D}_{s}}\right ).\label{eqn:correlation_matrix}
-\end{align}
-Now we can use the following intuition: given (i) the observed
-responses from a limited set of locations in $R_{s}$ ($Y_{s}$) and
-(ii) how each location's responses relate to all other responses
-($\hat{K}$), we can estimate the LFP data from patient
-$s$, for any arbitrary location in $\bar{R}$
-(Fig.~\ref{fig:methods}E).
+Having used the multi-patient data to estimate a full-brain
+correlation matrix at the set of locations in $\bar{R}$ that we wish
+to know about, we next use $\hat{K}$ to estimate activity patterns
+everywhere in $\bar{R}$, given observations at only a subset of
+locations in $\bar{R}$ (Fig.~\ref{fig:methods}E).
 
-Let $\alpha$ be the set of indices of patient $s$'s electrode locations in
-$\bar{R}$, and let $\beta$ be the set of indices of all other
-locations in $\bar{R}$. In other words, $\beta$ reflects the locations
+Let $\alpha_s$ be the set of indices of patient $s$'s electrode locations in
+$\bar{R}$, and let $\beta_s$ be the set of indices of all other
+locations in $\bar{R}$. In other words, $\beta_s$ reflects the locations
 in $\bar{R}$ where we did not observe a recording for patient $s$
@@
 \begin{align}
-\hat{K}_{\beta,\alpha} &= \hat{K}(\beta,\alpha),~\mathrm{and}\label{eqn:Kba}\\
-\hat{K}_{\alpha,\alpha} &= \hat{K}(\alpha,\alpha)\label{eqn:Kaa}.
+\hat{K}_{\beta_s,\alpha_s} &= \hat{K}(\beta_s,\alpha_s),~\mathrm{and}\label{eqn:Kba}\\
+\hat{K}_{\alpha_s,\alpha_s} &= \hat{K}(\alpha_s,\alpha_s)\label{eqn:Kaa}.
 \end{align}
-Here $\hat{K}_{\beta, \alpha}$ stores the correlations between the
-``unknown'' activity at the locations in $\beta$ and the observed
-activity at the locations in $\alpha$, and $\hat{K}_{\alpha, \alpha}$
-stores the correlations between the observed recordings (at the
-locations in $\alpha$).
+Here $\hat{K}_{\beta_s, \alpha_s}$ represents the correlations between
+the ``unknown'' activity at the locations in $\beta_s$ and the
+observed activity at the locations in $\alpha_s$, and
+$\hat{K}_{\alpha_s, \alpha_s}$ represents the correlations between the
+observed recordings (at the locations in $\alpha_s$).
 
-Let $Y_{s,k,\alpha}$ be the number-of-timepoints
-($T$) by length($\alpha$) matrix of (observed) voltages from the electrodes in $\alpha$ during session $k$ from patient $s$.
-Then we can estimate the voltage from patient $s$'s $k^{th}$ session at the locations in $\beta$ using~\cite{Rasm06}:
+Let $Y_{s,k,\alpha_s}$ be the number-of-timepoints ($T$) by
+length($\alpha_s$) matrix of (observed) voltages from the electrodes in
+$\alpha_s$ during session $k$ from patient $s$. Then we can estimate the
+voltage from patient $s$'s $k^{th}$ session at the locations in
+$\beta_s$ using~\cite{Rasm06}:
 
 \begin{align}
-Y_{s,k,\beta} &= ((\hat{K}_{\beta,\alpha}\cdot\hat{K}_{\alpha,\alpha}^{-1})\cdot Y_{s,k,\alpha}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
+Y_{s,k,\beta} &= ((\hat{K}_{\beta_s,\alpha_s}\cdot\hat{K}_{\alpha_s,\alpha_s}^{-1})\cdot Y_{s,k,\alpha_s}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
 \end{align}
-This equation is the foundation of the SuperEEG algorithm.  Whereas
-we observe the recordings only at the locations in $\alpha$,
+This equation is the foundation of the SuperEEG algorithm.  Whereas we
+observe recordings only at the locations in $\alpha_s$,
 Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
-at all locations in $\beta$, which we can define \textit{a priori} to
-include any locations we wish, throughout the brain.  This yields estimates of
-the time-varying voltages at \textit{every} location in $\bar{R}$.
+at all locations in $\beta_s$, which we can define \textit{a priori}
+to include any locations we wish, throughout the brain.  This yields
+estimates of the time-varying voltages at \textit{every} location in
+$\bar{R}$, provided that we define $\bar{R}$ in advance to include the
+union of all of the locations in $\alpha_s$ and all of the locations
+at which we wish to estimate recordings (i.e., a timeseries of
+voltages).
 
@@
 rather than attempting to recover absolute voltages. (This property
-reflects the fact that $\hat{K}_{\beta, \alpha}$ and
-$\hat{K}_{\alpha, \alpha}$ are correlation matrices rather than
+reflects the fact that $\hat{K}_{\beta_s, \alpha_s}$ and
+$\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
 covariance matrices.)  Also, note that
-Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
+Equation~\ref{eqn:reconstruction} directly requires computing a $T$ by $T$
 matrix, which can become computationally intractable when $T$ is very
-large (e.g.\ for the patient highlighted in Fig.~\ref{fig:recon}, $T = 20458799$). However, we may approximate $Y_{s,k,\beta}$ in a piecewise
-manner by filling in $Y_{s,k,\beta}$ in blocks of size $b$ samples
-(using the corresponding samples from $Y_{s, k, \alpha}$).  In our
-computations we set $b = 25000$.
+large (e.g., for the patient highlighted in Fig.~\ref{fig:recon}, $T =
+20458799$). However, because Equation~\ref{eqn:reconstruction} is time
+invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
+manner by filling in $Y_{s,k,\beta_s}$ one row at a time (using the
+corresponding samples from $Y_{s, k, \alpha_s}$).
 
@@
 locations in the set $\bar{R}$, \textit{even if we did not record that
-  patient's brain at all of those locations}.
+  patient's brain at all of those locations}.  We next turn to an
+evaluation of the accuracy of those estimates.
+
+\textbf{JRM STOPPED HERE}
 
 \section*{Results}
-To test the accuracy with which the SuperEEG algorithm reconstructs activity throughout the brain, we held out each electrode from the full
-dataset in turn and treated it as unobserved. We then asked: how
-closely did each of the SuperEEG-reconstructed LFPs match the
-observed data?  We sought to evaluate both the overall reconstruction
-accuracy as well as how reconstruction accuracy varied as a function
-of implantation location.
+To test the accuracy with which the SuperEEG algorithm reconstructs
+activity throughout the brain, we held out each electrode from the
+full dataset in turn and treated it as unobserved. We then asked: how
+closely did each of the SuperEEG-reconstructed LFPs match the observed
+data?  We sought to evaluate both the overall reconstruction accuracy
+as well as how reconstruction accuracy varied as a function of
+implantation location.
 
@@
 correlation matrix using every \textit{other} patient's data
-(i.e. every patient except the one who contributed the
+(i.e., every patient except the one who contributed the
 to-be-reconstructed electrode data).  In our analyses, we then
@@
 data?  It is important to recognize that the fact that variability
-(over time or across people) is predictive (e.g.\ of cognitive states
+(over time or across people) is predictive (e.g., of cognitive states
 during story listening or fluid intelligence scores) does not
@@
 SuperEEG approach that leverage resting state fMRI or structural data
-[e.g. diffusion tensor imaging (DTI)] to estimate Bayesian priors over
+[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
 the correlation matrices inferred, in the current framing, using only
@@
 matrix is stable (over time and/or across people), and/or
-incorporating more detailed brain conductance models (e.g.\ informed
+incorporating more detailed brain conductance models (e.g., informed
 by structural MRI scans) may improve the predictive performance of the

### 2018-10-04 file_io/file_io.py
new fileio script resampling to 250

@@ -27,11 +27,13 @@ def npz2bo(infile):
 
 results_dir = config['resultsdir']
 
-
+RESAMPLERATE=250
 fname = sys.argv[1]
 
 file_name = os.path.basename(os.path.splitext(fname)[0])
 bo = npz2bo(fname)
+
+bo.resample(RESAMPLERATE)
 
 bo.save(fname=os.path.join(results_dir, file_name))
 

### 2018-10-04 paper/main.tex

@@
 ($\pm$ .5 Hz) line noise from every recording (from every electrode).
-We then excluded any electrodes that showed putative epileptiform
-activity.  Specifically, we excluded from further analysis any
-electrode that exhibited an average kurtosis of 10 or greater across
-all of that patient's recording sessions.  We also excluded any
-patients with fewer than 2 electrodes that passed this criteria, as
-the SuperEEG algorithm requires measuring correlations between 2 or
-more electrodes from each patient.  For Dataset 1, this yielded clean
-recordings from 4168 electrodes implanted throughout the brains of 67
-patients (Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
+Next, we downsampled the recordings (regardless of the original
+samplerate) to 250 Hz.  (This downsampling step served to both
+normalize for differences in sampling rates across patients and to
+ease the computational burden of our subsequent analyses.)  We then
+excluded any electrodes that showed putative epileptiform activity.
+Specifically, we excluded from further analysis any electrode that
+exhibited an average kurtosis of 10 or greater across all of that
+patient's recording sessions.  We also excluded any patients with
+fewer than 2 electrodes that passed this criteria, as the SuperEEG
+algorithm requires measuring correlations between 2 or more electrodes
+from each patient.  For Dataset 1, this yielded clean recordings from
+4168 electrodes implanted throughout the brains of 67 patients
+(Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
 recordings from 2975 electrodes from 24 patients.  Each individual
@@
 
-\textbf{JRM STOPPED HERE}
-
 \section*{Results}
@@
 full dataset in turn and treated it as unobserved. We then asked: how
-closely did each of the SuperEEG-reconstructed LFPs match the observed
-data?  We sought to evaluate both the overall reconstruction accuracy
-as well as how reconstruction accuracy varied as a function of
-implantation location.
+closely did each of the SuperEEG-estimated recordings at those
+electrodes match the observed recordings from those electrodes?
 
-We first examined raw LFP traces and their associated Super
-EEG-derived reconstructions.  Figure~\ref{fig:recon}A displays the
-LFP from the red electrode in Figure~\ref{fig:methods}A, and its
-associated reconstruction, during a 5~s time window during one of the
-patient's 6 recording sessions.  Figure~\ref{fig:recon}B displays a 2D
-histogram of the observed versus reconstructed voltages for every
-sample across 14.2 total hours of recordings from that patient (correlation:
+\textbf{JRM STOPPED HERE}
+% JRM thoughts:
+% - Do we need to use the term "LFP"?
+% - Tie in stats from supplemental analyses.  Fig S4: total number of
+% electrodes, total number of used electrodes, prop thresholded, total
+% recording time, average session time, number of sessions.
+
+We first examined raw LFP traces and their associated SuperEEG-derived
+reconstructions.  Figure~\ref{fig:recon}A displays the LFP from the
+red electrode in Figure~\ref{fig:methods}A, and its associated
+reconstruction, during a 5~s time window during one of the patient's 6
+recording sessions.  Figure~\ref{fig:recon}B displays a 2D histogram
+of the observed versus reconstructed voltages for every sample across
+14.2 total hours of recordings from that patient (correlation:
 $r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
-algorithm recovered the recordings from this electrode well, we sought to
-quantify the algorithm's performance across the full dataset.
+algorithm recovered the recordings from this electrode well, we sought
+to quantify the algorithm's performance across the full dataset.
 
@@
 location in $\bar{R}$, reflecting how well the SuperEEG algorithm was
-able to recover the recording at that location by incorporating data across patients (Across shown in black, see Fig.~\ref{fig:corrmap}A).
-We also reconstructed activity for each electrode using a model trained on the remaining electrodes from only that patient, to account for reconstruction accuracy attributed to volume conductance alone (Within shown in gray, see Fig.~\ref{fig:corrmap}A).
-For the first dataset, we compared these two distributions of correlation coefficients (paired $t$-test
-between $z$-transformed mean correlation coefficients by patient:
-$t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated this analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with similar results (paired $t$-test
-between $z$-transformed mean correlation coefficients by patient: $t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially conservative
-test, given that the SuperEEG reconstructions exclude (from the
-correlation matrix estimates) all data from the patient whose data is
-being reconstructed.  Furthermore, we also replicated this finding for each independent experiment within dataset 2 (Fig. S3 (paired $t$-test
-between $z$-transformed mean correlation coefficients by patient for experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).
-That the SuperEEG-derived correlations were reliably
-stronger than these correlations obtained using a volume conductance null model is exciting
-for two reasons.  First, it implies that distant electrodes provide
-additional predictive power to the data reconstructions beyond the
-information contained in nearby electrodes.  Second, it implies that
-the spatial correlations driving the SuperEEG algorithm are, to some
-extent, shared across people.
+able to recover the recording at that location by incorporating data
+across patients (Across shown in black, see
+Fig.~\ref{fig:corrmap}A). We also reconstructed activity for each
+electrode using a model trained on the remaining electrodes from only
+that patient, to account for reconstruction accuracy attributed to
+volume conductance alone (Within shown in gray, see
+Fig.~\ref{fig:corrmap}A). For the first dataset, we compared these two
+distributions of correlation coefficients (paired $t$-test between
+$z$-transformed mean correlation coefficients by patient:
+$t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated this
+analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with similar
+results (paired $t$-test between $z$-transformed mean correlation
+coefficients by patient: $t(23) = 6.93, p <
+10\textsuperscript{-5}$). This is an especially conservative test,
+given that the SuperEEG reconstructions exclude (from the correlation
+matrix estimates) all data from the patient whose data is being
+reconstructed.  Furthermore, we also replicated this finding for each
+independent experiment within dataset 2 (Fig. S3 (paired $t$-test
+between $z$-transformed mean correlation coefficients by patient for
+experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and
+experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).  That the
+SuperEEG-derived correlations were reliably stronger than these
+correlations obtained using a volume conductance null model is
+exciting for two reasons.  First, it implies that distant electrodes
+provide additional predictive power to the data reconstructions beyond
+the information contained in nearby electrodes.  Second, it implies
+that the spatial correlations driving the SuperEEG algorithm are, to
+some extent, shared across people.
 

### 2018-10-04 code/file_io/file_io.py
code cleanup

@@ -32,8 +32,8 @@ fname = sys.argv[1]
 
 file_name = os.path.basename(os.path.splitext(fname)[0])
 bo = npz2bo(fname)
+bo.resample(resample_rate=RESAMPLERATE)
 
-bo.resample(RESAMPLERATE)
 
 bo.save(fname=os.path.join(results_dir, file_name))
 

### 2018-10-04 pni_recon/config.py

@@ -1,37 +1,0 @@
-import os
-import socket
-
-config = dict()
-
-config['template'] = 'run_job.sh'
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname() == 'vertex.kiewit.dartmouth.edu') or (socket.gethostname() == 'vertex.local'):
-    config['datadir'] = '/Users/lucyowen/Desktop/supereeg_env/pni_bo/'
-    config['workingdir'] = '/Users/lucyowen/Desktop/supereeg_env/pni_recon/'
-    config['startdir'] = '/Users/lucyowen/Desktop/supereeg_env/'  # directory to start the job in
-    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
-else:
-    config['datadir'] = '/idata/cdl/lowen/pni_bo'
-    config['workingdir'] = '/idata/cdl/lowen/pni_recon'
-    config['startdir'] = '/idata/cdl/lowen'
-    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
-
-# job creation options
-config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
-config['lockdir'] = os.path.join(config['workingdir'], 'locks')
-config['resultsdir'] = os.path.join(config['workingdir'], 'results')
-config['modeldir'] = os.path.join(config['startdir'], 'full_mats/results')
-config['avedir'] = os.path.join(config['startdir'], 'ave_mats/results')
-config['pyFRlocsdir'] = os.path.join(config['startdir'], 'pyFR_locs/results')
-
-# runtime options
-config['jobname'] = "pni_recon"  # default job name
-config['q'] = "default"  # options: default, testing, largeq
-config['nnodes'] = 1  # how many nodes to use for this one job
-config['ppn'] = 1  # how many processors to use for this one job (assume 4GB of RAM per processor)
-config['walltime'] = '00:10:00'  # maximum runtime, in h:MM:SS
-#config['startdir'] = '/ihome/lowen/repos/supereeg/examples'  # directory to start the job in
-config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
[…]

### 2018-10-04 pni_recon/make_gif.py

@@ -1,74 +1,0 @@
-import supereeg as se
-import matplotlib.pyplot as plt
-import numpy as np
-import pandas as pd
-import sys
-import os
-from config import config
-plt.switch_backend('agg')
-
-
-### for cluster:
-model_template = sys.argv[1]
-
-vox_size = sys.argv[2]
-
-results_dir = os.path.join(config['resultsdir'], model_template+ '_' + vox_size)
-
-window = sys.argv[3]
-
-cmap=plt.cm.get_cmap('RdBu')
-
-gif_args = {'cmap': cmap,
-            'display_mode': 'lyrz',
-            'threshold': 0,
-            'plot_abs': False,
-            'colorbar': True,
-            'vmin': -.25,
-            'vmax': .25}
-
-fname = 'nn_brain_data_5000_'+ model_template+'_'+vox_size+'.bo'
-
-
-bo = se.load(os.path.join(results_dir, fname))
-
-control = np.load(os.path.join(results_dir,'audio_control_5000.npy'))
-
-audio = np.load(os.path.join(results_dir,'audio_5000.npy'))
-
-pd_audio = pd.DataFrame(audio)
-pd_control = pd.DataFrame(control)
-
-rolling =bo.get_data().rolling(window=int(window)).corr(other=pd_audio[0])
-
-bo_s = se.Brain(data=rolling[int(window):], locs = bo.get_locs(), sample_rate=512)
-
-rolling_c =bo.get_data().rolling(window=int(window)).corr(other=pd_control[0])
-
-bo_c = se.Brain(data=rolling_c[int(window):], locs = bo.get_locs(), sample_rate=512)
-
-bo_s.save(os.path.join(results_dir,'audio_'+ window + '_' + fname))
-bo_c.save(os.path.join(results_dir,'control_'+ window + '_' +fname))
-
-bo_nii = bo_s.to_nii(vox_size=int(vox_size))
-bo_nii_c = bo_c.to_nii(vox_size=int(vox_size))
-
-gif_audio_dir = os.path.join(results_dir, 'gif_audio' + window)
-gif_control_dir = os.path.join(results_dir, 'gif_control' + window)
-
-try:
-    if not os.path.exists(gif_audio_dir):
-        os.makedirs(gif_audio_dir)
-except OSError as err:
-   print(err)
-
-
-try:
-    if not os.path.exists(gif_control_dir):
-        os.makedirs(gif_control_dir)
-except OSError as err:
[…]

### 2018-10-04 pni_recon/recon.py

@@ -1,44 +1,0 @@
-
-import supereeg as se
-from supereeg.helpers import _corr_column, get_rows
-import numpy as np
-import sys
-import os
-import matplotlib.pyplot as plt
-from config import config
-
-## load brain object,
-bo_fname = sys.argv[1]
-
-bo = se.load(bo_fname)
-
-file_name = os.path.basename(os.path.splitext(bo_fname)[0])
-
-model_template = sys.argv[2]
-
-radius = sys.argv[3]
-
-vox_size = sys.argv[4]
-
-## might want to do this.. expand the brain object to the model locations and add
-# mo_mo_fname = os.path.join(config['modeldir'], model_template + '_' + vox_size, file_name + '.mo')
-# mo_mo = se.load(mo_mo_fname)
-
-ave_dir = os.path.join(config['avedir'], model_template+ '_' + vox_size)
-
-results_dir = os.path.join(config['resultsdir'], model_template+ '_' + vox_size)
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-ave ='ave_mat.mo'
-mo = se.load(os.path.join(ave_dir, ave))
-
-bo.apply_filter()
-
-bo_r = mo.predict(bo, nearest_neighbor=True, force_update=True)
-
-bo_r.save(os.path.join(results_dir, file_name + '_' + model_template + '_' + vox_size + '.bo'))

### 2018-10-04 pni_recon/recon_job_submit.py

@@ -1,162 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import glob
-import os
-import socket
-import getpass
-import datetime as dt
-import supereeg as se
-from supereeg.helpers import filter_subj
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-
-def electrode_search(fname):
-    values = filter_subj(fname, return_locs=True)
-    if values is None:
-        return 0
-    else:
-        meta, locs = values
-        return locs.shape[0]
-
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'recon.py')
-
-# or make all:
-files = glob.glob(os.path.join(config['datadir'],'*.bo'))
-
-# options for model: 'pyFR_union'
-
-model = str('gray')
-
-# options for vox_size: 5, 10, 20, 30
-radius =  str('20')
-
-# options for vox_size: 5, 10, 20, 30
-vox_size =  str('20')
-
-job_commands = list(map(lambda x: x[0]+" "+str(x[1])+" " + model+" "+ radius+" "+ vox_size,
-                        zip([job_script]*len(files), files)))
-
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-
-job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_' + model +'_'+ radius+'_'+ vox_size + '.sh', files))
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
-        x = [i for i, char in enumerate(s) if char == '<']
-        y = [i for i, char in enumerate(s) if char == '>']
-        if len(x) == 0:
-            return s
-
-        q = ''
-        index = 0
-        for i in range(len(x)):
-            q += s[index:x[i]]
-            unpacked = eval(s[x[i]+1:y[i]])
-            q += str(unpacked)
-            index = y[i]+1
-        return q
-
[…]

### 2018-10-05 paper/main.tex
backing up changes (working on results; WIP)

@@
 
-The SuperEEG algorithm described above and in
-Figure~\ref{fig:methods} allows us to estimate (up to a constant
-scaling factor) LFPs for each patient at all arbitrarily chosen
-locations in the set $\bar{R}$, \textit{even if we did not record that
-  patient's brain at all of those locations}.  We next turn to an
-evaluation of the accuracy of those estimates.
+The SuperEEG algorithm described above and in Figure~\ref{fig:methods}
+allows us to estimate, up to a constant scaling factor, local field
+potentials (LFPs) for each patient at all arbitrarily chosen locations
+in the set $\bar{R}$, \textit{even if we did not record that patient's
+  brain at all of those locations}.  We next turn to an evaluation of
+the accuracy of those estimates.
 
@@
 
+We first examined held-out raw LFP traces and their associated
+SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A displays
+the observed LFP from the red electrode in Figure~\ref{fig:methods}A
+(red), and its associated reconstruction (black), during a 5~s time
+window during one of the example patient's six recording sessions.
+The two traces match closely ($r = XXX, p = XXX$).  Where the traces
+do not align, the predicted trace tends to be rounded towards zero,
+reflecting the zero-mean prior implicit in
+Equation~\ref{eqn:reconstruction} (paired $t$-test comparing absolute
+values of actual versus predicted voltages: $t(XXX) = XXX, p = XXX$).
+
 \textbf{JRM STOPPED HERE}
 % JRM thoughts:
-% - Do we need to use the term "LFP"?
 % - Tie in stats from supplemental analyses.  Fig S4: total number of
@@
 
-We first examined raw LFP traces and their associated SuperEEG-derived
-reconstructions.  Figure~\ref{fig:recon}A displays the LFP from the
-red electrode in Figure~\ref{fig:methods}A, and its associated
-reconstruction, during a 5~s time window during one of the patient's 6
-recording sessions.  Figure~\ref{fig:recon}B displays a 2D histogram
-of the observed versus reconstructed voltages for every sample across
-14.2 total hours of recordings from that patient (correlation:
+Figure~\ref{fig:recon}B displays a two-dimensional histogram of the
+actual versus reconstructed voltages for every sample across 14.2
+total hours of recordings from that patient (correlation:
 $r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG

### 2018-10-05 code/ave_mats/ave_mats.py
cleanup repo

@@ -1,34 +1,0 @@
-import supereeg as se
-import numpy as np
-import glob
-import sys
-import os
-from config import config
-
-
-
-model_template = sys.argv[1]
-
-radius = sys.argv[2]
-
-vox_size = sys.argv[3]
-
-if model_template == 'pyFR_union':
-    model_dir = os.path.join(config['datadir'],  model_template +"_" + vox_size)
-
-else:
-    model_dir = os.path.join(config['datadir'], model_template + "_" + vox_size)
-
-results_dir = os.path.join(config['resultsdir'],  model_template +"_"+ vox_size)
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-mos =glob.glob(os.path.join(model_dir, '*.mo'))
-
-mo = se.Model(mos, n_subs=len(mos))
-
-mo.save(os.path.join(results_dir, 'ave_mat'))

### 2018-10-05 code/ave_mats/ave_mats_job_submit.py

@@ -1,144 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import glob
-import os
-import socket
-import getpass
-import datetime as dt
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'ave_mats.py')
-
-# options for model: 'pyFR_union', 'example_model', 'gray'
-
-model = str('pyFR_union')
-#model = str('example_model')
-
-radius = str('20')
-
-# options for vox_size: 5, 10, 20, 30
-vox_size =  str('6')
-
-job_commands = list(map(lambda x: x[0]+" " + model+" "+ radius+" "+ vox_size, zip([job_script]*1, range(1))))
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-
-job_names = list(map(lambda x: 'model_'+ model + "_"+ radius+'_'+ vox_size + '.sh', range(len(job_commands))))
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
-        x = [i for i, char in enumerate(s) if char == '<']
-        y = [i for i, char in enumerate(s) if char == '>']
-        if len(x) == 0:
-            return s
-
-        q = ''
-        index = 0
-        for i in range(len(x)):
-            q += s[index:x[i]]
-            unpacked = eval(s[x[i]+1:y[i]])
-            q += str(unpacked)
-            index = y[i]+1
-        return q
-
-    # create script directory if it doesn't already exist
-    try:
-        os.stat(config['scriptdir'])
-    except:
-        os.makedirs(config['scriptdir'])
-
-    template_fd = open(config['template'], 'r')
-    job_fname = os.path.join(config['scriptdir'], name)
-    new_fd = open(job_fname, 'w+')
-
-    while True:
-        next_line = template_fd.readline()
-        if len(next_line) == 0:
-            break
[…]

### 2018-10-05 code/ave_mats/run_job.sh

@@ -1,32 +1,0 @@
-
-#!/bin/bash -l
-
-# DO NOT MODIFY THIS FILE!
-# MODIFY config.py AND create_and_submit_jobs.py AS NEEDED
-
-# Portable Batch System (PBS) lines begin with "#PBS".  to-be-replaced text is sandwiched between angled brackets
-
-# declare a name for this job
-#PBS -N <config['jobname']>
-
-# specify the queue the job will be added to (if more than 600, use largeq)
-#PBS -q <config['q']>
-
-# specify the number of cores and nodes (estimate 4GB of RAM per core)
-#PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
-
-# specify how long the job should run (wall time)
-#PBS -l walltime=<config['walltime']>
-
-# set the working directory *of this script* to the directory from which the job was submitted
-
-# set the working directory *of the job* to the specified start directory
-cd <config['startdir']>
-
-echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
-source activate supereeg_env
-
-# run the job
-<config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
-
-source deactivate supereeg_env

### 2018-10-05 code/file_io/file_io_job_submit.py

@@ -1,134 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import glob
-import os
-import socket
-import getpass
-import datetime as dt
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'file_io.py')
-files = glob.glob(os.path.join(config['datadir'],'npz/*'))
-job_commands = list(map(lambda x: x[0]+" "+str(x[1]), zip([job_script]*len(files), files)))
-
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'.sh', files))
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
-        x = [i for i, char in enumerate(s) if char == '<']
-        y = [i for i, char in enumerate(s) if char == '>']
-        if len(x) == 0:
-            return s
-
-        q = ''
-        index = 0
-        for i in range(len(x)):
-            q += s[index:x[i]]
-            unpacked = eval(s[x[i]+1:y[i]])
-            q += str(unpacked)
-            index = y[i]+1
-        return q
-
-    # create script directory if it doesn't already exist
-    try:
-        os.stat(config['scriptdir'])
-    except:
-        os.makedirs(config['scriptdir'])
-
-    template_fd = open(config['template'], 'r')
-    job_fname = os.path.join(config['scriptdir'], name)
-    new_fd = open(job_fname, 'w+')
-
-    while True:
-        next_line = template_fd.readline()
-        if len(next_line) == 0:
-            break
-        new_fd.writelines(create_helper(next_line, job_command))
-    template_fd.close()
-    new_fd.close()
-    return job_fname
-
-
-# noinspection PyBroadException
-def lock(lockfile):
-    try:
[…]

### 2018-10-05 code/full_mats/config.py

@@ -1,35 +1,0 @@
-import os
-import socket
-
-config = dict()
-
-config['template'] = 'run_job.sh'
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname() == 'vertex.kiewit.dartmouth.edu') or (socket.gethostname() == 'vertex.local'):
-    config['datadir'] = '/Users/lucyowen/Desktop/supereeg_env/bo/'
-    config['workingdir'] = '/Users/lucyowen/Desktop/supereeg_env/full_mats/'
-    config['startdir'] = '/Users/lucyowen/Desktop/supereeg_env/'  # directory to start the job in
-    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
-else:
-    config['datadir'] = '/idata/cdl/data/ECoG/pyFR/data/bo/'
-    config['workingdir'] = '/idata/cdl/lowen/full_mats'
-    config['startdir'] = '/idata/cdl/lowen'
-    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
-
-# job creation options
-config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
-config['lockdir'] = os.path.join(config['workingdir'], 'locks')
-config['resultsdir'] = os.path.join(config['workingdir'], 'results')
-config['pyFRlocsdir'] = os.path.join(config['startdir'], 'pyFR_locs/results')
-
-# runtime options
-config['jobname'] = "full_mats"  # default job name
-config['q'] = "default"  # options: default, testing, largeq
-config['nnodes'] = 6  # how many nodes to use for this one job
-config['ppn'] = 4  # how many processors to use for this one job (assume 4GB of RAM per processor)
-config['walltime'] = '18:00:00'  # maximum runtime, in h:MM:SS
-#config['startdir'] = '/ihome/lowen/repos/supereeg/examples'  # directory to start the job in
-config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
-config['modules'] = "(\"python/2.7.11\")"  # separate each module with a space and enclose in (escaped) double quotes
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======

### 2018-10-05 code/full_mats/full_mats.py

@@ -1,61 +1,0 @@
-
-import supereeg as se
-import numpy as np
-import sys
-import os
-from config import config
-
-
-fname = sys.argv[1]
-
-model_template = sys.argv[2]
-
-radius = sys.argv[3]
-
-vox_size = sys.argv[4]
-
-results_dir = os.path.join(config['resultsdir'], model_template +"_"+ vox_size)
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-
-def electrode_search(fname, threshold=10):
-    kurt_vals = se.load(fname, field='kurtosis')
-    thresh_bool = kurt_vals > threshold
-    return sum(~thresh_bool)
-
-if model_template == 'pyFR_union':
-    locs_file = os.path.join(config['pyFRlocsdir'], 'locs.npz')
-
-    R = np.load(locs_file)['locs']
-else:
-
-    R_nii = se.load(model_template, vox_size=int(vox_size))
-    R = R_nii.get_locs().as_matrix()
-
-elec_count = electrode_search(sys.argv[1])
-
-if elec_count > 1:
-
-    fname =os.path.basename(os.path.splitext(fname)[0])
-
-    print('creating model object: ' + fname)
-
-    # load brain object
-    bo = se.load(sys.argv[1])
-
-    # filter
-    bo.apply_filter()
-
-    # make model
-    mo = se.Model(bo, locs=R)
-
-    # save model
-    mo.save(os.path.join(results_dir, fname))
-
-else:
-    print('skipping model (not enough electrodes pass kurtosis threshold): ' + sys.argv[1])

### 2018-10-05 code/gif/create_gif.py

@@ -1,94 +1,0 @@
-import supereeg as se
-from supereeg.helpers import make_gif_pngs
-import sys
-import os
-import copy
-import pandas as pd
-import nibabel as nib
-from config import config
-import matplotlib.pyplot as plt
-plt.switch_backend('agg')
-
-cmap=plt.cm.get_cmap('gray')
-
-gif_args = {'window_min': 0,
-            'window_max': 8,
-            'cmap': cmap,
-            'display_mode': 'lyrz',
-            'threshold': 0,
-            'plot_abs': False,
-            'colorbar': False,
-            'vmin': -5,
-            'vmax': 5}
-
-
-model_template = sys.argv[1]
-
-fname = sys.argv[2]
-
-model_dir = os.path.join(config['datadir'], model_template)
-
-results_recon_dir = os.path.join(config['resultsdir'], model_template + '_' + fname + '_recon')
-
-results_obs_dir = os.path.join(config['resultsdir'], model_template + '_' + fname + '_obs')
-
-
-try:
-    os.stat(results_recon_dir)
-except:
-    os.makedirs(results_recon_dir)
-
-try:
-    os.stat(results_obs_dir)
-except:
-    os.makedirs(results_obs_dir)
-
-recon_file = os.path.join(results_recon_dir, 'recon.nii')
-obs_file = os.path.join(results_obs_dir, 'obs.nii')
-
-if not os.path.exists(recon_file):
-
-    model_data = os.path.join(model_dir, model_template + '.mo')
-
-    model = se.load(intern(model_data))
-
-    #bo = se.load(os.path.join(config['datadir'], fname))
-
-    bo = se.load(intern(fname))
-
-    bo.get_slice()
-
-    bo.info()
-
-    bo.resample(64)
-
-    bor = model.predict(bo)
-
-    # zbor = copy.copy(bor)
-    # zbor.data = pd.DataFrame(bor.get_zscore_data())
-
-    # find the observed indices
-    obs_inds = [i for i, x in enumerate(bor.label) if x == 'observed']
-
-    # make a copy of the brain object
-    o_bo = copy.copy(bor)
-
-    # replace fields with indexed data and locations
-    o_bo.data = pd.DataFrame(o_bo.get_data()[:, obs_inds])
-    o_bo.locs = pd.DataFrame(o_bo.get_locs()[obs_inds], columns=['x', 'y', 'z'])
-
[…]

### 2018-10-05 code/gif/create_gif_job_submit.py

@@ -1,144 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import os
-import socket
-import getpass
-import datetime as dt
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'create_gif.py')
-
-# options for bo: 'example_data' or 'CH003.bo' or 'filepath'
-fname = 'example_data'
-
-# options for model: 'pyFR_union', 'example_model', 'gray'
-#model = str('gray')
-model = str('example_model')
-
-# options for vox_size: '20', '6', or any value
-vox_size = 20
-
-job_commands = map(lambda x: x[0]+" " + model +" " + fname, zip([job_script]*1, range(1)))
-
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = map(lambda x: 'model_'+ model + '_' + fname + '.sh', range(len(job_commands)))
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
-        x = [i for i, char in enumerate(s) if char == '<']
-        y = [i for i, char in enumerate(s) if char == '>']
-        if len(x) == 0:
-            return s
-
-        q = ''
-        index = 0
-        for i in range(len(x)):
-            q += s[index:x[i]]
-            unpacked = eval(s[x[i]+1:y[i]])
-            q += str(unpacked)
-            index = y[i]+1
-        return q
-
-    # create script directory if it doesn't already exist
-    try:
-        os.stat(config['scriptdir'])
-    except:
-        os.makedirs(config['scriptdir'])
-
-    template_fd = open(config['template'], 'r')
-    job_fname = os.path.join(config['scriptdir'], name)
-    new_fd = open(job_fname, 'w+')
-
-    while True:
-        next_line = template_fd.readline()
-        if len(next_line) == 0:
-            break
[…]

### 2018-10-05 code/pyFR_locs/union_locs.py

@@ -1,60 +1,0 @@
-import supereeg as se
-from supereeg.helpers import _unique
-import numpy as np
-import glob
-import os
-import pandas as pd
-import matplotlib.pyplot as plt
-plt.switch_backend('agg')
-from config import config
-from nilearn import plotting as ni_plt
-
-## this script iterates over brain objects, filters them based on kurtosis value,
-## then compiles the clean electrodes into a numpy array as well as a list of the contributing brain objects
-
-
-results_dir = config['resultsdir']
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-
-data_dir = config['datadir']
-
-
-def electrode_search(fname, threshold=10):
-
-    kurt_vals = se.load(fname, field='kurtosis')
-    thresh_bool = kurt_vals > threshold
-    locs = se.load(fname, field='locs')
-    if sum(~thresh_bool) > 1:
-        locs = pd.DataFrame(locs, columns=['x', 'y', 'z'])
-        return locs[~thresh_bool]
-
-union_locs = []
-model_data = []
-
-brain_data = glob.glob(os.path.join(data_dir, '*.bo'))
-for i in brain_data:
-    try:
-        locs = electrode_search(i)
-        if not locs.empty:
-            if union_locs == []:
-                print(os.path.basename(i))
-                union_locs = locs.as_matrix()
-                model_data.append(os.path.basename(i))
-            else:
-                union_locs = np.vstack((union_locs, locs.as_matrix()))
-                model_data.append(os.path.basename(i))
-    except:
-        pass
-
-locations, l_indices = _unique(union_locs)
-
-results = os.path.join(results_dir, 'locs.npz')
-#results = os.path.join('/scratch/lucy.owen/supereeg/', 'locs.npz')
-
-np.savez(results, locs = locations, subjs = model_data)

### 2018-10-05 code/pyFR_locs/union_locs_job_submit.py

@@ -1,132 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import glob
-import os
-import socket
-import getpass
-import datetime as dt
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'union_locs.py')
-job_commands = list(map(lambda x: x[0]+" "+str(x[1]), zip([job_script]*1, range(1))))
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(map(lambda x: 'pyFR_locs_' + str(x) + '.sh', range(len(job_commands))))
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
-        x = [i for i, char in enumerate(s) if char == '<']
-        y = [i for i, char in enumerate(s) if char == '>']
-        if len(x) == 0:
-            return s
-
-        q = ''
-        index = 0
-        for i in range(len(x)):
-            q += s[index:x[i]]
-            unpacked = eval(s[x[i]+1:y[i]])
-            q += str(unpacked)
-            index = y[i]+1
-        return q
-
-    # create script directory if it doesn't already exist
-    try:
-        os.stat(config['scriptdir'])
-    except:
-        os.makedirs(config['scriptdir'])
-
-    template_fd = open(config['template'], 'r')
-    job_fname = os.path.join(config['scriptdir'], name)
-    new_fd = open(job_fname, 'w+')
-
-    while True:
-        next_line = template_fd.readline()
-        if len(next_line) == 0:
-            break
-        new_fd.writelines(create_helper(next_line, job_command))
-    template_fd.close()
-    new_fd.close()
-    return job_fname
-
-
-# noinspection PyBroadException
-def lock(lockfile):
-    try:
-        os.stat(lockfile)
-        return False
-    except:
[…]

### 2018-10-05 code/recon/recon.py

@@ -1,98 +1,0 @@
-
-import supereeg as se
-from supereeg.helpers import _corr_column, get_rows, known_unknown, remove_electrode
-import numpy as np
-import sys
-import os
-from config import config
-
-bo_fname = sys.argv[1]
-
-file_name = os.path.basename(os.path.splitext(bo_fname)[0])
-
-elec_ind = int(sys.argv[2])
-
-model_template = sys.argv[3]
-
-radius = sys.argv[4]
-
-mo_mo_fname = os.path.join(config['modeldir'], model_template + '_' + radius, file_name + '.mo')
-mo_mo = se.load(mo_mo_fname)
-
-ave_dir = os.path.join(config['avedir'], model_template+ '_' + radius)
-
-ave ='ave_mat.mo'
-mo = se.load(os.path.join(ave_dir, ave))
-
-R = mo.get_locs().as_matrix()
-
-mo_s = mo - mo_mo
-
-mo = None
-mo_mo = None
-
-print('models deleted')
-results_dir = os.path.join(config['resultsdir'], model_template+ '_' + radius)
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-bo = se.load(bo_fname)
-bo.apply_filter()
-
-print('filter applied')
-
-electrode = bo.get_locs().iloc[elec_ind]
-
-R_K_subj = bo.get_locs().as_matrix()
-
-R_K_removed, other_inds = remove_electrode(R_K_subj, R_K_subj, elec_ind)
-
-known_inds, unknown_inds, e_ind = known_unknown(R, R_K_removed, R_K_subj, elec_ind)
-
-electrode_ind = get_rows(R, electrode.values)
-actual = bo[:,elec_ind]
-bo = bo[:, other_inds]
-
-print('bo indexed')
-
-recon_outfile_across = os.path.join(results_dir, os.path.basename(sys.argv[1][:-3] + '_' + sys.argv[2] + '.npz'))
-
-recon_outfile_within = os.path.join(results_dir, os.path.basename(sys.argv[1][:-3] + '_' + sys.argv[2] + '_within.npz'))
-
-if not os.path.exists(recon_outfile_across):
-    bo_r = mo_s.predict(bo, recon_loc_inds=e_ind)
-
-
-    print(bo_r.get_locs())
-    print(electrode)
-    c = _corr_column(bo_r.data.as_matrix(), actual.get_zscore_data())
[…]

### 2018-10-05 code/recon/recon_job_submit.py

@@ -1,161 +1,0 @@
-#!/usr/bin/python
-
-# create a bunch of job scripts
-from config import config
-from subprocess import call
-import glob
-import os
-import socket
-import getpass
-import datetime as dt
-import supereeg as se
-from supereeg.helpers import filter_subj
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-
-def electrode_search(fname):
-    values = filter_subj(fname, return_locs=True)
-    if values is None:
-        return 0
-    else:
-        meta, locs = values
-        return locs.shape[0]
-
-
-# each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'recon.py')
-
-bos = ('BW001.bo', 'BW013.bo')
-files = list(map(lambda x: os.path.join(config['datadir'],x), bos))
-#print(files)
-#files = glob.glob(os.path.join(config['datadir'],'*.bo'))
-
-file_nums = [(a, i) for item, (a,b) in enumerate(zip(files, map(lambda e :electrode_search(e), files))) for i in range(b)]
-
-#file_nums =file_nums[0:12]
-# options for model: 'pyFR_union', 'example_model', 'gray'
-model = str('pyFR_union')
-
-radius = str('20')
-
-job_commands = list(map(lambda x: x[0]+" "+str(x[1][0])+" "+str(x[1][1])+" " + model + " " + radius, zip([job_script]* len(file_nums), file_nums)))
-
-# job_names should specify the file name of each script (as a list, of the same length as job_commands)
-job_names = list(map(lambda x: os.path.splitext(os.path.basename(x[0]))[0]+"_"+str(x[1])+"_" + model+ "_" + radius + '.sh', file_nums))
-
-
-
-# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
-
-assert(len(job_commands) == len(job_names))
-
-
-# job_command is referenced in the run_job.sh script
-# noinspection PyBroadException,PyUnusedLocal
-def create_job(name, job_command):
-    # noinspection PyUnusedLocal,PyShadowingNames
-    def create_helper(s, job_command):
-        x = [i for i, char in enumerate(s) if char == '<']
-        y = [i for i, char in enumerate(s) if char == '>']
-        if len(x) == 0:
-            return s
-
-        q = ''
-        index = 0
-        for i in range(len(x)):
[…]

### 2018-10-05 code/recon/run_job.sh

@@ -1,41 +1,0 @@
-#!/bin/bash -l
-
-# DO NOT MODIFY THIS FILE!
-# MODIFY config.py AND create_and_submit_jobs.py AS NEEDED
-
-# Portable Batch System (PBS) lines begin with "#PBS".  to-be-replaced text is sandwiched between angled brackets
-
-# declare a name for this job
-#PBS -N <config['jobname']>
-
-# specify the queue the job will be added to (if more than 600, use largeq)
-#PBS -q <config['q']>
-
-# specify the number of cores and nodes (estimate 4GB of RAM per core)
-#PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
-
-# specify more memory
-#PBS -l feature='cellk|cellm|cellj'
-
-# specify how long the job should run (wall time)
-#PBS -l walltime=<config['walltime']>
-
-#PBS -m ea
-export MKL_NUM_THREADS=16
-export NUMEXPR_NUM_THREADS=16
-export OMP_NUM_THREADS=16
-
-
-# set the working directory *of this script* to the directory from which the job was submitted
-
-# set the working directory *of the job* to the specified start directory
-cd <config['startdir']>
-
-echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
-source activate supereeg_env
-
-# run the job
-<config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
-
-source deactivate supereeg_env
-

### 2018-10-05 code/scripts/ave_mats/ave_mats_job_submit.py

@@ -1,0 +1,144 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from config import config
+from subprocess import call
+import glob
+import os
+import socket
+import getpass
+import datetime as dt
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+# each job command should be formatted as a string
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'ave_mats.py')
+
+# options for model: 'pyFR_union', 'example_model', 'gray'
+
+model = str('pyFR_union')
+#model = str('example_model')
+
+radius = str('20')
+
+# options for vox_size: 5, 10, 20, 30
+vox_size =  str('6')
+
+job_commands = list(map(lambda x: x[0]+" " + model+" "+ radius+" "+ vox_size, zip([job_script]*1, range(1))))
+# job_names should specify the file name of each script (as a list, of the same length as job_commands)
+
+job_names = list(map(lambda x: 'model_'+ model + "_"+ radius+'_'+ vox_size + '.sh', range(len(job_commands))))
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
+        for i in range(len(x)):
+            q += s[index:x[i]]
+            unpacked = eval(s[x[i]+1:y[i]])
+            q += str(unpacked)
+            index = y[i]+1
+        return q
+
+    # create script directory if it doesn't already exist
+    try:
+        os.stat(config['scriptdir'])
+    except:
+        os.makedirs(config['scriptdir'])
+
+    template_fd = open(config['template'], 'r')
+    job_fname = os.path.join(config['scriptdir'], name)
+    new_fd = open(job_fname, 'w+')
+
+    while True:
+        next_line = template_fd.readline()
+        if len(next_line) == 0:
+            break
[…]

### 2018-10-05 code/scripts/ave_mats/run_job.sh

@@ -1,0 +1,32 @@
+
+#!/bin/bash -l
+
+# DO NOT MODIFY THIS FILE!
+# MODIFY config.py AND create_and_submit_jobs.py AS NEEDED
+
+# Portable Batch System (PBS) lines begin with "#PBS".  to-be-replaced text is sandwiched between angled brackets
+
+# declare a name for this job
+#PBS -N <config['jobname']>
+
+# specify the queue the job will be added to (if more than 600, use largeq)
+#PBS -q <config['q']>
+
+# specify the number of cores and nodes (estimate 4GB of RAM per core)
+#PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
+
+# specify how long the job should run (wall time)
+#PBS -l walltime=<config['walltime']>
+
+# set the working directory *of this script* to the directory from which the job was submitted
+
+# set the working directory *of the job* to the specified start directory
+cd <config['startdir']>
+
+echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
+source activate supereeg_env
+
+# run the job
+<config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
+
+source deactivate supereeg_env

### 2018-10-05 code/scripts/file_io/config.py

@@ -1,0 +1,34 @@
+import os
+import socket
+
+config = dict()
+
+config['template'] = 'run_job.sh'
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname() == 'vertex.kiewit.dartmouth.edu') or (socket.gethostname() == 'vertex.local'):
+    config['datadir'] = '/Users/lucyowen/Desktop/supereeg_env'
+    config['workingdir'] = '/Users/lucyowen/Desktop/supereeg_env/bo'
+    config['startdir'] = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))  # directory to start the job in
+    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
+else:
+    config['datadir'] = '/idata/cdl/data/ECoG/pyFR/data/'
+    config['workingdir'] = '/idata/cdl/data/ECoG/pyFR/data/bo'
+    config['startdir'] = '/idata/cdl/lowen'
+    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
+
+# job creation options
+config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
+config['lockdir'] = os.path.join(config['workingdir'], 'locks')
+config['resultsdir'] = config['workingdir']
+
+# runtime options
+config['jobname'] = "file_io_npz_bo"  # default job name
+config['q'] = "default"  # options: default, testing, largeq
+config['nnodes'] = 1  # how many nodes to use for this one job
+config['ppn'] = 1  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['walltime'] = '02:00:00'  # maximum runtime, in h:MM:SS
+#config['startdir'] = '/ihome/lowen/repos/supereeg/examples'  # directory to start the job in
+config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
+config['modules'] = "(\"python/2.7.11\")"  # separate each module with a space and enclose in (escaped) double quotes
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======

### 2018-10-05 code/scripts/file_io/file_io_job_submit.py

@@ -1,0 +1,134 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from config import config
+from subprocess import call
+import glob
+import os
+import socket
+import getpass
+import datetime as dt
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+# each job command should be formatted as a string
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'file_io.py')
+files = glob.glob(os.path.join(config['datadir'],'npz/*'))
+job_commands = list(map(lambda x: x[0]+" "+str(x[1]), zip([job_script]*len(files), files)))
+
+# job_names should specify the file name of each script (as a list, of the same length as job_commands)
+job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'.sh', files))
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
+        for i in range(len(x)):
+            q += s[index:x[i]]
+            unpacked = eval(s[x[i]+1:y[i]])
+            q += str(unpacked)
+            index = y[i]+1
+        return q
+
+    # create script directory if it doesn't already exist
+    try:
+        os.stat(config['scriptdir'])
+    except:
+        os.makedirs(config['scriptdir'])
+
+    template_fd = open(config['template'], 'r')
+    job_fname = os.path.join(config['scriptdir'], name)
+    new_fd = open(job_fname, 'w+')
+
+    while True:
+        next_line = template_fd.readline()
+        if len(next_line) == 0:
+            break
+        new_fd.writelines(create_helper(next_line, job_command))
+    template_fd.close()
+    new_fd.close()
+    return job_fname
+
+
+# noinspection PyBroadException
+def lock(lockfile):
+    try:
[…]

### 2018-10-05 code/scripts/file_io/run_job.sh

@@ -1,0 +1,32 @@
+#!/bin/bash -l
+
+# DO NOT MODIFY THIS FILE!
+# MODIFY config.py AND create_and_submit_jobs.py AS NEEDED
+
+# Portable Batch System (PBS) lines begin with "#PBS".  to-be-replaced text is sandwiched between angled brackets
+
+# declare a name for this job
+#PBS -N <config['jobname']>
+
+# specify the queue the job will be added to (if more than 600, use largeq)
+#PBS -q <config['q']>
+
+# specify the number of cores and nodes (estimate 4GB of RAM per core)
+#PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
+
+# specify how long the job should run (wall time)
+#PBS -l walltime=<config['walltime']>
+
+# set the working directory *of this script* to the directory from which the job was submitted
+
+# set the working directory *of the job* to the specified start directory
+cd <config['startdir']>
+
+echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
+source activate supereeg_env
+
+# run the job
+<config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
+
+source deactivate supereeg_env
+

### 2018-10-05 code/scripts/full_mats/config.py

@@ -1,0 +1,35 @@
+import os
+import socket
+
+config = dict()
+
+config['template'] = 'run_job.sh'
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname() == 'vertex.kiewit.dartmouth.edu') or (socket.gethostname() == 'vertex.local'):
+    config['datadir'] = '/Users/lucyowen/Desktop/supereeg_env/bo/'
+    config['workingdir'] = '/Users/lucyowen/Desktop/supereeg_env/full_mats/'
+    config['startdir'] = '/Users/lucyowen/Desktop/supereeg_env/'  # directory to start the job in
+    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
+else:
+    config['datadir'] = '/idata/cdl/data/ECoG/pyFR/data/bo/'
+    config['workingdir'] = '/idata/cdl/lowen/full_mats'
+    config['startdir'] = '/idata/cdl/lowen'
+    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
+
+# job creation options
+config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
+config['lockdir'] = os.path.join(config['workingdir'], 'locks')
+config['resultsdir'] = os.path.join(config['workingdir'], 'results')
+config['pyFRlocsdir'] = os.path.join(config['startdir'], 'pyFR_locs/results')
+
+# runtime options
+config['jobname'] = "full_mats"  # default job name
+config['q'] = "default"  # options: default, testing, largeq
+config['nnodes'] = 6  # how many nodes to use for this one job
+config['ppn'] = 4  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['walltime'] = '18:00:00'  # maximum runtime, in h:MM:SS
+#config['startdir'] = '/ihome/lowen/repos/supereeg/examples'  # directory to start the job in
+config['cmd_wrapper'] = "python"  # replace with actual command wrapper (e.g. matlab, python, etc.)
+config['modules'] = "(\"python/2.7.11\")"  # separate each module with a space and enclose in (escaped) double quotes
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======

### 2018-10-05 code/scripts/full_mats/full_mats.py

@@ -1,0 +1,61 @@
+
+import supereeg as se
+import numpy as np
+import sys
+import os
+from config import config
+
+
+fname = sys.argv[1]
+
+model_template = sys.argv[2]
+
+radius = sys.argv[3]
+
+vox_size = sys.argv[4]
+
+results_dir = os.path.join(config['resultsdir'], model_template +"_"+ vox_size)
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+
+def electrode_search(fname, threshold=10):
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    return sum(~thresh_bool)
+
+if model_template == 'pyFR_union':
+    locs_file = os.path.join(config['pyFRlocsdir'], 'locs.npz')
+
+    R = np.load(locs_file)['locs']
+else:
+
+    R_nii = se.load(model_template, vox_size=int(vox_size))
+    R = R_nii.get_locs().as_matrix()
+
+elec_count = electrode_search(sys.argv[1])
+
+if elec_count > 1:
+
+    fname =os.path.basename(os.path.splitext(fname)[0])
+
+    print('creating model object: ' + fname)
+
+    # load brain object
+    bo = se.load(sys.argv[1])
+
+    # filter
+    bo.apply_filter()
+
+    # make model
+    mo = se.Model(bo, locs=R)
+
+    # save model
+    mo.save(os.path.join(results_dir, fname))
+
+else:
+    print('skipping model (not enough electrodes pass kurtosis threshold): ' + sys.argv[1])

### 2018-10-05 code/scripts/pyFR_locs/union_locs.py

@@ -1,0 +1,60 @@
+import supereeg as se
+from supereeg.helpers import _unique
+import numpy as np
+import glob
+import os
+import pandas as pd
+import matplotlib.pyplot as plt
+plt.switch_backend('agg')
+from config import config
+from nilearn import plotting as ni_plt
+
+## this script iterates over brain objects, filters them based on kurtosis value,
+## then compiles the clean electrodes into a numpy array as well as a list of the contributing brain objects
+
+
+results_dir = config['resultsdir']
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+
+data_dir = config['datadir']
+
+
+def electrode_search(fname, threshold=10):
+
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    locs = se.load(fname, field='locs')
+    if sum(~thresh_bool) > 1:
+        locs = pd.DataFrame(locs, columns=['x', 'y', 'z'])
+        return locs[~thresh_bool]
+
+union_locs = []
+model_data = []
+
+brain_data = glob.glob(os.path.join(data_dir, '*.bo'))
+for i in brain_data:
+    try:
+        locs = electrode_search(i)
+        if not locs.empty:
+            if union_locs == []:
+                print(os.path.basename(i))
+                union_locs = locs.as_matrix()
+                model_data.append(os.path.basename(i))
+            else:
+                union_locs = np.vstack((union_locs, locs.as_matrix()))
+                model_data.append(os.path.basename(i))
+    except:
+        pass
+
+locations, l_indices = _unique(union_locs)
+
+results = os.path.join(results_dir, 'locs.npz')
+#results = os.path.join('/scratch/lucy.owen/supereeg/', 'locs.npz')
+
+np.savez(results, locs = locations, subjs = model_data)

### 2018-10-05 code/scripts/recon/recon.py

@@ -1,0 +1,98 @@
+
+import supereeg as se
+from supereeg.helpers import _corr_column, get_rows, known_unknown, remove_electrode
+import numpy as np
+import sys
+import os
+from config import config
+
+bo_fname = sys.argv[1]
+
+file_name = os.path.basename(os.path.splitext(bo_fname)[0])
+
+elec_ind = int(sys.argv[2])
+
+model_template = sys.argv[3]
+
+radius = sys.argv[4]
+
+mo_mo_fname = os.path.join(config['modeldir'], model_template + '_' + radius, file_name + '.mo')
+mo_mo = se.load(mo_mo_fname)
+
+ave_dir = os.path.join(config['avedir'], model_template+ '_' + radius)
+
+ave ='ave_mat.mo'
+mo = se.load(os.path.join(ave_dir, ave))
+
+R = mo.get_locs().as_matrix()
+
+mo_s = mo - mo_mo
+
+mo = None
+mo_mo = None
+
+print('models deleted')
+results_dir = os.path.join(config['resultsdir'], model_template+ '_' + radius)
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+bo = se.load(bo_fname)
+bo.apply_filter()
+
+print('filter applied')
+
+electrode = bo.get_locs().iloc[elec_ind]
+
+R_K_subj = bo.get_locs().as_matrix()
+
+R_K_removed, other_inds = remove_electrode(R_K_subj, R_K_subj, elec_ind)
+
+known_inds, unknown_inds, e_ind = known_unknown(R, R_K_removed, R_K_subj, elec_ind)
+
+electrode_ind = get_rows(R, electrode.values)
+actual = bo[:,elec_ind]
+bo = bo[:, other_inds]
+
+print('bo indexed')
+
+recon_outfile_across = os.path.join(results_dir, os.path.basename(sys.argv[1][:-3] + '_' + sys.argv[2] + '.npz'))
+
+recon_outfile_within = os.path.join(results_dir, os.path.basename(sys.argv[1][:-3] + '_' + sys.argv[2] + '_within.npz'))
+
+if not os.path.exists(recon_outfile_across):
+    bo_r = mo_s.predict(bo, recon_loc_inds=e_ind)
+
+
+    print(bo_r.get_locs())
+    print(electrode)
+    c = _corr_column(bo_r.data.as_matrix(), actual.get_zscore_data())
[…]

### 2018-10-05 code/scripts/recon/recon_job_submit.py

@@ -1,0 +1,161 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from config import config
+from subprocess import call
+import glob
+import os
+import socket
+import getpass
+import datetime as dt
+import supereeg as se
+from supereeg.helpers import filter_subj
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+
+def electrode_search(fname):
+    values = filter_subj(fname, return_locs=True)
+    if values is None:
+        return 0
+    else:
+        meta, locs = values
+        return locs.shape[0]
+
+
+# each job command should be formatted as a string
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'recon.py')
+
+bos = ('BW001.bo', 'BW013.bo')
+files = list(map(lambda x: os.path.join(config['datadir'],x), bos))
+#print(files)
+#files = glob.glob(os.path.join(config['datadir'],'*.bo'))
+
+file_nums = [(a, i) for item, (a,b) in enumerate(zip(files, map(lambda e :electrode_search(e), files))) for i in range(b)]
+
+#file_nums =file_nums[0:12]
+# options for model: 'pyFR_union', 'example_model', 'gray'
+model = str('pyFR_union')
+
+radius = str('20')
+
+job_commands = list(map(lambda x: x[0]+" "+str(x[1][0])+" "+str(x[1][1])+" " + model + " " + radius, zip([job_script]* len(file_nums), file_nums)))
+
+# job_names should specify the file name of each script (as a list, of the same length as job_commands)
+job_names = list(map(lambda x: os.path.splitext(os.path.basename(x[0]))[0]+"_"+str(x[1])+"_" + model+ "_" + radius + '.sh', file_nums))
+
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
+        for i in range(len(x)):
[…]

### 2018-10-05 code/scripts/simulation/fmri_sim/compile_bo_locs.py

@@ -1,0 +1,54 @@
+import supereeg as se
+from supereeg.helpers import _unique
+import os
+import pandas as pd
+import numpy as np
+import glob as glob
+from config import config
+
+results_dir = config['locs_resultsdir']
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+
+def electrode_search(fname, threshold=10):
+
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    locs = se.load(fname, field='locs')
+    if sum(~thresh_bool) > 1:
+        locs = pd.DataFrame(locs, columns=['x', 'y', 'z'])
+        return locs[~thresh_bool]
+
+
+bos =glob.glob(os.path.join(config['bo_datadir'], '*.bo'))
+
+union_locs = []
+bo_locs = []
+for i in bos:
+    try:
+        locs = electrode_search(i)
+        if not locs.empty:
+            bo = se.load(i)
+            bo_locs.append(bo.get_locs().as_matrix())
+            if union_locs == []:
+                union_locs = locs.as_matrix()
+            else:
+                union_locs = np.vstack((union_locs, locs.as_matrix()))
+
+    except:
+        pass
+
+locations, l_indices = _unique(union_locs)
+
+results = os.path.join(results_dir, 'locs.npz')
+
+np.savez(results, locs = locations, loc_list = bo_locs)
+
+nii = se.load('gray', vox_size=3)
+
+nii.save(os.path.join(results_dir,'gray_3.nii'))

### 2018-10-05 code/scripts/simulation/fmri_sim/compile_compare_mats.py

@@ -1,0 +1,41 @@
+
+
+from config import config
+import os
+import glob as glob
+import pandas as pd
+import numpy as np
+import supereeg as se
+from supereeg.helpers import _z2r, _r2z
+
+compare_dir = os.path.join(config['compare_datadir'])
+
+
+results_dir = os.path.join(config['compiled_datadir'])
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+data = glob.glob(os.path.join(compare_dir , '*.npz'))
+all_compare = pd.DataFrame()
+
+for i in data:
+    compare_data = np.load(i, mmap_mode='r')
+    tempsub = os.path.basename(i)[16:-4]
+    temp_d_mo = compare_data['d_mo']
+    temp_d_ave = compare_data['d_ave']
+    temp_pd = pd.DataFrame()
+    for l, item in enumerate(temp_d_mo):
+
+        temp_pd = temp_pd.append(pd.DataFrame({'d_mo': [temp_d_mo[l]], 'd_ave': [temp_d_ave[l]], 'Subject': [tempsub]}))
+
+    if all_compare.empty:
+        all_compare = temp_pd
+    else:
+        all_compare = all_compare.append(temp_pd)
+
+all_compare_fmri_sim = os.path.join(results_dir, 'all_compare_fmri_sim.csv')
+all_compare.to_csv(all_compare_fmri_sim)

### 2018-10-05 code/scripts/simulation/fmri_sim/compile_recons.py

@@ -1,0 +1,41 @@
+
+
+from config import config
+import os
+import glob as glob
+import pandas as pd
+import numpy as np
+import supereeg as se
+from supereeg.helpers import _z2r, _r2z
+
+
+recon_dir = os.path.join(config['recon_datadir'])
+
+
+results_dir = os.path.join(config['compiled_datadir'])
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+recon_data = glob.glob(os.path.join(recon_dir , '*.npz'))
+all_corrs = pd.DataFrame()
+
+for i in recon_data:
+    corr_data = np.load(i, mmap_mode='r')
+    tempsub = os.path.basename(i)[16:-4]
+    tempcorr = corr_data['corrs']
+    tempR = corr_data['locs']
+    temp_pd = pd.DataFrame()
+    for l, item in enumerate(tempR):
+        temp_pd = temp_pd.append(pd.DataFrame({'R': [item], 'Correlation': [tempcorr[l]], 'Subject': [tempsub]}))
+
+    if all_corrs.empty:
+        all_corrs = temp_pd
+    else:
+        all_corrs = all_corrs.append(temp_pd)
+
+all_corrs_fmri_sim = os.path.join(results_dir, 'all_corrs_fmri_sim.csv')
+all_corrs.to_csv(all_corrs_fmri_sim)

### 2018-10-05 code/scripts/simulation/fmri_sim/fmri_sim_models.py

@@ -1,0 +1,49 @@
+import supereeg as se
+import numpy as np
+import sys
+import os
+import glob as glob
+from config import config
+
+
+
+fname = sys.argv[1]
+
+results_dir = os.path.join(config['model_datadir'])
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+
+# nii = se.load('gray', vox_size=3)
+#
+# locs = nii.get_locs()
+
+locs_dir = config['locs_resultsdir']
+
+mo_locs = np.load(os.path.join(locs_dir, 'mo_locs.npz'))
+
+## for full locations
+#locs = mo_locs['full_locs']
+
+## for every 100th locations
+locs = mo_locs['sub_locs']
+
+fname = os.path.basename(os.path.splitext(fname)[0])
+
+print('creating model object: ' + fname)
+
+# load brain object
+bo = se.load(sys.argv[1])
+
+# filter
+bo.filter=None
+
+# make model
+mo = se.Model(bo, locs=locs)
+
+# save model
+mo.save(os.path.join(results_dir, fname))

### 2018-10-05 code/scripts/simulation/fmri_sim/fmri_sim_recon.py

@@ -1,0 +1,81 @@
+
+import supereeg as se
+from supereeg.helpers import _corr_column, get_rows, known_unknown
+import numpy as np
+import sys
+import os
+from config import config
+
+bos_fname = sys.argv[1]
+
+file_name = os.path.basename(os.path.splitext(bos_fname)[0])
+
+bo_dir = config['bof_datadir']
+
+results_dir = os.path.join(config['recon_datadir'])
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+mo_mo_fname = os.path.join(config['model_datadir'], file_name + '.mo')
+mo_mo = se.load(mo_mo_fname)
+
+ave_dir = config['ave_datadir']
+
+ave ='sub_locs_ave_model.mo'
+# ave = 'ave_model.mo'
+
+mo = se.load(os.path.join(ave_dir, ave))
+
+## if we want to add pyfr info into it:
+
+# pyfr_ave ='pyfr_ave_mat.mo'
+# mo_pyfr = se.load(os.path.join(ave_dir, pyfr_ave))
+#
+# new_mo = se.Model(mo_pyfr, locs = mo.get_locs(), n_subs = mo_pyfr.n_subs)
+#
+# mo = new_mo + mo
+
+## if we want to remove subjects data:
+#mo = mo - mo_mo
+
+R = mo.get_locs().values
+
+bo_s = se.load(bos_fname)
+bo_s.filter=None
+
+bo_fname = os.path.join(bo_dir, 'sub-' + file_name.split('_')[-1] + '.bo')
+bo = se.load(bo_fname)
+bo.filter=None
+
+
+R_subj = bo.get_locs().values
+R_sub_subj = bo_s.get_locs().values
+
+
+known_inds, unknown_inds = known_unknown(R_subj, R, R)
+
+actual = bo[:,known_inds]
+
+print('bo indexed')
+
+recon_outfile = os.path.join(results_dir, os.path.basename(file_name + '.npz'))
+
+bo_r = mo.predict(bo_s)
+
+R_actual = actual.get_locs().values
+
+R_recon = bo_r.get_locs().values
+
+known_inds, unknown_inds = known_unknown(R_recon, R_actual)
+
+bo_r = bo_r[:,known_inds]
+
+c = _corr_column(bo_r.data.as_matrix(), actual.get_zscore_data())
+
+print(c)
+
+np.savez(recon_outfile, corrs=c, locs=bo_r.get_locs().values)

### 2018-10-05 code/scripts/simulation/simulate_job_submit.py

@@ -1,0 +1,140 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from config import config
+from subprocess import call
+import os
+import socket
+import getpass
+import datetime as dt
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+# job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'simulated_patient_data.py')
+# simulations = ('location_case_1', 'location_case_2', 'location_case_3')
+# job_commands = map(lambda x: x[0]+" "+str(x[1]), zip([job_script]*len(simulations), simulations))
+#
+# # job_names should specify the file name of each script (as a list, of the same length as job_commands)
+#
+# job_names = map(lambda x: os.path.basename(os.path.splitext(x)[0])+'.sh', simulations)
+
+# each job command should be formatted as a string
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'simulated_patient_data.py')
+job_commands = map(lambda x: x[0]+" "+str(x[1]), zip([job_script]*1, range(1)))
+# job_names should specify the file name of each script (as a list, of the same length as job_commands)
+job_names = map(lambda x: 'simulation_' + str(x) + '.sh', range(len(job_commands)))
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
+        for i in range(len(x)):
+            q += s[index:x[i]]
+            unpacked = eval(s[x[i]+1:y[i]])
+            q += str(unpacked)
+            index = y[i]+1
+        return q
+
+    # create script directory if it doesn't already exist
+    try:
+        os.stat(config['scriptdir'])
+    except:
+        os.makedirs(config['scriptdir'])
+
+    template_fd = open(config['template'], 'r')
[…]

### 2018-10-05 code/scripts/simulation/simulate_time_dffs.py

@@ -1,0 +1,123 @@
+# -*- coding: utf-8 -*-
+"""
+=============================
+Simulate data
+=============================
+
+In this example, we load in a single subject example, remove electrodes that exceed
+a kurtosis threshold (in place), load a model, and predict activity at all
+model locations.
+
+"""
+
+# Code source: Andrew Heusser & Lucy Owen
+# License: MIT
+
+import supereeg as se
+import os
+import sys
+import pandas as pd
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+#plt.switch_backend('agg')
+from supereeg.helpers import _corr_column
+from config import config
+
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+# simulate more locations
+locs = se.simulate_locations(n_elecs=100)
+
+# n_electrodes - number of electrodes for reconstructed patient
+n = 50
+
+# m_patients - number of patients in the model
+m_patients = [5, 10]
+
+# m_electrodes - number of electrodes for each patient in the model
+m = 50
+
+noise_vals = [0, .25, .5, .75, 1]
+#noise_vals = [0, .5]
+
+time_vals = [300]
+
+iter_val = 10
+
+append_d = pd.DataFrame()
+
+param_grid = [(p, t, no) for p in m_patients for t in time_vals for no in noise_vals]
+
+for p, t, no in param_grid:
+    d = []
+
+    for i in range(iter_val):
+        # create brain objects with m_patients and loop over the number of model locations and subset locations to build model
+        model_bos = [se.simulate_model_bos(n_samples=t, sample_rate=100, locs=locs, sample_locs=m, noise=no) for x in range(p)]
+
+        # create model from subsampled gray locations
+        model = se.Model(model_bos, locs=locs)
+
+        # brain object locations subsetted entirely from both model and gray locations
+        sub_locs = locs.sample(n).sort_values(['x', 'y', 'z'])
+
+        # simulate brain object
+        bo = se.simulate_bo(n_samples=t, sample_rate=100, locs=locs, noise=no)
+
+        # parse brain object to create synthetic patient data
+        data = bo.data.iloc[:, sub_locs.index]
+
+        # create synthetic patient (will compare remaining activations to predictions)
[…]

### 2018-10-05 code/scripts/simulation/simulated_patient_data.py

@@ -1,0 +1,123 @@
+# -*- coding: utf-8 -*-
+"""
+=============================
+Simulate data
+=============================
+
+In this example, we load in a single subject example, remove electrodes that exceed
+a kurtosis threshold (in place), load a model, and predict activity at all
+model locations.
+
+"""
+
+# Code source: Andrew Heusser & Lucy Owen
+# License: MIT
+
+import supereeg as se
+import os
+import sys
+import pandas as pd
+import numpy as np
+import seaborn as sns
+import matplotlib.pyplot as plt
+#plt.switch_backend('agg')
+from supereeg.helpers import _corr_column
+from config import config
+
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+# simulate more locations
+locs = se.simulate_locations(n_elecs=100)
+
+# n_electrodes - number of electrodes for reconstructed patient
+n_elecs = range(75, 100, 50)
+
+
+# m_patients - number of patients in the model
+m_patients = [5, 10]
+
+
+# m_electrodes - number of electrodes for each patient in the model
+m_elecs = range(75, 100, 50)
+
+
+iter_val = 5
+
+append_d = pd.DataFrame()
+
+param_grid = [(p, m, n) for p in m_patients for m in m_elecs for n in n_elecs]
+
+for p, m, n in param_grid:
+    d = []
+
+    for i in range(iter_val):
+        # create brain objects with m_patients and loop over the number of model locations and subset locations to build model
+        model_bos = [se.simulate_model_bos(n_samples=1000, sample_rate=100, locs=locs, sample_locs=m, noise=.3) for x in range(p)]
+
+        # create model from subsampled gray locations
+        model = se.Model(model_bos, locs=locs)
+
+        # brain object locations subsetted entirely from both model and gray locations
+        sub_locs = locs.sample(n).sort_values(['x', 'y', 'z'])
+
+        # simulate brain object
+        bo = se.simulate_bo(n_samples=1000, sample_rate=100, locs=locs, noise=.3)
+
+        # parse brain object to create synthetic patient data
+        data = bo.data.iloc[:, sub_locs.index]
+
+        # create synthetic patient (will compare remaining activations to predictions)
+        bo_sample = se.Brain(data=data.as_matrix(), sample_rate=100, locs=sub_locs)
+
+        # reconstruct at 'unknown' locations
[…]

### 2018-10-05 code/simulation/fmri_sim/compile_recons.py

@@ -1,41 +1,0 @@
-
-
-from config import config
-import os
-import glob as glob
-import pandas as pd
-import numpy as np
-import supereeg as se
-from supereeg.helpers import _z2r, _r2z
-
-
-recon_dir = os.path.join(config['recon_datadir'])
-
-
-results_dir = os.path.join(config['compiled_datadir'])
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-recon_data = glob.glob(os.path.join(recon_dir , '*.npz'))
-all_corrs = pd.DataFrame()
-
-for i in recon_data:
-    corr_data = np.load(i, mmap_mode='r')
-    tempsub = os.path.basename(i)[16:-4]
-    tempcorr = corr_data['corrs']
-    tempR = corr_data['locs']
-    temp_pd = pd.DataFrame()
-    for l, item in enumerate(tempR):
-        temp_pd = temp_pd.append(pd.DataFrame({'R': [item], 'Correlation': [tempcorr[l]], 'Subject': [tempsub]}))
-
-    if all_corrs.empty:
-        all_corrs = temp_pd
-    else:
-        all_corrs = all_corrs.append(temp_pd)
-
-all_corrs_fmri_sim = os.path.join(results_dir, 'all_corrs_fmri_sim.csv')
-all_corrs.to_csv(all_corrs_fmri_sim)

### 2018-10-05 code/simulation/fmri_sim/convert_fmri_bo.py

@@ -1,96 +1,0 @@
-
-import supereeg as se
-import os
-import numpy as np
-import pandas as pd
-from nilearn.input_data import NiftiMasker
-import nibabel as nib
-import warnings
-from config import config
-
-
-def nii2cmu(nifti_file, mask_file=None):
-    def fullfact(dims):
-        '''
-        Replicates MATLAB's fullfact function (behaves the same way)
-        '''
-        vals = np.asmatrix(range(1, dims[0] + 1)).T
-        if len(dims) == 1:
-            return vals
-        else:
-            aftervals = np.asmatrix(fullfact(dims[1:]))
-            inds = np.asmatrix(np.zeros((np.prod(dims), len(dims))))
-            row = 0
-            for i in range(aftervals.shape[0]):
-                inds[row:(row + len(vals)), 0] = vals
-                inds[row:(row + len(vals)), 1:] = np.tile(aftervals[i, :], (len(vals), 1))
-                row += len(vals)
-            return inds
-
-    with warnings.catch_warnings():
-        warnings.simplefilter("ignore")
-
-        img = nib.load(nifti_file)
-        mask = NiftiMasker(mask_strategy='background')
-        if mask_file is None:
-            mask.fit(nifti_file)
-        else:
-            mask.fit(mask_file)
-
-    hdr = img.header
-    S = img.get_sform()
-    vox_size = hdr.get_zooms()
-    im_size = img.shape
-
-    if len(img.shape) > 3:
-        N = img.shape[3]
-    else:
-        N = 1
-
-    Y = np.float64(mask.transform(nifti_file)).copy()
-    vmask = np.nonzero(np.array(np.reshape(mask.mask_img_.dataobj, (1, np.prod(mask.mask_img_.shape)), order='C')))[1]
-    vox_coords = fullfact(img.shape[0:3])[vmask, ::-1] - 1
-
-    R = np.array(np.dot(vox_coords, S[0:3, 0:3])) + S[:3, 3]
-
-    null_inds = ~np.all(Y == Y[0, :], axis=0)
-
-
-    Y = Y[:, null_inds]
-    R = R[null_inds]
-
-    return Y, R
-
-results_dir = config['bof_datadir']
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-fmri_dir = config['fmri_datadir']
-
[…]

### 2018-10-05 code/simulation/fmri_sim/fmri_compare_models.py

@@ -1,71 +1,0 @@
-import supereeg as se
-import numpy as np
-import sys
-import os
-import scipy.spatial.distance as sd
-from supereeg.helpers import get_rows
-from supereeg.helpers import _z2r, _r2z
-import glob as glob
-from config import config
-
-
-results_dir = os.path.join(config['compare_datadir'])
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-fname = sys.argv[1]
-
-model_dir = os.path.join(config['model_datadir'])
-
-bo_dir = config['bof_datadir']
-
-fname = os.path.basename(os.path.splitext(fname)[0])
-
-print('creating model object: ' + fname)
-
-# load brain object
-path_info, i, j = sys.argv[1][:-3].rsplit("_", 2)
-
-bo = se.load(os.path.join(bo_dir, 'sub-%d.bo' % int(j)))
-
-# filter
-bo.filter=None
-
-mo_fname = (sys.argv[1][:-3]+ '.mo').replace('bo_sub', 'models')
-
-# make model
-mo = se.load(mo_fname)
-
-ave_dir = config['ave_datadir']
-
-ave ='sub_locs_ave_model.mo'
-
-ave_mo = se.load(os.path.join(ave_dir, ave))
-
-sub_inds = get_rows(bo.get_locs().values, ave_mo.get_locs().values)
-
-subbo = bo[:, sub_inds]
-
-true_model = se.Model(subbo, locs = ave_mo.get_locs().values)
-
-def upper_tri_indexing(A):
-    m = A.shape[0]
-    r,c = np.triu_indices(m,1)
-    return A[r,c]
-
-def model_diff(z_model1, z_model2):
-
-    return np.abs(upper_tri_indexing(z_model1) - upper_tri_indexing(z_model2))
-
-d_mo = model_diff(mo.get_model(z_transform=True), true_model.get_model(z_transform=True))
-
-d_ave = model_diff(ave_mo.get_model(z_transform=True), true_model.get_model(z_transform=True))
-
-
-recon_outfile = os.path.join(results_dir, os.path.basename(fname + '.npz'))
-
-np.savez(recon_outfile, d_ave=d_ave.mean(), d_mo=d_mo.mean())

### 2018-10-05 code/simulation/fmri_sim/fmri_sim_ave_model.py

@@ -1,24 +1,0 @@
-import supereeg as se
-from supereeg.helpers import _unique
-import os
-import pandas as pd
-import numpy as np
-import glob as glob
-from config import config
-
-results_dir = os.path.join(config['ave_datadir'])
-
-try:
-    if not os.path.exists(results_dir):
-        os.makedirs(results_dir)
-except OSError as err:
-   print(err)
-
-mos =glob.glob(os.path.join(config['model_datadir'], '*.mo'))
-
-mo = se.Model(mos, n_subs=len(mos))
-
-mo.save(os.path.join(results_dir, 'sub_locs_ave_model'))
-
-#mo.save(os.path.join(results_dir, 'ave_model'))
-

### 2018-10-05 code/simulation/simulate_time_dffs.py

@@ -1,123 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-=============================
-Simulate data
-=============================
-
-In this example, we load in a single subject example, remove electrodes that exceed
-a kurtosis threshold (in place), load a model, and predict activity at all
-model locations.
-
-"""
-
-# Code source: Andrew Heusser & Lucy Owen
-# License: MIT
-
-import supereeg as se
-import os
-import sys
-import pandas as pd
-import numpy as np
-import seaborn as sns
-import matplotlib.pyplot as plt
-#plt.switch_backend('agg')
-from supereeg.helpers import _corr_column
-from config import config
-
-try:
-    os.stat(config['resultsdir'])
-except:
-    os.makedirs(config['resultsdir'])
-
-# simulate more locations
-locs = se.simulate_locations(n_elecs=100)
-
-# n_electrodes - number of electrodes for reconstructed patient
-n = 50
-
-# m_patients - number of patients in the model
-m_patients = [5, 10]
-
-# m_electrodes - number of electrodes for each patient in the model
-m = 50
-
-noise_vals = [0, .25, .5, .75, 1]
-#noise_vals = [0, .5]
-
-time_vals = [300]
-
-iter_val = 10
-
-append_d = pd.DataFrame()
-
-param_grid = [(p, t, no) for p in m_patients for t in time_vals for no in noise_vals]
-
-for p, t, no in param_grid:
-    d = []
-
-    for i in range(iter_val):
-        # create brain objects with m_patients and loop over the number of model locations and subset locations to build model
-        model_bos = [se.simulate_model_bos(n_samples=t, sample_rate=100, locs=locs, sample_locs=m, noise=no) for x in range(p)]
-
-        # create model from subsampled gray locations
-        model = se.Model(model_bos, locs=locs)
-
-        # brain object locations subsetted entirely from both model and gray locations
-        sub_locs = locs.sample(n).sort_values(['x', 'y', 'z'])
-
-        # simulate brain object
-        bo = se.simulate_bo(n_samples=t, sample_rate=100, locs=locs, noise=no)
-
-        # parse brain object to create synthetic patient data
-        data = bo.data.iloc[:, sub_locs.index]
-
-        # create synthetic patient (will compare remaining activations to predictions)
[…]

### 2018-10-05 paper_figs/code/plot.py

@@ -1,699 +1,0 @@
-import os
-import supereeg as se
-import hypertools as hyp
-import pandas as pd
-import numpy as np
-import glob as glob
-from scipy import stats, signal
-import scipy.spatial as spatial
-import numpy.matlib as mat
-import matplotlib.patches as patches
-from scipy.spatial.distance import cdist, pdist
-from sklearn.neighbors import NearestNeighbors
-from nilearn import plotting as ni_plt
-from supereeg.helpers import _log_rbf, _brain_to_nifti, _plot_borderless
-from supereeg.helpers import _corr_column, get_rows, known_unknown, remove_electrode
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-import matplotlib
-import matplotlib.ticker as mtick
-import matplotlib.cm as cm
-import seaborn as sns
-from scipy import stats
-
-############## General functions #################
-
-def r2z(r):
-    return 0.5 * (np.log(1 + r) - np.log(1 - r))
-
-def z2r(z):
-    r = np.divide((np.exp(2*z) - 1), (np.exp(2*z) + 1))
-    try:
-        r[np.isnan(r)] = 0
-        r[np.isinf(r)] = np.sign(r)[np.isinf(r)]
-    except:
-        pass
-
-    return r
-
-def compile_df_locs(df_column):
-
-    R_locs = []
-
-    for i, e in enumerate(df_column):
-
-        R = np.array(e[1:-1].split())
-        R = np.atleast_2d(np.array(R.astype(np.float)))
-        if R_locs == []:
-            R_locs = R
-        else:
-
-            R_locs = np.vstack((R_locs, R))
-
-    return R_locs
-
-
-############## Methods ##########################
-
-def plot_hist(dataframe, X='Correlation', title=None, outfile=None):
-    fig = plt.gcf()
-    fig.set_size_inches(18.5, 10.5)
-    sns.set_style("white")
-    df_corrs = pd.DataFrame()
-    df_corrs[X] = dataframe[X].values
-    n_count = len(df_corrs)
-    bin_values = np.arange(start=-1, stop=1, step=.025)
-    ax = sns.distplot(df_corrs, hist=True, kde=True,
-             bins=bin_values, color = 'k',
-             hist_kws={'edgecolor':'black'},
-             kde_kws={'linewidth': 4})
-
[…]

### 2018-10-05 code/scripts/recon/recon.py
changed notebook paths to be relative paths

@@ -75,7 +75,10 @@ if not os.path.exists(recon_outfile_across):
 
     np.savez(recon_outfile_across, coord=electrode, corrs=c)
 
-elif not os.path.exists(recon_outfile_within):
+else:
+    print('across reconstructions are done')
+
+if not os.path.exists(recon_outfile_within):
 
     Model = se.Model(bo, locs=R_K_subj)
 

### 2018-10-05 paper/main.tex

@@
 
-We first examined held-out raw LFP traces and their associated
-SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A displays
-the observed LFP from the red electrode in Figure~\ref{fig:methods}A
-(red), and its associated reconstruction (black), during a 5~s time
-window during one of the example patient's six recording sessions.
-The two traces match closely ($r = XXX, p = XXX$).  Where the traces
-do not align, the predicted trace tends to be rounded towards zero,
-reflecting the zero-mean prior implicit in
-Equation~\ref{eqn:reconstruction} (paired $t$-test comparing absolute
-values of actual versus predicted voltages: $t(XXX) = XXX, p = XXX$).
-
-\textbf{JRM STOPPED HERE}
-% JRM thoughts:
-% - Tie in stats from supplemental analyses.  Fig S4: total number of
-% electrodes, total number of used electrodes, prop thresholded, total
-% recording time, average session time, number of sessions.
-
-Figure~\ref{fig:recon}B displays a two-dimensional histogram of the
-actual versus reconstructed voltages for every sample across 14.2
-total hours of recordings from that patient (correlation:
-$r = 0.91, p < 10\textsuperscript{-10}$).  Although the SuperEEG
-algorithm recovered the recordings from this electrode well, we sought
-to quantify the algorithm's performance across the full dataset.
+We first examined individual held-out raw LFP traces and their
+associated SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A
+displays the observed LFP from the red electrode in
+Figure~\ref{fig:methods}A (red), and its associated reconstruction
+(blue), during a 5~s time window during one of the example patient's
+six recording sessions.  The two traces match closely
+($r = XXX, p = XXX$).
+%Where the traces do not align, the predicted
+%trace tends to be rounded towards zero, reflecting the zero-mean prior
+%implicit in Equation~\ref{eqn:reconstruction} (paired $t$-test
+%comparing absolute values of actual versus predicted voltages:
+%$t(XXX) = XXX, p = XXX$).
+Figure~\ref{fig:recon}B displays a
+two-dimensional histogram of the actual versus reconstructed voltages
+for the entire 14.2 total hours of recordings from the electrode
+(correlation: $r = XXX, p = XXX$).
+%Like in the shorter example trace
+%shown in panel A, the reconstructed voltages throughout the full
+%recording tended to be smaller in magnitude than the original
+%recording ($t(XXX) = XXX, p = XXX$).
+Having confirmed that the SuperEEG algorithm recovered the recordings
+from this electrode well, we next sought to quantify the algorithm's
+performance across the full dataset.
 
@@
   \caption{\textbf{Observed and reconstructed LFP from a single
-      electrode.} \textbf{A. Example LFP.}  A 2~s recording from the blue
-    electrode in Figure~\ref{fig:methods}A is displayed in red, and
-    the reconstructed LFP during the same time window is shown in
-   black.  All voltages are plotted in standard deviation units.
-    \textbf{B. Observed versus reconstructed voltages over 14.2~hours.}
-    The 2D histogram reflects the relation between distributions of
-    observed versus reconstructed voltages from one patient, across the
-    14.2 hours of recorded data collected in 6 recording sessions.  The
-    correlation reported in the panel is between the observed and reconstructed
-    voltages.}
+      electrode.} \textbf{A. Example LFP.}  A 5~s recording from the
+    red electrode in Figure~\ref{fig:methods}A is displayed in red,
+    and the reconstructed LFP during the same time window is shown in
+    blue.  \textbf{B. Observed versus reconstructed voltages over
+      14.2~hours.}  The two-dimensional histogram reflects the
+    relation between distributions of observed versus reconstructed
+    voltages from one patient, across the 14.2 hours of recorded data
+    collected over 6 recording sessions.  The correlation reported in
+    the panel is between the observed and reconstructed voltages.
+    Both panels: all voltages are represented in standard deviation units
+   (computed within session).}
   \label{fig:recon}

### 2018-10-05 code/notebooks/plot.py
update to work in docker

@@ -12,7 +12,7 @@ from scipy.spatial.distance import cdist, pdist
 from sklearn.neighbors import NearestNeighbors
 from nilearn import plotting as ni_plt
 from supereeg.helpers import _log_rbf, _brain_to_nifti, _plot_borderless
-from supereeg.helpers import _corr_column, get_rows, known_unknown, remove_electrode
+from supereeg.helpers import _corr_column, get_rows, known_unknown
 import matplotlib as mpl
 import matplotlib.pyplot as plt
 import matplotlib
@@ -35,6 +35,31 @@ def z2r(z):
         pass
 
     return r
+
+def remove_electrode(subkarray, subarray, electrode):
+    """
+        Removes electrode from larger array
+
+        Parameters
+        ----------
+        subkarray : ndarray
+            Subject's electrode locations that pass the kurtosis test
+
+        subarray : ndarray
+            Subject's electrode locations (all)
+
+        electrode : str
+            Index of electrode in subarray to remove
+
+        Returns
+        ----------
+        results : ndarray
+            Subject's electrode locations that pass kurtosis test with electrode removed
+
+        """
+    rm_ind = get_rows(subkarray, subarray[electrode])
+    other_inds = [i for i in range(np.shape(subkarray)[0]) if i != electrode]
+    return np.delete(subkarray, rm_ind, 0), other_inds
 
 def compile_df_locs(df_column):
 

### 2018-10-05 paper/main.tex
working on results; WIP

@@
 {\end{list}}
+
+\newcommand{\taskrecon}{S1}
+\newcommand{\per_exp_taskrecon}{S2}
+\newcommand{\per_exp_corrmaps}{S3}
 
@@
 \begin{align}
- \hat{K} = \mathrm{r} \left(  \frac{\sum  \hat{N}_{s}}{\sum \hat{D}_{s}}\right).\label{eqn:correlation_matrix}
+ \hat{K} = \mathrm{r} \left(  \frac{\sum  \hat{N}_{s}}{\sum \hat{D}_{s}}\right).\label{eqn:corrmat}
 \end{align}
@@
 \begin{align}
-Y_{s,k,\beta} &= ((\hat{K}_{\beta_s,\alpha_s}\cdot\hat{K}_{\alpha_s,\alpha_s}^{-1})\cdot Y_{s,k,\alpha_s}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
+\hat{Y}_{s,k,\beta_s} &= ((\hat{K}_{\beta_s,\alpha_s}\cdot\hat{K}_{\alpha_s,\alpha_s}^{-1})\cdot Y_{s,k,\alpha_s}^\mathrm{T})^\mathrm{T}.\label{eqn:reconstruction}
 \end{align}
@@
 \section*{Results}
-To test the accuracy with which the SuperEEG algorithm reconstructs
-activity throughout the brain, we held out each electrode from the
-full dataset in turn and treated it as unobserved. We then asked: how
-closely did each of the SuperEEG-estimated recordings at those
-electrodes match the observed recordings from those electrodes?
+We used a cross-validation approach to test the accuracy with which
+the SuperEEG algorithm reconstructs activity throughout the brain.
+For each patient in turn, we estimated full-brain correlation matrices
+(Eqn.~\ref{eqn:corrmat}) using data from all of the \textit{other}
+patients. This step ensured that the data we were reconstructing could
+not also be used to estimate the between-location correlations that
+drove the reconstructions via Equation~\ref{eqn:reconstruction}
+(otherwise the analysis would be circular).  For that held-out
+patient, for each of their electrodes in turn, we used
+Equation~\ref{eqn:reconstruction} to reconstruct activity at the
+held-out electrode location, using the correlation matrix trained on
+all other patients' data at $\hat{K}$, and using activity recorded
+from the other electrodes from the held-out patient as
+$Y_{s, k, \alpha_s}$.  We then asked: how closely did each of the
+SuperEEG-estimated recordings at those electrodes match the observed
+recordings from those electrodes (i.e., how closely did the estimated
+$\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$?).
 
-We first examined individual held-out raw LFP traces and their
-associated SuperEEG-derived reconstructions.  Figure~\ref{fig:recon}A
-displays the observed LFP from the red electrode in
-Figure~\ref{fig:methods}A (red), and its associated reconstruction
-(blue), during a 5~s time window during one of the example patient's
-six recording sessions.  The two traces match closely
-($r = XXX, p = XXX$).
+To illustrate our approach, we first examine and individual held-out
+raw LFP trace and its associated SuperEEG-derived reconstruction.
+Figure~\ref{fig:recon}A displays the observed LFP from the red
+electrode in Figure~\ref{fig:methods}A (red), and its associated
+reconstruction (blue), during a 5~s time window during one of the
+example patient's six recording sessions.  The two traces match
+closely ($r = XXX, p = XXX$).
 %Where the traces do not align, the predicted
@@
 two-dimensional histogram of the actual versus reconstructed voltages
-for the entire 14.2 total hours of recordings from the electrode
+for the entire 14.2 total hours of recordings from the example electrode
 (correlation: $r = XXX, p = XXX$).
@@
 %recording ($t(XXX) = XXX, p = XXX$).
-Having confirmed that the SuperEEG algorithm recovered the recordings
-from this electrode well, we next sought to quantify the algorithm's
+This example confirms that the SuperEEG algorithm recovers the recordings
+from this single electrode well.  Next, we quantify the algorithm's
 performance across the full dataset.
@@
     and the reconstructed LFP during the same time window is shown in
-    blue.  \textbf{B. Observed versus reconstructed voltages over
+    blue.  \textbf{B. Observed versus reconstructed LFP over
       14.2~hours.}  The two-dimensional histogram reflects the
@@
 
-Holding out each electrode from each patient in turn, we computed the
-average correlation (across recording sessions) between the Super
-EEG-reconstructed voltage traces and the observed voltage traces from
-that electrode.  For each reconstruction, we estimated the full-brain
-correlation matrix using every \textit{other} patient's data
-(i.e., every patient except the one who contributed the
-to-be-reconstructed electrode data).  In our analyses, we then
-substituted the average correlation matrix computed after excluding
-patient $s$'s data for $\hat{K}$ in Equations~\ref{eqn:Kba} and
-\ref{eqn:Kaa}.  This step ensured that the data we were reconstructing
-could not also be used to estimate the between-location correlations
-that drove the reconstructions via Equation~\ref{eqn:reconstruction}
-(otherwise the analysis would be circular).
+For each held-out electrode, from each held-out patient in turn, we we
+computed the average correlation (across recording sessions) between
+the SuperEEG-reconstructed voltage traces and the observed voltage
+traces from that electrode.  For this analysis we set $\bar{R}$ to be
+the union of all electrode locations across all patients.  This
+yielded a single correlation coefficient for each electrode location
+in $\bar{R}$, reflecting how well the SuperEEG algorithm was able to
+recover the recording at that location by incorporating data across
+patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
+Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations
+was centered well above zero (mean: XXX; $t$-test comparing mean of
+distribution of $z$-transformed per-electrode correlation coefficients
+to 0: $t(XXX) = XXX, p = XXX$), indicating that the SuperEEG algorithm
+recovers held-out activity patterns substantially better than random
+guessing.
 
-We obtained a single correlation coefficient for each electrode
-location in $\bar{R}$, reflecting how well the SuperEEG algorithm was
-able to recover the recording at that location by incorporating data
-across patients (Across shown in black, see
-Fig.~\ref{fig:corrmap}A). We also reconstructed activity for each
-electrode using a model trained on the remaining electrodes from only
-that patient, to account for reconstruction accuracy attributed to
-volume conductance alone (Within shown in gray, see
-Fig.~\ref{fig:corrmap}A). For the first dataset, we compared these two
-distributions of correlation coefficients (paired $t$-test between
-$z$-transformed mean correlation coefficients by patient:
-$t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated this
-analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with similar
-results (paired $t$-test between $z$-transformed mean correlation
-coefficients by patient: $t(23) = 6.93, p <
-10\textsuperscript{-5}$). This is an especially conservative test,
-given that the SuperEEG reconstructions exclude (from the correlation
-matrix estimates) all data from the patient whose data is being
-reconstructed.  Furthermore, we also replicated this finding for each
-independent experiment within dataset 2 (Fig. S3 (paired $t$-test
-between $z$-transformed mean correlation coefficients by patient for
-experiment 1: $t(23) = 6.23, p < 10\textsuperscript{-5}$ and
-experiment 2: $t(23) = 6.62, p < 10\textsuperscript{-5}$).  That the
-SuperEEG-derived correlations were reliably stronger than these
-correlations obtained using a volume conductance null model is
-exciting for two reasons.  First, it implies that distant electrodes
-provide additional predictive power to the data reconstructions beyond
-the information contained in nearby electrodes.  Second, it implies
-that the spatial correlations driving the SuperEEG algorithm are, to
-some extent, shared across people.
+As a stricter benchmark, we compared the quality of these
+across-participant reconstructions (i.e., computed using a correlation
+model derived from other patients' data) to reconstructions generated
+using a correlation model trained using the in-patient's data.  In
+other words, for this within-patient benchmark analysis we estimated
+$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
+using recordings from all of that patient's electrodes except at the
+location we were reconstructing.  These within-patient reconstructions
+serve as an estimate of how well data from all of the other electrodes
+from a single patient may be used to estimate held-out data.  This
+allows us to ask how much information about the activity at a given
+electrode might be inferred through (a) volume conductance or other
+sources of ``leakage'' from activity patterns measured from the
+patient's other electrodes and (b) across-electrode correlations
+learned from that single patient.  As shown in
+Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
+within-patient correlations was centered well above zero (mean: XXX;
+$t$-test comparing mean of distribution of $z$-transformed
+per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
+However, the across-patient correlations were substantially higher
+($t$-test comparing average $z$-transformed within versus across
+patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
+especially conservative test, given that the across-patient SuperEEG
+reconstructions exclude (from the correlation matrix estimates) all
+data from the patient whose data is being reconstructed.  We repeated
+each of these analyses on a second independent datset and found
+similar results (Fig.~\ref{corrmap}B, D; within versus across
+reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). Our finding,
+that when reconstructing held-out data from a given patient
+correlation models derived from \textit{other} patient's data yield
+higher reconstruction accuracy than correlation models derived from
+that patient, has two important implications.  First, it implies that
+distant electrodes provide additional predictive power to the data
+reconstructions beynd the information contained solely in nearby
+electrodes.  (This follows from the fact that each patient's
+electrodes are implanted in a unique set of locations, so for any
+given electrode the closest electrodes in the full dataset are likely
+to come from the same patient.)  Second, it implies that the spatial
+correlations derived from the SuperEEG algorithm are, to some extent,
+similar across people.
 
@@
   \includegraphics[width=\textwidth]{figs/corrmap}
-  \caption{\textbf{Reconstruction quality.}  \textbf{A. \& C.  Distributions
-      of correlation coefficients.}  Across all electrodes from all
-    patients in the labeled dataset, the panel displays the distribution of correlations between the observed and reconstructed LFP data using models trained on data from all other patients (Across, in black) and all other electrodes from the same patient (Within, in gray).
-    \textbf{B. \& D. Correlation maps.}  The glass brain maps display the
-    average correlation between the observed LFP data and the across-subjects model reconstructed data by location, for each labeled experiment.}
+  \caption{\textbf{Reconstruction quality across all electrodes in two
+      ECoG datasets.}  \textbf{A. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      Dataset 1.}  The across-patient distribution (black) reflects
+    reconstruction performance using a correlation model trained on
+    all but one patient, and then applied to the held-out patient's
+    data.  The within-patient distribution (gray) reflects performance using
+    a correlation model trained on the same patient who contributed
+    the to-be-reconstructed electrode.  \textbf{B. Distributions of
+      correlations for Dataset 2.}  This panel is in the same format
+    as Panel A, but reflects results obtained from Dataset 2.
+    \textbf{C.--D.  Reconstruction performance by location.} Each dot
+    reflects the location of a single implanted electrode from Dataset
+    1 (Panel C) or Dataset 2 (Panel D).  The dot colors denote the
+    average across-session correlation, using the across-patient
+    correlation model, between the observed and
+    reconstructed activity at the given electrode location.}
   \label{fig:corrmap}
@@
 
-We were interested in the task specific contributions to the reconstruction accuracy.
-Each patient in the the second dataset participated in two free recall experiments.
-We ran similar analyses for both experiments and found that activity was best reconstructed when limiting the training data to within task, as opposed to across task or incorporating data from both tasks (Fig.
-S1 (mean reconstruction accuracy incorporating data within task: 0.55, across task: 0.37, all tasks: .50)).
+The recordings we analyzed from Dataset 1 comprised data collected as
+the patients performed a variety of (essentially uncontrolled) tasks
+throughout each day's recording session.  That we observed reliable
+reconstruction accuracy across patients suggests that the spatial
+correlations derived from the SuperEEG algorithm are, to some extent,
+similar across tasks.  We tested this finding more explicitly using
+Dataset 2.  In Dataset 2, the recordings were limited to times when
+each patient was participating in each of two experiments (Experiment
+1, a random-word list free recall task, and Experiment 2, a
+categorized list free recall task).  We wondered whether a correlation
+model trained using data only from one experiment might yield good
+predictions for data from the other experiment.  Further, we wondered
+about the extent to which it might be benefitial or harmful to combine
+data across tasks.
+
+\textbf{JRM STOPPED HERE}
+
+We were interested in the task specific contributions to the
+reconstruction accuracy.  Each patient in the the second dataset
+participated in two free recall experiments.  We ran similar analyses
+for both experiments and found that activity was best reconstructed
+when limiting the training data to within task, as opposed to across
+task or incorporating data from both tasks (Fig.~\taskrecon (mean reconstruction accuracy incorporating data within task: 0.55, across task: 0.37, all tasks: .50)).
 Although reconstruction accuracy in the across task analysis was still better than the volume conductance model alone (paired $t$-test

### 2018-10-05 paper/main.tex
corrected latex error

@@
 \newcommand{\taskrecon}{S1}
-\newcommand{\per_exp_taskrecon}{S2}
-\newcommand{\per_exp_corrmaps}{S3}
+\newcommand{\perexptaskrecon}{S2}
+\newcommand{\perexpcorrmaps}{S3}
 
@@
 each of these analyses on a second independent datset and found
-similar results (Fig.~\ref{corrmap}B, D; within versus across
+similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
 reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). Our finding,

### 2018-10-06 paper/main.tex
backing up progress on results section [WIP]

@@
 \newcommand{\taskrecon}{S1}
-\newcommand{\perexptaskrecon}{S2}
-\newcommand{\perexpcorrmaps}{S3}
+\newcommand{\perexpcorrmaps}{S2}
+\newcommand{\perexptaskrecon}{S3}
+\newcommand{\perexptaskreconseparated}{S4}
 
@@
 similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
-reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). Our finding,
+reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). We also
+replicated this result separately for each of the two experiments from
+Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding,
 that when reconstructing held-out data from a given patient
@@
 
+To test the task-specificity of the SuperEEG-derived correlation
+models, we repeated our within- and across-patient cross validation
+procedures separately for Experiment 1 and Experiment 2 data from
+Dataset 2.  We then compared the reconstruction accuracies of held-out
+electrodes, for models trained within versus across the two
+experiments, or combining across both experiments
+(Fig.~\perexptaskrecon).  In every case we found that across-patient
+models trained using data from all other patients out-performed
+within-patient models trained on data only from the subject
+contributing the given electrode ($t$s$(XXX) > XXX, p$s$ < XXX$).  All
+reconstruction accuracies also reliably exceeded chance performance
+($t$s$(XXX) > XXX, p$s$ < XXX$).  Average reconstruction accuracy was
+highest for the across-patient models limited to data from the same
+experiment (mean accuracy: $0.55$), next-highest for the
+across-patient models that combined data across both experiments (mean
+accuracy: $0.50$), and lowest for models trained across task (mean
+accuracy: $0.37$).  This result also held for each of the Dataset 2
+experiments individually (Fig.~\perexptaskreconseparated).  Taken
+together, these results indicate that there are reliable commonalities
+in the spatial correlations of full-brain activity across tasks, but
+that there are also reliable differences in these spatial correlations
+across tasks.  Whereas reconstruction accuracy benefits from
+incorporating data from other patients, reconstruction accuracy is
+highest when constrained to within-task data, or data that includes a
+variety of tasks (e.g., Dataset 1, or combining across the two Dataset
+2 experiments).
+
 \textbf{JRM STOPPED HERE}
-
-We were interested in the task specific contributions to the
-reconstruction accuracy.  Each patient in the the second dataset
-participated in two free recall experiments.  We ran similar analyses
-for both experiments and found that activity was best reconstructed
-when limiting the training data to within task, as opposed to across
-task or incorporating data from both tasks (Fig.~\taskrecon (mean reconstruction accuracy incorporating data within task: 0.55, across task: 0.37, all tasks: .50)).
-Although reconstruction accuracy in the across task analysis was still better than the volume conductance model alone (paired $t$-test
-between $z$-transformed mean correlation coefficients by patient: $t(47) = 5.65, p < 10\textsuperscript{-5}$), these results suggests that having a common tasks for patients may yield better reconstruction accuracy.
 

### 2018-10-06 code/notebooks/plot.py
removed density in compile recon code and update plot.py with figure changes

@@ -139,7 +139,7 @@ def plot_times_series(time_data_df, lower_bound, upper_bound, outfile = None):
     sns.set_style("white")
     time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['actual'].plot(ax=ax, color='k', lw=1, fontsize=21)
     time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['predicted'].plot(ax=ax, color='r', lw=1)
-    ax.legend(['Actual', 'Predicted'], fontsize=21)
+    ax.legend(['Observed', 'Reconstructed'], fontsize=21)
     ax.set_xlabel("Time (s)", fontsize=21)
     ax.set_ylabel("Voltage (normalized)", fontsize=21)
 

### 2018-10-06 code/scripts/recon/compile_recons.py

@@ -94,7 +94,6 @@ def compile_corrs(bo_path, corr_path, threshold=10):
     corr_data = np.load(corr_path, mmap_mode='r')
     tempR = np.round(corr_data['coord'], 2)
     tempmeancorr = z2r(np.mean(r2z(corr_data['corrs'])))
-    bo_data = se.load(os.path.join(bo_path, f_name + '.bo'))
     tempsamplerate = np.mean(se.load(os.path.join(bo_path, f_name + '.bo'), field='sample_rate'))
     tempsamples = se.load(os.path.join(bo_path, f_name + '.bo'), field='sessions').shape[0]
     kurt_vals = se.load(os.path.join(bo_path, f_name + '.bo'), field='kurtosis')
@@ -145,7 +144,7 @@ for i in files:
         all_corrs_across = all_corrs_across.append(compile_temp)
         all_corrs_across.to_csv(os.path.join(dir, 'all_corrs_across.csv'))
 
-all_corrs_across['Density'] = density(all_corrs_across['R'].tolist(), 3)
+# all_corrs_across['Density'] = density(all_corrs_across['R'].tolist(), 3)
 
 all_corrs_across.to_csv(os.path.join(dir, 'all_corrs_across.csv'))
 

### 2018-10-06 paper/boneyard.tex

@@
 \section*{Introduction}
+% JRM thoughts:
+% - Tie in stats from supplemental analyses.  Fig S4: total number of
+% electrodes, total number of used electrodes, prop thresholded, total
+% recording time, average session time, number of sessions.
+
+(i.e.,
+relying on a combination of volume conductance
+
+(Across shown in black, see Fig.~\ref{fig:corrmap}A). We also
+reconstructed activity for each electrode using a model trained on the
+remaining electrodes from only that patient, to account for
+reconstruction accuracy attributed to volume conductance alone (Within
+shown in gray, see Fig.~\ref{fig:corrmap}A). For the first dataset, we
+compared these two distributions of correlation coefficients (paired
+$t$-test between $z$-transformed mean correlation coefficients by
+patient: $t(66) = 9.64, p < 10\textsuperscript{-10}$).  We repeated
+this analysis on a similar dataset Fig.~\ref{fig:corrmap}C) with
+similar results (paired $t$-test between $z$-transformed mean
+correlation coefficients by patient:
+$t(23) = 6.93, p < 10\textsuperscript{-5}$). This is an especially
+conservative test, given that the SuperEEG reconstructions exclude
+(from the correlation matrix estimates) all data from the patient
+whose data is being reconstructed.  Furthermore, we also replicated
+this finding for each independent experiment within dataset 2 (Fig. S3
+(paired $t$-test between $z$-transformed mean correlation coefficients
+by patient for experiment 1:
+$t(23) = 6.23, p < 10\textsuperscript{-5}$ and experiment 2:
+$t(23) = 6.62, p < 10\textsuperscript{-5}$).
+
+%%%
+
 Current human brain recording techniques are fraught with compromise.

### 2018-10-07 paper/main.tex
results section, density results [WIP]

@@
 
+Although both datasets we examined provide good full-brain coverage
+(when considering data from every patient; e.g.\
+Fig.~\ref{fig:corrmap}B, D), electrodes are not placed uniformly
+throughout the brain.  For example, electrodes are more likely to be
+implanted in regions like the medial temporal lobe (MTL), and are
+rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
+Separately for each dataset, for each voxel in the XXX~mm$^3$ voxel
+MNI152 brain, we computed the proportion of electrodes contained
+within a 20 MNI unit radius sphere centered on that voxel.  We defined
+the \textit{density} at that location as this proportion.  Across
+Datasets 1 and 2, the electrode placement densities were similar
+(correlation by voxel: $r = 0.57, p < 10^{-10}$).  We wondered whether
+regions with good covererage might be associated with better
+reconstruction accuracy (e.g. Fig.~\ref{fig:corrmap}B, D indicate that
+many electrodes in the MTL have relatively high reconstruction
+accuracy, and occiptal electrodes tend to have relatively low
+reconstruction accuracy).  To test whether this held more generally
+across the entire brain, for each dataset we computed the electrode
+placement density for each electrode from each patient (using the
+proportion of \textit{other} patients' electrodes within 20 MNI units
+of the given electrode).  We then correlated these density values with
+the across-patient reconstruction accuracies for each electrode.
+Contrary to our expectation, rather than positive correlations, we
+found weak (but reliable) negative correlations between reconstruction
+accuracy and density for both datasets (Dataset 1: $r = XXX, p = XXX$;
+Dataset 2: $r = -0.16, p < 10^{-10}$).  This indicates that the
+reconstruction accuracies we observed are not driven solely by
+sampling density, but rather may also reflect higher order properties
+of neural dynamics such as functional correlations between distant
+voxels~\citep{BetzEtal17b}.
+
 \textbf{JRM STOPPED HERE}
-
-We also wondered whether reconstruction quality (measured as the
-correlation between the observed and reconstructed data) varied with
-the electrode locations (Fig.~\ref{fig:corrmap}B \& D).
-In general, reconstruction quality remained high throughout the brain.
-Although reconstruction accuracy appeared high in the medial temporal lobe, which is a common epileptic focus (and therefore a common target for electrode implantation), we observed a weak but statistically reliable negative correlation between reconstruction quality and electrode density (defined as the proportion of electrodes within 20 MNI units for each location; dataset 1: $r = -0.07, p < 10^{-5}$, dataset 2: $r = -0.16, p < 10^{-10}$).
-This provides some evidence that our reconstruction accuracy results cannot be driven only by volume conductance.
-Qualitatively, it appeared that the distribution of electrodes was similar across the datasets, suggesting potential commonalities of target locations across patients and similarities in surgical decisions.
-Indeed, we found a relatively strong correlation between the electrode densities within the two datasets (defined as the proportion of electrodes within 20 MNI units for each 34686 voxels (Fig.~\ref{fig:density}A, B); $r = 0.57, p < 10^{-10}$).
 

### 2018-10-07 paper/main.tex
finishing up results, backing up progress on most informative locations analysis [WIP]

@@
   \includegraphics[width=\textwidth]{figs/methods}
-  \caption{\textbf{Methods overview.}  \textbf{A.  Electrode
+  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode
       locations.}  Each dot reflects the location of a single
-    electrode in dataset 1, colored according to 7 factor labels (see
-    Panel D for details). One patient's electrode locations are
-    highlighted in black and the to-be-reconstructed recording
-    location is highlighted in red. \textbf{B. Radial basis function
-      (RBF).}  Each electrode contributed by the patient (black)
-    weights on the full set of locations under consideration (all dots
-    in Panel A, defined as $\bar{R}$ in the text).  The weights fall
-    off with positional distance (in MNI space) according to an RBF.
-    \textbf{C. Per-patient correlation matrices.}  After computing the
+    electrode implanted in the brain of a Dataset 1 patient.  A
+    held-out recording location from one patient is indicated in red,
+    and the patient's remaining electrodes are indicated in black.
+    The electrodes from the remaining patients are colored by
+    $k$-means cluster (computed using the full-brain correlation model
+    shown in Panel D).  \textbf{B.~Radial basis function kernel.}
+    Each electrode contributed by the patient (black) weights on the
+    full set of locations under consideration (all dots in Panel A,
+    defined as $\bar{R}$ in the text).  The weights fall off with
+    positional distance (in MNI space) according to an RBF.
+    \textbf{C.~Per-patient correlation matrices.}  After computing the
     pairwise correlations between the recordings from each patient's
@@
     full-brain correlation matrix using each patient's
-    data. \textbf{D.  Combined correlation matrix.}  We estimate a
-    single full-brain correlation matrix by averaging the
-    patient-specific correlation matrices.  We sort the resulting
-    correlation matrix based on 7 factor labels obtained from k-means
-    clustering~\cite{YeoEtal11}). \textbf{E.  Reconstructing activity
-      throughout the brain.}  Given the observed activity from the
-    patient's electrodes and the estimated correlation matrix (Panel
-    D), we can compute a maximum likelihood estimate of the voltage
-    trace at any location in $\bar{R}$.  An example reconstruction (at
-    the red dot in Panel A) is shown in red, and the actual recording
-    at that location is highlighted above in blue.}
+    data. \textbf{D.~Merged correlation model.}  We combine the
+    per-patient correlation matrices (Panel C) to obtain a single
+    full-brain correlation model that captures information contributed
+    by every patient.  Here we have sorted the rows and columns to
+    reflect $k$-means clustering labels~\citep[using
+    $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their
+    correlations with the rest of the brain (i.e., rows of the matrix
+    displayed in the panel).  The boundaries denote the cluster
+    groups.  The rows and columns of Panel C have been sorted using
+    teh Panel D-derived cluster labels.  \textbf{E.~Reconstructing activity
+      throughout the brain.}  Given the observed recordings from the
+    given patient (shown in black; held-out recording is shown in
+    blue), along with a full-brain correlation model (Panel D), we
+    use Equation~\ref{eqn:reconstruction} to reconstruct the most
+    probable activity at the held-out location (red).}
   \label{fig:methods}
@@
 rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
-Separately for each dataset, for each voxel in the XXX~mm$^3$ voxel
+Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
 MNI152 brain, we computed the proportion of electrodes contained
@@
 
-\textbf{JRM STOPPED HERE}
-
 \begin{figure}
@@
   \includegraphics[width=\textwidth]{figs/density}
-  \caption{\textbf{Sampling density and reconstruction quality.}
-    \textbf{A. \& B. } The glass brain maps show sampling density by voxel location for dataset 1 and dataset 2. \textbf{C.}
-      Correlation of sampling density by voxel location for dataset 1 vs. dataset 2.}
+  \caption{\textbf{Electrode sampling density by location.}
+    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
+    voxel is colored by the proportion of total electrodes in the
+    dataset that are
+    located within a 20~MNI unit radius sphere centered on the given
+    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
+      2.}  This panel displays the sampling density map for Dataset 2,
+    in the same format as Panel A.  \textbf{C.~Correspondence in
+      sampling density by voxel across Datasets 1 and 2.}  The
+    two-dimensional histogram displays the by-voxel densities in the
+    two Datasets, and the one-dimensional histograms display the
+    proportions of voxels in each dataset with the given density
+    value.  The correlation reported in the panel is across voxels in
+    the 4~mm$^3$ MNI brain.}
   \label{fig:density}
@@
 
-In addition to exploring how reconstruction quality varies with
-location, we also wondered whether there might be effects of electrode
-placements on reconstruction quality.  For example, are there
-particular implantation locations that yield especially high
-reconstruction accuracies at other locations throughout the brain?
-To gain insights into this questions, we computed the average reconstruction correlation for each patient, then computed the average patient reconstruction correlation for any patients who had electrodes within a 20 MNI unit diameter sphere centered on each voxel location.
-The resulting maps highlight the locations of implanted electrodes from patients whose
-reconstructions were especially accurate  (Fig.~\ref{fig:informap}A and B).
-We found that the most informative locations were consistent across datasets which lends support to the notion that different electrode location are more informative about activity across patients (Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).
-The locations in dark red might therefore be good candidate
-implantation targets for neurosurgeons and neurologists who wish to
-use SuperEEG to reconstruct full-brain electrophysiological signals.
-The above findings, that one can infer brain activity throughout a person's brain 
-using recordings from a limited number of locations from that person's brain in conjunction with recordings from other people's brains, have deep
+In neurosurgical applications where one wishes to infer full-brain
+activity patterns, can our framework yield insights into where the
+electrodes should be placed?  A basic assumption of our approach (and
+of most prior ECoG work) is that electrode recordings are most
+informative about the neural activity near the recording surface of
+the electrode.  But if we consider that activity patterns throughout
+the brain are meaningfully correlated, are there particular
+implantation locations that, if present in a patient's brain, yield
+especially high reconstruction accuracies throughout the rest of the
+brain?  For example, one might hypothesize that brain structures that
+are heavily interconnected with many other structures could be more
+informative about full-brain activity patterns than comparatively
+isolated structures.
+
+To gain insights into whether particular electrode locations might be
+especially informative, we first computed the average reconstruction
+accuracy across all of each patient's electrodes (using the
+across-patients cross validation test; black histograms in
+Fig.~\ref{fig:corrmap}A and C).  We labeled each patient's electrodes
+in each dataset with the average reconstruction accuracy for that
+patient.  In other words, we assigned every electrode from each
+patient the same value, reflecting how well the activity patterns at
+those electrodes were reconstructed on average.  Next, for each voxel
+in the 4~mm$^3$ MNI brain, we computed the average value across any
+electrode (from any patient) that came within 20 MNI units of that
+voxel's center.  Effectively, we computed the average reconstruction
+accuracy across any patients with electrodes near each voxel, where
+the avearges were weighted to reflect patients who had more electrodes
+implanted near that location.
+
+\textbf{JRM STOPPED HERE}
+% - report most-informative locations (i.e. which brain structures?)
+% - can we say anything bout whether these most-informative regions are heavily
+% interconnected, e.g. perhaps from the resting state literature?
+
+To gain insights into this question, we
+computed the average reconstruction accuracy for each patient, then
+computed the average patient reconstruction correlation for any
+patients who had electrodes within a 20 MNI unit diameter sphere
+centered on each voxel location. The resulting maps highlight the
+locations of implanted electrodes from patients whose reconstructions
+were especially accurate (Fig.~\ref{fig:informap}A and B). We found
+that the most informative locations were consistent across datasets
+which lends support to the notion that different electrode location
+are more informative about activity across patients
+(Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations
+in dark red might therefore be good candidate implantation targets for
+neurosurgeons and neurologists who wish to use SuperEEG to reconstruct
+full-brain electrophysiological signals.  The above findings, that one
+can infer brain activity throughout a person's brain using recordings
+from a limited number of locations from that person's brain in
+conjunction with recordings from other people's brains, have deep
 implications for the structure of brain data.  The first implication
 is that the correlational structure of different people's brain data
-is largely preserved across individuals.
-Despite recent evidence that different people have stable but reliably different resting state connectome~\cite{FinnEtal15}, our results suggest that the correlational structure of different people's brain data is preserved enough across individuals to provide meaningful information.
+is largely preserved across individuals. Despite recent evidence that
+different people have stable but reliably different resting state
+connectome~\cite{FinnEtal15}, our results suggest that the
+correlational structure of different people's brain data is preserved
+enough across individuals to provide meaningful information.
 

### 2018-10-07 paper/main.tex
backing up progress-- almost done with first pass through results; working on fig 5 caption [WIP]

@@
 electrode (from any patient) that came within 20 MNI units of that
-voxel's center.  Effectively, we computed the average reconstruction
-accuracy across any patients with electrodes near each voxel, where
-the avearges were weighted to reflect patients who had more electrodes
-implanted near that location.
+voxel's center.  Effectively, we computed an \textit{information
+  score} for each voxel, reflecting the average reconstruction
+accuracy across any patients with electrodes near each voxel-- where
+the averages were weighted to reflect patients who had more electrodes
+implanted near that location. This yielded a single map for each
+dataset, highlighting regions that are especially promising
+implantation targets in terms of providing full-brain activity
+information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
+and patient differences across the two datasets, we nonetheless found
+that the maps of the most promising implantation targets derived from
+both datasets were similar (voxelwise correlation between information
+scores across the two datasets: $r = XXX, p = XXX$).  While the
+correspondence between the two maps was not perfect, our finding that there were
+some commonalities between the two maps lends support to the notion
+that different brain areas are differently informative about
+full-brain activity patterns.  Further, regions like XXX and XXX that
+exhibited strong information scores in both datasets may be especially
+promising implantation targets.
 
 \textbf{JRM STOPPED HERE}
-% - report most-informative locations (i.e. which brain structures?)
-% - can we say anything bout whether these most-informative regions are heavily
-% interconnected, e.g. perhaps from the resting state literature?
-
-To gain insights into this question, we
-computed the average reconstruction accuracy for each patient, then
-computed the average patient reconstruction correlation for any
-patients who had electrodes within a 20 MNI unit diameter sphere
-centered on each voxel location. The resulting maps highlight the
-locations of implanted electrodes from patients whose reconstructions
-were especially accurate (Fig.~\ref{fig:informap}A and B). We found
-that the most informative locations were consistent across datasets
-which lends support to the notion that different electrode location
-are more informative about activity across patients
-(Fig.~\ref{fig:informap}C); $r = 0.22, p < 10^{-10}$).  The locations
-in dark red might therefore be good candidate implantation targets for
-neurosurgeons and neurologists who wish to use SuperEEG to reconstruct
-full-brain electrophysiological signals.  The above findings, that one
-can infer brain activity throughout a person's brain using recordings
-from a limited number of locations from that person's brain in
-conjunction with recordings from other people's brains, have deep
-implications for the structure of brain data.  The first implication
-is that the correlational structure of different people's brain data
-is largely preserved across individuals. Despite recent evidence that
-different people have stable but reliably different resting state
-connectome~\cite{FinnEtal15}, our results suggest that the
-correlational structure of different people's brain data is preserved
-enough across individuals to provide meaningful information.
 

### 2018-10-08 paper/main.tex
finished draft of results

@@
 scores across the two datasets: $r = XXX, p = XXX$).  While the
-correspondence between the two maps was not perfect, our finding that there were
-some commonalities between the two maps lends support to the notion
-that different brain areas are differently informative about
-full-brain activity patterns.  Further, regions like XXX and XXX that
-exhibited strong information scores in both datasets may be especially
-promising implantation targets.
-
-\textbf{JRM STOPPED HERE}
+correspondence between the two maps was not perfect, our finding that
+there were some commonalities between the two maps lends support to
+the notion that different brain areas are differently informative
+about full-brain activity patterns.  Further, regions like XXX, XXX,
+and XXX that exhibited strong information scores in both datasets may
+be especially promising implantation targets.
 
@@
   \includegraphics[width=\textwidth]{figs/informap}
-  \caption{\textbf{Most informative electrode locations.} \textbf{A. \& B. } The glass
-    brain maps displays the average reconstruction correlations (by patient, across
-    all electrodes) for patients with electrodes within a 20 MNI unit diameter sphere centered on
-    each location for dataset 1 and dataset 2. \textbf{C.} Correlation between z-transformed correlations by voxel for dataset 1 vs. dataset 2.}
+  \caption{\textbf{Most informative electrode locations.}
+    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
+    reflect the weighted average reconstruction accuracy across all
+    electrodes from any patients with at least one electrode within 20
+    MNI units of the given voxel.  {B. Dataset 2 information score by
+      voxel.}  This panel is in the same format as Panel A.
+    \textbf{C. Correspondence in information scores by voxel across
+      Datasets 1 and 2.}  Same format as Figure~\ref{fig:density}C.}
   \label{fig:informap}
 \end{figure}
+
+\textbf{JRM STOPPED HERE}
 
@@
 task-driven timepoint-specific covariance fingerprints appear to be
-largely preserved across people~\cite{SimoEtal16, MannEtal17}).  These
+largely preserved across people~\cite{SimoEtal16, MannEtal18}).  These
 findings indicate that the full-brain covariance matrix is not stable
@@
 \bibliography{CDL-bibliography/memlab.bib}
-\bibliographystyle{Science}
+\bibliographystyle{apa}
 

### 2018-10-08 paper/boneyard.tex
JRM finished round of edits (still needs final coat of polish)

@@
+% old discussion section
+
+%DISCUSSION POINTS
+%recap main approach
+SuperEEG infers full-brain activity patterns by leveraging
+correlations in those patterns of brain activity within and across people.  Although
+the approach may, in principle, be used to infer brain activity
+\textit{anywhere} in the brain, the inferences perform slightly better for
+regions with dense electrode sampling across patients.
+(Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
+are included in the inference procedure, this suggests that reconstruction accuracy should improve.
+
+%why does it work?  redundancy of brain
+A fundamental assumption of the SuperEEG algorithm is that the data
+covariance matrix is stable over time and across people.  This is a
+useful simplification.  However, a growing body of evidence from the
+fMRI community suggests that the data covariance matrix changes in
+meaningful ways over time (for example, the data covariance matrix
+changes from moment-to-moment during story listening, serving as a
+unique ``fingerprint'' for each moment of the story; further, these
+task-driven timepoint-specific covariance fingerprints appear to be
+largely preserved across people~\cite{SimoEtal16, MannEtal18}).  These
+findings indicate that the full-brain covariance matrix is not stable
+over time.  Other recent work has shown that people's resting state
+connectivity matrices may be used to uniquely identify individuals and
+predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
+that the full-brain covariance matrix is not stable across people.  If
+the fundamental stability assumptions that SuperEEG relies on are
+violated, how can the SuperEEG algorithm still accurately recover LFP
+data?  It is important to recognize that the fact that variability
+(over time or across people) is predictive (e.g., of cognitive states
+during story listening or fluid intelligence scores) does not
+necessarily mean that this variability is large in magnitude.  Rather,
+we have long known that brain structure is tightly preserved across
+individuals (and over time, at least on the timescale of typical
+clinical and experimental recording sessions), and any functional
+changes must occur within the framework of the underlying structural
+anatomy.  Nevertheless, one could imagine future improvements to the
+SuperEEG approach that leverage resting state fMRI or structural data
+[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
+the correlation matrices inferred, in the current framing, using only
+ECoG data.  Further, relaxing the assumption that the covariance
+matrix is stable (over time and/or across people), and/or
+incorporating more detailed brain conductance models (e.g., informed
+by structural MRI scans) may improve the predictive performance of the
+approach.
+
+%This technique relies on recordings from many patients performing the
+%same basic cognitive task.  To what extent do these findings
+%generalize across studies?  For example, could one combine recordings
+%from several studies to improve our ability to reconstruct neural
+%activity?
+One potential limitation of the SuperEEG approach is that the above
+assumption of covariance stability across people may be violated even
+more if different patients are performing different cognitive tasks.
+To understand of the extent to which the current findings generalize across
+cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks.
+Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
+matrix.  Or, using a more sophisticated approach, one could create a
+hierarchical model whereby each task-specific covariance matrix was
+modeled as a perturbation of a ``global'' task-unspecific covariance
+matrix (which could in turn be informed by fMRI or DTI data).
+% Alternatively, if the covariance matrix is stable across tasks, this would
+% suggest that recordings from multiple studies could be combined to
+% improve the overall reconstruction accuracy.
+
+A second potential limitation of the SuperEEG approach is that it
+does not provide a natural means of estimating the precise timing of
+single-neuron action potentials.  Prior work has shown that gamma band
+and broadband activity in the LFP may be used to estimate the firing
+rates of neurons that underly the population contributing to the
+LFP~\cite{MannEtal09}.  Because SuperEEG reconstructs LFPs throughout
+the brain, one could in principle use gamma or broadband power in the
+reconstructed signals to estimate the corresponding firing rates
+(though not the timings of individual action potentials).
+
+Beyond providing a means of estimating ongoing activity throughout the
+brain using already implanted electrodes, our work also has
+implications for where to place the electrodes in the first place.
+Electrodes are typically implanted to maximize coverage of suspected
+epileptogenic tissue.  However, our findings suggest that this approach
+could be further optimized.  Specifically, one could leverage not only
+the non-invasive recordings taken during an initial monitoring period
+(as is currently done), but also recordings collected from other
+patients.  We could then ask: given everything we know about the other
+patients and from the scalp recordings of this new patient, where
+should we place a fixed number of electrodes to maximize our ability
+to map seizure foci?  As shown in Figure~\ref{fig:informap}, recordings
+from different locations are differently informative in terms of
+reconstructing the spatiotemporal patterns throughout the brain.
+This property might be leveraged in decisions about where to
+surgically implant electrodes in future patients.
+
+%%%%
+
 \section*{Introduction}

### 2018-10-08 paper/main.tex
JRM finished round of edits (still needs final coat of polish)

@@
     groups.  The rows and columns of Panel C have been sorted using
-    teh Panel D-derived cluster labels.  \textbf{E.~Reconstructing activity
+    the Panel D-derived cluster labels.  \textbf{E.~Reconstructing activity
       throughout the brain.}  Given the observed recordings from the
@@
 data from the patient whose data is being reconstructed.  We repeated
-each of these analyses on a second independent datset and found
+each of these analyses on a second independent dataset and found
 similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
@@
 distant electrodes provide additional predictive power to the data
-reconstructions beynd the information contained solely in nearby
+reconstructions beyond the information contained solely in nearby
 electrodes.  (This follows from the fact that each patient's
@@
 predictions for data from the other experiment.  Further, we wondered
-about the extent to which it might be benefitial or harmful to combine
+about the extent to which it might be beneficial or harmful to combine
 data across tasks.
@@
 many electrodes in the MTL have relatively high reconstruction
-accuracy, and occiptal electrodes tend to have relatively low
+accuracy, and occipital electrodes tend to have relatively low
 reconstruction accuracy).  To test whether this held more generally
@@
 
-\textbf{JRM STOPPED HERE}
+\section*{Discussion}
+Are our brain's networks static or dynamic?  And to what extent are
+the network properties of our brains stable across people and tasks?
+One body of work suggests that our brain's \textit{functional}
+networks are dynamic~\citep[e.g., ][]{MannEtal18},
+person-specific~\citep[e.g., ][]{FinnEtal15}, and
+task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the
+gross anatomical structure of our brains changes meaningfully over the
+course of years as our brains develop, on the timescales of typical
+neuroimaging experiments (i.e., hours to days) our anatomical networks
+are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many
+aspects of brain anatomy, including white matter structure, is largely
+preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13,
+  MoriEtal08} There are several possible means of reconciling this
+apparent inconsistency between dynamic person- and task-specific
+functional networks versus stable anatomical networks.  For example,
+relatively small magnitude anatomical differences across people may be
+reflected in reliable functional connectivity differences.  Along
+these lines, one recent study found that diffusion tensor imaging
+(DTI) structural data is similar across people, but may be used to
+predict person-specific resting state functional connectivity
+data~\citep{BeckEtal18}.  Similarly, other work indicates that
+task-specific functional connectivity may be predicted by resting
+state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.  Another
+(potentially complementary) possibility is that our functional
+networks are constrained by anatomy, but nevertheless exhibit
+(potentially rapid) task-dependent changes~\citep[e.g.,
+][]{SporBetz16}.
 
-\section*{Discussion}
-%DISCUSSION POINTS
-%recap main approach
-SuperEEG infers full-brain activity patterns by leveraging
-correlations in those patterns of brain activity within and across people.  Although
-the approach may, in principle, be used to infer brain activity
-\textit{anywhere} in the brain, the inferences perform slightly better for
-regions with dense electrode sampling across patients.
-(Taken to the logical extreme, we could not hope to accurately recover activity patterns from brain areas where no recordings existed from any patient.)   As more data
-are included in the inference procedure, this suggests that reconstruction accuracy should improve.
+Here we have taken a model-based approach to studying whether high
+spatiotemporal resolution activity patterns throughout the human brain
+may be explained by a static connectome model that is shared across
+people and tasks.  Specifically, we trained a model to take in
+recordings from a subset of brain locations, and then predicted
+activity patterns during the same interval, but at \textit{other}
+locations that were held out from the model.  Our model, based on
+Gaussian process regression, was built on three general hypotheses
+about the nature of the correlational structure of neural activity
+(each of which we tested).  First, we hypothesized that functional
+correlations are stable over time and across tasks.  We found that,
+although aspects of the patients' functional correlations that were
+stable across tasks, we achieved better reconstruction accuracy when
+we trained the model on within-task data~\citep[we acknowledge that
+our general approach could potentially be extended to better model
+across-task changes, following][and others]{ColeEtal16, TavoEtal16}.
+Second, we hypothesized that some of the correlational structure of
+people's brain activity is similar across individuals.  Consistent
+with this hypothesis, our model explained the data best when we
+trained the correlation model using data from \textit{other}
+patients-- even when compared to a correlation model trained using the
+same patient's data.  Third, we resolved ambiguities in the data by
+hypothesizing that neural activity from nearby sources will tend to be
+similar, all else being equal.  This hypothesis was supported through
+our finding that all of the models we trained that incorporated this
+spatial smoothness assumption predicted held-out data well above chance.
 
-%why does it work?  redundancy of brain
-A fundamental assumption of the SuperEEG algorithm is that the data
-covariance matrix is stable over time and across people.  This is a
-useful simplification.  However, a growing body of evidence from the
-fMRI community suggests that the data covariance matrix changes in
-meaningful ways over time (for example, the data covariance matrix
-changes from moment-to-moment during story listening, serving as a
-unique ``fingerprint'' for each moment of the story; further, these
-task-driven timepoint-specific covariance fingerprints appear to be
-largely preserved across people~\cite{SimoEtal16, MannEtal18}).  These
-findings indicate that the full-brain covariance matrix is not stable
-over time.  Other recent work has shown that people's resting state
-connectivity matrices may be used to uniquely identify individuals and
-predict fluid intelligence scores~\cite{FinnEtal15}.  This indicates
-that the full-brain covariance matrix is not stable across people.  If
-the fundamental stability assumptions that SuperEEG relies on are
-violated, how can the SuperEEG algorithm still accurately recover LFP
-data?  It is important to recognize that the fact that variability
-(over time or across people) is predictive (e.g., of cognitive states
-during story listening or fluid intelligence scores) does not
-necessarily mean that this variability is large in magnitude.  Rather,
-we have long known that brain structure is tightly preserved across
-individuals (and over time, at least on the timescale of typical
-clinical and experimental recording sessions), and any functional
-changes must occur within the framework of the underlying structural
-anatomy.  Nevertheless, one could imagine future improvements to the
-SuperEEG approach that leverage resting state fMRI or structural data
-[e.g., diffusion tensor imaging (DTI)] to estimate Bayesian priors over
-the correlation matrices inferred, in the current framing, using only
-ECoG data.  Further, relaxing the assumption that the covariance
-matrix is stable (over time and/or across people), and/or
-incorporating more detailed brain conductance models (e.g., informed
-by structural MRI scans) may improve the predictive performance of the
-approach.
-
-%This technique relies on recordings from many patients performing the
-%same basic cognitive task.  To what extent do these findings
-%generalize across studies?  For example, could one combine recordings
-%from several studies to improve our ability to reconstruct neural
-%activity?
-One potential limitation of the SuperEEG approach is that the above
-assumption of covariance stability across people may be violated even
-more if different patients are performing different cognitive tasks.
-To understand of the extent to which the current findings generalize across
-cognitive tasks, we replicated our initial findings using a dataset in which patients participated in two tasks, and limited the training data to either within task, across task, or using both tasks.
-Since we found the most accurate reconstructions using task-specific data, this would suggest building up new databases for estimating each task-specific covariance
-matrix.  Or, using a more sophisticated approach, one could create a
-hierarchical model whereby each task-specific covariance matrix was
-modeled as a perturbation of a ``global'' task-unspecific covariance
-matrix (which could in turn be informed by fMRI or DTI data).
-% Alternatively, if the covariance matrix is stable across tasks, this would
-% suggest that recordings from multiple studies could be combined to
-% improve the overall reconstruction accuracy.
-
-A second potential limitation of the SuperEEG approach is that it
-does not provide a natural means of estimating the precise timing of
-single-neuron action potentials.  Prior work has shown that gamma band
-and broadband activity in the LFP may be used to estimate the firing
-rates of neurons that underly the population contributing to the
-LFP~\cite{MannEtal09}.  Because SuperEEG reconstructs LFPs throughout
-the brain, one could in principle use gamma or broadband power in the
-reconstructed signals to estimate the corresponding firing rates
-(though not the timings of individual action potentials).
+One potential limitation of our approach is that it does not provide a
+natural means of estimating the precise timing of single-neuron action
+potentials.  Prior work has shown that gamma band and broadband
+activity in the LFP may be used to estimate the firing rates of
+neurons that underly the population contributing to the
+LFP~\cite{MillEtal08, MannEtal09, JacoEtal10, CronEtal11}.  Because
+SuperEEG reconstructs LFPs throughout the brain, one could in
+principle use gamma or broadband power in the reconstructed signals to
+estimate the corresponding firing rates (though not the timings of
+individual action potentials).
 
@@
 the non-invasive recordings taken during an initial monitoring period
-(as is currently done), but also recordings collected from other
+(as is currently done routinely), but also recordings collected from other
 patients.  We could then ask: given everything we know about the other
@@
 \section*{Code availability}
-We have released an open-source SuperEEG Python toolbox.
-All of the code used in this manuscript is on GitHub, and the code may be shared using a GitHub account accessible to the reviewers upon request.
+We have published an open-source toolbox implementing the SuperEEG
+algorithm.  It may be downloaded \href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}.
 
 \section*{Data availability}
-The dataset analyzed in this study was generously shared by Michael J.
-Kahana.
-A portion of the dataset may be downloaded \href{http://memory.psych.upenn.edu/Request_EEG_access?paper=SedeEtal03}{\underline{here}}.
+The dataset analyzed in this study was generously shared by Michael Kahana.  A portion of Dataset 1 may be downloaded
+\href{http://memory.psych.upenn.edu/Request_EEG_access?paper=SedeEtal03}{\underline{here}}.
+Dataset 2 may be downloaded
+\href{http://memory.psych.upenn.edu/Request_EEG_access?paper=EzzyEtal17}{\underline{here}}.
+
 \section*{Acknowledgements}
-We are grateful for useful discussions with Luke J. Chang and Matthijs van der Meer.  We are also grateful to Michael J. Kahana for generously sharing
-the ECoG dataset we analyzed in our paper, which was collected under
-NIMH grant MH55687 to MJK.
-Our work was also supported in part by NSF EPSCoR Award Number 1632738.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+We are grateful for useful discussions with Luke J. Chang, Uri Hasson,
+Josh Jacobs, Michael Kahana, and Matthijs van der Meer.  We are also
+grateful to Michael Kahana for generously sharing the ECoG data we
+analyzed in our paper, which was collected under NIMH grant MH55687
+and DARPA RAM Cooperative Agreement N66001-14-2-4-032, both to MJK.
+Our work was also supported in part by NSF EPSCoR Award Number 1632738
+and by a sub-award of DARPA RAM Cooperative Agreement
+N66001-14-2-4-032 to JRM.  The content is solely the responsibility of
+the authors and does not necessarily represent the official views of
+our supporting organizations.
+
 \section*{Author Contributions}

### 2018-10-08 code/notebooks/plot.py
WIP figure updates

@@ -20,6 +20,7 @@ import matplotlib.ticker as mtick
 import matplotlib.cm as cm
 import seaborn as sns
 from scipy import stats
+import math
 
 ############## General functions #################
 
@@ -142,21 +143,24 @@ def plot_times_series(time_data_df, lower_bound, upper_bound, outfile = None):
     ax.legend(['Observed', 'Reconstructed'], fontsize=21)
     ax.set_xlabel("Time (s)", fontsize=21)
     ax.set_ylabel("Voltage (normalized)", fontsize=21)
-
-    xvals = ax.get_xticks()
-    #ax.set_xticklabels([np.round(x, 4) for x in xvals])
-
-    ax.set_xticklabels([np.round(x / 400, 4) for x in xvals])
-    for index, label in enumerate(ax.xaxis.get_ticklabels()):
-        if index % 2 == 0:
-            label.set_visible(False)
-    ax.spines['right'].set_visible(False)
-    ax.spines['top'].set_visible(False)
     ax.tick_params(axis='x', labelsize=18)
     ax.tick_params(axis='y', labelsize=18)
+    xvals = ax.get_xticks()
+    print(xvals)
+    xvals = np.asarray([750, 1000, 1250, 1500, 1750, 2000, 2250, 2500, 2750])
+
+    #ax.set_yticklabels([int(np.round(x / 2, 1)) for x in yvals])
+    #ax.set_xticklabels([math.ceil(np.round(x / 250, 4)) for x in xvals])
+    ax.set_xticklabels([np.round(x / 250, 4) for x in xvals])
+
+    # for index, label in enumerate(ax.xaxis.get_ticklabels()):
+    #     if index == 0:
+    #         print(index)
+    #         label.set_visible(True)
+    ax.spines['right'].set_visible(False)
+    ax.spines['top'].set_visible(False)
 
     plt.tight_layout()
-
     if not outfile is None:
         plt.savefig(outfile)
     else:
@@ -566,8 +570,8 @@ def plot_2d_corr_hist(df, outfile=None):
             horizontalalignment='left',
             verticalalignment='top',
             transform=ax.transAxes, fontsize=24)
-    ax.set_xlabel("Dataset 1 \n z-transformed correlations", fontsize=30)
-    ax.set_ylabel("Dataset 2 \n z-transformed correlations", fontsize=30)
[…]

### 2018-10-08 paper/main.tex

@@
-% Use only LaTeX2e, calling the article.cls class and 12-point type.
-
 \documentclass[11pt]{article}
-
-% Users of the {thebibliography} environment or BibTeX should use the
-% scicite.sty package, downloadable from *Science* at
-% www.sciencemag.org/about/authors/prep/TeX_help/ .
-% This package should properly format in-text
-% reference calls and reference-list numbers.
-
-%\usepackage{scicite}
 \usepackage[numbers, square, sort, compress]{natbib}
-
-% Use times if you have the font installed; otherwise, comment out the
-% following line.
-
-\usepackage{times}
+\usepackage{newpxtext,newpxmath}
+\usepackage[T1]{fontenc}
 \usepackage{hyperref}
@@
 \linenumbers
-% The preamble here sets up a lot of new/revised commands and
-% environments.  It's annoying, but please do *not* try to strip these
-% out into a separate .sty file (which could lead to the loss of some
-% information when we convert the file to other formats).  Instead, keep
-% them in the preamble of your main LaTeX source file.
-
-% The following parameters seem to provide a reasonable page setup.
 
@@
 
-% If your reference list includes text notes as well as references,
-% include the following line; otherwise, comment it out.
-
-\renewcommand\refname{References and Notes}
-
-% The following lines set up an environment for the last note in the
-% reference list, which commonly includes acknowledgments of funding,
-% help, etc.  It's intended for users of BibTeX or the {thebibliography}
-% environment.  Users who are hand-coding their references at the end
-% using a list environment such as {enumerate} can simply add another
-% item at the end, and it will be numbered automatically.
-
-\newcounter{lastnote}
-\newenvironment{scilastnote}{%
-\setcounter{lastnote}{\value{enumiv}}%
-\addtocounter{lastnote}{+1}%
-\begin{list}
-{\arabic{lastnote}.}
-{\setlength{\leftmargin}{.22in}}
-{\setlength{\labelsep}{.5em}}}
-{\end{list}}
-
 \newcommand{\taskrecon}{S1}
@@
 \newcommand{\perexptaskreconseparated}{S4}
+\newcommand{\suppstats}{S5}
 
@@
 \title{Towards human SuperEEG} 
-
-% Place the author information here.  Please hand-code the contact
-% information and notecalls; do *not* use \footnote commands.  Let the
-% author contact information appear immediately below the author names
-% as shown.  We would also prefer that you don't change the type-size
-% settings shown here.
-
-\author
-{Lucy L. W. Owen$^{1}$, Andrew C. Heusser$^{1, 2}$, and Jeremy R. Manning$^{1\ast}$\\\\
+\author{
+  Lucy L. W. Owen$^{1}$,
+  Andrew C. Heusser$^{1, 2}$, and
+  Jeremy R. Manning$^{1\ast}$\\\\
 $^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
@@
 
-% Include the date command, but leave its argument blank.
-
 \date{}
-
-%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
 
@@
 
-% Double-space the manuscript.
-
 \baselineskip24pt
-
-% Make the title.
-
 \maketitle
@@
   brain: given recordings from a limited set of locations in that
-  individual's brain, along with the observed spatial correlations in
-  other people's recordings, what would recordings most likely have
-  looked like at \textit{other} locations in that individual's
-  brain?\\\\
+  individual's brain, along with the observed spatial correlations
+  learned from other people's recordings, how much can be inferred
+  about ongoing activity at \textit{other} locations in that
+  individual's brain?\\\\
   \footnotesize{\textbf{Keywords: Electrocorticography (ECoG),
@@
 (intracranial EEG; iEEG).  However, these intracranial approaches also
-require compromise: the high temporal and spatial resolutions of
+require compromise: the high spatiotemporal resolutions of
 intracranial recordings comes at the cost of substantially reduced
@@
 
-Another approach to obtaining high spatial and temporal resolution
+Another approach to obtaining high spatiotemporal resolution
 neural data has been to collect fMRI and EEG data simultaneously.
@@
 ideally suited to each technique individually are somewhat at odds.
-For example, fMRI experiments typically lock stimulus presentation
+For example, fMRI experiments often lock stimulus presentation
 events to the regularly spaced image acquisition time (TR), which
@@
 patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  Each recording session lasted from XXX--XXX hours, and
-includes data recorded roughly from when the patients woke up each
-morning, to before they went to sleep at the end of each day.  In
-addition to typical bed-ridden hospital patient activities (e.g.,
-lying in bed, reading, watching television, using personal electronic
-devices, listening to music, visiting with family and friends, etc.),
-the patients also performed a variety of experimental cognitive tasks
-throughout their day (primarily list-learning memory tasks).  For the
-purposes of the Dataset 1 analyses presented here, we aggregated all
-data across each recording session, ignoring the particular activities
-or tasks the patients were performing at any given moment.  We used
-Dataset 1 to develop and debug our main SuperEEG approach, and to
-examine the extent to which SuperEEG might be able to generate
-task-general predictions.  Dataset 2 comprised multi-session
-recordings from XXX electrodes implanted in the brains of XXX epilepsy
-patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
-  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Whereas
-Dataset 1 included recordings taken during a wide variety of
-behaviors, Dataset 2 included recordings taken as each patient
-performed each of two memory tasks: a random word list free recall
-task and a categorized word list free recall task.  We used Dataset 2
-to further examine the ability of SuperEEG to generalize its
-predictions within versus across tasks.
+  MannEtal12}.  Each recording session lasted from XXX--XXX hours
+(Fig.~\suppstats A), and includes data recorded roughly from when the
+patients woke up each morning, to before they went to sleep at the end
+of each day.  In addition to typical bed-ridden hospital patient
+activities (e.g., lying in bed, reading, watching television, using
+personal electronic devices, listening to music, visiting with family
+and friends, etc.), the patients also performed a variety of
+experimental cognitive tasks throughout their day (primarily
+list-learning memory tasks).  For the purposes of the Dataset 1
+analyses presented here, we aggregated all data across each recording
+session, ignoring the particular activities or tasks the patients were
+performing at any given moment.  We used Dataset 1 to develop our main
+SuperEEG approach, and to examine the extent to which SuperEEG might
+be able to generate task-general predictions.  Dataset 2 comprised
+multi-session recordings from XXX electrodes implanted in the brains
+of XXX epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
+  KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
+  KuceEtal18}.  Each recording session lasted from XXX--XXX hours
+(Fig.~\suppstats B).  Whereas Dataset 1 included recordings taken during a
+wide variety of behaviors, Dataset 2 included recordings taken as each
+patient performed each of two memory tasks: a random word list free
+recall task and a categorized word list free recall task.  We used
+Dataset 2 to further examine the ability of SuperEEG to generalize its
+predictions within versus across tasks.  Figure~\suppstats~provides
+additional details on both datasets.
 
@@
 from each patient.  For Dataset 1, this yielded clean recordings from
-4168 electrodes implanted throughout the brains of 67 patients
+XXX electrodes implanted throughout the brains of XXX patients
 (Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
@@
 A second mechanism whereby a given region $x$ can contribute to the
-recording at $\eta$ is through anatomical connections between
-structures near $x$ and $\eta$.  We use spatial correlations in the
-data to estimate these anatomical connections~\citep{BeckEtal18}.  Let
-$\bar{R}$ be the set of locations at which we wish to estimate local
-field potentials, and let $R_{s}$ be set of locations at which we
-observe local field potentials from patient $s$ (excluding the
-electrodes that did not pass the kurtosis test described above). In
-the analyses below we define $\bar{R} = \cup_{s=1}^S R_s$.  We can
-calculate the expected inter-electrode correlation matrix for patient
-$s$, where $C_{s,k}(i,j)$ is the correlation between the time series
-of voltages for electrodes $i$ and $j$ from subject $s$ during session
-$k$, using:
+recording at $\eta$ is through (direct or indirect) anatomical
+connections between structures near $x$ and $\eta$.  We use temporal
+correlations in the data to estimate these anatomical
+connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations
+at which we wish to estimate local field potentials, and let
+$R_{s} \subseteq \bar{R}$ be set of locations at which we observe local
+field potentials from patient $s$ (excluding the electrodes that did
+not pass the kurtosis test described above). In the analyses below we
+define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate the expected
+inter-electrode correlation matrix for patient $s$, where
+$C_{s,k}(i,j)$ is the correlation between the time series of voltages
+for electrodes $i$ and $j$ from subject $s$ during session $k$, using:
 
@@
 ($\hat{D}_{s}$) placeholders for each $\hat{C}_{s}$, we aggregate these
-estimates across patients to obtain a single expected full-brain
+estimates across the $S$ patients to obtain a single expected full-brain
 correlation matrix ($\hat{K}$; Fig.~\ref{fig:methods}D):
 \begin{align}
- \hat{K} = \mathrm{r} \left(  \frac{\sum  \hat{N}_{s}}{\sum \hat{D}_{s}}\right).\label{eqn:corrmat}
+ \hat{K} = \mathrm{r} \left(  \frac{\sum_{s=1}^S  \hat{N}_{s}}{\sum_{s=1}^S \hat{D}_{s}}\right).\label{eqn:corrmat}
 \end{align}
@@
 Let $\alpha_s$ be the set of indices of patient $s$'s electrode locations in
-$\bar{R}$, and let $\beta_s$ be the set of indices of all other
+$\bar{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of indices of all other
 locations in $\bar{R}$. In other words, $\beta_s$ reflects the locations
@@
 Let $Y_{s,k,\alpha_s}$ be the number-of-timepoints ($T$) by
-length($\alpha_s$) matrix of (observed) voltages from the electrodes in
+$\left|\alpha_s\right|$ matrix of (observed) voltages from the electrodes in
 $\alpha_s$ during session $k$ from patient $s$. Then we can estimate the
@@
 This equation is the foundation of the SuperEEG algorithm.  Whereas we
-observe recordings only at the locations in $\alpha_s$,
+observe recordings only at the locations indexed by $\alpha_s$,
 Equation~\ref{eqn:reconstruction} allows us to estimate the recordings
-at all locations in $\beta_s$, which we can define \textit{a priori}
+at all locations indexed by $\beta_s$, which we can define \textit{a priori}
 to include any locations we wish, throughout the brain.  This yields
@@
 $\bar{R}$, provided that we define $\bar{R}$ in advance to include the
-union of all of the locations in $\alpha_s$ and all of the locations
+union of all of the locations in $R_s$ and all of the locations
 at which we wish to estimate recordings (i.e., a timeseries of
@@
 covariance matrices.)  Also, note that
-Equation~\ref{eqn:reconstruction} directly requires computing a $T$ by $T$
+Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
 matrix, which can become computationally intractable when $T$ is very
@@
 Equation~\ref{eqn:reconstruction} to reconstruct activity at the
-held-out electrode location, using the correlation matrix trained on
-all other patients' data at $\hat{K}$, and using activity recorded
+held-out electrode location, using the correlation matrix learned from
+all other patients' data as $\hat{K}$, and using activity recorded
 from the other electrodes from the held-out patient as
@@
 %recording ($t(XXX) = XXX, p = XXX$).
-This example confirms that the SuperEEG algorithm recovers the recordings
-from this single electrode well.  Next, we quantify the algorithm's
-performance across the full dataset.
+This example confirms that the SuperEEG algorithm recovers the
+recordings from this single electrode well.  Next, we used this
+general approach to quantify the algorithm's performance across the
+full dataset.
 
@@
 
-For each held-out electrode, from each held-out patient in turn, we we
+For each held-out electrode, from each held-out patient in turn, we
 computed the average correlation (across recording sessions) between
@@
 across-participant reconstructions (i.e., computed using a correlation
-model derived from other patients' data) to reconstructions generated
+model learned from other patients' data) to reconstructions generated
 using a correlation model trained using the in-patient's data.  In
@@
 serve as an estimate of how well data from all of the other electrodes
-from a single patient may be used to estimate held-out data.  This
-allows us to ask how much information about the activity at a given
-electrode might be inferred through (a) volume conductance or other
-sources of ``leakage'' from activity patterns measured from the
-patient's other electrodes and (b) across-electrode correlations
-learned from that single patient.  As shown in
+from that single patient may be used to estimate held-out data from
+the same patient.  This allows us to ask how much information about
+the activity at a given electrode might be inferred through (a) volume
+conductance or other sources of ``leakage'' from activity patterns
+measured from the patient's other electrodes and (b) across-electrode
+correlations learned from that single patient.  As shown in
 Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
@@
 replicated this result separately for each of the two experiments from
-Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding,
-that when reconstructing held-out data from a given patient
-correlation models derived from \textit{other} patient's data yield
-higher reconstruction accuracy than correlation models derived from
-that patient, has two important implications.  First, it implies that
+Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding, that
+reconstructions of held-out data using correlation models learned from
+\textit{other} patient's data yield higher reconstruction accuracy
+than correlation models learned from the patient whose data is being
+reconstructed, has two important implications.  First, it implies that
 distant electrodes provide additional predictive power to the data
@@
 to come from the same patient.)  Second, it implies that the spatial
-correlations derived from the SuperEEG algorithm are, to some extent,
+correlations learned using the SuperEEG algorithm are, to some extent,
 similar across people.
@@
       Dataset 1.}  The across-patient distribution (black) reflects
-    reconstruction performance using a correlation model trained on
-    all but one patient, and then applied to the held-out patient's
-    data.  The within-patient distribution (gray) reflects performance using
-    a correlation model trained on the same patient who contributed
-    the to-be-reconstructed electrode.  \textbf{B. Distributions of
-      correlations for Dataset 2.}  This panel is in the same format
-    as Panel A, but reflects results obtained from Dataset 2.
-    \textbf{C.--D.  Reconstruction performance by location.} Each dot
-    reflects the location of a single implanted electrode from Dataset
-    1 (Panel C) or Dataset 2 (Panel D).  The dot colors denote the
-    average across-session correlation, using the across-patient
-    correlation model, between the observed and
-    reconstructed activity at the given electrode location.}
+    reconstruction accuracy (correlation) using a correlation model
+    learned from all but one patient's data, and then applied to that
+    held-out patient's data.  The within-patient distribution (gray)
+    reflects performance using a correlation model learned from the same
+    patient who contributed the to-be-reconstructed electrode.
+    \textbf{B. Distributions of correlations for Dataset 2.}  This
+    panel is in the same format as Panel A, but reflects results
+    obtained from Dataset 2.  The histograms aggregate data across
+    both Dataset 2 experiments; for results broken down by experiment
+    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
+      performance by location.} Each dot reflects the location of a
+    single implanted electrode from Dataset 1 (Panel C) or Dataset 2
+    (Panel D).  The dot colors denote the average across-session
+    correlation, using the across-patient correlation model, between
+    the observed and reconstructed activity at the given electrode
+    location.}
   \label{fig:corrmap}
@@
 The recordings we analyzed from Dataset 1 comprised data collected as
-the patients performed a variety of (essentially uncontrolled) tasks
+the patients performed a variety of (largely idiosyncratic) tasks
 throughout each day's recording session.  That we observed reliable
@@
 categorized list free recall task).  We wondered whether a correlation
-model trained using data only from one experiment might yield good
-predictions for data from the other experiment.  Further, we wondered
+model learned from data from one experiment might yield good
+predictions of data from the other experiment.  Further, we wondered
 about the extent to which it might be beneficial or harmful to combine
@@
 To test the task-specificity of the SuperEEG-derived correlation
-models, we repeated our within- and across-patient cross validation
+models, we repeated the above within- and across-patient cross validation
 procedures separately for Experiment 1 and Experiment 2 data from
-Dataset 2.  We then compared the reconstruction accuracies of held-out
+Dataset 2.  We then compared the reconstruction accuracies for held-out
 electrodes, for models trained within versus across the two
@@
 highest for the across-patient models limited to data from the same
-experiment (mean accuracy: $0.55$), next-highest for the
+experiment (mean accuracy: $0.55$); next-highest for the
 across-patient models that combined data across both experiments (mean
-accuracy: $0.50$), and lowest for models trained across task (mean
+accuracy: $0.50$); and lowest for models trained across task (mean
 accuracy: $0.37$).  This result also held for each of the Dataset 2
@@
 (when considering data from every patient; e.g.\
-Fig.~\ref{fig:corrmap}B, D), electrodes are not placed uniformly
+Fig.~\ref{fig:corrmap}C, D), electrodes are not placed uniformly
 throughout the brain.  For example, electrodes are more likely to be
@@
 Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
-MNI152 brain, we computed the proportion of electrodes contained
-within a 20 MNI unit radius sphere centered on that voxel.  We defined
-the \textit{density} at that location as this proportion.  Across
-Datasets 1 and 2, the electrode placement densities were similar
-(correlation by voxel: $r = 0.57, p < 10^{-10}$).  We wondered whether
-regions with good covererage might be associated with better
-reconstruction accuracy (e.g. Fig.~\ref{fig:corrmap}B, D indicate that
-many electrodes in the MTL have relatively high reconstruction
-accuracy, and occipital electrodes tend to have relatively low
-reconstruction accuracy).  To test whether this held more generally
-across the entire brain, for each dataset we computed the electrode
-placement density for each electrode from each patient (using the
-proportion of \textit{other} patients' electrodes within 20 MNI units
-of the given electrode).  We then correlated these density values with
-the across-patient reconstruction accuracies for each electrode.
-Contrary to our expectation, rather than positive correlations, we
-found weak (but reliable) negative correlations between reconstruction
-accuracy and density for both datasets (Dataset 1: $r = XXX, p = XXX$;
-Dataset 2: $r = -0.16, p < 10^{-10}$).  This indicates that the
-reconstruction accuracies we observed are not driven solely by
-sampling density, but rather may also reflect higher order properties
-of neural dynamics such as functional correlations between distant
+MNI152 brain, we computed the proportion of electrodes in the dataset
+that were contained within a 20 MNI unit radius sphere centered on
+that voxel.  We defined the \textit{density} at that location as this
+proportion.  Across Datasets 1 and 2, the electrode placement
+densities were similar (correlation by voxel:
+$r = XXX, p = XXX$).  We wondered whether regions with good
+covererage might be associated with better reconstruction accuracy
+(e.g. Fig.~\ref{fig:corrmap}C, D indicate that many electrodes in the
+MTL have relatively high reconstruction accuracy, and occipital
+electrodes tend to have relatively low reconstruction accuracy).  To
+test whether this held more generally across the entire brain, for
+each dataset we computed the electrode placement density for each
+electrode from each patient (using the proportion of \textit{other}
+patients' electrodes within 20 MNI units of the given electrode).  We
+then correlated these density values with the across-patient
+reconstruction accuracies for each electrode.  Contrary to our
+expectation, rather than positive correlations, we found weak (but
+reliable) negative correlations between reconstruction accuracy and
+density for both datasets (Dataset 1: $r = XXX, p = XXX$; Dataset 2:
+$r = -0.16, p < 10^{-10}$).  This indicates that the reconstruction
+accuracies we observed are not driven solely by sampling density, but
+rather may also reflect higher order properties of neural dynamics
+such as functional correlations between distant
 voxels~\citep{BetzEtal17b}.
@@
 across-patients cross validation test; black histograms in
-Fig.~\ref{fig:corrmap}A and C).  We labeled each patient's electrodes
+Fig.~\ref{fig:corrmap}A and B).  We labeled each patient's electrodes
 in each dataset with the average reconstruction accuracy for that
-patient.  In other words, we assigned every electrode from each
+patient.  In other words, we assigned every electrode from each given
 patient the same value, reflecting how well the activity patterns at
@@
 implanted near that location. This yielded a single map for each
-dataset, highlighting regions that are especially promising
+dataset, highlighting regions that are potentially promising
 implantation targets in terms of providing full-brain activity
@@
     electrodes from any patients with at least one electrode within 20
-    MNI units of the given voxel.  {B. Dataset 2 information score by
+    MNI units of the given voxel.  \textbf{B. Dataset 2 information score by
       voxel.}  This panel is in the same format as Panel A.
@@
 trained the correlation model using data from \textit{other}
-patients-- even when compared to a correlation model trained using the
+patients-- even when compared to a correlation model trained on the
 same patient's data.  Third, we resolved ambiguities in the data by
@@
 Electrodes are typically implanted to maximize coverage of suspected
-epileptogenic tissue.  However, our findings suggest that this approach
-could be further optimized.  Specifically, one could leverage not only
-the non-invasive recordings taken during an initial monitoring period
-(as is currently done routinely), but also recordings collected from other
-patients.  We could then ask: given everything we know about the other
-patients and from the scalp recordings of this new patient, where
-should we place a fixed number of electrodes to maximize our ability
-to map seizure foci?  As shown in Figure~\ref{fig:informap}, recordings
-from different locations are differently informative in terms of
-reconstructing the spatiotemporal patterns throughout the brain.
-This property might be leveraged in decisions about where to
+epileptogenic tissue.  However, our findings suggest that this
+approach could be further optimized.  Specifically, one could leverage
+not only the non-invasive recordings taken during an initial
+monitoring period (as is currently done routinely), but also
+recordings collected from other patients.  We could then ask: given
+what we learn from other patients' data (and potentially from the
+scalp EEG recordings of this new patient), where should we place a
+fixed number of electrodes to maximize our ability to map seizure
+foci?  As shown in Figure~\ref{fig:informap}, recordings from
+different locations are differently informative in terms of
+reconstructing the spatiotemporal activity patterns throughout the
+brain.  This property might be leveraged in decisions about where to
 surgically implant electrodes in future patients.
@@
 an alternative approach that leverages the rich correlational
-structure of a large dataset of human intracranial recordings.  In
+structure of two large datasets of human intracranial recordings.  In
 doing so, we are one step closer to observing, and perhaps

### 2018-10-08 code/notebooks/plot.py
change paths and update figs

@@ -138,7 +138,7 @@ def plot_times_series(time_data_df, lower_bound, upper_bound, outfile = None):
     fig, ax = plt.subplots()
     fig.set_size_inches(10, 8)
     sns.set_style("white")
-    time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['actual'].plot(ax=ax, color='k', lw=1, fontsize=21)
+    time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['actual'].plot(ax=ax, color='b', lw=1, fontsize=21)
     time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['predicted'].plot(ax=ax, color='r', lw=1)
     ax.legend(['Observed', 'Reconstructed'], fontsize=21)
     ax.set_xlabel("Time (s)", fontsize=21)
@@ -149,14 +149,8 @@ def plot_times_series(time_data_df, lower_bound, upper_bound, outfile = None):
     print(xvals)
     xvals = np.asarray([750, 1000, 1250, 1500, 1750, 2000, 2250, 2500, 2750])
 
-    #ax.set_yticklabels([int(np.round(x / 2, 1)) for x in yvals])
-    #ax.set_xticklabels([math.ceil(np.round(x / 250, 4)) for x in xvals])
     ax.set_xticklabels([np.round(x / 250, 4) for x in xvals])
 
-    # for index, label in enumerate(ax.xaxis.get_ticklabels()):
-    #     if index == 0:
-    #         print(index)
-    #         label.set_visible(True)
     ax.spines['right'].set_visible(False)
     ax.spines['top'].set_visible(False)
 

### 2018-10-09 code/notebooks/plot.py
redo paths and figures, updated pvals, and started the new best locs analysis

@@ -720,3 +720,31 @@ def plot_hist_by_patient(dataframe, X, bins=20, title=None, outfile=None):
     print('mean: ' + str(np.round(df[X].mean(),3)))
     if outfile:
         plt.savefig(outfile)
+
+def plot_contour(dataframe, X, Y, title=None, outfile=None):
+
+    sns.set_style("white")
+    g = (sns.jointplot(x=X, y=Y,data=dataframe, kind="kde", color='k',
+                       height=8).set_axis_labels(X, 'Correlation', fontsize=24))
+    ax = g.ax_joint
+    ax.tick_params(axis='x', labelsize=18)
+    ax.tick_params(axis='y', labelsize=18)
+    #ax.set_ylim(-1, 1)
+    #ax = plt.gca()
+    for index, label in enumerate(ax.xaxis.get_ticklabels()):
+        if index % 2 != 0:
+            label.set_visible(False)
+    for index, label in enumerate(ax.yaxis.get_ticklabels()):
+        if index % 2 == 0:
+            label.set_visible(False)
+    left, width = .55, .5
+    bottom, height = .05, .5
+    rstat = stats.pearsonr(dataframe[X], dataframe[Y])
+    ax.text(left, bottom, 'r = ' + str(np.round(rstat[0],2)),
+            horizontalalignment='left',
+            verticalalignment='bottom',
+            transform=ax.transAxes, fontsize=18)
+    print(rstat)
+    plt.tight_layout()
+    if outfile:
+        plt.savefig(outfile)

### 2018-10-09 paper/main.tex
swapped in newer figures for main text; supp figures still in progress
checking in remaining edits from meeting with lucy

@@
 
-\newcommand{\taskrecon}{S1}
-\newcommand{\perexpcorrmaps}{S2}
-\newcommand{\perexptaskrecon}{S3}
-\newcommand{\perexptaskreconseparated}{S4}
-\newcommand{\suppstats}{S5}
+\newcommand{\perexpcorrmaps}{S1}
+\newcommand{\perexptaskrecon}{S2}
+\newcommand{\perexptaskreconseparated}{S3}
+\newcommand{\suppstats}{S4}
 
@@
 location throughout the brain, including those without dense electrode
-coverage (which implies a large value of $\lambda$). Using our prior
-work as a guide~\citep{MannEtal14b, MannEtal18}, we set $\lambda = 20$,
-although this could in theory be optimized, e.g., using cross
-validation or a formal model~\citep[e.g.,][]{MannEtal18}.
+coverage (which implies a large value of $\lambda$).  Here we set
+$\lambda = 20$, guided in part by our prior work~\citep{MannEtal14b,
+  MannEtal18}, and in part by examining the brain coverage with
+non-zero weights achieved by placing RBFs at each electrode location
+in Dataset 1 and taking the sum (across all electrodes) at each voxel
+in a 4~mm$^3$ MNI brain.  (We then held $\lambda$ fixed for our
+analyses of Dataset 2.)  We note that this value could in theory be
+further optimized, e.g., using cross validation or a formal
+model~\citep[e.g.,][]{MannEtal18}.
 
@@
 example patient's six recording sessions.  The two traces match
-closely ($r = XXX, p = XXX$).
-%Where the traces do not align, the predicted
-%trace tends to be rounded towards zero, reflecting the zero-mean prior
-%implicit in Equation~\ref{eqn:reconstruction} (paired $t$-test
-%comparing absolute values of actual versus predicted voltages:
-%$t(XXX) = XXX, p = XXX$).
-Figure~\ref{fig:recon}B displays a
+closely ($r = XXX, p = XXX$).  Figure~\ref{fig:recon}B displays a
 two-dimensional histogram of the actual versus reconstructed voltages
-for the entire 14.2 total hours of recordings from the example electrode
-(correlation: $r = XXX, p = XXX$).
-%Like in the shorter example trace
-%shown in panel A, the reconstructed voltages throughout the full
-%recording tended to be smaller in magnitude than the original
-%recording ($t(XXX) = XXX, p = XXX$).
-This example confirms that the SuperEEG algorithm recovers the
-recordings from this single electrode well.  Next, we used this
-general approach to quantify the algorithm's performance across the
-full dataset.
+for the entire 14.2 total hours of recordings from the example
+electrode (correlation: $r = XXX, p = XXX$).  This example confirms
+that the SuperEEG algorithm recovers the recordings from this single
+electrode well.  Next, we used this general approach to quantify the
+algorithm's performance across the full dataset.
 
@@
     electrodes from any patients with at least one electrode within 20
-    MNI units of the given voxel.  \textbf{B. Dataset 2 information score by
-      voxel.}  This panel is in the same format as Panel A.
+    MNI units of the given voxel.  \textbf{B. Dataset 2 information
+      score by voxel.}  This panel is in the same format as Panel A.
+    In Panels A and B the contours indicate the intersections between
+    the top 10\% most informative voxels in each map.
     \textbf{C. Correspondence in information scores by voxel across

### 2018-10-09 code/notebooks/plot.py
update to supp 4, rename e_corrs to pyFR_df, rename groupby columns, and cluster analysis for ram

@@ -724,12 +724,13 @@ def plot_hist_by_patient(dataframe, X, bins=20, title=None, outfile=None):
 def plot_contour(dataframe, X, Y, title=None, outfile=None):
 
     sns.set_style("white")
-    g = (sns.jointplot(x=X, y=Y,data=dataframe, kind="kde", color='k',
-                       height=8).set_axis_labels(X, 'Correlation', fontsize=24))
+
+    g = (sns.jointplot(x=X, y=Y,data=dataframe, kind="reg", color='k',
+                       height=8).set_axis_labels(X, 'z-transformed correlation', fontsize=24))
     ax = g.ax_joint
     ax.tick_params(axis='x', labelsize=18)
     ax.tick_params(axis='y', labelsize=18)
-    #ax.set_ylim(-1, 1)
+    ax.set_ylim(0, 1.5)
     #ax = plt.gca()
     for index, label in enumerate(ax.xaxis.get_ticklabels()):
         if index % 2 != 0:
@@ -737,13 +738,13 @@ def plot_contour(dataframe, X, Y, title=None, outfile=None):
     for index, label in enumerate(ax.yaxis.get_ticklabels()):
         if index % 2 == 0:
             label.set_visible(False)
-    left, width = .55, .5
+    left, width = .35, .5
     bottom, height = .05, .5
     rstat = stats.pearsonr(dataframe[X], dataframe[Y])
-    ax.text(left, bottom, 'r = ' + str(np.round(rstat[0],2)),
+    ax.text(left, bottom, 'r = ' + str(np.round(rstat[0],2)) + ', p = '+ str(np.round(rstat[1],2)),
             horizontalalignment='left',
             verticalalignment='bottom',
-            transform=ax.transAxes, fontsize=18)
+            transform=ax.transAxes, fontsize=24)
     print(rstat)
     plt.tight_layout()
     if outfile:

### 2018-10-10 code/notebooks/plot.py
code for network diversity

@@ -520,8 +520,10 @@ def most_informative_locs_plot(df, vox_size=5, width=10, outfile=None):
 
     most_info = np.array([])
 
+    z_df = df.copy(deep=True)
+    z_df['Correlation'] = r2z(z_df['Correlation'])
     for l in sub_locs:
-        most_info = np.append(most_info, df['Correlation'][point_tree.query_ball_point(l, width)].mean())
+        most_info = np.append(most_info, z_df['Correlation'][point_tree.query_ball_point(l, width)].mean())
 
     bo_nii = se.Brain(data=np.atleast_2d(z2r(most_info)), locs=sub_locs)
     nii_bo = se.helpers._brain_to_nifti(bo_nii, sub_nii)
@@ -543,10 +545,13 @@ def most_informative_locs(df, vox_size=5, width=10):
 
     most_info = np.array([])
 
+    z_df = df.copy(deep=True)
+    z_df['Correlation'] = r2z(z_df['Correlation'])
     for l in sub_locs:
-        most_info = np.append(most_info, df['Correlation'][point_tree.query_ball_point(l, width)].mean())
 
-    return most_info
+        most_info = np.append(most_info, z_df['Correlation'][point_tree.query_ball_point(l, width)].mean())
+
+    return z2r(most_info)
 
 def plot_2d_corr_hist(df, outfile=None):
 
@@ -557,7 +562,7 @@ def plot_2d_corr_hist(df, outfile=None):
     g = (sns.jointplot('RAM', 'PyFR', df, kind="kde", color='k', height=8).set_axis_labels('RAM', 'PyFR', fontsize=30))
     ax = g.ax_joint
 
-    left, width = .05, .5
+    left, width = .35, .5
     bottom, height = .1, .5
     rstat = stats.pearsonr(df['RAM'], df['PyFR'])
     ax.text(left, bottom, 'r = ' + str(np.round(rstat[0],2)) + '   p < '+ str(10**-10),
@@ -595,7 +600,9 @@ def plot_split_violin(df, legend=True, yticks=True, outfile=None):
     ax.set_xticklabels(['Within', 'Across','All'])
     ax.set_xlabel('Experiment', fontsize=30)
 
-    yposlist_df = df.groupby(['Experiment', 'Subject'])['Correlation'].mean()
+    z_df = df.copy(deep=True)
+    z_df['Correlation'] = r2z(z_df['Correlation'])
[…]

### 2018-10-10 paper/_region_.tex
redo paths and figures, updated pvals, and started the new best locs analysis
WIP main text.  up to density stats

--- 2018-10-08 paper/main.tex
@@
-\documentclass[11pt]{article}
+\message{ !name(main.tex)}\documentclass[11pt]{article}
 \usepackage[numbers, square, sort, compress]{natbib}
@@
 \begin{document}
+
+\message{ !name(main.tex) !offset(-3) }
 
@@
 patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  Each recording session lasted from XXX--XXX hours
+  MannEtal12}.  Each recording session lasted from 0.3--14.2 hours
 (Fig.~\suppstats A), and includes data recorded roughly from when the
@@
 be able to generate task-general predictions.  Dataset 2 comprised
-multi-session recordings from XXX electrodes implanted in the brains
-of XXX epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
+multi-session recordings from 3159 electrodes implanted in the brains
+of 24 epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
   KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
-  KuceEtal18}.  Each recording session lasted from XXX--XXX hours
+  KuceEtal18}.  Each recording session lasted from .4--6.6 hours
 (Fig.~\suppstats B).  Whereas Dataset 1 included recordings taken during a
@@
 from each patient.  For Dataset 1, this yielded clean recordings from
-XXX electrodes implanted throughout the brains of XXX patients
+4168 electrodes implanted throughout the brains of 67 patients
 (Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
-recordings from 2975 electrodes from 24 patients.  Each individual
+recordings from 3159 electrodes from 24 patients.  Each individual
 patient contributes electrodes from a limited set of brain locations,
@@
 
-To illustrate our approach, we first examine and individual held-out
+To illustrate our approach, we first examine an individual held-out
 raw LFP trace and its associated SuperEEG-derived reconstruction.
@@
 example patient's six recording sessions.  The two traces match
-closely ($r = XXX, p = XXX$).
-%Where the traces do not align, the predicted
-%trace tends to be rounded towards zero, reflecting the zero-mean prior
-%implicit in Equation~\ref{eqn:reconstruction} (paired $t$-test
-%comparing absolute values of actual versus predicted voltages:
-%$t(XXX) = XXX, p = XXX$).
-Figure~\ref{fig:recon}B displays a
+closely ($r = 0.869, p = 10\textsuperscript{-10]$).  Figure~\ref{fig:recon}B displays a
 two-dimensional histogram of the actual versus reconstructed voltages
-for the entire 14.2 total hours of recordings from the example electrode
-(correlation: $r = XXX, p = XXX$).
-%Like in the shorter example trace
-%shown in panel A, the reconstructed voltages throughout the full
-%recording tended to be smaller in magnitude than the original
-%recording ($t(XXX) = XXX, p = XXX$).
-This example confirms that the SuperEEG algorithm recovers the
-recordings from this single electrode well.  Next, we used this
-general approach to quantify the algorithm's performance across the
-full dataset.
+for the entire 14.2 total hours of recordings from the example
+electrode (correlation: $r = 0.909, p = 10\textsuperscript{-10}$).  This example confirms
+that the SuperEEG algorithm recovers the recordings from this single
+electrode well.  Next, we used this general approach to quantify the
+algorithm's performance across the full dataset.
 
@@
 \end{document}
+
+\message{ !name(main.tex) !offset(-850) }

### 2018-10-10 paper/main.tex
WIP main text.  up to density stats

@@
 example patient's six recording sessions.  The two traces match
-closely ($r = XXX, p = XXX$).  Figure~\ref{fig:recon}B displays a
+closely ($r = 0.869, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
 two-dimensional histogram of the actual versus reconstructed voltages
 for the entire 14.2 total hours of recordings from the example
-electrode (correlation: $r = XXX, p = XXX$).  This example confirms
+electrode (correlation: $r = 0.909, p < 10^{-10}$).  This example confirms
 that the SuperEEG algorithm recovers the recordings from this single
@@
 Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations
-was centered well above zero (mean: XXX; $t$-test comparing mean of
+was centered well above zero (mean: 0.52; $t$-test comparing mean of
 distribution of $z$-transformed per-electrode correlation coefficients
-to 0: $t(XXX) = XXX, p = XXX$), indicating that the SuperEEG algorithm
+to 0: $t(66) = 25.08, p < 10^{-30}$), indicating that the SuperEEG algorithm
 recovers held-out activity patterns substantially better than random
@@
 Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
-within-patient correlations was centered well above zero (mean: XXX;
+within-patient correlations was centered well above zero (mean: 0.32;
 $t$-test comparing mean of distribution of $z$-transformed
-per-electrode correlation coefficients to 0: $t(XXX) = XXX, p = XXX$).
+per-electrode correlation coefficients to 0: $t(66) = 15.16, p < 10^{-20}$).
 However, the across-patient correlations were substantially higher
 ($t$-test comparing average $z$-transformed within versus across
-patient electrode correlations: $t(XXX) = XXX, p = XXX$).  This is an
+patient electrode correlations: $t(66) = 9.62, p < 10^{-10}$).  This is an
 especially conservative test, given that the across-patient SuperEEG
@@
 within-patient models trained on data only from the subject
-contributing the given electrode ($t$s$(XXX) > XXX, p$s$ < XXX$).  All
+contributing the given electrode ($t$s$(24) > 6.50, p$s$ < 10^{-5}$).  All
 reconstruction accuracies also reliably exceeded chance performance
-($t$s$(XXX) > XXX, p$s$ < XXX$).  Average reconstruction accuracy was
+($t$s$(24) > 8.00, p$s$ < 10^{-8}$).  Average reconstruction accuracy was
 highest for the across-patient models limited to data from the same
-experiment (mean accuracy: $0.55$); next-highest for the
+experiment (mean accuracy: $0.68$); next-highest for the
 across-patient models that combined data across both experiments (mean
-accuracy: $0.50$); and lowest for models trained across task (mean
-accuracy: $0.37$).  This result also held for each of the Dataset 2
+accuracy: $0.61$); and lowest for models trained across task (mean
+accuracy: $0.47$).  This result also held for each of the Dataset 2
 experiments individually (Fig.~\perexptaskreconseparated).  Taken

### 2018-10-10 code/notebooks/plot.py

@@ -263,6 +263,16 @@ def normalizeRows(M):
 def plot_2_histograms(df, X, Y, xticks=True, legend=True, outfile=None):
 
     grouped_results = df.groupby('Subject')[Y, X].mean()
+    one_sided_t_across = stats.ttest_1samp(grouped_results[Y],  0)
+    one_sided_t_within = stats.ttest_1samp(grouped_results[X],  0)
+
+    print('one sided t test for across: ')
+    print(one_sided_t_across)
+
+
+    print('one sided t test for within: ')
+    print(one_sided_t_within)
+
     t_stat_group = stats.ttest_rel(grouped_results[Y],grouped_results[X])
 
     fig = plt.gcf()
@@ -343,6 +353,7 @@ def plot_2_histograms(df, X, Y, xticks=True, legend=True, outfile=None):
     if outfile:
         plt.savefig(outfile)
 
+    print('t test: ')
     print(t_stat_group)
 
 def interp_corr_old(locs, corrs, width=10, vox_size=10, outfile=None):

### 2018-10-10 paper/main.tex
updated stats for results

@@
 densities were similar (correlation by voxel:
-$r = XXX, p = XXX$).  We wondered whether regions with good
+$r = 0.56, p < 10^{-10}$).  We wondered whether regions with good
 covererage might be associated with better reconstruction accuracy
@@
 reliable) negative correlations between reconstruction accuracy and
-density for both datasets (Dataset 1: $r = XXX, p = XXX$; Dataset 2:
-$r = -0.16, p < 10^{-10}$).  This indicates that the reconstruction
+density for both datasets (Dataset 1: $r = -0.07, p < 10^{-5}$; Dataset 2:
+$r = -0.18, p < 10^{-10}$).  This indicates that the reconstruction
 accuracies we observed are not driven solely by sampling density, but
@@
 both datasets were similar (voxelwise correlation between information
-scores across the two datasets: $r = XXX, p = XXX$).  While the
+scores across the two datasets: $r = 0.23, p < 10^{-10}$).  While the
 correspondence between the two maps was not perfect, our finding that
@@
 the notion that different brain areas are differently informative
-about full-brain activity patterns.  Further, regions like XXX, XXX,
-and XXX that exhibited strong information scores in both datasets may
+about full-brain activity patterns.  Further, regions like the right post
+central gyrus, right supramarginal gyrus,
+and the right nucleus accumbens that exhibited strong information scores in both datasets may
 be especially promising implantation targets.

### 2018-10-10 code/notebooks/plot.py

@@ -587,6 +587,7 @@ def plot_2d_corr_hist(df, outfile=None):
     ax.yaxis.set_major_locator(matplotlib.ticker.MaxNLocator(nbins=5))
 
     plt.tight_layout()
+    print(rstat)
     if not outfile is None:
         plt.savefig(outfile)
     else:

### 2018-10-10 paper/main.tex
small changes in read through

@@
 large (e.g., for the patient highlighted in Fig.~\ref{fig:recon}, $T =
-20458799$). However, because Equation~\ref{eqn:reconstruction} is time
+12786750$). However, because Equation~\ref{eqn:reconstruction} is time
 invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
@@
 Figure~\ref{fig:recon}A displays the observed LFP from the red
-electrode in Figure~\ref{fig:methods}A (red), and its associated
-reconstruction (blue), during a 5~s time window during one of the
+electrode in Figure~\ref{fig:methods}A (blue), and its associated
+reconstruction (red), during a 5~s time window during one of the
 example patient's six recording sessions.  The two traces match
@@
       electrode.} \textbf{A. Example LFP.}  A 5~s recording from the
-    red electrode in Figure~\ref{fig:methods}A is displayed in red,
+    red electrode in Figure~\ref{fig:methods}A is displayed in blue,
     and the reconstructed LFP during the same time window is shown in
-    blue.  \textbf{B. Observed versus reconstructed LFP over
+    red.  \textbf{B. Observed versus reconstructed LFP over
       14.2~hours.}  The two-dimensional histogram reflects the
@@
 are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many
-aspects of brain anatomy, including white matter structure, is largely
+aspects of brain anatomy, including white matter structure, are largely
 preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13,
-  MoriEtal08} There are several possible means of reconciling this
+  MoriEtal08}. There are several possible means of reconciling this
 apparent inconsistency between dynamic person- and task-specific

### 2018-10-11 paper/_region_.tex
edits to paper and figures

@@
 patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  Each recording session lasted from 0.3--14.2 hours
-(Fig.~\suppstats A), and includes data recorded roughly from when the
-patients woke up each morning, to before they went to sleep at the end
-of each day.  In addition to typical bed-ridden hospital patient
+  MannEtal12}.  Each recording session lasted from {0.3}--14.2 hours
+(Fig.~\suppstats A), and includes data from a list-learning memory experiment
+for up to one hour varying by patient with additional buffer time in
+which the patients performed typical bed-ridden hospital
 activities (e.g., lying in bed, reading, watching television, using
 personal electronic devices, listening to music, visiting with family
-and friends, etc.), the patients also performed a variety of
-experimental cognitive tasks throughout their day (primarily
-list-learning memory tasks).  For the purposes of the Dataset 1
+and friends, etc.).  For the purposes of the Dataset 1
 analyses presented here, we aggregated all data across each recording
@@
 be able to generate task-general predictions.  Dataset 2 comprised
-multi-session recordings from 3159 electrodes implanted in the brains
-of 24 epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
+multi-session recordings from 4436 electrodes implanted in the brains
+of 40 epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
   KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
-  KuceEtal18}.  Each recording session lasted from .4--6.6 hours
+  KuceEtal18}.  Each recording session lasted from {0.4}--6.6 hours
 (Fig.~\suppstats B).  Whereas Dataset 1 included recordings taken during a
@@
 Figure~\ref{fig:recon}A displays the observed LFP from the red
-electrode in Figure~\ref{fig:methods}A (red), and its associated
-reconstruction (blue), during a 5~s time window during one of the
+electrode in Figure~\ref{fig:methods}A (blue), and its associated
+reconstruction (red), during a 5~s time window during one of the
 example patient's six recording sessions.  The two traces match
-closely ($r = 0.869, p = 10\textsuperscript{-10]$).  Figure~\ref{fig:recon}B displays a
+closely ($r = 0.869, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
 two-dimensional histogram of the actual versus reconstructed voltages
 for the entire 14.2 total hours of recordings from the example
-electrode (correlation: $r = 0.909, p = 10\textsuperscript{-10}$).  This example confirms
+electrode (correlation: $r = 0.909, p < 10^{-10}$).  This example confirms
 that the SuperEEG algorithm recovers the recordings from this single
@@
 
-\message{ !name(main.tex) !offset(-850) }
+\message{ !name(main.tex) !offset(-849) }

### 2018-10-11 paper/main.tex
edits to paper and figures

@@
 \newcommand{\suppstats}{S4}
+\newcommand{\intersectmap}{S5}
 
@@
 patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  Each recording session lasted from 0.3--14.2 hours
-(Fig.~\suppstats A), and includes data recorded roughly from when the
-patients woke up each morning, to before they went to sleep at the end
-of each day.  In addition to typical bed-ridden hospital patient
-activities (e.g., lying in bed, reading, watching television, using
-personal electronic devices, listening to music, visiting with family
-and friends, etc.), the patients also performed a variety of
-experimental cognitive tasks throughout their day (primarily
-list-learning memory tasks).  For the purposes of the Dataset 1
+  MannEtal12}.  Each recording session lasted from {0.2}--{3.0}
+(total recording time: {0.3}--14.2 hours; Fig.~\suppstats A), and includes data from a list-learning memory experiment
+for up to one hour varying by patient with additional buffer time in
+which the patients performed typical bed-ridden hospital
+activities.  For the purposes of the Dataset 1
 analyses presented here, we aggregated all data across each recording
@@
 be able to generate task-general predictions.  Dataset 2 comprised
-multi-session recordings from 3159 electrodes implanted in the brains
-of 24 epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
+multi-session recordings from 4436 electrodes implanted in the brains
+of 40 epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
   KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
-  KuceEtal18}.  Each recording session lasted from .4--6.6 hours
-(Fig.~\suppstats B).  Whereas Dataset 1 included recordings taken during a
+  KuceEtal18}.  Each recording session lasted from {0.4}--2.2 hours
+(total recording time: {0.4}--6.6 hours; Fig.~\suppstats B).  Whereas Dataset 1 included recordings taken during a
 wide variety of behaviors, Dataset 2 included recordings taken as each
@@
 example patient's six recording sessions.  The two traces match
-closely ($r = 0.869, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
+closely ($r = 0.86, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
 two-dimensional histogram of the actual versus reconstructed voltages
 for the entire 14.2 total hours of recordings from the example
-electrode (correlation: $r = 0.909, p < 10^{-10}$).  This example confirms
+electrode (correlation: $r = 0.91, p < 10^{-10}$).  This example confirms
 that the SuperEEG algorithm recovers the recordings from this single
@@
 was centered well above zero (mean: 0.52; $t$-test comparing mean of
-distribution of $z$-transformed per-electrode correlation coefficients
-to 0: $t(66) = 25.08, p < 10^{-30}$), indicating that the SuperEEG algorithm
+distribution of $z$-transformed average patient correlation coefficients
+to 0: $t(66) = 25.08, p < 10^{-10}$), indicating that the SuperEEG algorithm
 recovers held-out activity patterns substantially better than random
@@
 $t$-test comparing mean of distribution of $z$-transformed
-per-electrode correlation coefficients to 0: $t(66) = 15.16, p < 10^{-20}$).
+average patient correlation coefficients to 0: $t(66) = 15.16, p < 10^{-10}$).
 However, the across-patient correlations were substantially higher
@@
 both datasets were similar (voxelwise correlation between information
-scores across the two datasets: $r = 0.23, p < 10^{-10}$).  While the
+scores across the two datasets: $r = 0.03, p < 10^{-10}$).  While the
 correspondence between the two maps was not perfect, our finding that
@@
 the notion that different brain areas are differently informative
-about full-brain activity patterns.  Further, regions like the right post
-central gyrus, right supramarginal gyrus,
+about full-brain activity patterns.  Further, we found the
+intersection of the top 10\% of the most informative voxels between
+the two datasets (Fig.~\intersectmap) and found gray matter regions like the right postcentral gyrus, right supramarginal gyrus,
 and the right nucleus accumbens that exhibited strong information scores in both datasets may
@@
       score by voxel.}  This panel is in the same format as Panel A.
-    In Panels A and B the contours indicate the intersections between
+    In both panels the contours indicate the intersections between
     the top 10\% most informative voxels in each map.
@@
 We have published an open-source toolbox implementing the SuperEEG
-algorithm.  It may be downloaded \href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}.
+algorithm.  It may be downloaded
+\href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}. Additionally,
+we have provided notebooks for all analyses and figures reported
+here.
 

### 2018-10-11 paper/supporting_information.tex
add compiled supporting info pdf
edits to paper and figures

@@
 
-\title{\textit{Supporting Information for}: Towards human Super EEG?}
+\title{\textit{Extended data for}: Towards human Super EEG?}
 \author{Lucy L.
@@
 
-\begin{figure}[p!]
+\begin{figure}[phtb]
 \centering
@@
 
-\begin{figure}[p!]
+\begin{figure}[ptb]
 \centering
@@
 
+\begin{figure}[ptb]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_4}
+\caption{\small \textbf{Reconstruction accuracy predicted by data
+    features for each dataset.} \textbf{A.-F. \& G.-L.  Correspondence
+    between average
+    reconstruction accuracy
+    and data feature for datasets 1 and 2.} The scatterplots display the z-transformed
+  average patient correlation coefficient versus different features of
+  the data (\textbf{A. & G.} total electrodes, \textbf{B. & H.}  proportion thresholded, \textbf{C. & I.} total recording time,
+  \textbf{D. & J.}  number thresholded, \textbf{E. & K.}  number of sessions, and \textbf{F. & L.}  average session
+  length). The one-dimensional histograms report the distribution of
+  the z-transformed correlation coeffiencients and the associated data
+feature.}
+\label{fig:supplemental_4}
+\end{figure}
+
+\begin{figure}[ptb]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_5}
+\caption{\small \textbf{ Top 10\% most informative voxels.}
+ Voxels in yellow indicate the intersections between
+    the top 10\% most informative voxels in each brain map from Figure
+    5, indicated by the white contours.}
+\label{fig:supplemental_5}
+\end{figure}
+
 % \newpage

### 2018-10-11 code/notebooks/plot.py
clean up of notebooks and plot.py code

@@ -135,25 +135,23 @@ def plot_times_series(time_data_df, lower_bound, upper_bound, outfile = None):
     results : plotted timeseries
          If outfile in arguments, the plot is saved.  Otherwise, it the plot is shown.
     """
+
+    data = time_data_df.loc[(time_data_df['time'] >= lower_bound) & (time_data_df['time'] < upper_bound)]
     fig, ax = plt.subplots()
     fig.set_size_inches(10, 8)
     sns.set_style("white")
-    time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['actual'].plot(ax=ax, color='b', lw=1, fontsize=21)
-    time_data_df[(time_data_df['time'] > lower_bound) & (time_data_df['time'] < upper_bound)]['predicted'].plot(ax=ax, color='r', lw=1)
-    ax.legend(['Observed', 'Reconstructed'], fontsize=21)
-    ax.set_xlabel("Time (s)", fontsize=21)
-    ax.set_ylabel("Voltage (normalized)", fontsize=21)
-    ax.tick_params(axis='x', labelsize=18)
-    ax.tick_params(axis='y', labelsize=18)
-    xvals = ax.get_xticks()
-    print(xvals)
-    xvals = np.asarray([750, 1000, 1250, 1500, 1750, 2000, 2250, 2500, 2750])
 
-    ax.set_xticklabels([np.round(x / 250, 4) for x in xvals])
+    plt.plot(data['time'], data['predicted'], 'r')
+    plt.plot(data['time'], data['actual'], 'b')
+    plt.legend(['Reconstructed','Observed'], fontsize=21)
+    plt.gca().set_xticks(np.linspace(lower_bound, upper_bound, np.round(upper_bound-lower_bound)+1))
+    plt.xlabel('Time (s)', fontsize=21)
+    plt.ylabel('Voltage (normalized)', fontsize=21)
+    plt.gca().tick_params(axis='x', labelsize=18)
+    plt.gca().tick_params(axis='y', labelsize=18)
 
     ax.spines['right'].set_visible(False)
     ax.spines['top'].set_visible(False)
-
     plt.tight_layout()
     if not outfile is None:
         plt.savefig(outfile)
@@ -356,7 +354,7 @@ def plot_2_histograms(df, X, Y, xticks=True, legend=True, outfile=None):
     print('t test: ')
     print(t_stat_group)
 
[…]

### 2018-10-11 paper/main.tex
checking in minor edits

@@
       Terminal Experiment}~\cite{Sawy95}} entails measuring ongoing
-  neural activity with perfect precision and at arbitrarily high
-  spatiotemporal resolution.  Although true SuperEEG is impossible
-  using existing methods, here we present a model-based method for
-  \textit{inferring} neural activity at millimeter-scale spatial
-  resolutions and millisecond-scale temporal resolutions using
-  standard human intracranial recordings.  Our approach assumes that
-  different people's brains exhibit similar spatial correlations, and
-  that (all else being equal) neural activity at nearby locations will
-  tend to be similar.  One can then ask, for an arbitrary individual's
-  brain: given recordings from a limited set of locations in that
-  individual's brain, along with the observed spatial correlations
-  learned from other people's recordings, how much can be inferred
-  about ongoing activity at \textit{other} locations in that
+  neural activity throughout the entire living brain with perfect
+  precision and arbitrarily high spatiotemporal resolution.  Although
+  true SuperEEG is impossible using existing methods, here we present
+  a model-based method for \textit{inferring} full-brain neural
+  activity at millimeter-scale spatial resolutions and
+  millisecond-scale temporal resolutions using standard human
+  intracranial recordings.  Our approach assumes that different
+  people's brains exhibit similar spatial correlations, and that
+  activity and correlation patterns are spatially smooth.  One can
+  then ask, for an arbitrary individual's brain: given recordings from
+  a limited set of locations in that individual's brain, along with
+  the observed spatial correlations learned from other people's
+  recordings, how much can be inferred about ongoing activity at
+  \textit{other} locations in that
   individual's brain?\\\\
@@
 (intracranial EEG; iEEG).  However, these intracranial approaches also
-require compromise: the high spatiotemporal resolutions of
+require compromise: the high spatiotemporal resolution of
 intracranial recordings comes at the cost of substantially reduced
@@
 person's brain (i.e., independent of their electrode placements).  We
-test SuperEEG approach using two large datasets of intracranial
+test our SuperEEG approach using two large datasets of intracranial
 recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
@@
 that influence how accurately activity may be estimated (recovered),
-which may have important implications for electrode design and
+which may have implications for electrode design and
 placement in neurosurgical applications.
@@
 patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  Each recording session lasted from {0.2}--{3.0}
-(total recording time: {0.3}--14.2 hours; Fig.~\suppstats A), and includes data from a list-learning memory experiment
-for up to one hour varying by patient with additional buffer time in
-which the patients performed typical bed-ridden hospital
-activities.  For the purposes of the Dataset 1
-analyses presented here, we aggregated all data across each recording
-session, ignoring the particular activities or tasks the patients were
-performing at any given moment.  We used Dataset 1 to develop our main
-SuperEEG approach, and to examine the extent to which SuperEEG might
-be able to generate task-general predictions.  Dataset 2 comprised
-multi-session recordings from 4436 electrodes implanted in the brains
-of 40 epilepsy patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17,
-  KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
-  KuceEtal18}.  Each recording session lasted from {0.4}--2.2 hours
-(total recording time: {0.4}--6.6 hours; Fig.~\suppstats B).  Whereas Dataset 1 included recordings taken during a
-wide variety of behaviors, Dataset 2 included recordings taken as each
-patient performed each of two memory tasks: a random word list free
-recall task and a categorized word list free recall task.  We used
-Dataset 2 to further examine the ability of SuperEEG to generalize its
+  MannEtal12}.  Each recording session lasted from 0.2--3~h (total
+recording time: 0.3--14.2~h; Fig.~\suppstats A).  During each
+recording session, the patients participated in a free recall list
+learning task, which lasted for up to approximately 1~h.  In addition,
+the recordings included ``buffer'' time (the length varied by patient)
+before and after each experimental session, during which the patients
+went about their regular hospital activities (confined to their
+hospital room, and primarily in bed).  These additional activities
+included interactions with medical staff and family, watching
+television, reading, and other similar activities.  For the purposes
+of the Dataset 1 analyses presented here, we aggregated all data
+across each recording session, including recordings taken during the
+main experimental task as well as during non-experimental time.  We
+used Dataset 1 to develop our main SuperEEG approach, and to examine
+the extent to which SuperEEG might be able to generate task-general
+predictions.  Dataset 2 comprised multi-session recordings from 4436
+electrodes implanted in the brains of 40 epilepsy
+patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
+  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Each
+recording session lasted from 0.4--2.2~h (total recording time:
+0.4--6.6~h; Fig.~\suppstats B).  Whereas Dataset 1 included recordings
+taken as the patients participated in a variety of activities, Dataset
+2 included recordings taken as each patient performed each of two
+specific experimental memory tasks: a random word list free recall
+task (Experiment 1) and a categorized word list free recall task
+(Experiment 2).  We used Dataset 2
+to further examine the ability of SuperEEG to generalize its
 predictions within versus across tasks.  Figure~\suppstats~provides
-additional details on both datasets.
+additional information about both datasets.
 

### 2018-10-11 paper/main.tex
another pass through main.tex [WIP]

@@
 
-\title{Towards human SuperEEG} 
+\title{A Gaussian process model of human electrocorticographic data} 
 \author{
@@
 \begin{abstract}
-  Human \textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by
-    Robert J. Sawyer in his popular science fiction novel \textit{The
-      Terminal Experiment}~\cite{Sawy95}} entails measuring ongoing
-  neural activity throughout the entire living brain with perfect
-  precision and arbitrarily high spatiotemporal resolution.  Although
-  true SuperEEG is impossible using existing methods, here we present
-  a model-based method for \textit{inferring} full-brain neural
+  We present a model-based method for inferring full-brain neural
   activity at millimeter-scale spatial resolutions and
@@
   recordings, how much can be inferred about ongoing activity at
-  \textit{other} locations in that
-  individual's brain?\\\\
+  \textit{other} locations throughout that
+  individual's brain?  We show that our approach generalizes across
+  people and tasks, thereby providing a person- and task-general means
+  of inferring high spatiotemporal resolution full-brain neural
+  dynamics from standard low-density intracranial recordings.
+  \\\\
   \footnotesize{\textbf{Keywords: Electrocorticography (ECoG),
@@
 \textit{other} people's brains?  Here we develop an approach, which we
-call \textit{SuperEEG}, based on Gaussian process
-regression~\cite{Rasm06}.  SuperEEG entails using data from multiple
-people to estimate activity patterns at arbitrary locations in each
-person's brain (i.e., independent of their electrode placements).  We
-test our SuperEEG approach using two large datasets of intracranial
-recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
-  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  We show
-that the SuperEEG algorithm recovers signals well from electrodes that
-were held out of the training dataset.  We also examine the factors
-that influence how accurately activity may be estimated (recovered),
-which may have implications for electrode design and
-placement in neurosurgical applications.
+call \textit{SuperEEG}\textit{SuperEEG}\footnote{The term ``SuperEEG''
+  was coined by Robert J. Sawyer in his popular science fiction novel
+  \textit{The Terminal Experiment}~\cite{Sawy95}.  SuperEEG is a
+  fictional technology that measures ongoing neural activity
+  throughout the entire living human brain with perfect precision and
+  at arbitrarily high spatiotemporal resolution.}, based on Gaussian
+process regression~\cite{Rasm06}.  SuperEEG entails using data from
+multiple people to estimate activity patterns at arbitrary locations
+in each person's brain (i.e., independent of their electrode
+placements).  We test our SuperEEG approach using two large datasets
+of intracranial recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b,
+  MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17,
+  KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
+  KuceEtal18}.  We show that the SuperEEG algorithm recovers signals
+well from electrodes that were held out of the training dataset.  We
+also examine the factors that influence how accurately activity may be
+estimated (recovered), which may have implications for electrode
+design and placement in neurosurgical applications.
 

### 2018-10-11 paper/supporting_information.tex
typo fixes in supporting info to get latex to compile
supporting info updated

@@
 \caption{\small \textbf{Reconstruction accuracy predicted by data
-    features for each dataset.} \textbf{A.-F. \& G.-L.  Correspondence
-    between average
-    reconstruction accuracy
-    and data feature for datasets 1 and 2.} The scatterplots display the z-transformed
-  average patient correlation coefficient versus different features of
-  the data (\textbf{A. & G.} total electrodes, \textbf{B. & H.}  proportion thresholded, \textbf{C. & I.} total recording time,
-  \textbf{D. & J.}  number thresholded, \textbf{E. & K.}  number of sessions, and \textbf{F. & L.}  average session
-  length). The one-dimensional histograms report the distribution of
+    features for each dataset.} \textbf{A.--F.  Features from Dataset
+    1.}  Features include: (\textbf{A.}) number of electrodes,
+  (\textbf{B.}) proportion thresholded, (\textbf{C.}), total recording
+  time, (\textbf{D.}) number thresholded, (\textbf{E.}) number of
+  sessions, and (\textbf{F.}) average session length.
+ \textbf{G.--L. Features from Dataset 2.}  Analogous format to
+  Panels A--F. The one-dimensional histograms report the distribution of
   the z-transformed correlation coeffiencients and the associated data

### 2018-10-11 paper/boneyard.tex

@@
 % old discussion section
+Human \textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by
+    Robert J. Sawyer in his popular science fiction novel \textit{The
+      Terminal Experiment}~\cite{Sawy95}.  SuperEEG is a fictional
+    technology that measures ongoing
+  neural activity throughout the entire living human brain with perfect
+  precision and at arbitrarily high spatiotemporal resolution.}
 

### 2018-10-11 paper/main.tex
working on supplement

@@
   intracranial recordings.  Our approach assumes that different
-  people's brains exhibit similar spatial correlations, and that
-  activity and correlation patterns are spatially smooth.  One can
+  people's brains exhibit similar correlational structure, and that
+  activity and correlation patterns vary smoothly over space.  One can
   then ask, for an arbitrary individual's brain: given recordings from

### 2018-10-11 paper/supporting_information.tex
working on supplement

--- 2018-10-02 paper/supporting_information.tex
@@
-\documentclass{article}
+\documentclass[10pt]{article}
 \usepackage[utf8]{inputenc}
@@
 
-\title{\textit{Supporting Information for}: Towards human Super EEG?}
-\author{Lucy L.
-W.
-Owen, Andrew C.
-Heusser, and Jeremy R.
-Manning\\Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755, USA\\Corresponding author: jeremy.r.manning@dartmouth.edu}
+\title{\textit{Supplemental Figures for}: A Gaussian process model of human electrocorticographic data} 
+\author{
+  Lucy L. W. Owen$^{1}$,
+  Andrew C. Heusser$^{1, 2}$, and
+  Jeremy R. Manning$^{1\ast}$\\\\
+$^{1}$Department of Psychological and Brain Sciences, Dartmouth College,\\
+Hanover, NH 03755, USA\\
+$^{2}$Akili Interactive,\\
+Boston, MA 02110, USA}
 
@@
 
-\section*{Overview}
-This document provides additional details about the methods we used in the main text.  We also include some additional analyses referenced in the main text.
-
-\begin{figure}[p!]
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.75\textwidth]{figs/supplemental_1}
-\caption{\small \textbf{Reconstruction quality for datasets 1 and 2.} \textbf{A. Distributions
-      of correlation coefficients.}  Although patients in dataset 1 all participated in the same experiment, we did not limit our analyses to task specific data.
-Instead we incorporated data from their entire recording session (sometimes up to 14 hours of data) and classify this as training our model on across experiment information.
-The split violin plot shows the distributions of reconstruction accuracy using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray).
-\textbf{B.
-Distributions of correlation coefficients.} Since all patients participated in two experiments in dataset 2, we limit our analyses to task specific data.
-The violin plots compare distributions of reconstruction accuracy using data from the same task (Within Experiment), the other task (Across Experiment), and from both tasks (All Experiment), using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray).}
+\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
+\caption{\textbf{Reconstruction quality for datasets 1 and 2.}
+  \textbf{A. Distributions of correlations between observed versus
+    reconstructed activity by electrode, for Dataset 1.} The split violin
+  plot reflects the same data as Figure~3A, presented here for
+  comparison.  The ``\textbf{B. Distributions of correlation between
+    observed versus reconstructed activity by electrode, for Dataset
+    1.}  The right-most split violin plot (``All'') reflects the same data as Figure~3B,
+  presented here for comparison.  The ``Within'' plot reflects the
+  same analyses, but limited to models that were trained and tested on
+  the same Dataset 2 experiments.  The ``Across'' plot reflects the
+  same analyses, but limited to models that were trained and tested on
+  \textit{different} Dataset 2 experiments.  All plots: the dark gray
+  distributions denote across-subject correlations (model trained on
+  all but one patient and tested on the held-out patient), and the
+  light gray distributions denote within-subject correlations (model
+  trained on all but one electrode from one patient, and tested on the
+  held-out electrode).  The horizontal bars denote $t$-tests between
+  the corresponding distributions, and the white numbers reflect the
+  distribution means.  The symbols denote the corresponding $p$-values
+of those statistical tests.}
 \label{fig:supplemental_1}
@@
 
-\begin{figure}[p!]
+\begin{figure}[p]
 \centering
 \includegraphics[width=\textwidth]{figs/supplemental_2}
-\caption{\small \textbf{Reconstruction quality for experiments 1 and 2.} \textbf{A. Distributions
-      of correlation coefficients.} For experiment 1, the split violin plots compare distributions of reconstruction accuracy using data from just experiment 1 (Within Experiment), just experiment 2 (Across Experiment), and from both experiments (All Experiment), using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray).
-\textbf{B.
-Distributions
-      of correlation coefficients.} For experiment 2, the split violin plots compare distributions of reconstruction accuracy using data from just experiment 2 (Within Experiment), just experiment 1 (Across Experiment), and from both experiments (All Experiment), using models trained on data from all other patients (Across Subject, in black) and all other electrodes from the same patient (Within Subject, in gray).
-}
+\caption{\textbf{Reconstruction quality for Dataset 2,
+    Experiments 1 and 2.} \textbf{A. Distributions of correlations
+    between observed versus reconstructed activity by electrode, for
+    Experiment 1.}  Each split violin plot and horizontal bar is in
+  the same format as the plots in Figure~\ref{fig:supplemental_1}.
+  ``Within'' denotes within-subject correlations (model trained on all
+  but one electrode from one patient, and tested on the held-out
+  electrode); ``Across'' denotes across-subject correlations (model
+  trained an all but one patient and tested on the held-out patient);
+  ``All'' denotes a model trained on all data from all patients,
+  except for one held-out electrode (and tested on the held-out
+  electrode).  \textbf{B. Distributions of correlations between
+    observed versus reconstructed activity by electrode, for
+    Experiment 2.}  All of the plots and bars are in the same format
+  as those in Panel A.}
 \label{fig:supplemental_2}
@@
 
-\begin{figure}[p!]
+\begin{figure}[p]
 \centering
 \includegraphics[width=\textwidth]{figs/supplemental_3}
-\caption{\small \textbf{Reconstruction quality for each experiment.} \textbf{A. \& C.  Distributions
+\caption{\textbf{Reconstruction quality for each experiment.} \textbf{A. \& C.  Distributions
       of correlation coefficients.}  Across all electrodes from all
@@
 
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_4}
+\caption{\textbf{Reconstruction accuracy predicted by data
+    features for each dataset.} \textbf{A.--F.  Features from Dataset
+    1.}  Features include: (\textbf{A.}) number of electrodes,
+  (\textbf{B.}) proportion thresholded, (\textbf{C.}), total recording
+  time, (\textbf{D.}) number thresholded, (\textbf{E.}) number of
+  sessions, and (\textbf{F.}) average session length.  The histograms
+  report the distributions of the z-transformed correlation
+  coefficients and the associated data feature.
+  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
+  A--F.}
+\label{fig:supplemental_4}
+\end{figure}
+
+\begin{figure}[ptb]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_5}
+\caption{\textbf{ Top 10\% most informative voxels.}
+ Voxels in yellow indicate the intersections between
+    the top 10\% most informative voxels in each brain map from Figure
+    5, indicated by the white contours.}
+\label{fig:supplemental_5}
+\end{figure}
+
 % \newpage

### 2018-10-11 paper/supporting_information.tex
figure edits, supp caption edits, recompiled all docs

@@
 \includegraphics[width=\textwidth]{figs/supplemental_3}
-\caption{\textbf{Reconstruction quality for each experiment.} \textbf{A. \& C.  Distributions
-      of correlation coefficients.}  Across all electrodes from all
-    patients in the labeled experiment from dataset 2, the panel displays the distribution of correlations between the observed and reconstructed LFP data using models trained on data from all other patients (Across, in black) and all other electrodes from the same patient (Within, in gray).
-    \textbf{B. \& D. Correlation maps.}  The glass brain maps display the
-    average correlation between the observed LFP data and the across-subjects model reconstructed data by location, for each labeled experiment.}
+\caption{\textbf{Reconstruction quality across all electrodes in two
+      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
+    in Figure~\ref{fig:supplemental_2}A (rightmost violin plot).
+ \textbf{B. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      Experiment 2.}  Same format as Figure~3A and B, but reflects
+    data shown in Figure~\ref{fig:supplemental_2}B (rightmost violin
+    plot).  \textbf{C.--D.  Reconstruction
+      performance by location.} Each dot reflects the location of a
+    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
+    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
+    average within-experiment (across-session)
+    correlation, using the across-patient correlation model, between
+    the observed and reconstructed activity at the given electrode
+    location.}
 \label{fig:supplemental_3}
@@
 \includegraphics[width=\textwidth]{figs/supplemental_4}
-\caption{\textbf{Reconstruction accuracy predicted by data
-    features for each dataset.} \textbf{A.--F.  Features from Dataset
-    1.}  Features include: (\textbf{A.}) number of electrodes,
-  (\textbf{B.}) proportion thresholded, (\textbf{C.}), total recording
-  time, (\textbf{D.}) number thresholded, (\textbf{E.}) number of
-  sessions, and (\textbf{F.}) average session length.  The histograms
-  report the distributions of the z-transformed correlation
-  coefficients and the associated data feature.
-  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
-  A--F.}
+\caption{\textbf{Reconstruction accuracy versus within-subject data
+    features for two ECoG datasets.} \textbf{A.--F.  Features from
+    Dataset 1.}  Features include: (\textbf{A.}) total number of
+  electrodes implanted in each patient's brain, (\textbf{B.})
+  per-patient number of electrodes that were filtered out due to
+  having an average kurtosis greater than 10, (\textbf{C.})
+  per-patient proportion of electrodes that were filtered out due to
+  having an average kurtosis greater than 10, (\textbf{D.})
+  per-patient number of recording sessions, (\textbf{E.}) per-patient
+  total recording time (h), and (\textbf{F.}) per-patient average
+  session length (h).  \textbf{G.--L. Features from Dataset 2.}
+  Analogous format to Panels A--F.}
 \label{fig:supplemental_4}
@@
 \includegraphics[width=\textwidth]{figs/supplemental_5}
-\caption{\textbf{ Top 10\% most informative voxels.}
- Voxels in yellow indicate the intersections between
-    the top 10\% most informative voxels in each brain map from Figure
-    5, indicated by the white contours.}
+\caption{\textbf{Most informative electrode locations.}  This map
+  shows the region outlined in white from Figure~5 in greater detail.
+Across Datasets 1 and 2, electrodes in these locations were identified as yielding the (10\%)
+best reconstruction accuracies at \textit{other} locations throughout
+the brain.}
 \label{fig:supplemental_5}

### 2018-10-12 paper/main.tex
final edits through approach

@@
 \textit{other} people's brains?  Here we develop an approach, which we
-call \textit{SuperEEG}\textit{SuperEEG}\footnote{The term ``SuperEEG''
+call \textit{SuperEEG}\footnote{The term ``SuperEEG''
   was coined by Robert J. Sawyer in his popular science fiction novel
@@
   MannEtal12}.  Each recording session lasted from 0.2--3~h (total
-recording time: 0.3--14.2~h; Fig.~\suppstats A).  During each
+recording time: 0.3--14.2~h; Fig.~\suppstats E).  During each
 recording session, the patients participated in a free recall list
@@
 recording session lasted from 0.4--2.2~h (total recording time:
-0.4--6.6~h; Fig.~\suppstats B).  Whereas Dataset 1 included recordings
+0.4--6.6~h; Fig.~\suppstats K).  Whereas Dataset 1 included recordings
 taken as the patients participated in a variety of activities, Dataset
@@
 which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
-example Dataset 1 patient's 54 electrodes that passed the predefined
-kurtosis test are highlighted in black and red.
+example Dataset 1 patient's 54 electrodes that passed the above
+kurtosis threshold test are highlighted in black and red.
 
@@
 Here $\hat{K}_{\beta_s, \alpha_s}$ represents the correlations between
-the ``unknown'' activity at the locations in $\beta_s$ and the
-observed activity at the locations in $\alpha_s$, and
+the ``unknown'' activity at the locations indexed by $\beta_s$ and the
+observed activity at the locations indexed by $\alpha_s$, and
 $\hat{K}_{\alpha_s, \alpha_s}$ represents the correlations between the
-observed recordings (at the locations in $\alpha_s$).
+observed recordings (at the locations indexed by $\alpha_s$).
 
@@
 $\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
-covariance matrices.)  Also, note that
+covariance matrices.)  Also, we note that
 Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$

### 2018-10-12 paper/main.tex
finished a full pass through the main text

@@
 (otherwise the analysis would be circular).  For that held-out
-patient, for each of their electrodes in turn, we used
+patient, we held out each electrode in turn.  We used
 Equation~\ref{eqn:reconstruction} to reconstruct activity at the
@@
 recordings from those electrodes (i.e., how closely did the estimated
-$\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$?).
+$\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$)?
 
@@
 electrode in Figure~\ref{fig:methods}A (blue), and its associated
-reconstruction (red), during a 5~s time window during one of the
-example patient's six recording sessions.  The two traces match
-closely ($r = 0.86, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
+reconstruction (red), during the 5~s time window during one of the
+example patient's six recording sessions shown in
+Figure~\ref{fig:methods}E.  The two traces match closely
+($r = 0.86, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
 two-dimensional histogram of the actual versus reconstructed voltages
 for the entire 14.2 total hours of recordings from the example
-electrode (correlation: $r = 0.91, p < 10^{-10}$).  This example confirms
-that the SuperEEG algorithm recovers the recordings from this single
-electrode well.  Next, we used this general approach to quantify the
-algorithm's performance across the full dataset.
+electrode (correlation: $r = 0.91, p < 10^{-10}$).  This example
+confirms that the SuperEEG algorithm recovers the recordings from this
+single electrode well.  Next, we used this general approach to
+quantify the algorithm's performance across the full dataset.
 
@@
 within-patient correlations was centered well above zero (mean: 0.32;
-$t$-test comparing mean of distribution of $z$-transformed
-average patient correlation coefficients to 0: $t(66) = 15.16, p < 10^{-10}$).
+$t$-test comparing mean of distribution of $z$-transformed average
+patient correlation coefficients to 0: $t(66) = 15.16, p < 10^{-10}$).
 However, the across-patient correlations were substantially higher
 ($t$-test comparing average $z$-transformed within versus across
-patient electrode correlations: $t(66) = 9.62, p < 10^{-10}$).  This is an
-especially conservative test, given that the across-patient SuperEEG
-reconstructions exclude (from the correlation matrix estimates) all
-data from the patient whose data is being reconstructed.  We repeated
-each of these analyses on a second independent dataset and found
-similar results (Fig.~\ref{fig:corrmap}B, D; within versus across
-reconstruction accuracy: $t(23) = 6.93, p < 10^{-5}$). We also
-replicated this result separately for each of the two experiments from
-Dataset 2 (Fig.~\perexpcorrmaps).  This overall finding, that
-reconstructions of held-out data using correlation models learned from
-\textit{other} patient's data yield higher reconstruction accuracy
-than correlation models learned from the patient whose data is being
-reconstructed, has two important implications.  First, it implies that
-distant electrodes provide additional predictive power to the data
-reconstructions beyond the information contained solely in nearby
-electrodes.  (This follows from the fact that each patient's
-electrodes are implanted in a unique set of locations, so for any
-given electrode the closest electrodes in the full dataset are likely
-to come from the same patient.)  Second, it implies that the spatial
-correlations learned using the SuperEEG algorithm are, to some extent,
-similar across people.
+patient electrode correlations: $t(66) = 9.62, p < 10^{-10}$).  This
+is an especially conservative test, given that the across-patient
+SuperEEG reconstructions exclude (from the correlation matrix
+estimates) all data from the patient whose data is being
+reconstructed.  We repeated each of these analyses on a second
+independent dataset and found similar results
+(Fig.~\ref{fig:corrmap}B, D; within versus across reconstruction
+accuracy: $t(23) = 6.93, p < 10^{-5}$). We also replicated this result
+separately for each of the two experiments from Dataset 2
+(Fig.~\perexpcorrmaps).  This overall finding, that reconstructions of
+held-out data using correlation models learned from \textit{other}
+patient's data yield higher reconstruction accuracy than correlation
+models learned from the patient whose data is being reconstructed, has
+two important implications.  First, it implies that distant electrodes
+provide additional predictive power to the data reconstructions beyond
+the information contained solely in nearby electrodes.  (This follows
+from the fact that each patient's grid, strip, and depth electrodes
+are implanted in a unique set of locations, so for any given electrode
+the closest electrodes in the full dataset tend to come from the
+same patient.)  Second, it implies that the spatial correlations
+learned using the SuperEEG algorithm are, to some extent, similar
+across people.
 
@@
 correlations derived from the SuperEEG algorithm are, to some extent,
-similar across tasks.  We tested this finding more explicitly using
+similar across tasks.  We tested this finding more directly using
 Dataset 2.  In Dataset 2, the recordings were limited to times when
@@
 within-patient models trained on data only from the subject
-contributing the given electrode ($t$s$(24) > 6.50, p$s$ < 10^{-5}$).  All
+contributing the given electrode ($t$s$(23) > 6.50, p$s$ < 10^{-5}$).  All
 reconstruction accuracies also reliably exceeded chance performance
-($t$s$(24) > 8.00, p$s$ < 10^{-8}$).  Average reconstruction accuracy was
+($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average reconstruction accuracy was
 highest for the across-patient models limited to data from the same
 experiment (mean accuracy: $0.68$); next-highest for the
-across-patient models that combined data across both experiments (mean
-accuracy: $0.61$); and lowest for models trained across task (mean
+models that combined data across both experiments (mean
+accuracy: $0.61$); and lowest for models trained across tasks (mean
 accuracy: $0.47$).  This result also held for each of the Dataset 2
@@
 both datasets were similar (voxelwise correlation between information
-scores across the two datasets: $r = 0.03, p < 10^{-10}$).  While the
-correspondence between the two maps was not perfect, our finding that
+scores across the two datasets: $r = 0.20, p < 10^{-10}$).  While the
+correspondence between the two maps was imperfect, our finding that
 there were some commonalities between the two maps lends support to
 the notion that different brain areas are differently informative
-about full-brain activity patterns.  Further, we found the
-intersection of the top 10\% of the most informative voxels between
-the two datasets (Fig.~\intersectmap) and found gray matter regions like the right postcentral gyrus, right supramarginal gyrus,
-and the right nucleus accumbens that exhibited strong information scores in both datasets may
-be especially promising implantation targets.
+about full-brain activity patterns.  We also examined the intersection
+between the top 10\% most informative voxels across the two datasets
+(white outlines in Fig.~\ref{fig:informap}A, B, Fig.~\intersectmap).
+Supporting the notion that structures that are highly interconnected
+with the rest of the brain might be especially good targets for
+implantation, this intersecting set of voxels with the highest
+information scores included major portions of the dorsal attention
+network (e.g., inferior parietal lobule, precuneus, inferior temporal
+gyrus, thalamus, and striatum) as well as some portions of the default
+mode network (e.g., angular gyrus) that are highly interconnected with
+a large proportion of the brain's gray matter~\citep[e.g., ][]{TomaVolk11}.
 
@@
 correlations are stable over time and across tasks.  We found that,
-although aspects of the patients' functional correlations that were
+although aspects of the patients' functional correlations were
 stable across tasks, we achieved better reconstruction accuracy when
@@
 neurons that underly the population contributing to the
-LFP~\cite{MillEtal08, MannEtal09, JacoEtal10, CronEtal11}.  Because
+LFP~\cite{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.  Because
 SuperEEG reconstructs LFPs throughout the brain, one could in
@@
 fixed number of electrodes to maximize our ability to map seizure
-foci?  As shown in Figure~\ref{fig:informap}, recordings from
+foci?  As shown in Figures~\ref{fig:informap} and~\intersectmap, recordings from
 different locations are differently informative in terms of
@@
 \href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}. Additionally,
-we have provided notebooks for all analyses and figures reported
-here.
+we have provided code for all analyses and figures reported in the
+current manuscript, available
+\href{https://github.com/ContextLab/supereeg_paper}{\underline{here}}.
 
 \section*{Data availability}
-The dataset analyzed in this study was generously shared by Michael Kahana.  A portion of Dataset 1 may be downloaded
+The dataset analyzed in this study was generously shared by Michael
+J. Kahana.  A portion of Dataset 1 may be downloaded
 \href{http://memory.psych.upenn.edu/Request_EEG_access?paper=SedeEtal03}{\underline{here}}.
@@
 We are grateful for useful discussions with Luke J. Chang, Uri Hasson,
-Josh Jacobs, Michael Kahana, and Matthijs van der Meer.  We are also
-grateful to Michael Kahana for generously sharing the ECoG data we
-analyzed in our paper, which was collected under NIMH grant MH55687
-and DARPA RAM Cooperative Agreement N66001-14-2-4-032, both to MJK.
-Our work was also supported in part by NSF EPSCoR Award Number 1632738
-and by a sub-award of DARPA RAM Cooperative Agreement
-N66001-14-2-4-032 to JRM.  The content is solely the responsibility of
-the authors and does not necessarily represent the official views of
-our supporting organizations.
+Josh Jacobs, Michael J. Kahana, and Matthijs van der Meer.  We are
+also grateful to Michael J. Kahana for generously sharing the ECoG
+data we analyzed in our paper, which was collected under NIMH grant
+MH55687 and DARPA RAM Cooperative Agreement N66001-14-2-4-032, both to
+M.J.K.  Our work was also supported in part by NSF EPSCoR Award Number
+1632738 and by a sub-award of DARPA RAM Cooperative Agreement
+N66001-14-2-4-032 to J.R.M.  The content is solely the responsibility
+of the authors and does not necessarily represent the official views
+of our supporting organizations.
 
 \section*{Author Contributions}
-J.R.M conceived and initiated the project. L.L.W.O. and A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the manuscript.
+J.R.M conceived and initiated the project. L.L.W.O. and
+A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the
+manuscript.
 

### 2018-10-12 paper/supporting_information.tex
finished pass through supplemental figures document

@@
 
-\title{\textit{Supplemental Figures for}: A Gaussian process model of human electrocorticographic data} 
+\title{\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data} 
 \author{
@@
 \includegraphics[width=0.6\textwidth]{figs/supplemental_1}
-\caption{\textbf{Reconstruction quality for datasets 1 and 2.}
+\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
   \textbf{A. Distributions of correlations between observed versus
-    reconstructed activity by electrode, for Dataset 1.} The split violin
-  plot reflects the same data as Figure~3A, presented here for
-  comparison.  The ``\textbf{B. Distributions of correlation between
+    reconstructed activity by electrode, for Dataset 1.} The split
+  violin plot reflects the same data as Figure~3A, presented here for
+  comparison.  \textbf{B. Distributions of correlation between
     observed versus reconstructed activity by electrode, for Dataset
-    1.}  The right-most split violin plot (``All'') reflects the same data as Figure~3B,
-  presented here for comparison.  The ``Within'' plot reflects the
-  same analyses, but limited to models that were trained and tested on
-  the same Dataset 2 experiments.  The ``Across'' plot reflects the
-  same analyses, but limited to models that were trained and tested on
-  \textit{different} Dataset 2 experiments.  All plots: the dark gray
-  distributions denote across-subject correlations (model trained on
-  all but one patient and tested on the held-out patient), and the
-  light gray distributions denote within-subject correlations (model
-  trained on all but one electrode from one patient, and tested on the
-  held-out electrode).  The horizontal bars denote $t$-tests between
-  the corresponding distributions, and the white numbers reflect the
-  distribution means.  The symbols denote the corresponding $p$-values
-of those statistical tests.}
+    2.}  The right-most split violin plot (``All'') reflects the same
+  data as Figure~3B, presented here for comparison.  The ``Within''
+  plot reflects the same analyses, but limited to models that were
+  trained and tested on only one of the Dataset 2 experiments at a
+  time.  The ``Across'' plot reflects the same analyses, but limited
+  to models that were trained and tested on \textit{different} Dataset
+  2 experiments.  All plots: the dark gray distributions denote
+  across-subject correlations (model trained on all but one patient
+  and tested on the held-out patient), and the medium gray
+  distributions denote within-subject correlations (model trained on
+  all but one electrode from one patient, and tested on the held-out
+  electrode).  The horizontal bars denote $t$-tests between the
+  corresponding distributions (after $z$-transforming the
+  correlations), and the white numbers reflect the distribution means.
+  The symbols denote the corresponding $p$-values of those statistical
+  tests.}
 \label{fig:supplemental_1}
@@
   shows the region outlined in white from Figure~5 in greater detail.
-Across Datasets 1 and 2, electrodes in these locations were identified as yielding the (10\%)
-best reconstruction accuracies at \textit{other} locations throughout
-the brain.}
+  Across Datasets 1 and 2, electrodes in these locations were
+  identified as yielding the (10\%) best reconstruction accuracies at
+  \textit{other} locations throughout the brain.  The $x$-coordinates
+  in each panel denote the positions of the sagittal slices in MNI space.}
 \label{fig:supplemental_5}

### 2018-10-12 paper/main.tex
finished pass through supplemental figures document
corrected kurtosis thresholding description, addressed ACH letter comments

@@
 Specifically, we excluded from further analysis any electrode that
-exhibited an average kurtosis of 10 or greater across all of that
+exhibited an maximum kurtosis of 10 or greater across all of that
 patient's recording sessions.  We also excluded any patients with
@@
       score by voxel.}  This panel is in the same format as Panel A.
-    In both panels the contours indicate the intersections between
-    the top 10\% most informative voxels in each map.
-    \textbf{C. Correspondence in information scores by voxel across
-      Datasets 1 and 2.}  Same format as Figure~\ref{fig:density}C.}
+    In both panels the contours indicate the intersections between the
+    top 10\% most informative voxels in each map (also see
+    Fig.~\intersectmap).  \textbf{C. Correspondence in information
+      scores by voxel across Datasets 1 and 2.}  Same format as
+    Figure~\ref{fig:density}C.}
   \label{fig:informap}

### 2018-10-12 paper/supporting_information.tex
corrected kurtosis thresholding description, addressed ACH letter comments

@@
   per-patient number of electrodes that were filtered out due to
-  having an average kurtosis greater than 10, (\textbf{C.})
-  per-patient proportion of electrodes that were filtered out due to
-  having an average kurtosis greater than 10, (\textbf{D.})
-  per-patient number of recording sessions, (\textbf{E.}) per-patient
-  total recording time (h), and (\textbf{F.}) per-patient average
-  session length (h).  \textbf{G.--L. Features from Dataset 2.}
-  Analogous format to Panels A--F.}
+  having an maximum kurtosis greater than 10 across all recording
+  sessions, (\textbf{C.})  per-patient proportion of electrodes that
+  were filtered out due to having an average kurtosis greater than 10,
+  (\textbf{D.})  per-patient number of recording sessions,
+  (\textbf{E.}) per-patient total recording time (h), and
+  (\textbf{F.}) per-patient average session length (h).
+  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
+  A--F.}
 \label{fig:supplemental_4}

### 2018-10-12 paper/supporting_information.tex
updated supp fig caption per lucy's comments

@@
     observed versus reconstructed activity by electrode, for Dataset
-    2.}  The right-most split violin plot (``All'') reflects the same
-  data as Figure~3B, presented here for comparison.  The ``Within''
-  plot reflects the same analyses, but limited to models that were
-  trained and tested on only one of the Dataset 2 experiments at a
-  time.  The ``Across'' plot reflects the same analyses, but limited
-  to models that were trained and tested on \textit{different} Dataset
+    2.}  The left-most split violin plot (``Within'') reflects the
+  same data as Figure~3B, presented here for comparison.  The
+  ``Across'' plot reflects the same analyses, but limited to models
+  that were trained and tested on \textit{different} Dataset 2
+  experiments.  The ``All'' plot reflects the same analyses, but
+  including models that were trained and tested on both of the Dataset
   2 experiments.  All plots: the dark gray distributions denote
@@
       Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
-    in Figure~\ref{fig:supplemental_2}A (rightmost violin plot).
+    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
  \textbf{B. Distributions of correlations
@@
       Experiment 2.}  Same format as Figure~3A and B, but reflects
-    data shown in Figure~\ref{fig:supplemental_2}B (rightmost violin
+    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
     plot).  \textbf{C.--D.  Reconstruction

### 2018-10-12 paper/main.tex
added text file for abstract, corrected sampling density vs accuracy stats

@@
 then correlated these density values with the across-patient
-reconstruction accuracies for each electrode.  Contrary to our
-expectation, rather than positive correlations, we found weak (but
-reliable) negative correlations between reconstruction accuracy and
-density for both datasets (Dataset 1: $r = -0.07, p < 10^{-5}$; Dataset 2:
-$r = -0.18, p < 10^{-10}$).  This indicates that the reconstruction
+reconstruction accuracies for each electrode.  We found no reliable
+correlations between reconstruction accuracy and density for either
+dataset (Dataset 1: $r = 0.09, p = 0.44$; Dataset 2:
+$r = -0.30, p = 0.15$).  This indicates that the reconstruction
 accuracies we observed are not driven solely by sampling density, but

### 2019-01-09 paper/main.tex
updated gitignore file, reformatting references
minor citations format update

@@
 \documentclass[11pt]{article}
-\usepackage[numbers, square, sort, compress]{natbib}
+\usepackage[round,sort&compress]{natbib}
+\setcitestyle{aysep={}}
 \usepackage{newpxtext,newpxmath}
@@
 obtaining adequate signal quality often requires averaging the
-measured responses over tens to hundreds of responses or trials
-(e.g., see review by~\cite{HillEtal05}).
+measured responses over tens to hundreds of responses or trials~\citep[e.g., see review by][]{HillEtal05}).
 
@@
 
-\bibliography{CDL-bibliography/memlab.bib}
-\bibliographystyle{apa}
+\bibliography{memlab}
+\bibliographystyle{CSE}
 

### 2019-01-10 paper/main.tex
another reference formatting thing
updated cite to citep

@@
 called \textit{beamforming} to solve the biomagnetic or bioelectrical
-inverse problem~\cite{Sarv87}.  This approach entails using detailed
+inverse problem~\citep{Sarv87}.  This approach entails using detailed
 brain conductance models (often informed by high spatial resolution
@@
 and that individual sources are small relative to their distances to
-the sensors~\cite{Snyd91, BailEtal01, HillEtal05}.  The second, and in
+the sensors~\citep{Snyd91, BailEtal01, HillEtal05}.  The second, and in
 some ways much more serious, obstacle is that the magnetic fields
@@
 obtaining adequate signal quality often requires averaging the
-measured responses over tens to hundreds of responses or trials~\citep[e.g., see review by][]{HillEtal05}).
+measured responses over tens to hundreds of responses or trials~\citep[e.g., see review by][]{HillEtal05}.
 
@@
 however, the signal quality of both recordings suffers substantially
-when the two techniques are applied simultaneously (e.g., see review
-by~\cite{HustEtal12}).  In addition, the experimental designs that are
+when the two techniques are applied simultaneously~\citep[e.g., see review by][]{HustEtal12}.  In addition, the experimental designs that are
 ideally suited to each technique individually are somewhat at odds.
@@
   at arbitrarily high spatiotemporal resolution.}, based on Gaussian
-process regression~\cite{Rasm06}.  SuperEEG entails using data from
+process regression~\citep{Rasm06}.  SuperEEG entails using data from
 multiple people to estimate activity patterns at arbitrary locations
@@
 placements).  We test our SuperEEG approach using two large datasets
-of intracranial recordings~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b,
+of intracranial recordings~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b,
   MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17,
@@
 electrodes implanted in the brains of 88 epilepsy
-patients~\cite{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
+patients~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
   MannEtal12}.  Each recording session lasted from 0.2--3~h (total
@@
 neurons that underly the population contributing to the
-LFP~\cite{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.  Because
+LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.  Because
 SuperEEG reconstructs LFPs throughout the brain, one could in
@@
 
-\bibliography{memlab}
+\bibliography{CDL-bibliography/memlab}
 \bibliographystyle{CSE}

### 2019-11-21 code/scripts/visbrain_plots/freq_plots.py
WIP paper figs

@@ -3,7 +3,7 @@ import supereeg as se
 import os
 from visbrain.objects import BrainObj, SceneObj, SourceObj
 
-cmap = "Spectral"
+cmap = "viridis_spliced"
 
 nii_bo_dir = '../../../data/niis/freq'
 
@@ -70,20 +70,20 @@ s_obj_all = s_obj_7 + s_obj_6 + s_obj_5 + s_obj_4+ s_obj_3 + s_obj_2 + s_obj_1
 #s_obj_all = s_obj_1
 
 b_obj_proj_left = BrainObj(template_brain, hemisphere='left', translucent=False)
-b_obj_proj_left.project_sources(s_obj_all, clim=(1, 7), cmap='spec_spliced')
+b_obj_proj_left.project_sources(s_obj_all, clim=(1, 7), cmap='viridis_spliced')
 sc.add_to_subplot(b_obj_proj_left, row=0, col=0, rotate='left', use_this_cam=True)
 
 
 b_obj_proj_left = BrainObj(template_brain, hemisphere='left', translucent=False)
-b_obj_proj_left.project_sources(s_obj_all, clim=(1, 7), cmap='spec_spliced')
-sc.add_to_subplot(b_obj_proj_left, row=0, col=1, rotate='right', use_this_cam=True)
+b_obj_proj_left.project_sources(s_obj_all, clim=(1, 7), cmap='viridis_spliced')
+sc.add_to_subplot(b_obj_proj_left, row=1, col=0, rotate='right', use_this_cam=True)
 
 b_obj_proj_right = BrainObj(template_brain, hemisphere='right', translucent=False)
-b_obj_proj_right.project_sources(s_obj_all, clim=(1, 7), cmap='spec_spliced')
-sc.add_to_subplot(b_obj_proj_right, row=0, col=2, rotate='left', use_this_cam=True)
+b_obj_proj_right.project_sources(s_obj_all, clim=(1, 7), cmap='viridis_spliced')
+sc.add_to_subplot(b_obj_proj_right, row=1, col=1, rotate='left', use_this_cam=True)
 
 b_obj_proj_right = BrainObj(template_brain, hemisphere='right', translucent=False)
-b_obj_proj_right.project_sources(s_obj_all, clim=(1, 7), cmap='spec_spliced')
-sc.add_to_subplot(b_obj_proj_right, row=0, col=3, rotate='right', use_this_cam=True)
[…]

### 2019-11-22 paper/main.tex
updated author list

@@
   Lucy L. W. Owen$^{1}$,
-  Andrew C. Heusser$^{1, 2}$, and
+  Tudor A. Muntianu$^{1}$,
+  Andrew C. Heusser$^{1, 2}$, \\
+  Patrick Daly$^{3}$,
+  Katherine Scangos$^{3}$, and
   Jeremy R. Manning$^{1\ast}$\\\\
@@
 $^{2}$Akili Interactive,\\
-Boston, MA 02110, USA}
+Boston, MA 02110, USA\\
+$^{3}$Weill Institute for Neurosciences, University of California, San Francisco,\\
+San Francisco, CA 94121, USA}
 

### 2019-11-22 paper/main.tex
removed figure 2

@@
 
-To illustrate our approach, we first examine an individual held-out
-raw LFP trace and its associated SuperEEG-derived reconstruction.
-Figure~\ref{fig:recon}A displays the observed LFP from the red
-electrode in Figure~\ref{fig:methods}A (blue), and its associated
-reconstruction (red), during the 5~s time window during one of the
-example patient's six recording sessions shown in
-Figure~\ref{fig:methods}E.  The two traces match closely
-($r = 0.86, p < 10^{-10}$).  Figure~\ref{fig:recon}B displays a
-two-dimensional histogram of the actual versus reconstructed voltages
-for the entire 14.2 total hours of recordings from the example
-electrode (correlation: $r = 0.91, p < 10^{-10}$).  This example
-confirms that the SuperEEG algorithm recovers the recordings from this
-single electrode well.  Next, we used this general approach to
-quantify the algorithm's performance across the full dataset.
-
-%sample trace & reconstruction, several frames of activity snapshot?
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/recon}
-  \caption{\textbf{Observed and reconstructed LFP from a single
-      electrode.} \textbf{A. Example LFP.}  A 5~s recording from the
-    red electrode in Figure~\ref{fig:methods}A is displayed in blue,
-    and the reconstructed LFP during the same time window is shown in
-    red.  \textbf{B. Observed versus reconstructed LFP over
-      14.2~hours.}  The two-dimensional histogram reflects the
-    relation between distributions of observed versus reconstructed
-    voltages from one patient, across the 14.2 hours of recorded data
-    collected over 6 recording sessions.  The correlation reported in
-    the panel is between the observed and reconstructed voltages.
-    Both panels: all voltages are represented in standard deviation units
-   (computed within session).}
-  \label{fig:recon}
-\end{figure}
-
-For each held-out electrode, from each held-out patient in turn, we
+We used this general approach to
+quantify the algorithm's performance across the full dataset.For each held-out electrode, from each held-out patient in turn, we
 computed the average correlation (across recording sessions) between

### 2019-12-09 paper/main.tex
added new corrmat stability analysis

@@
 Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations
-was centered well above zero (mean: 0.52; $t$-test comparing mean of
+was centered well above zero (mean: 0.51; $t$-test comparing mean of
 distribution of $z$-transformed average patient correlation coefficients
-to 0: $t(66) = 25.08, p < 10^{-10}$), indicating that the SuperEEG algorithm
+to 0: $t(66) = 23.55, p < 10^{-10}$), indicating that the SuperEEG algorithm
 recovers held-out activity patterns substantially better than random
@@
 ($t$-test comparing average $z$-transformed within versus across
-patient electrode correlations: $t(66) = 9.62, p < 10^{-10}$).  This
+patient electrode correlations: $t(66) = 9.17, p < 10^{-10}$).  This
 is an especially conservative test, given that the across-patient
@@
 (Fig.~\ref{fig:corrmap}B, D; within versus across reconstruction
-accuracy: $t(23) = 6.93, p < 10^{-5}$). We also replicated this result
+accuracy: $t(77) = 11.25, p < 10^{-10}$). We also replicated this result
 separately for each of the two experiments from Dataset 2
@@
     see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
-      performance by location.} Each dot reflects the location of a
-    single implanted electrode from Dataset 1 (Panel C) or Dataset 2
-    (Panel D).  The dot colors denote the average across-session
+      performance by location.} The colors denote the average across-session
     correlation, using the across-patient correlation model, between
     the observed and reconstructed activity at the given electrode
-    location.}
+    location projected to the cortical surface.}
   \label{fig:corrmap}
@@
 Dataset 2.  In Dataset 2, the recordings were limited to times when
-each patient was participating in each of two experiments (Experiment
-1, a random-word list free recall task, and Experiment 2, a
-categorized list free recall task).  We wondered whether a correlation
+each patient was participating in one of two experiments.  Experiment
+1 is a random-word list free recall task; Experiment 2 is a
+categorized list free recall task (24 patients particpated in both).  We wondered whether a correlation
 model learned from data from one experiment might yield good
@@
 To test the task-specificity of the SuperEEG-derived correlation
-models, we repeated the above within- and across-patient cross validation
+models, we restricted the dataset to the 24 patients that participated
+in both experiments and repeated the above within- and across-patient cross validation
 procedures separately for Experiment 1 and Experiment 2 data from
@@
 densities were similar (correlation by voxel:
-$r = 0.56, p < 10^{-10}$).  We wondered whether regions with good
+$r = 0.6, p < 10^{-10}$).  We wondered whether regions with good
 covererage might be associated with better reconstruction accuracy
@@
 then correlated these density values with the across-patient
-reconstruction accuracies for each electrode.  We found no reliable
-correlations between reconstruction accuracy and density for either
-dataset (Dataset 1: $r = 0.09, p = 0.44$; Dataset 2:
+reconstruction accuracies for each electrode.  We found a negative
+correlation between reconstruction accuracy and density for Dataset 1,
+but was unreliable for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$; Dataset 2:
 $r = -0.30, p = 0.15$).  This indicates that the reconstruction
-accuracies we observed are not driven solely by sampling density, but
+accuracies we observed are not driven by sampling density, but
 rather may also reflect higher order properties of neural dynamics
@@
 both datasets were similar (voxelwise correlation between information
-scores across the two datasets: $r = 0.20, p < 10^{-10}$).  While the
+scores across the two datasets: $r = 0.18, p < 10^{-10}$).  While the
 correspondence between the two maps was imperfect, our finding that
@@
 between the top 10\% most informative voxels across the two datasets
-(white outlines in Fig.~\ref{fig:informap}A, B, Fig.~\intersectmap).
+(gray areas in Fig.~\ref{fig:informap}C).
 Supporting the notion that structures that are highly interconnected
@@
     top 10\% most informative voxels in each map (also see
-    Fig.~\intersectmap).  \textbf{C. Correspondence in information
+    Fig.~\intersectmap).  \textbf{C. Intersection.}  
+    Gray areas indicate the intersections between the
+    top 10\% most informative voxels in each map.  \textbf{D. Correspondence in information
       scores by voxel across Datasets 1 and 2.}  Same format as
@@
   \label{fig:informap}
+\end{figure}
+
+We also wondered what frequency properties contributed to the
+reconstruction accuracy.  For this analysis, we INSTERT TUDORS
+DESCRIPTION FOR FREQ ANALYSIS.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/frequency}
+  \caption{\textbf{Reconstruction quality across all electrodes in two
+      ECoG datasets for each frequency band.}  \textbf{A. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      each frequency band in Dataset 1.}  The across-patient
+    distribution (left jitter barplot) reflects
+    reconstruction accuracy (correlation) using a correlation model
+    learned from all but one patient's data, and then applied to that
+    held-out patient's data.  The within-patient distribution (right
+    jitter barplot in lighter color)
+    reflects performance using a correlation model learned from the same
+    patient who contributed the to-be-reconstructed electrode.
+    \textbf{B.~Statistical summary of across-patient reconstruction
+      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
+    map, warmer colors (positive t-values) indicate that the
+    distribution of
+    reconstruction accuracy for the frequency band in a given row
+    yielded was greater than the frequency band in the given
+    column. Cooler colors (negative t-values) indicate that the
+    frequency band in the given row yielded lower reconstruction
+    accuracy than the frequency band in the given column. The lower
+    triangles of each map denote the corresponding p-values for the
+    t-tests. The diagonal entries display the relative average
+    reconstruction accuracy given to each frequency band. \textbf{C.~Statistical summary ofwithin-patient reconstruction
+      quality by electrode for each frequency band in Dataset 1.}
+    This panel displays the within-patient statistical summary,
+    in the same format as Panel B.  \textbf{D.~Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      each frequency band in Dataset 2.}  This panel displays
+    reconstruction accuracy distributions for each frequency band for
+    Dataset 2 in
+    the same format as Panel A. \textbf{E.~Statistical summary of
+      across-patient reconstruction quality by electrode for each
+      frequency band in Dataset 2.} This is the same format as Panel
+    B for Dataset 2. \textbf{F.~Statistical summary of
+      within-patient reconstruction quality by electrode for each
+      frequency band in Dataset 2.}This is the same format as Panel
+    C for Dataset 2.}
+  \label{fig: frequency}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/networks}
+  \caption{\textbf{Electrode sampling density by location.}
+    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
+    voxel is colored by the proportion of total electrodes in the
+    dataset that are
+    located within a 20~MNI unit radius sphere centered on the given
+    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
+      2.}  This panel displays the sampling density map for Dataset 2,
+    in the same format as Panel A.  \textbf{C.~Correspondence in
+      sampling density by voxel across Datasets 1 and 2.}  The
+    two-dimensional histogram displays the by-voxel densities in the
+    two Datasets, and the one-dimensional histograms display the
+    proportions of voxels in each dataset with the given density
+    value.  The correlation reported in the panel is across voxels in
+    the 4~mm$^3$ MNI brain.}
+  \label{fig: networks}
 \end{figure}

### 2019-12-09 code/notebooks/plot.py

@@ -800,7 +800,7 @@ def plot_split_barplot_colors(df, X, Y, H, x_order, hue_order, left_colors, righ
     
     sns.set(style="white")
 
-    fig, axes = plt.subplots(1, len(x_order), figsize=(20, 10), sharey='all')
+    fig, axes = plt.subplots(1, len(x_order), figsize=(13, 8), sharey='all')
 
 
     for e, freq in enumerate(x_order):
@@ -810,7 +810,7 @@ def plot_split_barplot_colors(df, X, Y, H, x_order, hue_order, left_colors, righ
         #offset = long_form_freq['Correlation'].min()
         offset = -.2
         df_temp['Correlation'] = df_temp['Correlation'] - offset
-        sns.barplot(x=X, y=Y, hue=H, data=df_temp, linewidth=4.5, facecolor=(1, 1, 1, 0), 
+        sns.barplot(x=X, y=Y, hue=H, data=df_temp, linewidth=6, alpha=1, facecolor=(1, 1, 1, 0), 
                     errcolor=left_colors[e], edgecolor=left_colors[e], palette={hue_order[0]: left_colors[e], hue_order[1]: right_colors[e]}, ax=axes[e])
         sns.stripplot(x=X, y=Y, hue=H, data=df_temp, jitter=.4, split=True, alpha=.15,
                     palette={hue_order[0]: left_colors[e], hue_order[1]: right_colors[e]}, ax=axes[e])

### 2019-12-09 code/scripts/corrmat_stability_time/config.py

@@ -1,0 +1,38 @@
+import os
+import socket
+
+config = dict()
+
+config['template'] = 'run_job.sh'
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname() == 'vertex.kiewit.dartmouth.edu') or \
+        (socket.gethostname() == 'vertex.local') or (socket.gethostname() == 'vpn-two-factor-general-230-139-212.dartmouth.edu'):
+    config['pyfrdatadir'] = '/Users/lucyowen/Desktop/supereeg_env/bo/'
+    config['ramdatadir'] = '/Users/lucyowen/Desktop/supereeg_env/bo/'
+    config['workingdir'] = '/Users/lucyowen/Desktop/supereeg_env/corrmat_stability_time/'
+    config['startdir'] = '/Users/lucyowen/Desktop/supereeg_env/'  # directory to start the job in
+    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
+else:
+    config['pyfrdatadir'] = '/idata/cdl/data/ECoG/pyFR/data/bo'
+    config['ramdatadir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/RAM_analysis/bos'
+    config['workingdir'] = '/idata/cdl/lowen/corrmat_stability_time'
+    config['startdir'] = '/idata/cdl/lowen'
+    config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
+
+# job creation options
+config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
+config['lockdir'] = os.path.join(config['workingdir'], 'locks')
+config['resultsdir'] = os.path.join(config['workingdir'], 'results')
+config['pyFRlocsdir'] = os.path.join(config['startdir'], 'pyFR_locs/results')
+
+# runtime options
+config['jobname'] = "full_mats"  # default job name
+config['q'] = "default"  # options: default, testing, largeq
+config['nnodes'] = 6  # how many nodes to use for this one job
+config['ppn'] = 4  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['walltime'] = '18:00:00'  # maximum runtime, in h:MM:SS
+#config['startdir'] = '/ihome/lowen/repos/supereeg/examples'  # directory to start the job in
[…]

### 2019-12-09 code/scripts/corrmat_stability_time/corrmats_stability_time.py

@@ -1,0 +1,165 @@
+
+import supereeg as se
+import numpy as np
+import sys
+import os
+import matplotlib.ticker as tkr
+from scipy.spatial.distance import cdist
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+from config import config
+
+
+fname = sys.argv[1]
+
+data = sys.argv[2]
+
+chunk_size = 10000
+
+rand_iters = 2
+
+results_dir = os.path.join(config['resultsdir'], data)
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+
+def electrode_search(fname, threshold=10):
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    return sum(~thresh_bool)
+
+
+def corr_corrmats(bo_1, bo_2):
+
+    mo_1 = se.Model(bo_1)
+    mo_2 = se.Model(bo_2)
+
+    tril_1 = np.atleast_2d(mo_1.get_model()[np.tril_indices(locs_total, k=-1)])
+    tril_2 = np.atleast_2d(mo_2.get_model()[np.tril_indices(locs_total, k=-1)])
+
+    return 1 - cdist(tril_1, tril_2, 'correlation')
+
+
+print(fname)
+
+elec_count = electrode_search(sys.argv[1])
+
+if elec_count > 1:
+
+    fname =os.path.basename(os.path.splitext(fname)[0])
+
+    print('running time stability for : ' + fname)
+
+    # load brain object
+    bo = se.load(sys.argv[1])
+
+    # filter
+    bo.apply_filter()
+
+    time_total = bo.get_data().shape[0]
+    locs_total = bo.get_data().shape[1]
+
+    divided_time = int(time_total/ 2)
+
+    chunk_totals = int(divided_time / chunk_size)
+
+    full_data = bo.get_data().values
+
+    all_idx = np.arange(time_total)
+    half_1_idx = np.random.choice(time_total, replace=False, size=divided_time)
+    half_2_idx = np.delete(all_idx, half_1_idx)
+
+    n_samples = chunk_totals
+
+    corrs_rand = np.zeros((rand_iters, n_samples))
+
+    half_1_bo = bo[half_1_idx]
+    half_2_bo = bo[half_2_idx]
+
+
+    for r in np.arange(rand_iters):
+
+        unused = np.arange(divided_time)
[…]

### 2019-12-09 code/scripts/corrmat_stability_time/corrmats_stability_time_submit.py

@@ -1,0 +1,146 @@
+#!/usr/bin/python
+
+# create a bunch of job scripts
+from config import config
+from subprocess import call
+import glob
+import os
+import socket
+import getpass
+import datetime as dt
+
+
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+try:
+    os.stat(config['resultsdir'])
+except:
+    os.makedirs(config['resultsdir'])
+
+# each job command should be formatted as a string
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'corrmats_stability_time.py')
+
+# only make a few:
+
+# files = map(lambda x: os.path.join(config['datadir'],x), bos)
+
+data = str('pyfr')
+
+# or make all:
+files = glob.glob(os.path.join(config[data+'datadir'],'*.bo'))
+
+
+job_commands = list(map(lambda x: x[0]+" "+str(x[1])+" " + data,
+                        zip([job_script]*len(files), files)))
+
+# job_names should specify the file name of each script (as a list, of the same length as job_commands)
+
+job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_' + data +'.sh', files))
+# ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
+assert(len(job_commands) == len(job_names))
+
+
+# job_command is referenced in the run_job.sh script
+# noinspection PyBroadException,PyUnusedLocal
+def create_job(name, job_command):
+    # noinspection PyUnusedLocal,PyShadowingNames
+    def create_helper(s, job_command):
+        x = [i for i, char in enumerate(s) if char == '<']
+        y = [i for i, char in enumerate(s) if char == '>']
+        if len(x) == 0:
+            return s
+
+        q = ''
+        index = 0
+        for i in range(len(x)):
+            q += s[index:x[i]]
+            unpacked = eval(s[x[i]+1:y[i]])
+            q += str(unpacked)
+            index = y[i]+1
+        return q
+
+    # create script directory if it doesn't already exist
+    try:
+        os.stat(config['scriptdir'])
+    except:
+        os.makedirs(config['scriptdir'])
+
+    template_fd = open(config['template'], 'r')
+    job_fname = os.path.join(config['scriptdir'], name)
+    new_fd = open(job_fname, 'w+')
+
+    while True:
+        next_line = template_fd.readline()
+        if len(next_line) == 0:
+            break
[…]

### 2019-12-09 code/scripts/visbrain_plots/corr_plot.py

@@ -17,7 +17,7 @@ KW = dict(title_size=14., zoom=2)
 
 template_brain = 'B3'
 
-bo_list = glob.glob(os.path.join(nii_bo_dir, '*_raw_*.bo'))
+bo_list = glob.glob(os.path.join(nii_bo_dir, '*.bo'))
 
 for b in bo_list:
 
@@ -63,4 +63,4 @@ for b in bo_list:
 
     #sc.add_to_subplot(cb_proj, row=0, col=2, width_max=100)
 
-    sc.screenshot(os.path.join(fig_dir, fname + '.pdf'), transparent=True)
+    sc.screenshot(os.path.join(fig_dir, fname + '.png'), transparent=True)

### 2019-12-11 code/scripts/corrmat_stability_time/config.py
updates to corrmate stability

@@ -16,8 +16,8 @@ if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname(
 else:
     config['pyfrdatadir'] = '/idata/cdl/data/ECoG/pyFR/data/bo'
     config['ramdatadir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/RAM_analysis/bos'
-    config['workingdir'] = '/idata/cdl/lowen/corrmat_stability_time'
-    config['startdir'] = '/idata/cdl/lowen'
+    config['workingdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/supereeg_revision/corrmat_stability_time'
+    config['startdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/supereeg_revision/'
     config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
 
 # job creation options

### 2019-12-11 code/scripts/corrmat_stability_time/corrmats_stability_time_submit.py

@@ -133,7 +133,7 @@ for n, c in zip(job_names, job_commands):
             next_job = create_job(n, c)
 
             if (socket.gethostname() == 'discovery.hpcc.dartmouth.edu') or (socket.gethostname() == 'ndoli.hpcc.dartmouth.edu'):
-                submit_command = 'echo "[SUBMITTING JOB: ' + next_job + ']"; qsub'
+                submit_command = 'echo "[SUBMITTING JOB: ' + next_job + ']"; mksub'
             else:
                 submit_command = 'echo "[RUNNING JOB: ' + next_job + ']"; sh'
 

### 2019-12-11 code/scripts/corrmat_stability_time/run_job.sh

@@ -22,6 +22,8 @@
 # set the working directory *of the job* to the specified start directory
 cd <config['startdir']>
 
+module load python
+
 echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
 source activate supereeg_env
 

### 2019-12-11 code/scripts/corrmat_stability_time/corrmats_stability_time_submit.py
update cluster

@@ -132,7 +132,7 @@ for n, c in zip(job_names, job_commands):
         if lock(next_lockfile):
             next_job = create_job(n, c)
 
-            if (socket.gethostname() == 'discovery.hpcc.dartmouth.edu') or (socket.gethostname() == 'ndoli.hpcc.dartmouth.edu'):
+            if (socket.gethostname() == 'discovery7.hpcc.dartmouth.edu') or (socket.gethostname() == 'ndoli.hpcc.dartmouth.edu'):
                 submit_command = 'echo "[SUBMITTING JOB: ' + next_job + ']"; mksub'
             else:
                 submit_command = 'echo "[RUNNING JOB: ' + next_job + ']"; sh'

### 2019-12-12 code/scripts/corrmat_stability_patient/corrmats_stability_patient.py
added corrmat stability for patients

@@ -1,0 +1,114 @@
+
+import supereeg as se
+import numpy as np
+import sys
+import os
+import glob as glob
+import matplotlib.ticker as tkr
+from scipy.spatial.distance import cdist
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+from config import config
+
+
+data = sys.argv[1]
+
+
+rand_iters = 2
+
+results_dir = os.path.join(config['resultsdir'], data)
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+
+def electrode_search(fname, threshold=10):
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    return sum(~thresh_bool)
+
+
+def corr_corrmats(mo_1, mo_2):
+
+    locs_total = mo_1.get_model().shape[1]
+
+    tril_1 = np.atleast_2d(mo_1.get_model()[np.tril_indices(locs_total, k=-1)])
+    tril_2 = np.atleast_2d(mo_2.get_model()[np.tril_indices(locs_total, k=-1)])
+
+    return 1 - cdist(tril_1, tril_2, 'correlation')
+
+
+
+print('running time stability across patients for: ' + data)
+
+files = glob.glob(os.path.join(config[data + 'datadir'], '*.mo'))
+#
+# for f in files:
+#
+#     model = se.load(f)
+#     try_parse = model.get_slice(np.arange(100))
+#     try_parse.save(f)
+
+
+total_patients = len(files)
+
+divided_patients = int(total_patients/ 2)
+
+all_idx = np.arange(total_patients)
+half_1_idx = np.random.choice(total_patients, replace=False, size=divided_patients)
+half_2_idx = np.delete(all_idx, half_1_idx)
+
+np.random.shuffle(half_2_idx)
+
+n_samples = len(half_2_idx)
+
+corrs_rand = np.zeros((rand_iters, n_samples))
+
+
+half_1_mo = se.Model(list(np.array(files)[half_1_idx]), n_subs=len(half_1_idx))
+
+
+for r in np.arange(rand_iters):
+
+    for e, i in enumerate(half_2_idx):
+
+        if e == 0:
+
+            mo_2 = se.Model(np.array(files)[half_2_idx[e]], n_subs=1)
+
[…]

### 2019-12-12 code/scripts/corrmat_stability_patient/corrmats_stability_patient_submit.py

@@ -25,16 +25,11 @@ job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'corrmats
 
 data = str('pyfr')
 
-# or make all:
-files = glob.glob(os.path.join(config[data+'datadir'],'*.bo'))
-
-
-job_commands = list(map(lambda x: x[0]+" "+str(x[1])+" " + data,
-                        zip([job_script]*len(files), files)))
-
+job_commands = list(map(lambda x: x[0]+" " + data, zip([job_script]*1, range(1))))
 # job_names should specify the file name of each script (as a list, of the same length as job_commands)
 
-job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_' + data +'.sh', files))
+job_names = list(map(lambda x: 'model_'+ data + '.sh', range(len(job_commands))))
+
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
 
 assert(len(job_commands) == len(job_names))

### 2019-12-12 code/scripts/corrmat_stability_patient/run_job.sh

@@ -1,0 +1,34 @@
+#!/bin/bash -l
+
+# DO NOT MODIFY THIS FILE!
+# MODIFY config.py AND create_and_submit_jobs.py AS NEEDED
+
+# Portable Batch System (PBS) lines begin with "#PBS".  to-be-replaced text is sandwiched between angled brackets
+
+# declare a name for this job
+#PBS -N <config['jobname']>
+
+# specify the queue the job will be added to (if more than 600, use largeq)
+#PBS -q <config['q']>
+
+# specify the number of cores and nodes (estimate 4GB of RAM per core)
+#PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
+
+# specify how long the job should run (wall time)
+#PBS -l walltime=<config['walltime']>
+
+# set the working directory *of this script* to the directory from which the job was submitted
+
+# set the working directory *of the job* to the specified start directory
+cd <config['startdir']>
+
+module load python
+
+echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
+source activate supereeg_env
+
+# run the job
+<config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
+
+source deactivate supereeg_env
+

### 2019-12-12 code/scripts/corrmat_stability_patient/corrmats_stability_patient.py
add compilation code

@@ -45,12 +45,6 @@ def corr_corrmats(mo_1, mo_2):
 print('running time stability across patients for: ' + data)
 
 files = glob.glob(os.path.join(config[data + 'datadir'], '*.mo'))
-#
-# for f in files:
-#
-#     model = se.load(f)
-#     try_parse = model.get_slice(np.arange(100))
-#     try_parse.save(f)
 
 
 total_patients = len(files)
@@ -87,28 +81,10 @@ for r in np.arange(rand_iters):
 
         corrs_rand[r, e] = corr_corrmats(half_1_mo, mo_2)[0][0]
 
-corrs_rand = np.mean(corrs_rand, axis=0)
+#corrs_rand = np.mean(corrs_rand, axis=0)
 
 stable_npz = os.path.join(results_dir, data + '.npz')
 
 np.savez(stable_npz, rand=corrs_rand)
 
 
-#
-# def numfmt(x, pos):
-#     s = '{}'.format(np.round((x / (100 / percent_increase) + (percent_increase / 100)), 2))
-#     return s
-
-
-#yfmt = tkr.FuncFormatter(numfmt)  # create your custom formatter function
-
-# fig, ax = plt.subplots()
-# #fig.gca().xaxis.set_major_formatter(yfmt)
-# ax.plot(corrs_close, 'k', label='Close')
-# ax.plot(corrs_apart, 'r', label='Apart')
-# ax.plot(corrs_rand, 'g', label='Random')
-# leg = ax.legend()
-# plt.ylabel('Correlation of matrices')
-# plt.xlabel('% Time')
-#
-# plt.show()

### 2019-12-12 code/scripts/corrmat_stability_time/compile_cormmats_stabile.py

@@ -1,0 +1,69 @@
+
+from config import config
+import os
+import glob as glob
+import pandas as pd
+import sys
+from sklearn.neighbors import NearestNeighbors
+import numpy as np
+import supereeg as se
+
+### for cluster:
+
+data = sys.argv[1]
+
+chunk_size = 10000
+
+rand_iters = 2
+
+results_dir = os.path.join(config['resultsdir'], data)
+
+
+def compile_corrs(file_path):
+    """
+        Compiles correlation values - as well as other subject specific paramters - creates the compiled pandas dataframe used for figures
+
+        Parameters
+        ----------
+
+        file_path : string
+            path to npz file containing correlation values
+
+        Returns
+        ----------
+        results : dataframe
+            compiled dataframe with: Subject, electrode, correlation, samples, and sample rate
+
+        """
+
+    data = np.load(file_path, mmap_mode='r')
+    f_name = os.path.splitext(os.path.basename(file_path))[0]
+    # rand=data['rand']
+    # apart = data['apart']
+    # close=data['close']
+    # sample_rate= data['sample_rate']
+    # samples=data['samples']
+
+    return pd.DataFrame({'rand': data['rand'], 'apart': data['apart'], 'close': data['close'],
+                         'Subject': f_name, 'sample_rate': data['sample_rate'], 'samples': data['samples']})
+
+
+files = glob.glob(os.path.join(results_dir, '*.npz'))
+
+all_corrs = pd.DataFrame()
+
+for f in files:
+
+    compile_temp = compile_corrs(f)
+    if all_corrs.empty:
+        all_corrs = compile_temp
+    else:
+        all_corrs = all_corrs.append(compile_temp)
+
+
+print('Nans for :' + str(all_corrs['Subject'][all_corrs['rand'].isna()].unique()))
+
+all_corrs.dropna(inplace=True)
+
+all_corrs.to_csv(os.path.join(config['resultsdir'], data + '.csv'))
+

### 2020-01-21 paper/main.tex
updates to stability code and pdf

@@
 \newcommand{\perexptaskreconseparated}{S3}
-\newcommand{\suppstats}{S4}
-\newcommand{\intersectmap}{S5}
+\newcommand{\freqpower}{S4}
+\newcommand{\networkpower}{S5}
+\newcommand{\suppstats}{S6}
 
@@
 recording at $\eta$ is through (direct or indirect) anatomical
-connections between structures near $x$ and $\eta$.  We use temporal
+connections between structures near $x$ and $\eta$.  Although
+anatomical and function correlations can differ
+markedly~\citep[e.g.,][]{AdacEtal11, HoneEtal09, GoniEtal14}, we use temporal
 correlations in the data to estimate these anatomical
@@
 matrix, which can become computationally intractable when $T$ is very
-large (e.g., for the patient highlighted in Fig.~\ref{fig:recon}, $T =
+large (e.g., for an example patient in Dataset 1, $T =
 12786750$). However, because Equation~\ref{eqn:reconstruction} is time
@@
     the observed and reconstructed activity at the given electrode
-    location projected to the cortical surface.}
+    location projected to the cortical surface~\citep{CombEtal19}.}
   \label{fig:corrmap}
@@
     top 10\% most informative voxels in each map (also see
-    Fig.~\intersectmap).  \textbf{C. Intersection.}  
+    Fig.~\networks Panels A.-C. All for networks within this region).  \textbf{C. Intersection.}  
     Gray areas indicate the intersections between the
-    top 10\% most informative voxels in each map.  \textbf{D. Correspondence in information
+    top 10\% most informative voxels in each map and projected onto the cortical surface~\citep{CombEtal19}. \textbf{D. Correspondence in information
       scores by voxel across Datasets 1 and 2.}  Same format as
@@
 We also wondered what frequency properties contributed to the
-reconstruction accuracy.  For this analysis, we INSTERT TUDORS
-DESCRIPTION FOR FREQ ANALYSIS.
+reconstruction accuracy. To recover frequency-band specific voltage activity
+from each recording, a second-order Butterworth filter was applied
+across bands $\delta$, $\theta$, $\alpha$, $\beta$, $\gamma_L$, and
+$\gamma_H$ with respective frequency ranges 2-4 Hz, 4-8 Hz, 8-12 Hz,
+12-30 Hz, 30-60 Hz, and 60-100 Hz. Bandpass signals contain
+information about the phase and amplitude of the underlying frequency
+band, providing the most detailed view of the activity at that
+frequency. Additionally, we calculated the reconstruction accuracies
+using power at each band by taking the absolute
+value of the Hilbert tranform of the bandpassed signal (see Fig.~\freqpower). To compute the broadband power (BB), we
+first computed instantaneous power at 50 log-spaced frequencies
+between 2 and 100 Hz using Morlet wavelets (n=4). Then, for each time
+point and electrode, we fitted a robust Huber regression to frequency
+and power in log-space, and calculated the mean height of the
+resulting line. We then followed the same procedure outlined above
+(see Fig.~\ref{fig:methods}) to
+obtain the reconstruction accuracy at each bandpassed frequency as well
+as broadband power for both datasets (see Fig.~\ref{fig:frequency}).
+We found
+the best average reconstruction accuracy for each dataset was obtained using broadband
+power, which is a correlate of neural firing
+~\citep{MannEtal09}. We also found a similar trend in reconstruction
+accuracy for frequency bands across the two datasets, performing better at lower
+frequencies (peaking at $\alpha$) and worst at high frequencies.
 
@@
     reflects performance using a correlation model learned from the same
-    patient who contributed the to-be-reconstructed electrode.
+    patient who contributed the to-be-reconstructed electrode, colored
+    by frequency and includes the raw voltages displayed in
+    Fig.~\ref{fig:corrmap}A in gray.
     \textbf{B.~Statistical summary of across-patient reconstruction
@@
     triangles of each map denote the corresponding p-values for the
-    t-tests. The diagonal entries display the relative average
-    reconstruction accuracy given to each frequency band. \textbf{C.~Statistical summary ofwithin-patient reconstruction
+    t-tests. The diagonal entries display the average
+    reconstruction accuracy given to each frequency
+    band. \textbf{C.~Statistical summary of within-patient reconstruction
       quality by electrode for each frequency band in Dataset 1.}
@@
     reconstruction accuracy distributions for each frequency band for
-    Dataset 2 in
-    the same format as Panel A. \textbf{E.~Statistical summary of
+    Dataset 2. \textbf{E.~Statistical summary of
       across-patient reconstruction quality by electrode for each
@@
     C for Dataset 2.}
-  \label{fig: frequency}
+  \label{fig:frequency}
 \end{figure}
+
+We also wanted to see how the most informative regions changed by
+frequency. Lower frequency oscillations, such as delta, theta, and alpha, have
+been posited to be processing modes which span large swaths of
+cortical regions and are thought to serve the purpose of integration
+across many cortical sites ~\citep{Knya12}. Higher frequency
+oscillations such as beta and gamma, are more limited to topographic
+area ~\citep{Nune95}, and are modulated by slow oscillations
+hierarchically ~\citep{EngeEtal10}. Using the frequency-specific reconstruction accuracies, we
+followed the process outlined in Fig.~\ref{fig:informap}C, to obtain
+the most informative locations for each frequency.  When we examined the intersection
+between the top 10\% most informative voxels across the two datasets
+for each bandpassed frequency, we found a somewhat consistent hierarchical
+structure (see Fig.~\ref{fig:networks}E).
+
+We then wondered which
+networks were involved in each of
+these frequency-specific intersecting regions.  To better understand the networks involved
+we colored the regions (Fig.~\ref{fig:networks}A) based on the
+network parcellation ~\citep[using $k$=7;][]{YeoEtal11}} (Fig.~\ref{fig:networks}D) and calculated the proportion of each
+of those networks (Fig.~\ref{fig:networks}B).  Consistent with the idea outlined
+above, we found networks most involved in the lowest frequency band,
+$\delta$, were networks involved integration and global processing
+(specifically the dorsal attention ~\citep{MarzEtal13}, default mode,
+and frontoparietal networks).  Although these networks are also seen
+in the $\theta$ intersection, they are less proportionally to the
+visual network.  Alpha power is consistently modulated in EEG studies
+of attention and visuo-motor ~\citep{MartiEtal10, MarzEtal13}, and we
+similarly found a high proportion of visual and somatomotor networks
+within this band.  We found $\beta$ intersections to predominantly
+consist of somatomotor network, consistent with~\citep{RittEtal08,
+  VanEEtal11}.  Also consistent with heavily cited
+literature~\citep{FrieEtal07}, the network most predominant in the
+$\gamma$ intersection was the visual network.  Lastly, broadband power
+was found predominantly in frontoparietal and default mode networks,
+consistent with ~\{OssaEtal11}.  We then carried out a
+meta analysis using Neurosynth~\citep{RubiEtal17} to identify the 5
+terms most commonly associated with the given map
+(Fig.~\ref{fig:networks}C).
 
@@
   \includegraphics[width=\textwidth]{figs/networks}
-  \caption{\textbf{Electrode sampling density by location.}
-    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
-    voxel is colored by the proportion of total electrodes in the
-    dataset that are
-    located within a 20~MNI unit radius sphere centered on the given
-    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
-      2.}  This panel displays the sampling density map for Dataset 2,
-    in the same format as Panel A.  \textbf{C.~Correspondence in
-      sampling density by voxel across Datasets 1 and 2.}  The
-    two-dimensional histogram displays the by-voxel densities in the
-    two Datasets, and the one-dimensional histograms display the
-    proportions of voxels in each dataset with the given density
-    value.  The correlation reported in the panel is across voxels in
-    the 4~mm$^3$ MNI brain.}
-  \label{fig: networks}
+  \caption{\textbf{Most informative electrode locations by frequency
+      and the networks involved.}
+    \textbf{A.~Intersections across datasets for each frequency.} The
+    inflated brain plots display the intersections between the
+    top 10\% most informative voxels were calculated as described in Fig.~\ref{fig:informap}
+    for each frequency and projected onto the cortical surface~\citep{CombEtal19}. Intersecting voxels are colored according to the 7 networks
+    from~\citep{YeoEtal11}.
+    \textbf{B.~Proportion of networks in most informative electrode locations by
+    frequency.}  Pie graphs display the proportion of the 7 networks
+  ~\citep{YeoEtal11} in the most informative locations by
+  frequency, and are sized relative to the average reconstruction
+  accuracy for each frequency. \textbf{C.~Terms associated with most informative
+    electrode locations.}  The
+    lists of terms display the top five Neurosynth
+    terms~\citep{RubiEtal17} decoded from the corresponding brain
+    maps, and colored according the frequency (see Panel
+    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
+    Seven network parcellation as described
+    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
+      frequency.} The inflated brain plot displays the locations of
+    the most informative locations (Panel A), colored by frequency,
+    and projected onto the cortical surface~\citep{CombEtal19}.}
+  \label{fig:networks}
 \end{figure}
@@
 SuperEEG reconstructs LFPs throughout the brain, one could in
-principle use gamma or broadband power in the reconstructed signals to
+principle use broadband power in the reconstructed signals to
 estimate the corresponding firing rates (though not the timings of
-individual action potentials).
+individual action potentials). Interestingly, our frequency-specific
+analysis yielded the best reconstruction accuracies using broadband
+power.
 

### 2020-01-21 paper/supporting_information.tex
updates to stability code and pdf

@@
 \begin{document}
+
+\begin{titlepage}
   \maketitle
+  \end{titlepage}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{figs/supplemental_1}
+\includegraphics[width=\textwidth]{figs/supplemental_1}
 \caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
@@
     the observed and reconstructed activity at the given electrode
-    location.}
+    location projected to the cortical surface~\citep{CombEtal19}.}
 \label{fig:supplemental_3}
@@
 \includegraphics[width=\textwidth]{figs/supplemental_4}
+\caption{\textbf{Reconstruction quality across all electrodes in two
+      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      each frequency band in Dataset 1.} Same format as Figure~5A, but
+    using power at each frequency.
+    \textbf{B.~Statistical summary of across-patient reconstruction
+      quality by electrode for each frequency band in Dataset 1.} Same format as Figure~5B, but
+    using power at each frequency.\textbf{C.~Statistical summary of within-patient reconstruction
+      quality by electrode for each frequency band in Dataset 1.}
+    This panel displays the within-patient statistical summary,
+    in the same format as Panel B.  \textbf{D.~Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      each frequency band in Dataset 2.}  This panel displays
+    reconstruction accuracy distributions for each frequency band for
+    Dataset 2. \textbf{E.~Statistical summary of
+      across-patient reconstruction quality by electrode for each
+      frequency band in Dataset 2.} This is the same format as Panel
+    B for Dataset 2. \textbf{F.~Statistical summary of
+      within-patient reconstruction quality by electrode for each
+      frequency band in Dataset 2.}This is the same format as Panel
+    C for Dataset 2.}
+\label{fig:supplemental_4}
+\end{figure}
+
+\begin{figure}[ptb]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_5}
+\caption{\textbf{Most informative electrode locations by frequency
+      and the networks involved.}
+    \textbf{A.~Intersections across datasets for each frequency.}  Same format as Figure~6A, but
+    using power at each frequency.
+    \textbf{B.~Proportion of networks in most informative electrode locations by
+    frequency.}  Pie graphs display the proportion of the 7 networks
+  ~\citep{YeoEtal11} in the most informative locations by
+  frequency, and are sized relative to the average reconstruction
+  accuracy for each frequency. \textbf{C.~Terms associated with most informative
+    electrode locations.}  The
+    lists of terms display the top five Neurosynth
+    terms~\citep{RubiEtal17} decoded from the corresponding brain
+    maps, and colored according the frequency (see Panel
+    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
+    Seven network parcellation as described
+    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
+      frequency.} The inflated brain plot displays the locations of
+    the most informative locations (Panel A), colored by frequency,
+    and projected onto the cortical surface~\citep{CombEtal19}.}
+\label{fig:supplemental_5}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_6}
 \caption{\textbf{Reconstruction accuracy versus within-subject data
@@
   A--F.}
-\label{fig:supplemental_4}
+\label{fig:supplemental_6}
 \end{figure}
 
-\begin{figure}[ptb]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_5}
-\caption{\textbf{Most informative electrode locations.}  This map
-  shows the region outlined in white from Figure~5 in greater detail.
-  Across Datasets 1 and 2, electrodes in these locations were
-  identified as yielding the (10\%) best reconstruction accuracies at
-  \textit{other} locations throughout the brain.  The $x$-coordinates
-  in each panel denote the positions of the sagittal slices in MNI space.}
-\label{fig:supplemental_5}
-\end{figure}
-
+\bibliography{CDL-bibliography/memlab}
+\bibliographystyle{CSE}
 % \newpage

### 2020-01-21 paper/supporting_information.tex
updates to paper

@@
 \usepackage{natbib}
+\usepackage{hyperref}
 \usepackage{pxfonts}
@@
 
-\bibliographystyle{apa}
+%\bibliographystyle{apa}
 
 \begin{document}
-
-\begin{titlepage}
-  \maketitle
-  \end{titlepage}
 
@@
 \renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\bibnumfmt}[1]{[S#1]}
-\renewcommand{\citenumfont}[1]{S#1}
+
+\begin{titlepage}
+  \maketitle
+\end{titlepage}
 
@@
 
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_7}
+\caption{\textbf{Stability of correlation matrix across time.} \textbf{A.--B.  Features from
+    Dataset 1.}  Features include: (\textbf{A. Correlation of split
+  halves by the percent samples included.})  For each patient, we
+  split the timeseries data in
+  half and created a correlation matrix with one half.  With the
+  remaining data, we created the second correlation matrix with more
+  and more time samples (in 1000 sample increments).  These time
+  samples were either drawn randomly (``Random'') , or were drawn sequentially from
+  either the closest timepoint (``Close'' ) or the furthest timepoint
+  (``Apart'' ). The two correlation matrices were then correlated, and the
+  coefficient plotted relative to the percentage of data included.  (\textbf{B. Correlation of split
+  halves by the number of time samples included.})
+Same analysis as Panel A, but the
+  coefficient plotted relative to the total number of samples included.
+  \textbf{C.--D. Features from Dataset 2.}  Analogous format to Panels
+  A--B.}
+\label{fig:supplemental_7}
+\end{figure}
+
+\begin{figure}[p]
+\centering
+\includegraphics[width=\textwidth]{figs/supplemental_8}
+\caption{\textbf{Stability of correlation matrix across patients.} \textbf{A.--B.  Features from
+    Dataset 1.}  Features include: (\textbf{A. Correlation of split
+  halves by number of patients included.})  For 500 iterations, we randomly split the
+patient-specific correlations in half, then created one correlation
+matrix with the first half and created the second correlation matrix
+using more and more patients. The two correlation matrices were then correlated, and the
+  coefficient plotted relative to the number of patients included.
+  (\textbf{B. Standard error of the mean across iterations by the
+    number of patients included.})
+To measure the variability across the iterations, we plot the standard
+error of the mean as a function of the number of patients included in
+the second correlation matix.  
+  \textbf{C.--D. Features from Dataset 2.}  Analogous format to Panels
+  A--B.}
+\label{fig:supplemental_8}
+\end{figure}
+
+\renewcommand{\bibnumfmt}[1]{[S#1]}
+\renewcommand{\citenumfont}[1]{S#1}
 \bibliography{CDL-bibliography/memlab}

### 2020-01-23 code/scripts/ave_mats/run_job.sh
removing intermediate commits

@@ -1,4 +1,3 @@
-
 #!/bin/bash -l
 
 # DO NOT MODIFY THIS FILE!
@@ -15,18 +14,20 @@
 # specify the number of cores and nodes (estimate 4GB of RAM per core)
 #PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
 
+# no more #PBS -l feature=<config['feature']>
+
 # specify how long the job should run (wall time)
 #PBS -l walltime=<config['walltime']>
 
 # set the working directory *of this script* to the directory from which the job was submitted
 
 # set the working directory *of the job* to the specified start directory
-cd <config['startdir']>
+# cd <config['startdir']>
 
 echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
-source activate supereeg_env
+
+# conda init bash
+conda activate supereeg_env
 
 # run the job
 <config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
-
-source deactivate supereeg_env

### 2020-01-23 code/scripts/full_mats/bandbrain.py

@@ -1,0 +1,64 @@
+from supereeg import Brain
+import copy
+
+class BandBrain(Brain):
+    def __init__(self, bo, og_bo=None, og_filter_inds=None):
+        super().__init__(bo)
+        self.og_filter_inds = og_filter_inds
+        self.og_bo = og_bo
+
+    """ A brain sublass that filters electrodes based on the original .bo (og_bo) """
+    def apply_filter(self, og_bo=None, inplace=True):
+        """ Return a filtered copy """
+        if og_bo is None:
+            og_bo = self.og_bo
+
+        if self.filter is None:
+            if not inplace:
+                return copy.deepcopy(self)
+            else:
+                return None
+
+        x = copy.copy(self.__dict__)
+        x['data'] = self.get_data()
+        x['locs'] = self.get_locs()
+        x['kurtosis'] = og_bo.kurtosis
+
+        if self.filter == 'kurtosis':
+            x['kurtosis'] = x['kurtosis'][x['kurtosis'] <= x['kurtosis_threshold']]
+
+        for key in ['n_subs', 'n_elecs', 'n_sessions', 'dur', 'filter_inds','og_filter_inds', 'nifti_shape', 'og_bo']:
+            if key in x.keys():
+                x.pop(key)
+
+        boc = Brain(**x)
+        boc.filter = None
+        boc.update_info()
+        if inplace:
+            self.__init__(boc, og_bo)
+        else:
+            return boc
+
+    def get_data(self, og_bo=None):
+        """
+        Gets data from brain object
+        """
+        # if og_bo is not None:
+        #     og_bo.update_filter_inds()
+        # try:
+        #     filter_inds = self.og_bo.filter_inds
+        # except:
+        #     filter_inds = self.og_filter_inds
+        return self.data.iloc[:, self.og_filter_inds.ravel()].reset_index(drop=True)
+
+    def get_locs(self, og_bo=None):
+        """
+        Gets locations from brain object
+        """
+        # if og_bo is not None:
+        #     og_bo.update_filter_inds()
+        # try:
+        #     filter_inds = self.og_bo.filter_inds
+        # except:
+        #     filter_inds = self.og_filter_inds
+        return self.locs.iloc[self.og_filter_inds.ravel(), :].reset_index(drop=True)

### 2020-01-23 code/scripts/full_mats/config.py

@@ -12,24 +12,25 @@ if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname(
     config['startdir'] = '/Users/lucyowen/Desktop/supereeg_env/'  # directory to start the job in
     config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
 else:
-    config['datadir'] = '/idata/cdl/data/ECoG/pyFR/data/bo/'
-    config['workingdir'] = '/idata/cdl/lowen/full_mats'
-    config['startdir'] = '/idata/cdl/lowen'
+    config['datadir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64/freqs'
+    config['workingdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64/'
+    config['startdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64/'
     config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
 
 # job creation options
 config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
 config['lockdir'] = os.path.join(config['workingdir'], 'locks')
-config['resultsdir'] = os.path.join(config['workingdir'], 'results')
-config['pyFRlocsdir'] = os.path.join(config['startdir'], 'pyFR_locs/results')
+config['resultsdir'] = os.path.join(config['workingdir'], 'results','union')
+config['locsdir'] = os.path.join(config['workingdir'], 'results')
+config['og_bodir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/RAM_analysis/bos'
+config['og_bodir'] = '/idata/cdl/data/ECoG/pyFR/data/bo'
 
 # runtime options
 config['jobname'] = "full_mats"  # default job name
 config['q'] = "default"  # options: default, testing, largeq
-config['nnodes'] = 6  # how many nodes to use for this one job
-config['ppn'] = 4  # how many processors to use for this one job (assume 4GB of RAM per processor)
+config['nnodes'] = 1  # how many nodes to use for this one job
+config['ppn'] = 8  # how many processors to use for this one job (assume 4GB of RAM per processor)
 config['walltime'] = '18:00:00'  # maximum runtime, in h:MM:SS
-#config['startdir'] = '/ihome/lowen/repos/supereeg/examples'  # directory to start the job in
[…]

### 2020-01-23 code/scripts/full_mats/debug.py

@@ -1,0 +1,53 @@
+
+import supereeg as se
+import numpy as np
+import sys
+import os
+from config import config
+from bandbrain import BandBrain
+
+sys.path.append(os.path.dirname(__file__))
+
+
+fname = os.path.join(os.path.dirname(__file__), 'R1065J_RAM_FR1_0_broadband.bo')
+
+def electrode_search(fname, threshold=10):
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    return sum(~thresh_bool)
+
+locs_file =  os.path.join(os.path.dirname(__file__), 'broadband_locs.npz')
+R = np.load(locs_file)['locs']
+
+elec_count = electrode_search(os.path.join(os.path.dirname(__file__), 'R1065J_RAM_FR1_0.bo'))
+
+
+if elec_count > 1:
+
+    print('creating model object: ' + fname)
+
+    # load brain object
+    bo = se.load(fname)
+
+    # turn it into my fancy ~BandBrain~
+    bo = BandBrain(bo)
+
+    # load original brain object
+    og_bo = se.load(os.path.join(os.path.dirname(__file__), 'R1065J_RAM_FR1_0.bo'))
+    # og_bo.apply_filter()
+    # mo = se.Model(og_bo, locs=R)
+
+    # filter
+    bo.apply_filter(og_bo)
+
+    # turn it back into a vanilla Brain
+    bo = se.Brain(bo)
+
+    # make model
+    mo = se.Model(bo, locs=R)
+
+    # save model
+    mo.save('out.mo')
+
+else:
+    print('skipping model (not enough electrodes pass kurtosis threshold): ' + sys.argv[1])

### 2020-01-23 code/scripts/full_mats/full_mats_job_submit.py

@@ -19,30 +19,27 @@ except:
 # each job command should be formatted as a string
 job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'full_mats.py')
 
-# only make a few:
-bos = ('FR029.mo', 'TJ001.mo', 'TJ015.mo','TJ017.mo', 'TJ025.mo','TJ027.mo')
-#
-# files = map(lambda x: os.path.join(config['datadir'],x), bos)
-
-# or make all:
 files = glob.glob(os.path.join(config['datadir'],'*.bo'))
+# completed = set([os.path.basename(x).split('.mo')[0] for x in glob.glob(os.path.join(config['resultsdir'], 'union', '*.mo'))])
+completed = []
+freqs = ['alpha', 'beta', 'delta', 'theta', 'lgamma', 'hgamma']
+for freq in freqs:
+    completed += glob.glob('/dartfs/rc/lab/D/DBIC/CDL/f003f64/ram_results_voltage/RAM_union/*' + freq + '*')
 
-# options for model: 'pyFR_union'
-model = str('pyFR_union')
-#model = str('gray')
 
-# options for vox_size: 5, 10, 20, 30
-radius =  str('20')
+fcompleted = glob.glob(os.path.join(config['resultsdir'], 'union', '*'))
+fcompleted = set([os.path.basename(x).split('.mo')[0] for x in fcompleted])
+completed = set([os.path.basename(x).split('.mo')[0] for x in completed])
+files = set([os.path.basename(x).split('.bo')[0] for x in files])
+files = [os.path.join(config['datadir'], x + '.bo') for x in completed-fcompleted]
 
-# options for vox_size: 5, 10, 20, 30
-vox_size =  str('6')
 
-job_commands = list(map(lambda x: x[0]+" "+str(x[1])+" " + model+" "+ radius+" "+ vox_size,
-                        zip([job_script]*len(files), files)))
+
+job_commands = list(map(lambda x: x[0] + ' ' + str(x[1]), zip([job_script]*len(files), files)))
 
 # job_names should specify the file name of each script (as a list, of the same length as job_commands)
 
-job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_' + model +'_'+ radius+'_'+ vox_size + '.sh', files))
+job_names = list(map(lambda x: os.path.basename(os.path.splitext(x)[0])+'_model.sh', files))
[…]

### 2020-01-23 code/scripts/make_broadband/run_job.sh

@@ -11,6 +11,8 @@
 # specify the queue the job will be added to (if more than 600, use largeq)
 #PBS -q <config['q']>
 
+# getting rid of this line temporarily #PBS -l feature=<config['feature']> 
+
 # specify the number of cores and nodes (estimate 4GB of RAM per core)
 #PBS -l nodes=<config['nnodes']>:ppn=<config['ppn']>
 
@@ -22,8 +24,9 @@
 # set the working directory *of the job* to the specified start directory
 cd <config['startdir']>
 
-echo ACTIVATING supereeg VIRTUAL ENVIRONMENT
+echo ACTIVATING supereeg_env VIRTUAL ENVIRONMENT
 conda activate supereeg_env
 
 # run the job
 <config['cmd_wrapper']> <job_command> #note: job_command is reserved for the job command; it should not be specified in config.py
+

### 2020-01-23 code/scripts/make_freqs/config.py

@@ -7,32 +7,28 @@ config['template'] = 'run_job.sh'
 
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
 if (socket.gethostname() == 'Lucys-MacBook-Pro-3.local') or (socket.gethostname() == 'vertex.kiewit.dartmouth.edu') or (socket.gethostname() == 'vertex.local'):
-    config['datadir'] = '/Users/lucyowen/Desktop/supereeg_env/bo/'
-    config['workingdir'] = '/Users/lucyowen/Desktop/supereeg_env/recon/'
-    config['startdir'] = '/Users/lucyowen/Desktop/supereeg_env/'  # directory to start the job in
+    config['datadir'] = '/Users/lucyowen/Desktop/seizure_data/edfs'
+    config['workingdir'] = '/Users/lucyowen/Desktop/seizure_data'
+    config['startdir'] = os.path.dirname(os.path.dirname(os.path.realpath(__file__)))  # directory to start the job in
     config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job_local.sh')
 else:
-    config['datadir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64/freqs'
+    config['datadir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/RAM_analysis/bos'
+    config['datadir'] = '/idata/cdl/data/ECoG/pyFR/data/bo'
     config['workingdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64'
-    config['startdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64/'
+    config['startdir'] = '/dartfs/rc/lab/D/DBIC/CDL/f003f64'
     config['template'] = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'run_job.sh')
 
 # job creation options
 config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
 config['lockdir'] = os.path.join(config['workingdir'], 'locks')
-config['resultsdir'] = os.path.join(config['workingdir'], 'results')
-config['modeldir'] = os.path.join(config['resultsdir'], 'union')
-config['avedir'] = os.path.join(config['startdir'], 'ave_mats/results')
-config['og_bodir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/RAM_analysis/bos'
[…]

### 2020-01-23 code/scripts/make_freqs/make_freq_bos.py

@@ -1,0 +1,50 @@
+import sys
+import os
+import glob as glob
+import supereeg as se
+from helpers import power_breakdown, butter_filt, butter_bandpass_filter
+import pandas as pd
+import numpy as np
+from config import config
+import traceback
+
+SAMPLE_RATE=200
+
+freq = sys.argv[1]
+
+filterfreqs = np.array([[2,4], [4,8], [8,12], [12,30], [30, 60], [60,SAMPLE_RATE/2 - 1]])
+freqnames = ['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma']
+
+freq_range = filterfreqs[freqnames.index(freq)]
+
+bodir = config['datadir']
+bo_files = glob.glob(os.path.join(bodir, '*.bo'))
+
+for s, bo_file in enumerate(bo_files):
+    try:
+        fname = os.path.splitext(os.path.basename(bo_file))[0]
+
+        bo_f_file = os.path.join(config['resultsdir'], fname + '_' + freq + '.bo')
+
+        if not os.path.exists(bo_f_file):
+
+            bo = se.load(bo_file)
+            bo.filter = None
+
+            # f_data = butter_filt(bo.data.values, 60, bo.sample_rate[0])
+            f_data = power_breakdown(bo.data.values, freq_range, SAMPLE_RATE)
+
+            bo_f = se.Brain(data=f_data, locs=bo.locs, sample_rate=bo.sample_rate,
+                                    sessions=bo.sessions.values, kurtosis=bo.kurtosis)
+
+            bo_f.save(bo_f_file)
+
+            print('saving: ' + bo_f_file)
+
+        else:
+            print(bo_f_file + ' already exists')
+
+
+    except:
+        print('issue with ' + bo_file)
+        traceback.print_exc()

### 2020-01-23 code/scripts/make_freqs/make_freq_bos_submit.py

@@ -2,71 +2,34 @@
 
 # create a bunch of job scripts
 from config import config
-from subprocess import call, run, PIPE
-import glob
+from subprocess import call
+import glob as glob
 import os
 import socket
 import getpass
 import datetime as dt
-import supereeg as se
-from supereeg.load import load
-import time
-import pandas as pd
-from supereeg.helpers import filter_subj as filtsub
 import numpy as np
 
+
 # ====== MODIFY ONLY THE CODE BETWEEN THESE LINES ======
+
 try:
     os.stat(config['resultsdir'])
 except:
     os.makedirs(config['resultsdir'])
 
-def electrode_search(fname, threshold=10):
-    basefname = os.path.basename(fname)
-    freq = fname.split('_')[-1].split('.bo')[0]
-    og_fname = os.path.join(config['og_bodir'], basefname.split('_' + freq)[0] + '.bo')
-    if not freq in set(['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma', 'broadband', 'raw']):
-        og_fname = fname 
-    kurt_vals = se.load(og_fname, field='kurtosis')
-    thresh_bool = kurt_vals > threshold
-    return sum(~thresh_bool)
+# frequencies to loop over
+filterfreqs = np.array([[2,4], [4,8], [8,12], [12,30], [30, 60], [60,125]])
+freqnames = ['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma']
 
 
 # each job command should be formatted as a string
-job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'recon.py')
+job_script = os.path.join(os.path.dirname(os.path.realpath(__file__)), 'make_freq_bos.py')
 
-freqnames = ['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma', 'broadband']
-completed = []
-for freq in freqnames:
-    completed += glob.glob(os.path.join(config['resultsdir'], freq + '_recon', '*_within.npz'))
-
-
-completed = set(['_'.join(os.path.basename(os.path.splitext(f)[0]).split('_')[:-2]) for f in completed])
-
-all_files = set(glob.glob(os.path.join(config['datadir'],'*.bo')))
-
-files = all_files - completed
-
-# bos = ('BW001.bo', 'BW013.bo')file_
-# files = list(map(lambda x: os.path.join(config['datadir'],x), bos))
-#print(files)
[…]

### 2020-01-23 code/scripts/make_freqs/make_freq_bos_voltage.py

@@ -1,0 +1,50 @@
+import sys
+import os
+import glob as glob
+import supereeg as se
+from helpers import power_breakdown, butter_filt, butter_bandpass_filter
+import pandas as pd
+import numpy as np
+from config import config
+import traceback
+
+SAMPLE_RATE=200
+
+freq = sys.argv[1]
+
+filterfreqs = np.array([[2,4], [4,8], [8,12], [12,30], [30, 60], [60,SAMPLE_RATE/2 - 1]])
+freqnames = ['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma']
+
+freq_range = filterfreqs[freqnames.index(freq)]
+
+bodir = config['resultsdir']
+bo_files = glob.glob(os.path.join(bodir, '*.bo'))
+
+for s, bo_file in enumerate(bo_files):
+    try:
+        fname = os.path.splitext(os.path.basename(bo_file))[0]
+
+        bo_f_file = os.path.join(config['resultsdir'], fname + '_' + freq + '.bo')
+
+        if not os.path.exists(bo_f_file):
+
+            bo = se.load(bo_file)
+            bo.filter = None
+
+            # f_data = butter_filt(bo.data.values, 60, bo.sample_rate[0])
+            f_data = power_breakdown(f_data, freq_range, SAMPLE_RATE)
+
+            bo_f = se.Brain(data=f_data, locs=bo.locs, sample_rate=bo.sample_rate,
+                                    sessions=bo.sessions.values, kurtosis=bo.kurtosis)
+
+            bo_f.save(bo_f_file)
+
+            print('saving: ' + bo_f_file)
+
+        else:
+            print(bo_f_file + ' already exists')
+
+
+    except:
+        print('issue with ' + bo_file)
+        traceback.print_exc()

### 2020-01-23 code/scripts/pyFR_locs/config.py

@@ -21,11 +21,13 @@ else:
 config['scriptdir'] = os.path.join(config['workingdir'], 'scripts')
 config['lockdir'] = os.path.join(config['workingdir'], 'locks')
 config['resultsdir'] = os.path.join(config['workingdir'], 'results')
+config['og_bodir'] = '/dartfs/rc/lab/D/DBIC/CDL/f002s72/RAM_analysis/bos'
+config['og_bodir'] = '/idata/cdl/data/ECoG/pyFR/data/bo'
 
 # runtime options
 config['jobname'] = "compile_locs"  # default job name
 config['q'] = "default"  # options: default, testing, largeq
-config['nnodes'] = 4  # how many nodes to use for this one job
+config['nnodes'] = 1  # how many nodes to use for this one job
 config['ppn'] = 16  # how many processors to use for this one job (assume 4GB of RAM per processor)
 config['walltime'] = '20:00:00'  # maximum runtime, in h:MM:SS
 config['cmd_wrapper'] = "python3"  # replace with actual command wrapper (e.g. matlab, python, etc.)

### 2020-01-23 code/scripts/pyFR_locs/union_locs.py

@@ -4,14 +4,13 @@ import numpy as np
 import glob
 import os
 import pandas as pd
-import matplotlib.pyplot as plt
-plt.switch_backend('agg')
 from config import config
-from nilearn import plotting as ni_plt
+import sys
 
 ## this script iterates over brain objects, filters them based on kurtosis value,
 ## then compiles the clean electrodes into a numpy array as well as a list of the contributing brain objects
 
+freq = sys.argv[1]
 
 results_dir = config['resultsdir']
 
@@ -26,7 +25,9 @@ data_dir = config['datadir']
 
 
 def electrode_search(fname, threshold=10):
-
+    # searching original .bo
+    fname = os.path.basename(os.path.splitext(fname)[0])
+    fname = os.path.join(config['og_bodir'], fname.split('_' + freq)[0] + '.bo')
     kurt_vals = se.load(fname, field='kurtosis')
     thresh_bool = kurt_vals > threshold
     locs = se.load(fname, field='locs')
@@ -34,29 +35,37 @@ def electrode_search(fname, threshold=10):
         locs = pd.DataFrame(locs, columns=['x', 'y', 'z'])
         return locs[~thresh_bool]
 
-freqnames = ['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma', 'broadband']
+union_locs = []
+model_data = []
 
-for freq in freqnames:
-    union_locs = []
-    model_data = []
+brain_data = glob.glob(os.path.join(data_dir, '*' + freq + '.bo'))
 
-    brain_data = glob.glob(os.path.join(data_dir, '*' + freq + '.bo'))
-    for i in brain_data:
-        try:
-            locs = electrode_search(i)
-            if not locs.empty:
-                if union_locs == []:
-                    print(os.path.basename(i))
-                    union_locs = locs.as_matrix()
-                    model_data.append(os.path.basename(i))
-                else:
-                    union_locs = np.vstack((union_locs, locs.as_matrix()))
-                    model_data.append(os.path.basename(i))
-        except:
-            pass
+if freq in 'raw':
+    brain_data = glob.glob(os.path.join(config['og_bodir'], '*.bo'))
 
-    locations, l_indices = _unique(union_locs)
+bos_used = []
 
-    results = os.path.join(results_dir, freq + '_locs.npz')
+for i in brain_data:
+    try:
+        locs = electrode_search(i)
+        if not locs.empty:
+            if union_locs == []:
+                print(os.path.basename(i))
[…]

### 2020-01-23 code/scripts/recon/debug_filtering.py

@@ -1,0 +1,59 @@
+import supereeg as se
+import os, glob
+from config import config
+from bandbrain import BandBrain
+from supereeg.load import load
+import pandas as pd
+
+
+files = glob.glob(os.path.join(config['og_bodir'], '*'))
+fullmatdict = dict()
+def electrode_search(fname, threshold=10):
+    kurt_vals = se.load(fname, field='kurtosis')
+    thresh_bool = kurt_vals > threshold
+    return sum(~thresh_bool)
+
+for f in files:
+    num_elecs = electrode_search(f)
+    fullmatdict[f] = num_elecs
+
+def filter_subj(bo, measure='kurtosis', return_locs=False, threshold=10):
+    locs = load(bo, field='locs')
+    kurt_vals = load(bo, field='kurtosis')
+    meta = load(bo, field='meta')
+    thresh_bool = kurt_vals > threshold
+    if sum(~thresh_bool) < 2:
+        pass
+    else:
+        if return_locs:
+            locs = pd.DataFrame(locs, columns=['x', 'y', 'z'])
+            return meta, locs[~thresh_bool]
+        else:
+            return meta
+
+
+def electrode_search2(fname):
+    values = filter_subj(fname, return_locs=True)
+    if values is None:
+        return 0
+    else:
+        meta, locs = values
+        return locs.shape[0]
+    
+
+recondict = dict()
+for f in files:
+    num_elecs = electrode_search2(f)
+    recondict[f] = num_elecs
+
+diffdict = dict()
+for k in recondict.keys():
+    diffdict[k] = - recondict[k] + fullmatdict[k]
+
+
+fname = glob.glob(os.path.join(config['datadir'], '*'))[0]
+freq = os.path.basename(fname).split('_')[-1].split('.bo')[0]
+og_fname = os.path.join(config['og_bodir'], os.path.basename(fname).split('_'+freq)[0] + '.bo')
+bo = se.load(fname)
+og_bo = se.load(og_fname)
+band = BandBrain(bo, og_bo)

### 2020-01-23 code/scripts/recon/recon_iter.py

@@ -1,0 +1,135 @@
+import supereeg as se
+from supereeg.helpers import _corr_column, get_rows, known_unknown, remove_electrode
+import numpy as np
+import sys, time
+import os
+from config import config
+from bandbrain import BandBrain
+import warnings
+import gc
+
+warnings.simplefilter('ignore')
+
+bo_fname = sys.argv[1]
+
+freq = bo_fname.split('_')[-1].split('.bo')[0]
+
+if not freq in set(['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma', 'broadband', 'raw']):
+    freq = 'raw'
+
+results_dir = os.path.join(config['resultsdir'], freq + '_recon')
+
+file_name = os.path.basename(os.path.splitext(bo_fname)[0])
+print(file_name)
+
+mo_mo_fname = os.path.join(config['modeldir'], file_name + '.mo')
+numtries = 0
+loaded = False
+while not loaded and numtries < 20:
+    try:
+        mo_mo = se.load(mo_mo_fname)
+        loaded = True
+    except:
+        numtries += 1
+        time.sleep(5)
+
+ave_dir = os.path.join(config['resultsdir'])
+
+ave ='ave_mat_' + freq + '.mo'
+
+numtries = 0
+loaded = False
+while not loaded and numtries < 20:
+    try:
+        mo = se.load(os.path.join(ave_dir, ave))
+        loaded = True
+    except:
+        numtries += 1
+        time.sleep(5)
+
+R = mo.get_locs().values
+
+mo_s = mo - mo_mo
+
+del mo
+del mo_mo
+gc.collect()
+
+print('models deleted')
+
+try:
+    if not os.path.exists(results_dir):
+        os.makedirs(results_dir)
+except OSError as err:
+   print(err)
+
+freq_bo = se.load(bo_fname)
+basefname = os.path.basename(bo_fname)
+freq = bo_fname.split('_')[-1].split('.bo')[0]
+og_fname = os.path.join(config['og_bodir'], basefname.split('_' + freq)[0] + '.bo')
+if not freq in set(['delta', 'theta', 'alpha', 'beta', 'lgamma', 'hgamma', 'broadband', 'raw']):
+    og_fname = bo_fname
+og_bo = se.load(og_fname)
+filter_inds = og_bo.filter_inds
+kurtosis = og_bo.kurtosis
+bo = BandBrain(freq_bo, og_bo)
[…]

### 2020-01-28 paper/main.tex

@@
 (Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
-recordings from 3159 electrodes from 24 patients.  Each individual
+recordings from 5023 electrodes from 78 patients.  Each individual
 patient contributes electrodes from a limited set of brain locations,
@@
 connections between structures near $x$ and $\eta$.  Although
-anatomical and function correlations can differ
-markedly~\citep[e.g.,][]{AdacEtal11, HoneEtal09, GoniEtal14}, we use temporal
+anatomical and functional correlations can differ
+markedly~\citep[e.g.,][]{AdacEtal12, HoneEtal09, GoniEtal14}, we use temporal
 correlations in the data to estimate these anatomical
@@
 matrix, which can become computationally intractable when $T$ is very
-large (e.g., for an example patient in Dataset 1, $T =
+large (e.g., an example patient in Dataset 1, $T =
 12786750$). However, because Equation~\ref{eqn:reconstruction} is time
@@
 covererage might be associated with better reconstruction accuracy
-(e.g. Fig.~\ref{fig:corrmap}C, D indicate that many electrodes in the
+(e.g. Fig.~\ref{fig:corrmap}C and D indicate that many electrodes in the
 MTL have relatively high reconstruction accuracy, and occipital
@@
 implantation targets in terms of providing full-brain activity
-information via SuperEEG (Fig.~\ref{fig:informap}A, B).  Despite task
+information via SuperEEG (Fig.~\ref{fig:informap}A and B).  Despite task
 and patient differences across the two datasets, we nonetheless found
@@
 between the top 10\% most informative voxels across the two datasets
-(gray areas in Fig.~\ref{fig:informap}C).
+(gray areas in Fig.~\ref{fig:informap}C, networks shown in
+Fig.~\ref{fig:networks}A (All)).
 Supporting the notion that structures that are highly interconnected
@@
 accuracy for frequency bands across the two datasets, performing better at lower
-frequencies (peaking at $\alpha$) and worst at high frequencies.
+frequencies (peaking at $\alpha$) and worst at high frequencies (see Fig.~\ref{fig:frequency}).
 
@@
 We also wanted to see how the most informative regions changed by
-frequency. Lower frequency oscillations, such as delta, theta, and alpha, have
-been posited to be processing modes which span large swaths of
+frequency. Lower frequency oscillations, such as $\delta$, $\theta$, and $\alpha$, have
+been posited to be involved in processing modes which span large swaths of
 cortical regions and are thought to serve the purpose of integration
 across many cortical sites ~\citep{Knya12}. Higher frequency
-oscillations such as beta and gamma, are more limited to topographic
-area ~\citep{Nune95}, and are modulated by slow oscillations
+oscillations such as $\beta$ and $\gamma$, are more limited to topographic
+areas ~\citep{Nune95}, and are modulated by slow oscillations
 hierarchically ~\citep{EngeEtal10}. Using the frequency-specific reconstruction accuracies, we
@@
 visual network.  Alpha power is consistently modulated in EEG studies
-of attention and visuo-motor ~\citep{MartiEtal10, MarzEtal13}, and we
-similarly found a high proportion of visual and somatomotor networks
+of attention and visuo-motor ~\citep{MantEtal07, MarzEtal13}, and we
+similarly found a high proportion of visual, somatomotor, and dorsal attentio networks
 within this band.  We found $\beta$ intersections to predominantly
-consist of somatomotor network, consistent with~\citep{RittEtal08,
-  VanEEtal11}.  Also consistent with heavily cited
+consist of somatomotor network, in line with~\citep{RittEtal09, VaneEtal11}.  Also accordant with heavily cited
 literature~\citep{FrieEtal07}, the network most predominant in the
@@
 was found predominantly in frontoparietal and default mode networks,
-consistent with ~\{OssaEtal11}.  We then carried out a
-meta analysis using Neurosynth~\citep{RubiEtal17} to identify the 5
-terms most commonly associated with the given map
-(Fig.~\ref{fig:networks}C).
+consistent with ~\citep{OssaEtal11}.
 
@@
 \section*{Author Contributions}
-J.R.M conceived and initiated the project. L.L.W.O. and
+J.R.M conceived and initiated the project. L.L.W.O., T.A.M, and
 A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the

### 2020-02-11 paper/main.tex
minor updates to paper and correlation between best locations by frequency

@@
 (in \textit{Results}) our approach using a two large previously
-collected dataset comprising multi-session intracranial recordings.
+collected datasets comprising multi-session intracranial recordings.
 Dataset 1 comprises multi-session recordings taken from 6876
@@
 Next, we downsampled the recordings (regardless of the original
-samplerate) to 250 Hz.  (This downsampling step served to both
+sample rate) to 250 Hz.  (This downsampling step served to both
 normalize for differences in sampling rates across patients and to
@@
 We used this general approach to
-quantify the algorithm's performance across the full dataset.For each held-out electrode, from each held-out patient in turn, we
+quantify the algorithm's performance across the full dataset. For each held-out electrode, from each held-out patient in turn, we
 computed the average correlation (across recording sessions) between
@@
 of attention and visuo-motor ~\citep{MantEtal07, MarzEtal13}, and we
-similarly found a high proportion of visual, somatomotor, and dorsal attentio networks
+similarly found a high proportion of visual, somatomotor, and dorsal attention networks
 within this band.  We found $\beta$ intersections to predominantly

### 2020-02-13 paper/main.tex
backing up edits...

@@
 ($\pm$ .5 Hz) line noise from every recording (from every electrode).
-Next, we downsampled the recordings (regardless of the original
-sample rate) to 250 Hz.  (This downsampling step served to both
-normalize for differences in sampling rates across patients and to
-ease the computational burden of our subsequent analyses.)  We then
-excluded any electrodes that showed putative epileptiform activity.
+Next, we downsampled the recordings (regardless of the original sample
+rate) to 250 Hz.  (This downsampling step served to both normalize for
+differences in sampling rates across patients and to ease the
+computational burden of our subsequent analyses.)  We then excluded
+any electrodes that showed putative epileptiform activity.
 Specifically, we excluded from further analysis any electrode that
-exhibited an maximum kurtosis of 10 or greater across all of that
+exhibited a maximum kurtosis of 10 or greater across all of that
 patient's recording sessions.  We also excluded any patients with
@@
 4168 electrodes implanted throughout the brains of 67 patients
-(Fig.~\ref{fig:methods}A); for Dataset 2, this yielded clean
-recordings from 5023 electrodes from 78 patients.  Each individual
-patient contributes electrodes from a limited set of brain locations,
-which we localized in a common space~\citep[MNI152;][]{GrabEtal06}; an
-example Dataset 1 patient's 54 electrodes that passed the above
-kurtosis threshold test are highlighted in black and red.
+(Fig.~\ref{fig:methods}A, colored dots); for Dataset 2, this yielded
+clean recordings from 5023 electrodes implanted in 78 patients.  Each
+individual patient contributed electrodes from a limited set of brain
+locations, which we localized in a common
+space~\citep[MNI152;][]{GrabEtal06}; an example Dataset 1 patient's 54
+electrodes that survived the kurtosis thresholding procedure are
+highlighted in black and red (Fig.~\ref{fig:methods}A).
 
@@
 coverage (which implies a large value of $\lambda$).  Here we set
-$\lambda = 20$, guided in part by our prior work~\citep{MannEtal14b,
+$\lambda = 20$, guided in part by our prior related work~\citep{MannEtal14b,
   MannEtal18}, and in part by examining the brain coverage with
@@
   \bar{C}_{s} &=
-  \mathrm{r}(\frac{1}{n}(\sum_{k=1}^{n}\mathrm{z}(C_{s,k}))),\label{eqn:inter_corr}~\mathrm{where}\\
+  \mathrm{r}\left(\frac{1}{n}\left(\sum_{k=1}^{n}\mathrm{z}(C_{s,k})\right)\right),\label{eqn:inter_corr}~\mathrm{where}\\
 \mathrm{z}(r) &= \frac{\log(1+r) - \log(1 - r)}{2}~\mathrm{is~the~Fisher}~z \mathrm{-transformation~and}\label{eqn:fishersz}\\
@@
 voltage from patient $s$'s $k^{th}$ session at the locations in
-$\beta_s$ using~\cite{Rasm06}:
+$\beta_s$ as follows~\citep{Rasm06}:
 
@@
 matrix, which can become computationally intractable when $T$ is very
-large (e.g., an example patient in Dataset 1, $T =
-12786750$). However, because Equation~\ref{eqn:reconstruction} is time
-invariant, we may compute $Y_{s,k,\beta_s}$ in a piecewise
-manner by filling in $Y_{s,k,\beta_s}$ one row at a time (using the
-corresponding samples from $Y_{s, k, \alpha_s}$).
+large (e.g., an example patient in Dataset 1, $T = 12,786,750$; also
+see Fig.~\suppstats, Panels E and K). However, because
+Equation~\ref{eqn:reconstruction} is time invariant, we may compute
+$Y_{s,k,\beta_s}$ in a piecewise manner by filling in
+$Y_{s,k,\beta_s}$ one row at a time (using the corresponding samples
+from $Y_{s, k, \alpha_s}$).
 
@@
 
-We used this general approach to
-quantify the algorithm's performance across the full dataset. For each held-out electrode, from each held-out patient in turn, we
-computed the average correlation (across recording sessions) between
-the SuperEEG-reconstructed voltage traces and the observed voltage
-traces from that electrode.  For this analysis we set $\bar{R}$ to be
-the union of all electrode locations across all patients.  This
-yielded a single correlation coefficient for each electrode location
-in $\bar{R}$, reflecting how well the SuperEEG algorithm was able to
-recover the recording at that location by incorporating data across
-patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
-Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations
-was centered well above zero (mean: 0.51; $t$-test comparing mean of
-distribution of $z$-transformed average patient correlation coefficients
-to 0: $t(66) = 23.55, p < 10^{-10}$), indicating that the SuperEEG algorithm
+We used this general approach to quantify the algorithm's performance
+across the full dataset. For each held-out electrode, from each
+held-out patient in turn, we computed the average correlation (across
+recording sessions) between the SuperEEG-reconstructed voltage traces
+and the observed voltage traces from that electrode.  For this
+analysis we set $\bar{R}$ to be the union of all electrode locations
+across all patients.  This yielded a single correlation coefficient
+for each electrode location in $\bar{R}$, reflecting how well the
+SuperEEG algorithm was able to recover the recording at that location
+by incorporating data across patients (black histogram in
+Fig.~\ref{fig:corrmap}A, map in Fig.~\ref{fig:corrmap}C).  The
+observed distribution of correlations was centered well above zero
+(mean: 0.51; $t$-test comparing mean of distribution of
+$z$-transformed average patient correlation coefficients to 0:
+$t(66) = 23.55, p < 10^{-10}$), indicating that the SuperEEG algorithm
 recovers held-out activity patterns substantially better than random
@@
 
-As a stricter benchmark, we compared the quality of these
+Next, we compared the quality of these
 across-participant reconstructions (i.e., computed using a correlation
@@
 models, we restricted the dataset to the 24 patients that participated
-in both experiments and repeated the above within- and across-patient cross validation
-procedures separately for Experiment 1 and Experiment 2 data from
-Dataset 2.  We then compared the reconstruction accuracies for held-out
-electrodes, for models trained within versus across the two
-experiments, or combining across both experiments
+in both experiments and repeated the above within- and across-patient
+cross validation procedures separately for Experiment 1 and Experiment
+2 data from Dataset 2.  We then compared the reconstruction accuracies
+for held-out electrodes, for models trained within versus across the
+two experiments, or combining across both experiments
 (Fig.~\perexptaskrecon).  In every case we found that across-patient
@@
 within-patient models trained on data only from the subject
-contributing the given electrode ($t$s$(23) > 6.50, p$s$ < 10^{-5}$).  All
-reconstruction accuracies also reliably exceeded chance performance
-($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average reconstruction accuracy was
-highest for the across-patient models limited to data from the same
-experiment (mean accuracy: $0.68$); next-highest for the
-models that combined data across both experiments (mean
-accuracy: $0.61$); and lowest for models trained across tasks (mean
-accuracy: $0.47$).  This result also held for each of the Dataset 2
-experiments individually (Fig.~\perexptaskreconseparated).  Taken
-together, these results indicate that there are reliable commonalities
-in the spatial correlations of full-brain activity across tasks, but
-that there are also reliable differences in these spatial correlations
-across tasks.  Whereas reconstruction accuracy benefits from
-incorporating data from other patients, reconstruction accuracy is
-highest when constrained to within-task data, or data that includes a
-variety of tasks (e.g., Dataset 1, or combining across the two Dataset
-2 experiments).
+contributing the given electrode ($t$s$(23) > 6.50, p$s$ < 10^{-5}$).
+All reconstruction accuracies also reliably exceeded chance
+performance ($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average
+reconstruction accuracy was highest for the across-patient models
+limited to data from the same experiment (mean accuracy: $0.68$);
+next-highest for the models that combined data across both experiments
+(mean accuracy: $0.61$); and lowest for models trained across tasks
+(mean accuracy: $0.47$).  This pattern of results also held for each
+of the Dataset 2 experiments individually
+(Fig.~\perexptaskreconseparated).  Taken together, these results
+indicate that there are reliable commonalities in the spatial
+correlations of full-brain activity across tasks, but that there are
+also reliable differences in these spatial correlations across tasks.
+Whereas reconstruction accuracy benefits from incorporating data from
+other patients, reconstruction accuracy is highest when constrained to
+within-task data, or data that includes a variety of tasks (e.g.,
+Dataset 1, or combining across the two Dataset 2 experiments).
 
@@
 (when considering data from every patient; e.g.\
-Fig.~\ref{fig:corrmap}C, D), electrodes are not placed uniformly
+Fig.~\ref{fig:corrmap}C, D), electrodes were not sampled uniformly
 throughout the brain.  For example, electrodes are more likely to be
@@
 $r = 0.6, p < 10^{-10}$).  We wondered whether regions with good
-covererage might be associated with better reconstruction accuracy
-(e.g. Fig.~\ref{fig:corrmap}C and D indicate that many electrodes in the
-MTL have relatively high reconstruction accuracy, and occipital
-electrodes tend to have relatively low reconstruction accuracy).  To
-test whether this held more generally across the entire brain, for
-each dataset we computed the electrode placement density for each
-electrode from each patient (using the proportion of \textit{other}
-patients' electrodes within 20 MNI units of the given electrode).  We
-then correlated these density values with the across-patient
-reconstruction accuracies for each electrode.  We found a negative
-correlation between reconstruction accuracy and density for Dataset 1,
-but was unreliable for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$; Dataset 2:
-$r = -0.30, p = 0.15$).  This indicates that the reconstruction
-accuracies we observed are not driven by sampling density, but
-rather may also reflect higher order properties of neural dynamics
-such as functional correlations between distant
-voxels~\citep{BetzEtal17b}.
+covererage might be associated with better reconstruction accuracy.
+For example, Figures~\ref{fig:corrmap}C and D indicate that many
+electrodes in the MTL (which tends to be relatively densely sampled)
+have relatively high reconstruction accuracy, and occipital electrodes
+(which tends to be relatively sparsely sampled) tend to have
+relatively low reconstruction accuracy.  To test whether this held
+more generally across the entire brain, for each dataset we computed
+the electrode placement density for each electrode from each patient
+(using the proportion of \textit{other} patients' electrodes within 20
+MNI units of the given electrode).  We then correlated these density
+values with the across-patient reconstruction accuracies for each
+electrode.  We found a statistically reliable negative correlation
+between reconstruction accuracy and density for Dataset 1, but no
+reliable correlation for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$;
+Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
+reconstruction accuracies we observed are \textit{not} driven solely
+by sampling density, but rather may also reflect higher order
+properties of neural dynamics such as functional correlations between
+distant voxels~\citep{BetzEtal17b}.
+
+%%%%%%%%%%%%%%%%%%%%% MOVE FREQEUNCY STUFF HERE
 

### 2020-02-13 paper/main.tex
finished revamping freq breakdown section, starting on most informative electrode section

@@
 MNI units of the given electrode).  We then correlated these density
-values with the across-patient reconstruction accuracies for each
+values with the across-patient reconstruction accuracies for eachg
 electrode.  We found a statistically reliable negative correlation
@@
 
-%%%%%%%%%%%%%%%%%%%%% MOVE FREQEUNCY STUFF HERE
+Prior work in humans and animals has shown that the spatial profile of
+the local field potential differs by frequency band~\citep[e.g., with
+respect to volume conductance properties and contribution to the local
+field potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example,
+lower frequency components of the local field potential tend to have
+higher power and extend further in space than high-frequency
+components~\citep[e.g., ][]{MillEtal07, MannEtal09}.  We therefore
+wondered whether the reconstructions we observed might be differently
+weighting or considering the contributions of activity at different
+frequency bands.  We therefore examined a range of frequency bands
+($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$:
+12--30 Hz; $\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along
+with a measure of broadband power~\citep[defined as the mean height of
+a linear robust regression fit in log-log space to the order 4 Morelet
+wavelet-computed power spectrum at 50 log-spaced frequencies from from
+2--100 Hz;][]{MannEtal09}.  We used second-order Butterworth bandpass
+filters to compute the activity patterns within each narrow frequency
+band.  We then repeated our within-subject and across-subject
+cross-validated reconstruction accuracy tests (analogous to
+Fig.~\ref{fig:corrmaps}) separately for each frequency band
+(Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis
+on the Hilbert transform-computed spectral power within each narrow
+band; see Fig.~\freqpower.)  Across both datasets, we found that our
+approach is best at reconstructing patterns of broadband activity
+(right-most bars in Figs.~\ref{fig:frequency}A and D), a correlate of
+population firing rate~\citep{MannEtal09}.  We also achieved good
+reconstruction accuracy within each narrow frequency band
+(Figs.~\ref{fig:frequency} and \freqpower).  Activity at lower
+frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
+reconstructed better than high-frequency patterns ($\gamma_L$ and
+$\gamma_H$), with reconstruction accuracy peaking in the $\alpha$
+band.  Overall, these results indicate that our approach is able to
+accurately recover information within the 2--100 Hz range, although
+those reconstructions are most accurate for low-frequency or broadband patterns.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{figs/frequency}
+  \caption{\textbf{Reconstruction quality across all electrodes in two
+      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      each frequency band in Dataset 1.}  The across-patient
+    distribution (left jitter barplot) reflects
+    reconstruction accuracy (correlation) using a correlation model
+    learned from all but one patient's data, and then applied to that
+    held-out patient's data.  The within-patient distribution (right
+    jitter barplot in lighter color)
+    reflects performance using a correlation model learned from the same
+    patient who contributed the to-be-reconstructed electrode, colored
+    by frequency and includes the raw voltages displayed in
+    Fig.~\ref{fig:corrmap}A in gray.
+    \textbf{B.~Statistical summary of across-patient reconstruction
+      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
+    map, warmer colors (positive t-values) indicate that the
+    distribution of
+    reconstruction accuracy for the frequency band in a given row
+    yielded was greater than the frequency band in the given
+    column. Cooler colors (negative t-values) indicate that the
+    frequency band in the given row yielded lower reconstruction
+    accuracy than the frequency band in the given column. The lower
+    triangles of each map denote the corresponding p-values for the
+    t-tests. The diagonal entries display the average
+    reconstruction accuracy given to each frequency
+    band. \textbf{C.~Statistical summary of within-patient reconstruction
+      quality by electrode for each frequency band in Dataset 1.}
+    This panel displays the within-patient statistical summary,
+    in the same format as Panel B.  \textbf{D.~Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      each frequency band in Dataset 2.}  This panel displays
+    reconstruction accuracy distributions for each frequency band for
+    Dataset 2. \textbf{E.~Statistical summary of
+      across-patient reconstruction quality by electrode for each
+      frequency band in Dataset 2.} This is the same format as Panel
+    B for Dataset 2. \textbf{F.~Statistical summary of
+      within-patient reconstruction quality by electrode for each
+      frequency band in Dataset 2.}This is the same format as Panel
+    C for Dataset 2.}
+  \label{fig:frequency}
+\end{figure}
 
@@
 \end{figure}
+
+%%%%%%%%% STOPPED HERE
 
@@
   \label{fig:informap}
-\end{figure}
-
-We also wondered what frequency properties contributed to the
-reconstruction accuracy. To recover frequency-band specific voltage activity
-from each recording, a second-order Butterworth filter was applied
-across bands $\delta$, $\theta$, $\alpha$, $\beta$, $\gamma_L$, and
-$\gamma_H$ with respective frequency ranges 2-4 Hz, 4-8 Hz, 8-12 Hz,
-12-30 Hz, 30-60 Hz, and 60-100 Hz. Bandpass signals contain
-information about the phase and amplitude of the underlying frequency
-band, providing the most detailed view of the activity at that
-frequency. Additionally, we calculated the reconstruction accuracies
-using power at each band by taking the absolute
-value of the Hilbert tranform of the bandpassed signal (see Fig.~\freqpower). To compute the broadband power (BB), we
-first computed instantaneous power at 50 log-spaced frequencies
-between 2 and 100 Hz using Morlet wavelets (n=4). Then, for each time
-point and electrode, we fitted a robust Huber regression to frequency
-and power in log-space, and calculated the mean height of the
-resulting line. We then followed the same procedure outlined above
-(see Fig.~\ref{fig:methods}) to
-obtain the reconstruction accuracy at each bandpassed frequency as well
-as broadband power for both datasets (see Fig.~\ref{fig:frequency}).
-We found
-the best average reconstruction accuracy for each dataset was obtained using broadband
-power, which is a correlate of neural firing
-~\citep{MannEtal09}. We also found a similar trend in reconstruction
-accuracy for frequency bands across the two datasets, performing better at lower
-frequencies (peaking at $\alpha$) and worst at high frequencies (see Fig.~\ref{fig:frequency}).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/frequency}
-  \caption{\textbf{Reconstruction quality across all electrodes in two
-      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      each frequency band in Dataset 1.}  The across-patient
-    distribution (left jitter barplot) reflects
-    reconstruction accuracy (correlation) using a correlation model
-    learned from all but one patient's data, and then applied to that
-    held-out patient's data.  The within-patient distribution (right
-    jitter barplot in lighter color)
-    reflects performance using a correlation model learned from the same
-    patient who contributed the to-be-reconstructed electrode, colored
-    by frequency and includes the raw voltages displayed in
-    Fig.~\ref{fig:corrmap}A in gray.
-    \textbf{B.~Statistical summary of across-patient reconstruction
-      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
-    map, warmer colors (positive t-values) indicate that the
-    distribution of
-    reconstruction accuracy for the frequency band in a given row
-    yielded was greater than the frequency band in the given
-    column. Cooler colors (negative t-values) indicate that the
-    frequency band in the given row yielded lower reconstruction
-    accuracy than the frequency band in the given column. The lower
-    triangles of each map denote the corresponding p-values for the
-    t-tests. The diagonal entries display the average
-    reconstruction accuracy given to each frequency
-    band. \textbf{C.~Statistical summary of within-patient reconstruction
-      quality by electrode for each frequency band in Dataset 1.}
-    This panel displays the within-patient statistical summary,
-    in the same format as Panel B.  \textbf{D.~Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      each frequency band in Dataset 2.}  This panel displays
-    reconstruction accuracy distributions for each frequency band for
-    Dataset 2. \textbf{E.~Statistical summary of
-      across-patient reconstruction quality by electrode for each
-      frequency band in Dataset 2.} This is the same format as Panel
-    B for Dataset 2. \textbf{F.~Statistical summary of
-      within-patient reconstruction quality by electrode for each
-      frequency band in Dataset 2.}This is the same format as Panel
-    C for Dataset 2.}
-  \label{fig:frequency}
 \end{figure}

### 2020-02-14 paper/main.tex
backing up progress

@@
 
-%%%%%%%%% STOPPED HERE
-
-In neurosurgical applications where one wishes to infer full-brain
-activity patterns, can our framework yield insights into where the
-electrodes should be placed?  A basic assumption of our approach (and
+A basic assumption of our approach (and
 of most prior ECoG work) is that electrode recordings are most
@@
 informative about full-brain activity patterns than comparatively
-isolated structures.
-
-To gain insights into whether particular electrode locations might be
-especially informative, we first computed the average reconstruction
-accuracy across all of each patient's electrodes (using the
+isolated structures.  To test this hypothesis, we computed the average reconstruction
+accuracy across all of each patient's electrodes (using our
 across-patients cross validation test; black histograms in
-Fig.~\ref{fig:corrmap}A and B).  We labeled each patient's electrodes
-in each dataset with the average reconstruction accuracy for that
-patient.  In other words, we assigned every electrode from each given
-patient the same value, reflecting how well the activity patterns at
-those electrodes were reconstructed on average.  Next, for each voxel
+Fig.~\ref{fig:corrmap}A and B).  We first labeled each patient's electrodes,
+in each dataset, with the average reconstruction accuracy for that
+patient.  In other words, we assigned every electrode from each
+patient the same value, reflecting how well the activity patterns for that patient were reconstructed.  Next, for each voxel
 in the 4~mm$^3$ MNI brain, we computed the average value across any
 electrode (from any patient) that came within 20 MNI units of that
-voxel's center.  Effectively, we computed an \textit{information
+voxel's center.  This yielded an \textit{information
   score} for each voxel, reflecting the average reconstruction
@@
 the averages were weighted to reflect patients who had more electrodes
-implanted near that location. This yielded a single map for each
-dataset, highlighting regions that are potentially promising
-implantation targets in terms of providing full-brain activity
-information via SuperEEG (Fig.~\ref{fig:informap}A and B).  Despite task
+implanted near that location. We created a single map of these information scores for each
+dataset, highlighting regions that are especially informative about activity in \textit{other} brain areas
+(Fig.~\ref{fig:informap}A and B).  Despite task
 and patient differences across the two datasets, we nonetheless found
@@
 
-We also wanted to see how the most informative regions changed by
-frequency. Lower frequency oscillations, such as $\delta$, $\theta$, and $\alpha$, have
-been posited to be involved in processing modes which span large swaths of
+We also wondered whether the map of information scores might vary as a function of the spectral
+components of the activity patterns under consideration.  For example, low frequency $\delta$ activity in the thalamus has been implicated in
+supporting connectivity with cortex~\citep[e.g.,][]{Jone09}; $\theta$ activity
+in frontal regions have been implicated in memory consolidation~\citep{NishEtal09} and integration~\citep{BackEtal16}; parietal and occipital $\alpha activity has been
+implicated in attention modulation~\citep[e.g., see][]{Klim12}; $\beta$ activity in motor cortex have been implicated in motor control and processing~\citep{BrovEtal04, KoelEtal08, RubiEtal06};
+and occipital $\gamma$ activity has been implicated in visual attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
+We computed analogous maps of information scores for each individual frequency band.  Across Datasets 1 and 2 we observed a weak, but statistically reliable, correspondence in
+these maps, aside from in the $\alpha$ band ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).
+
+%%%% STOPPED HERE...
+
+as $\delta$, $\theta$, and $\alpha$, have
+been implicated in processing modes which span large swaths of
 cortical regions and are thought to serve the purpose of integration

### 2020-02-15 paper/main.tex
working on information maps section

@@
 and occipital $\gamma$ activity has been implicated in visual attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
-We computed analogous maps of information scores for each individual frequency band.  Across Datasets 1 and 2 we observed a weak, but statistically reliable, correspondence in
-these maps, aside from in the $\alpha$ band ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).
+We computed analogous maps of information scores for each individual frequency band.  Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed reliable positive correlations
+between the voxel-by-voxel maps of information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).
 
-%%%% STOPPED HERE...
+%%%%STOPPED HERE
 

### 2020-02-17 paper/main.tex
working on results section-- updated network results

@@
 and occipital $\gamma$ activity has been implicated in visual attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
-We computed analogous maps of information scores for each individual frequency band.  Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed reliable positive correlations
-between the voxel-by-voxel maps of information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).
+We computed analogous maps of information scores for each individual frequency band.
+Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed reliable positive correlations
+between the voxel-by-voxel maps of information scores ($\delta$: $r = 0.09, p < 10^{-57}$;
+$\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$,
+$\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$;
+$\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).
+
+To gain additional insight into which regions were most informative about
+full-brain activity patterns at different frequency ranges, we next computed (for each frequency range)
+the intersection of the top 10\% highest information scores across the maps for
+Datasets 1 and 2 (analogous to our approach in Fig.~\ref{fig:informap}C).
+This yielded a single map of the (reliably) most informative locations for each frequency range we examined.
+We then carried out two \textit{post hoc} analyses on each of these maps to better characterize
+the underlying structural and functional properties of each set of regions we identified
+as being particularly informative about one or more neural patterns.
+
+A growing body of neuroscientific research is concerned with characterizing the \textit{parcellations}
+of anatomical and functional brain networks~\citep[for review see][]{ZaleEtal10, ArslEtal18}.
+The dominant approaches entail obtaining a full-brain connectivity matrix using either diffusion tensor imaging to identify the brain's network of
+white matter connections, or functional connectivity (typically applied to resting state data) to
+correlate the patterns of activity exhibited by different brain structures.  One can then apply graph theoretic approaches
+to assign each brain structure (typically a single fMRI voxel) to one or more networks~\citep[for review see][]{BullSpor09}.
+The result is a set of distinct (or partially overlapping) brain ``networks'' that may be
+further examined to elucidate their potential functional role.  We overlaid a well-cited seven-network
+parcellation map identified by \cite{YeoEtal11} onto the maps of brain locations that were most informative
+about each neural pattern.  For each of these information maps, we computed the proportion of voxels in the most informative
+brain regions that belonged to each of the seven networks identified by \cite{YeoEtal11}.
+We found that the regions we identified as being most informative about different neural patterns varied
+markedly with respect to which functional networks they belonged to (Fig.~\ref{fig:networks}A, B).  This is consistent with
+the notion that there is no ``universal'' brain region that consistently reflects activity in the rest of the brain.  Rather,
+each region's activity patterns appear to be characterized by different spectral profiles, and the ability to
+infer activity patterns at a particular frequency range depends on the structural and functional
+connectome specific to that frequency range.
+
+%next: neurosynth
 

### 2020-02-20 paper/boneyard.tex
finished draft of results section

@@
+as $\delta$, $\theta$, and $\alpha$, have been implicated in processing modes
+which span large swaths of cortical regions and are thought to serve the purpose
+of integration across many cortical sites ~\citep{Knya12}. Higher frequency
+oscillations such as $\beta$ and $\gamma$, are more limited to topographic areas
+~\citep{Nune95}, and are modulated by slow oscillations hierarchically
+~\citep{EngeEtal10}. Using the frequency-specific reconstruction accuracies, we
+followed the process outlined in Fig.~\ref{fig:informap}C, to obtain the most
+informative locations for each frequency.  When we examined the intersection
+between the top 10\% most informative voxels across the two datasets for each
+bandpassed frequency, we found a somewhat consistent hierarchical structure (see
+Fig.~\ref{fig:networks}E).
+
+; $\theta$ activity
+in frontal regions have been implicated in memory
+consolidation~\citep{NishEtal09} and integration~\citep{BackEtal16}; parietal
+and occipital $\alpha$ activity has been implicated in attention
+modulation~\citep[e.g., see][]{Klim12}; $\beta$ activity in motor cortex have
+been implicated in motor control and processing~\citep{BrovEtal04, KoelEtal08,
+RubiEtal06}; and occipital $\gamma$ activity has been implicated in visual
+attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
+
+%next: neurosynth
+
+%%%%STOPPED HERE
+
+We then wondered which networks were involved in each of these
+frequency-specific intersecting regions.  To better understand the networks
+involved we colored the regions (Fig.~\ref{fig:networks}A) based on the network
+parcellation ~\citep[using $k$=7;][]{YeoEtal11}} (Fig.~\ref{fig:networks}D) and
+calculated the proportion of each of those networks (Fig.~\ref{fig:networks}B).
+Consistent with the idea outlined above, we found networks most involved in the
+lowest frequency band, $\delta$, were networks involved integration and global
+processing (specifically the dorsal attention ~\citep{MarzEtal13}, default mode,
+and frontoparietal networks).  Although these networks are also seen in the
+$\theta$ intersection, they are less proportionally to the visual network.
+Alpha power is consistently modulated in EEG studies of attention and
+visuo-motor ~\citep{MantEtal07, MarzEtal13}, and we similarly found a high
+proportion of visual, somatomotor, and dorsal attention networks within this
+band.  We found $\beta$ intersections to predominantly consist of somatomotor
+network, in line with~\citep{RittEtal09, VaneEtal11}.  Also accordant with
+heavily cited literature~\citep{FrieEtal07}, the network most predominant in the
+$\gamma$ intersection was the visual network.  Lastly, broadband power was found
+predominantly in frontoparietal and default mode networks, consistent with
+~\citep{OssaEtal11}.
+
 % old discussion section

### 2020-02-20 paper/main.tex
backing up progress
finished draft of results section

@@
 
-Another approach to obtaining high spatiotemporal resolution
-neural data has been to collect fMRI and EEG data simultaneously.
-Simultaneous fMRI-EEG has the potential to balance the high spatial
-resolution of fMRI with the high temporal resolution of scalp EEG,
-thereby, in theory, providing the best of both worlds.  In practice,
-however, the signal quality of both recordings suffers substantially
-when the two techniques are applied simultaneously~\citep[e.g., see review by][]{HustEtal12}.  In addition, the experimental designs that are
-ideally suited to each technique individually are somewhat at odds.
-For example, fMRI experiments often lock stimulus presentation
-events to the regularly spaced image acquisition time (TR), which
-maximizes the number of post-stimulus samples.  By contrast, EEG
-experiments typically employ jittered stimulus presentation times to
-maximize the experimentalist's ability to distinguish electrical brain
-activity from external noise sources such as from 60 Hz alternating
-current power sources.
+Another approach to obtaining high spatiotemporal resolution neural data has
+been to collect fMRI and EEG data simultaneously. Simultaneous fMRI-EEG has the
+potential to balance the high spatial resolution of fMRI with the high temporal
+resolution of scalp EEG, thereby, in theory, providing the best of both worlds.
+In practice, however, the signal quality of both recordings suffers
+substantially when the two techniques are applied simultaneously~\citep[e.g.,
+see review by][]{HustEtal12}. In addition, the experimental designs that are
+ideally suited to each technique individually are somewhat at odds. For example,
+fMRI experiments often lock stimulus presentation events to the regularly spaced
+image acquisition time (TR), which maximizes the number of post-stimulus
+samples.  By contrast, EEG experiments typically employ jittered stimulus
+presentation times to maximize the experimentalist's ability to distinguish
+electrical brain activity from external noise sources such as from 60 Hz
+alternating current power sources.
 
-The current ``gold standard'' for precisely localizing signals and
-sampling at high temporal resolution is to take (ECoG or iEEG)
-recordings from implanted electrodes (but from a limited set of
-locations in any given brain).  This begs the following question: what
-can we infer about the activity exhibited by the rest of a person's
-brain, given what we learn from the limited intracranial recordings we
-have from their brain and additional recordings taken from
-\textit{other} people's brains?  Here we develop an approach, which we
-call \textit{SuperEEG}\footnote{The term ``SuperEEG''
-  was coined by Robert J. Sawyer in his popular science fiction novel
-  \textit{The Terminal Experiment}~\cite{Sawy95}.  SuperEEG is a
-  fictional technology that measures ongoing neural activity
-  throughout the entire living human brain with perfect precision and
-  at arbitrarily high spatiotemporal resolution.}, based on Gaussian
-process regression~\citep{Rasm06}.  SuperEEG entails using data from
-multiple people to estimate activity patterns at arbitrary locations
-in each person's brain (i.e., independent of their electrode
-placements).  We test our SuperEEG approach using two large datasets
-of intracranial recordings~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b,
-  MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17,
-  KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
-  KuceEtal18}.  We show that the SuperEEG algorithm recovers signals
-well from electrodes that were held out of the training dataset.  We
-also examine the factors that influence how accurately activity may be
-estimated (recovered), which may have implications for electrode
-design and placement in neurosurgical applications.
+The current ``gold standard'' for precisely localizing signals and sampling at
+high temporal resolution is to take (ECoG or iEEG) recordings from implanted
+electrodes (but from a limited set of locations in any given brain).  This begs
+the following question: what can we infer about the activity exhibited by the
+rest of a person's brain, given what we learn from the limited intracranial
+recordings we have from their brain and additional recordings taken from
+\textit{other} people's brains?  Here we develop an approach, which we call
+\textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by Robert J. Sawyer
+in his popular science fiction novel \textit{The Terminal
+Experiment}~\cite{Sawy95}.  SuperEEG is a fictional technology that measures
+ongoing neural activity throughout the entire living human brain with perfect
+precision and at arbitrarily high spatiotemporal resolution.}, based on Gaussian
+process regression~\citep{Rasm06}.  SuperEEG entails using data from multiple
+people to estimate activity patterns at arbitrary locations in each person's
+brain (i.e., independent of their electrode placements).  We test our SuperEEG
+approach using two large datasets of intracranial recordings~\citep{SedeEtal03,
+SedeEtal07a, SedeEtal07b, MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17,
+KragEtal17, KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
+KuceEtal18}.  We show that the SuperEEG algorithm recovers signals well from
+electrodes that were held out of the training dataset.  We also examine the
+factors that influence how accurately activity may be estimated (recovered),
+which may have implications for electrode design and placement in neurosurgical
+applications.
 
-\section*{Approach}
-The SuperEEG approach to inferring high temporal resolution full-brain
-activity patterns is outlined and summarized in
-Figure~\ref{fig:methods}. We describe (in this section) and evaluate
-(in \textit{Results}) our approach using a two large previously
-collected datasets comprising multi-session intracranial recordings.
-Dataset 1 comprises multi-session recordings taken from 6876
-electrodes implanted in the brains of 88 epilepsy
-patients~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-  MannEtal12}.  Each recording session lasted from 0.2--3~h (total
-recording time: 0.3--14.2~h; Fig.~\suppstats E).  During each
-recording session, the patients participated in a free recall list
-learning task, which lasted for up to approximately 1~h.  In addition,
-the recordings included ``buffer'' time (the length varied by patient)
-before and after each experimental session, during which the patients
-went about their regular hospital activities (confined to their
-hospital room, and primarily in bed).  These additional activities
-included interactions with medical staff and family, watching
-television, reading, and other similar activities.  For the purposes
-of the Dataset 1 analyses presented here, we aggregated all data
-across each recording session, including recordings taken during the
-main experimental task as well as during non-experimental time.  We
-used Dataset 1 to develop our main SuperEEG approach, and to examine
-the extent to which SuperEEG might be able to generate task-general
-predictions.  Dataset 2 comprised multi-session recordings from 4436
-electrodes implanted in the brains of 40 epilepsy
-patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17,
-  LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Each
-recording session lasted from 0.4--2.2~h (total recording time:
-0.4--6.6~h; Fig.~\suppstats K).  Whereas Dataset 1 included recordings
-taken as the patients participated in a variety of activities, Dataset
-2 included recordings taken as each patient performed each of two
-specific experimental memory tasks: a random word list free recall
-task (Experiment 1) and a categorized word list free recall task
-(Experiment 2).  We used Dataset 2
-to further examine the ability of SuperEEG to generalize its
-predictions within versus across tasks.  Figure~\suppstats~provides
-additional information about both datasets.
+\section*{Approach} The SuperEEG approach to inferring high temporal resolution
+full-brain activity patterns is outlined and summarized in
+Figure~\ref{fig:methods}. We describe (in this section) and evaluate (in
+\textit{Results}) our approach using a two large previously collected datasets
+comprising multi-session intracranial recordings. Dataset 1 comprises
+multi-session recordings taken from 6876 electrodes implanted in the brains of
+88 epilepsy patients~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
+MannEtal12}.  Each recording session lasted from 0.2--3~h (total recording time:
+0.3--14.2~h; Fig.~\suppstats E).  During each recording session, the patients
+participated in a free recall list learning task, which lasted for up to
+approximately 1~h.  In addition, the recordings included ``buffer'' time (the
+length varied by patient) before and after each experimental session, during
+which the patients went about their regular hospital activities (confined to
+their hospital room, and primarily in bed).  These additional activities
+included interactions with medical staff and family, watching television,
+reading, and other similar activities.  For the purposes of the Dataset 1
+analyses presented here, we aggregated all data across each recording session,
+including recordings taken during the main experimental task as well as during
+non-experimental time.  We used Dataset 1 to develop our main SuperEEG approach,
+and to examine the extent to which SuperEEG might be able to generate
+task-general predictions.  Dataset 2 comprised multi-session recordings from
+4436 electrodes implanted in the brains of 40 epilepsy
+patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17,
+SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Each recording session lasted
+from 0.4--2.2~h (total recording time: 0.4--6.6~h; Fig.~\suppstats K).  Whereas
+Dataset 1 included recordings taken as the patients participated in a variety of
+activities, Dataset 2 included recordings taken as each patient performed each
+of two specific experimental memory tasks: a random word list free recall task
+(Experiment 1) and a categorized word list free recall task (Experiment 2).  We
+used Dataset 2 to further examine the ability of SuperEEG to generalize its
+predictions within versus across tasks.  Figure~\suppstats~provides additional
+information about both datasets.
 
 \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/methods}
-  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode
-      locations.}  Each dot reflects the location of a single
-    electrode implanted in the brain of a Dataset 1 patient.  A
-    held-out recording location from one patient is indicated in red,
-    and the patient's remaining electrodes are indicated in black.
-    The electrodes from the remaining patients are colored by
-    $k$-means cluster (computed using the full-brain correlation model
-    shown in Panel D).  \textbf{B.~Radial basis function kernel.}
-    Each electrode contributed by the patient (black) weights on the
-    full set of locations under consideration (all dots in Panel A,
-    defined as $\bar{R}$ in the text).  The weights fall off with
-    positional distance (in MNI space) according to an RBF.
-    \textbf{C.~Per-patient correlation matrices.}  After computing the
-    pairwise correlations between the recordings from each patient's
-    electrodes, we use RBF-weighted averages to estimate correlations
-    between all locations in $\bar{R}$.  We obtain an estimated
-    full-brain correlation matrix using each patient's
-    data. \textbf{D.~Merged correlation model.}  We combine the
-    per-patient correlation matrices (Panel C) to obtain a single
-    full-brain correlation model that captures information contributed
-    by every patient.  Here we have sorted the rows and columns to
-    reflect $k$-means clustering labels~\citep[using
-    $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their
-    correlations with the rest of the brain (i.e., rows of the matrix
-    displayed in the panel).  The boundaries denote the cluster
-    groups.  The rows and columns of Panel C have been sorted using
-    the Panel D-derived cluster labels.  \textbf{E.~Reconstructing activity
-      throughout the brain.}  Given the observed recordings from the
-    given patient (shown in black; held-out recording is shown in
-    blue), along with a full-brain correlation model (Panel D), we
-    use Equation~\ref{eqn:reconstruction} to reconstruct the most
-    probable activity at the held-out location (red).}
-  \label{fig:methods}
+  \centering \includegraphics[width=\textwidth]{figs/methods}
+  \caption{\textbf{Methods overview.}  \textbf{A.~Electrode locations.}  Each
+  dot reflects the location of a single electrode implanted in the brain of a
+  Dataset 1 patient.  A held-out recording location from one patient is
+  indicated in red, and the patient's remaining electrodes are indicated in
+  black. The electrodes from the remaining patients are colored by $k$-means
+  cluster (computed using the full-brain correlation model shown in Panel D).
+  \textbf{B.~Radial basis function kernel.} Each electrode contributed by the
+  patient (black) weights on the full set of locations under consideration (all
+  dots in Panel A, defined as $\bar{R}$ in the text).  The weights fall off with
+  positional distance (in MNI space) according to an RBF. \textbf{C.~Per-patient
+  correlation matrices.}  After computing the pairwise correlations between the
+  recordings from each patient's electrodes, we use RBF-weighted averages to
+  estimate correlations between all locations in $\bar{R}$.  We obtain an
+  estimated full-brain correlation matrix using each patient's data.
+  \textbf{D.~Merged correlation model.}  We combine the per-patient correlation
+  matrices (Panel C) to obtain a single full-brain correlation model that
+  captures information contributed by every patient.  Here we have sorted the
+  rows and columns to reflect $k$-means clustering labels~\citep[using
+  $k$=7;][]{YeoEtal11}, whereby we grouped locations based on their correlations
+  with the rest of the brain (i.e., rows of the matrix displayed in the panel).
+  The boundaries denote the cluster groups.  The rows and columns of Panel C
+  have been sorted using the Panel D-derived cluster labels.
+  \textbf{E.~Reconstructing activity throughout the brain.}  Given the observed
+  recordings from the given patient (shown in black; held-out recording is shown
+  in blue), along with a full-brain correlation model (Panel D), we use
+  Equation~\ref{eqn:reconstruction} to reconstruct the most probable activity at
+  the held-out location (red).} \label{fig:methods}
 \end{figure}
 
-We first applied fourth order Butterworth notch filter to remove 60 Hz
-($\pm$ .5 Hz) line noise from every recording (from every electrode).
-Next, we downsampled the recordings (regardless of the original sample
-rate) to 250 Hz.  (This downsampling step served to both normalize for
-differences in sampling rates across patients and to ease the
-computational burden of our subsequent analyses.)  We then excluded
-any electrodes that showed putative epileptiform activity.
-Specifically, we excluded from further analysis any electrode that
-exhibited a maximum kurtosis of 10 or greater across all of that
-patient's recording sessions.  We also excluded any patients with
-fewer than 2 electrodes that passed this criteria, as the SuperEEG
-algorithm requires measuring correlations between 2 or more electrodes
-from each patient.  For Dataset 1, this yielded clean recordings from
-4168 electrodes implanted throughout the brains of 67 patients
-(Fig.~\ref{fig:methods}A, colored dots); for Dataset 2, this yielded
-clean recordings from 5023 electrodes implanted in 78 patients.  Each
-individual patient contributed electrodes from a limited set of brain
-locations, which we localized in a common
-space~\citep[MNI152;][]{GrabEtal06}; an example Dataset 1 patient's 54
-electrodes that survived the kurtosis thresholding procedure are
-highlighted in black and red (Fig.~\ref{fig:methods}A).
+We first applied fourth order Butterworth notch filter to remove 60 Hz ($\pm$ .5
+Hz) line noise from every recording (from every electrode). Next, we downsampled
+the recordings (regardless of the original sample rate) to 250 Hz.  (This
+downsampling step served to both normalize for differences in sampling rates
+across patients and to ease the computational burden of our subsequent
+analyses.)  We then excluded any electrodes that showed putative epileptiform
+activity. Specifically, we excluded from further analysis any electrode that
+exhibited a maximum kurtosis of 10 or greater across all of that patient's
+recording sessions.  We also excluded any patients with fewer than 2 electrodes
+that passed this criteria, as the SuperEEG algorithm requires measuring
+correlations between 2 or more electrodes from each patient.  For Dataset 1,
+this yielded clean recordings from 4168 electrodes implanted throughout the
+brains of 67 patients (Fig.~\ref{fig:methods}A, colored dots); for Dataset 2,
+this yielded clean recordings from 5023 electrodes implanted in 78 patients.
+Each individual patient contributed electrodes from a limited set of brain
+locations, which we localized in a common space~\citep[MNI152;][]{GrabEtal06};
+an example Dataset 1 patient's 54 electrodes that survived the kurtosis
+thresholding procedure are highlighted in black and red
+(Fig.~\ref{fig:methods}A).
 
-The recording from a given electrode is maximally informative about
-the activity of the neural tissue immediately surrounding its
-recording surface.  However, brain regions that are distant from the
-recording surface of the electrode also contribute to the recording,
-albeit (ceteris paribus) to a much lesser extent.  One mechanism
-underlying these contributions is volume conduction.  The precise rate
-of falloff due to volume conduction (i.e., how much a small volume of
-brain tissue at location $x$ contributes to the recording from an
-electrode at location $\eta$) depends on the size of the recording
-surface, the electrode's impedance, and the conductance profile of the
-volume of brain between $x$ and $\eta$.  As an approximation of this
-intuition, we place a Gaussian radial basis function (RBF) at the
-location $\eta$ of each electrode's recording surface
-(Fig.~\ref{fig:methods}B).  We use the values of the RBF at any brain
-location $x$ as a rough estimate of how much structures around $x$
-contributed to the recording from location $\eta$:
-\begin{align}
-  \mathrm{rbf}(x|\eta,\lambda) & =
+The recording from a given electrode is maximally informative about the activity
+of the neural tissue immediately surrounding its recording surface.  However,
+brain regions that are distant from the recording surface of the electrode also
+contribute to the recording, albeit (ceteris paribus) to a much lesser extent.
+One mechanism underlying these contributions is volume conduction.  The precise
+rate of falloff due to volume conduction (i.e., how much a small volume of brain
+tissue at location $x$ contributes to the recording from an electrode at
+location $\eta$) depends on the size of the recording surface, the electrode's
+impedance, and the conductance profile of the volume of brain between $x$ and
+$\eta$.  As an approximation of this intuition, we place a Gaussian radial basis
+function (RBF) at the location $\eta$ of each electrode's recording surface
+(Fig.~\ref{fig:methods}B).  We use the values of the RBF at any brain location
+$x$ as a rough estimate of how much structures around $x$ contributed to the
+recording from location $\eta$: \begin{align} \mathrm{rbf}(x|\eta,\lambda) & =
 \mathrm{exp}\left\{ -\frac{||x - \eta||^2}{\lambda} \right\},\label{eqn:rbf}
-\end{align}
-where the width variable $\lambda$ is a parameter of the algorithm
-(which may in principle be set according to location-specific tissue
-conductance profiles) that governs the level of spatial smoothing.  In
-choosing $\lambda$ for the analyses presented here, we sought to
-maximize spatial resolution (which implies a small value of $\lambda$)
-while also maximizing the algorithm's ability to generalize to any
-location throughout the brain, including those without dense electrode
-coverage (which implies a large value of $\lambda$).  Here we set
-$\lambda = 20$, guided in part by our prior related work~\citep{MannEtal14b,
-  MannEtal18}, and in part by examining the brain coverage with
-non-zero weights achieved by placing RBFs at each electrode location
-in Dataset 1 and taking the sum (across all electrodes) at each voxel
-in a 4~mm$^3$ MNI brain.  (We then held $\lambda$ fixed for our
-analyses of Dataset 2.)  We note that this value could in theory be
-further optimized, e.g., using cross validation or a formal
-model~\citep[e.g.,][]{MannEtal18}.
+\end{align} where the width variable $\lambda$ is a parameter of the algorithm
+(which may in principle be set according to location-specific tissue conductance
+profiles) that governs the level of spatial smoothing.  In choosing $\lambda$
+for the analyses presented here, we sought to maximize spatial resolution (which
+implies a small value of $\lambda$) while also maximizing the algorithm's
+ability to generalize to any location throughout the brain, including those
+without dense electrode coverage (which implies a large value of $\lambda$).
+Here we set $\lambda = 20$, guided in part by our prior related
+work~\citep{MannEtal14b, MannEtal18}, and in part by examining the brain
+coverage with non-zero weights achieved by placing RBFs at each electrode
+location in Dataset 1 and taking the sum (across all electrodes) at each voxel
+in a 4~mm$^3$ MNI brain.  (We then held $\lambda$ fixed for our analyses of
+Dataset 2.)  We note that this value could in theory be further optimized, e.g.,
+using cross validation or a formal model~\citep[e.g.,][]{MannEtal18}.
 
-A second mechanism whereby a given region $x$ can contribute to the
-recording at $\eta$ is through (direct or indirect) anatomical
-connections between structures near $x$ and $\eta$.  Although
-anatomical and functional correlations can differ
+A second mechanism whereby a given region $x$ can contribute to the recording at
+$\eta$ is through (direct or indirect) anatomical connections between structures
+near $x$ and $\eta$.  Although anatomical and functional correlations can differ
 markedly~\citep[e.g.,][]{AdacEtal12, HoneEtal09, GoniEtal14}, we use temporal
 correlations in the data to estimate these anatomical
-connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations
-at which we wish to estimate local field potentials, and let
-$R_{s} \subseteq \bar{R}$ be set of locations at which we observe local
-field potentials from patient $s$ (excluding the electrodes that did
-not pass the kurtosis test described above). In the analyses below we
-define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate the expected
-inter-electrode correlation matrix for patient $s$, where
-$C_{s,k}(i,j)$ is the correlation between the time series of voltages
-for electrodes $i$ and $j$ from subject $s$ during session $k$, using:
+connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations at which
+we wish to estimate local field potentials, and let $R_{s} \subseteq \bar{R}$ be
+set of locations at which we observe local field potentials from patient $s$
+(excluding the electrodes that did not pass the kurtosis test described above).
+In the analyses below we define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate
+the expected inter-electrode correlation matrix for patient $s$, where
+$C_{s,k}(i,j)$ is the correlation between the time series of voltages for
+electrodes $i$ and $j$ from subject $s$ during session $k$, using:
 
@@
   \mathrm{r}\left(\frac{1}{n}\left(\sum_{k=1}^{n}\mathrm{z}(C_{s,k})\right)\right),\label{eqn:inter_corr}~\mathrm{where}\\
-\mathrm{z}(r) &= \frac{\log(1+r) - \log(1 - r)}{2}~\mathrm{is~the~Fisher}~z \mathrm{-transformation~and}\label{eqn:fishersz}\\
-\mathrm{z}^{-1}(z) = \mathrm{r}(z) &= \frac{\exp(2z) - 1}{\exp(2z) + 1}\mathrm{~is~its~inverse}.\label{eqn:invfishersz}
-\end{align}
-Next, we use Equation~\ref{eqn:rbf} to construct a number of
-to-be-estimated locations by number of patient electrode locations
-weight matrix, $W_s$.  Specifically, $W_s$ approximates how informative the
-recordings at each location in $R_s$ are in reconstructing activity at
-each location in $\bar{R}$, where the contributions fall off with an RBF according to
-the distances between the corresponding locations:
+  \mathrm{z}(r) &= \frac{\log(1+r) - \log(1 - r)}{2}~\mathrm{is~the~Fisher}~z
+  \mathrm{-transformation~and}\label{eqn:fishersz}\\ \mathrm{z}^{-1}(z) =
+  \mathrm{r}(z) &= \frac{\exp(2z) - 1}{\exp(2z) +
+  1}\mathrm{~is~its~inverse}.\label{eqn:invfishersz} \end{align} Next, we use
+  Equation~\ref{eqn:rbf} to construct a number of to-be-estimated locations by
+  number of patient electrode locations weight matrix, $W_s$.  Specifically,
+  $W_s$ approximates how informative the recordings at each location in $R_s$
+  are in reconstructing activity at each location in $\bar{R}$, where the
+  contributions fall off with an RBF according to the distances between the
+  corresponding locations:
 
@@
 
-Given this weight matrix, $W_s$,
-and the observed inter-electrode correlation matrix for patient $s$,
-$\bar{C}_{s}$, we can estimate the correlation matrix for all locations in
-$\bar{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:
+Given this weight matrix, $W_s$, and the observed inter-electrode correlation
+matrix for patient $s$, $\bar{C}_{s}$, we can estimate the correlation matrix
+for all locations in $\bar{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:
 
@@
 
-Having used the multi-patient data to estimate a full-brain
-correlation matrix at the set of locations in $\bar{R}$ that we wish
-to know about, we next use $\hat{K}$ to estimate activity patterns
-everywhere in $\bar{R}$, given observations at only a subset of
-locations in $\bar{R}$ (Fig.~\ref{fig:methods}E).
+Having used the multi-patient data to estimate a full-brain correlation matrix
+at the set of locations in $\bar{R}$ that we wish to know about, we next use
+$\hat{K}$ to estimate activity patterns everywhere in $\bar{R}$, given
+observations at only a subset of locations in $\bar{R}$
+(Fig.~\ref{fig:methods}E).
 
 Let $\alpha_s$ be the set of indices of patient $s$'s electrode locations in
-$\bar{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of indices of all other
-locations in $\bar{R}$. In other words, $\beta_s$ reflects the locations
-in $\bar{R}$ where we did not observe a recording for patient $s$
-(these are the recording locations we will want to fill in using SuperEEG).
-We can sub-divide $\hat{K}$ as follows:
+$\bar{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of
+indices of all other locations in $\bar{R}$. In other words, $\beta_s$ reflects
+the locations in $\bar{R}$ where we did not observe a recording for patient $s$
+(these are the recording locations we will want to fill in using SuperEEG). We
+can sub-divide $\hat{K}$ as follows:
 
@@
 $\left|\alpha_s\right|$ matrix of (observed) voltages from the electrodes in
-$\alpha_s$ during session $k$ from patient $s$. Then we can estimate the
-voltage from patient $s$'s $k^{th}$ session at the locations in
-$\beta_s$ as follows~\citep{Rasm06}:
+$\alpha_s$ during session $k$ from patient $s$. Then we can estimate the voltage
+from patient $s$'s $k^{th}$ session at the locations in $\beta_s$ as
+follows~\citep{Rasm06}:
 
@@
 
-We designed our approach to be agnostic to electrode impedances, as
-electrodes that do not exist do not have impedances.  Therefore our
-algorithm recovers voltages in standard deviation ($z$-scored) units
-rather than attempting to recover absolute voltages. (This property
-reflects the fact that $\hat{K}_{\beta_s, \alpha_s}$ and
-$\hat{K}_{\alpha_s, \alpha_s}$ are correlation matrices rather than
-covariance matrices.)  Also, we note that
-Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$
-matrix, which can become computationally intractable when $T$ is very
-large (e.g., an example patient in Dataset 1, $T = 12,786,750$; also
-see Fig.~\suppstats, Panels E and K). However, because
-Equation~\ref{eqn:reconstruction} is time invariant, we may compute
-$Y_{s,k,\beta_s}$ in a piecewise manner by filling in
-$Y_{s,k,\beta_s}$ one row at a time (using the corresponding samples
-from $Y_{s, k, \alpha_s}$).
+We designed our approach to be agnostic to electrode impedances, as electrodes
+that do not exist do not have impedances.  Therefore our algorithm recovers
+voltages in standard deviation ($z$-scored) units rather than attempting to
+recover absolute voltages. (This property reflects the fact that
+$\hat{K}_{\beta_s, \alpha_s}$ and $\hat{K}_{\alpha_s, \alpha_s}$ are correlation
+matrices rather than covariance matrices.)  Also, we note that
+Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$ matrix, which
+can become computationally intractable when $T$ is very large (e.g., an example
+patient in Dataset 1, $T = 12,786,750$; also see Fig.~\suppstats, Panels E and
+K). However, because Equation~\ref{eqn:reconstruction} is time invariant, we may
+compute $Y_{s,k,\beta_s}$ in a piecewise manner by filling in $Y_{s,k,\beta_s}$
+one row at a time (using the corresponding samples from $Y_{s, k, \alpha_s}$).
 
-The SuperEEG algorithm described above and in Figure~\ref{fig:methods}
-allows us to estimate, up to a constant scaling factor, local field
-potentials (LFPs) for each patient at all arbitrarily chosen locations
-in the set $\bar{R}$, \textit{even if we did not record that patient's
-  brain at all of those locations}.  We next turn to an evaluation of
-the accuracy of those estimates.
+The SuperEEG algorithm described above and in Figure~\ref{fig:methods} allows us
+to estimate, up to a constant scaling factor, local field potentials (LFPs) for
+each patient at all arbitrarily chosen locations in the set $\bar{R}$,
+\textit{even if we did not record that patient's brain at all of those
+locations}.  We next turn to an evaluation of the accuracy of those estimates.
 
 \section*{Results}
-We used a cross-validation approach to test the accuracy with which
-the SuperEEG algorithm reconstructs activity throughout the brain.
-For each patient in turn, we estimated full-brain correlation matrices
-(Eqn.~\ref{eqn:corrmat}) using data from all of the \textit{other}
-patients. This step ensured that the data we were reconstructing could
-not also be used to estimate the between-location correlations that
-drove the reconstructions via Equation~\ref{eqn:reconstruction}
-(otherwise the analysis would be circular).  For that held-out
-patient, we held out each electrode in turn.  We used
-Equation~\ref{eqn:reconstruction} to reconstruct activity at the
-held-out electrode location, using the correlation matrix learned from
-all other patients' data as $\hat{K}$, and using activity recorded
-from the other electrodes from the held-out patient as
-$Y_{s, k, \alpha_s}$.  We then asked: how closely did each of the
-SuperEEG-estimated recordings at those electrodes match the observed
-recordings from those electrodes (i.e., how closely did the estimated
-$\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$)?
+We used a cross-validation approach to test the accuracy with
+which the SuperEEG algorithm reconstructs activity throughout the brain. For
+each patient in turn, we estimated full-brain correlation matrices
+(Eqn.~\ref{eqn:corrmat}) using data from all of the \textit{other} patients.
+This step ensured that the data we were reconstructing could not also be used to
+estimate the between-location correlations that drove the reconstructions via
+Equation~\ref{eqn:reconstruction} (otherwise the analysis would be circular).
+For that held-out patient, we held out each electrode in turn.  We used
+Equation~\ref{eqn:reconstruction} to reconstruct activity at the held-out
+electrode location, using the correlation matrix learned from all other
+patients' data as $\hat{K}$, and using activity recorded from the other
+electrodes from the held-out patient as $Y_{s, k, \alpha_s}$.  We then asked:
+how closely did each of the SuperEEG-estimated recordings at those electrodes
+match the observed recordings from those electrodes (i.e., how closely did the
+estimated $\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$)?
 
-We used this general approach to quantify the algorithm's performance
-across the full dataset. For each held-out electrode, from each
-held-out patient in turn, we computed the average correlation (across
-recording sessions) between the SuperEEG-reconstructed voltage traces
-and the observed voltage traces from that electrode.  For this
-analysis we set $\bar{R}$ to be the union of all electrode locations
-across all patients.  This yielded a single correlation coefficient
-for each electrode location in $\bar{R}$, reflecting how well the
-SuperEEG algorithm was able to recover the recording at that location
-by incorporating data across patients (black histogram in
-Fig.~\ref{fig:corrmap}A, map in Fig.~\ref{fig:corrmap}C).  The
-observed distribution of correlations was centered well above zero
-(mean: 0.51; $t$-test comparing mean of distribution of
-$z$-transformed average patient correlation coefficients to 0:
-$t(66) = 23.55, p < 10^{-10}$), indicating that the SuperEEG algorithm
-recovers held-out activity patterns substantially better than random
-guessing.
+We used this general approach to quantify the algorithm's performance across the
+full dataset. For each held-out electrode, from each held-out patient in turn,
+we computed the average correlation (across recording sessions) between the
+SuperEEG-reconstructed voltage traces and the observed voltage traces from that
+electrode.  For this analysis we set $\bar{R}$ to be the union of all electrode
+locations across all patients.  This yielded a single correlation coefficient
+for each electrode location in $\bar{R}$, reflecting how well the SuperEEG
+algorithm was able to recover the recording at that location by incorporating
+data across patients (black histogram in Fig.~\ref{fig:corrmap}A, map in
+Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations was
+centered well above zero (mean: 0.51; $t$-test comparing mean of distribution of
+$z$-transformed average patient correlation coefficients to 0: $t(66) = 23.55, p
+< 10^{-10}$), indicating that the SuperEEG algorithm recovers held-out activity
+patterns substantially better than random guessing.
 
-Next, we compared the quality of these
-across-participant reconstructions (i.e., computed using a correlation
-model learned from other patients' data) to reconstructions generated
-using a correlation model trained using the in-patient's data.  In
-other words, for this within-patient benchmark analysis we estimated
-$\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in turn,
-using recordings from all of that patient's electrodes except at the
-location we were reconstructing.  These within-patient reconstructions
-serve as an estimate of how well data from all of the other electrodes
-from that single patient may be used to estimate held-out data from
-the same patient.  This allows us to ask how much information about
-the activity at a given electrode might be inferred through (a) volume
-conductance or other sources of ``leakage'' from activity patterns
-measured from the patient's other electrodes and (b) across-electrode
-correlations learned from that single patient.  As shown in
-Figure~\ref{fig:corrmap}A (gray histogram), the distribution of
-within-patient correlations was centered well above zero (mean: 0.32;
-$t$-test comparing mean of distribution of $z$-transformed average
-patient correlation coefficients to 0: $t(66) = 15.16, p < 10^{-10}$).
-However, the across-patient correlations were substantially higher
-($t$-test comparing average $z$-transformed within versus across
-patient electrode correlations: $t(66) = 9.17, p < 10^{-10}$).  This
-is an especially conservative test, given that the across-patient
-SuperEEG reconstructions exclude (from the correlation matrix
-estimates) all data from the patient whose data is being
-reconstructed.  We repeated each of these analyses on a second
-independent dataset and found similar results
-(Fig.~\ref{fig:corrmap}B, D; within versus across reconstruction
-accuracy: $t(77) = 11.25, p < 10^{-10}$). We also replicated this result
-separately for each of the two experiments from Dataset 2
-(Fig.~\perexpcorrmaps).  This overall finding, that reconstructions of
-held-out data using correlation models learned from \textit{other}
-patient's data yield higher reconstruction accuracy than correlation
-models learned from the patient whose data is being reconstructed, has
-two important implications.  First, it implies that distant electrodes
-provide additional predictive power to the data reconstructions beyond
-the information contained solely in nearby electrodes.  (This follows
-from the fact that each patient's grid, strip, and depth electrodes
-are implanted in a unique set of locations, so for any given electrode
-the closest electrodes in the full dataset tend to come from the
-same patient.)  Second, it implies that the spatial correlations
-learned using the SuperEEG algorithm are, to some extent, similar
-across people.
+Next, we compared the quality of these across-participant reconstructions (i.e.,
+computed using a correlation model learned from other patients' data) to
+reconstructions generated using a correlation model trained using the
+in-patient's data.  In other words, for this within-patient benchmark analysis
+we estimated $\hat{C}_{s}$ (Eqn.~\ref{eqn:subj_corrmat}) for each patient in
+turn, using recordings from all of that patient's electrodes except at the
+location we were reconstructing.  These within-patient reconstructions serve as
+an estimate of how well data from all of the other electrodes from that single
+patient may be used to estimate held-out data from the same patient.  This
+allows us to ask how much information about the activity at a given electrode
+might be inferred through (a) volume conductance or other sources of ``leakage''
+from activity patterns measured from the patient's other electrodes and (b)
+across-electrode correlations learned from that single patient.  As shown in
+Figure~\ref{fig:corrmap}A (gray histogram), the distribution of within-patient
+correlations was centered well above zero (mean: 0.32; $t$-test comparing mean
+of distribution of $z$-transformed average patient correlation coefficients to
+0: $t(66) = 15.16, p < 10^{-10}$). However, the across-patient correlations were
+substantially higher ($t$-test comparing average $z$-transformed within versus
+across patient electrode correlations: $t(66) = 9.17, p < 10^{-10}$).  This is
+an especially conservative test, given that the across-patient SuperEEG
+reconstructions exclude (from the correlation matrix estimates) all data from
+the patient whose data is being reconstructed.  We repeated each of these
+analyses on a second independent dataset and found similar results
+(Fig.~\ref{fig:corrmap}B, D; within versus across reconstruction accuracy:
+$t(77) = 11.25, p < 10^{-10}$). We also replicated this result separately for
+each of the two experiments from Dataset 2 (Fig.~\perexpcorrmaps).  This overall
+finding, that reconstructions of held-out data using correlation models learned
+from \textit{other} patient's data yield higher reconstruction accuracy than
+correlation models learned from the patient whose data is being reconstructed,
+has two important implications.  First, it implies that distant electrodes
+provide additional predictive power to the data reconstructions beyond the
+information contained solely in nearby electrodes.  (This follows from the fact
+that each patient's grid, strip, and depth electrodes are implanted in a unique
+set of locations, so for any given electrode the closest electrodes in the full
+dataset tend to come from the same patient.)  Second, it implies that the
+spatial correlations learned using the SuperEEG algorithm are, to some extent,
+similar across people.
 
@@
 
-The recordings we analyzed from Dataset 1 comprised data collected as
-the patients performed a variety of (largely idiosyncratic) tasks
-throughout each day's recording session.  That we observed reliable
-reconstruction accuracy across patients suggests that the spatial
-correlations derived from the SuperEEG algorithm are, to some extent,
-similar across tasks.  We tested this finding more directly using
-Dataset 2.  In Dataset 2, the recordings were limited to times when
-each patient was participating in one of two experiments.  Experiment
-1 is a random-word list free recall task; Experiment 2 is a
-categorized list free recall task (24 patients particpated in both).  We wondered whether a correlation
-model learned from data from one experiment might yield good
-predictions of data from the other experiment.  Further, we wondered
-about the extent to which it might be beneficial or harmful to combine
-data across tasks.
+The recordings we analyzed from Dataset 1 comprised data collected as the
+patients performed a variety of (largely idiosyncratic) tasks throughout each
+day's recording session.  That we observed reliable reconstruction accuracy
+across patients suggests that the spatial correlations derived from the SuperEEG
+algorithm are, to some extent, similar across tasks.  We tested this finding
+more directly using Dataset 2.  In Dataset 2, the recordings were limited to
+times when each patient was participating in one of two experiments.  Experiment
+1 is a random-word list free recall task; Experiment 2 is a categorized list
+free recall task (24 patients particpated in both).  We wondered whether a
+correlation model learned from data from one experiment might yield good
+predictions of data from the other experiment.  Further, we wondered about the
+extent to which it might be beneficial or harmful to combine data across tasks.
 
-To test the task-specificity of the SuperEEG-derived correlation
-models, we restricted the dataset to the 24 patients that participated
-in both experiments and repeated the above within- and across-patient
-cross validation procedures separately for Experiment 1 and Experiment
-2 data from Dataset 2.  We then compared the reconstruction accuracies
-for held-out electrodes, for models trained within versus across the
-two experiments, or combining across both experiments
-(Fig.~\perexptaskrecon).  In every case we found that across-patient
-models trained using data from all other patients out-performed
-within-patient models trained on data only from the subject
-contributing the given electrode ($t$s$(23) > 6.50, p$s$ < 10^{-5}$).
-All reconstruction accuracies also reliably exceeded chance
-performance ($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average
-reconstruction accuracy was highest for the across-patient models
-limited to data from the same experiment (mean accuracy: $0.68$);
-next-highest for the models that combined data across both experiments
-(mean accuracy: $0.61$); and lowest for models trained across tasks
-(mean accuracy: $0.47$).  This pattern of results also held for each
-of the Dataset 2 experiments individually
-(Fig.~\perexptaskreconseparated).  Taken together, these results
-indicate that there are reliable commonalities in the spatial
-correlations of full-brain activity across tasks, but that there are
-also reliable differences in these spatial correlations across tasks.
-Whereas reconstruction accuracy benefits from incorporating data from
-other patients, reconstruction accuracy is highest when constrained to
-within-task data, or data that includes a variety of tasks (e.g.,
+To test the task-specificity of the SuperEEG-derived correlation models, we
+restricted the dataset to the 24 patients that participated in both experiments
+and repeated the above within- and across-patient cross validation procedures
+separately for Experiment 1 and Experiment 2 data from Dataset 2.  We then
+compared the reconstruction accuracies for held-out electrodes, for models
+trained within versus across the two experiments, or combining across both
+experiments (Fig.~\perexptaskrecon).  In every case we found that across-patient
+models trained using data from all other patients out-performed within-patient
+models trained on data only from the subject contributing the given electrode
+($t$s$(23) > 6.50, p$s$ < 10^{-5}$). All reconstruction accuracies also reliably
+exceeded chance performance ($t$s$(23) > 8.00, p$s$ < 10^{-8}$).  Average
+reconstruction accuracy was highest for the across-patient models limited to
+data from the same experiment (mean accuracy: $0.68$); next-highest for the
+models that combined data across both experiments (mean accuracy: $0.61$); and
+lowest for models trained across tasks (mean accuracy: $0.47$).  This pattern of
+results also held for each of the Dataset 2 experiments individually
+(Fig.~\perexptaskreconseparated).  Taken together, these results indicate that
+there are reliable commonalities in the spatial correlations of full-brain
+activity across tasks, but that there are also reliable differences in these
+spatial correlations across tasks. Whereas reconstruction accuracy benefits from
+incorporating data from other patients, reconstruction accuracy is highest when
+constrained to within-task data, or data that includes a variety of tasks (e.g.,
 Dataset 1, or combining across the two Dataset 2 experiments).
 
-Although both datasets we examined provide good full-brain coverage
-(when considering data from every patient; e.g.\
-Fig.~\ref{fig:corrmap}C, D), electrodes were not sampled uniformly
-throughout the brain.  For example, electrodes are more likely to be
-implanted in regions like the medial temporal lobe (MTL), and are
-rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
-Separately for each dataset, for each voxel in the 4~mm$^3$ voxel
-MNI152 brain, we computed the proportion of electrodes in the dataset
-that were contained within a 20 MNI unit radius sphere centered on
-that voxel.  We defined the \textit{density} at that location as this
-proportion.  Across Datasets 1 and 2, the electrode placement
-densities were similar (correlation by voxel:
-$r = 0.6, p < 10^{-10}$).  We wondered whether regions with good
-covererage might be associated with better reconstruction accuracy.
-For example, Figures~\ref{fig:corrmap}C and D indicate that many
-electrodes in the MTL (which tends to be relatively densely sampled)
-have relatively high reconstruction accuracy, and occipital electrodes
-(which tends to be relatively sparsely sampled) tend to have
-relatively low reconstruction accuracy.  To test whether this held
-more generally across the entire brain, for each dataset we computed
-the electrode placement density for each electrode from each patient
-(using the proportion of \textit{other} patients' electrodes within 20
-MNI units of the given electrode).  We then correlated these density
-values with the across-patient reconstruction accuracies for eachg
-electrode.  We found a statistically reliable negative correlation
-between reconstruction accuracy and density for Dataset 1, but no
-reliable correlation for Dataset 2 (Dataset 1: $r = -0.21, p = 0.05$;
-Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
-reconstruction accuracies we observed are \textit{not} driven solely
-by sampling density, but rather may also reflect higher order
-properties of neural dynamics such as functional correlations between
-distant voxels~\citep{BetzEtal17b}.
+Although both datasets we examined provide good full-brain coverage (when
+considering data from every patient; e.g.\ Fig.~\ref{fig:corrmap}C, D),
+electrodes were not sampled uniformly throughout the brain.  For example,
+electrodes are more likely to be implanted in regions like the medial temporal
+lobe (MTL), and are rarely implanted in occipital cortex
+(Fig.~\ref{fig:density}A, B). Separately for each dataset, for each voxel in the
+4~mm$^3$ voxel MNI152 brain, we computed the proportion of electrodes in the
+dataset that were contained within a 20 MNI unit radius sphere centered on that
+voxel.  We defined the \textit{density} at that location as this proportion.
+Across Datasets 1 and 2, the electrode placement densities were similar
+(correlation by voxel: $r = 0.6, p < 10^{-10}$).  We wondered whether regions
+with good covererage might be associated with better reconstruction accuracy.
+For example, Figures~\ref{fig:corrmap}C and D indicate that many electrodes in
+the MTL (which tends to be relatively densely sampled) have relatively high
+reconstruction accuracy, and occipital electrodes (which tends to be relatively
+sparsely sampled) tend to have relatively low reconstruction accuracy.  To test
+whether this held more generally across the entire brain, for each dataset we
+computed the electrode placement density for each electrode from each patient
+(using the proportion of \textit{other} patients' electrodes within 20 MNI units
+of the given electrode).  We then correlated these density values with the
+across-patient reconstruction accuracies for eachg electrode.  We found a
+statistically reliable negative correlation between reconstruction accuracy and
+density for Dataset 1, but no reliable correlation for Dataset 2 (Dataset 1: $r
+= -0.21, p = 0.05$; Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
+reconstruction accuracies we observed are \textit{not} driven solely by sampling
+density, but rather may also reflect higher order properties of neural dynamics
+such as functional correlations between distant voxels~\citep{BetzEtal17b}.
 
-Prior work in humans and animals has shown that the spatial profile of
-the local field potential differs by frequency band~\citep[e.g., with
-respect to volume conductance properties and contribution to the local
-field potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example,
-lower frequency components of the local field potential tend to have
-higher power and extend further in space than high-frequency
-components~\citep[e.g., ][]{MillEtal07, MannEtal09}.  We therefore
-wondered whether the reconstructions we observed might be differently
-weighting or considering the contributions of activity at different
-frequency bands.  We therefore examined a range of frequency bands
-($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$:
-12--30 Hz; $\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along
-with a measure of broadband power~\citep[defined as the mean height of
-a linear robust regression fit in log-log space to the order 4 Morelet
-wavelet-computed power spectrum at 50 log-spaced frequencies from from
-2--100 Hz;][]{MannEtal09}.  We used second-order Butterworth bandpass
-filters to compute the activity patterns within each narrow frequency
-band.  We then repeated our within-subject and across-subject
-cross-validated reconstruction accuracy tests (analogous to
+Prior work in humans and animals has shown that the spatial profile of the local
+field potential differs by frequency band~\citep[e.g., with respect to volume
+conductance properties and contribution to the local field
+potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example, lower frequency
+components of the local field potential tend to have higher power and extend
+further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
+MannEtal09}.  We therefore wondered whether the reconstructions we observed
+might be differently weighting or considering the contributions of activity at
+different frequency bands.  We therefore examined a range of frequency bands
+($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz;
+$\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of
+broadband power~\citep[defined as the mean height of a linear robust regression
+fit in log-log space to the order 4 Morelet wavelet-computed power spectrum at
+50 log-spaced frequencies from from 2--100 Hz;][]{MannEtal09}.  We used
+second-order Butterworth bandpass filters to compute the activity patterns
+within each narrow frequency band.  We then repeated our within-subject and
+across-subject cross-validated reconstruction accuracy tests (analogous to
 Fig.~\ref{fig:corrmaps}) separately for each frequency band
-(Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis
-on the Hilbert transform-computed spectral power within each narrow
-band; see Fig.~\freqpower.)  Across both datasets, we found that our
-approach is best at reconstructing patterns of broadband activity
-(right-most bars in Figs.~\ref{fig:frequency}A and D), a correlate of
-population firing rate~\citep{MannEtal09}.  We also achieved good
-reconstruction accuracy within each narrow frequency band
-(Figs.~\ref{fig:frequency} and \freqpower).  Activity at lower
-frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
-reconstructed better than high-frequency patterns ($\gamma_L$ and
-$\gamma_H$), with reconstruction accuracy peaking in the $\alpha$
-band.  Overall, these results indicate that our approach is able to
-accurately recover information within the 2--100 Hz range, although
-those reconstructions are most accurate for low-frequency or broadband patterns.
+(Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis on the
+Hilbert transform-computed spectral power within each narrow band; see
+Fig.~\freqpower.)  Across both datasets, we found that our approach is best at
+reconstructing patterns of broadband activity (right-most bars in
+Figs.~\ref{fig:frequency}A and D), a correlate of population firing
+rate~\citep{MannEtal09}.  We also achieved good reconstruction accuracy within
+each narrow frequency band (Figs.~\ref{fig:frequency} and \freqpower).  Activity
+at lower frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
+reconstructed better than high-frequency patterns ($\gamma_L$ and $\gamma_H$),
+with reconstruction accuracy peaking in the $\alpha$ band.  Overall, these
+results indicate that our approach is able to accurately recover information
+within the 2--100 Hz range, although those reconstructions are most accurate for
+low-frequency or broadband patterns.
 
@@
 
-A basic assumption of our approach (and
-of most prior ECoG work) is that electrode recordings are most
-informative about the neural activity near the recording surface of
-the electrode.  But if we consider that activity patterns throughout
-the brain are meaningfully correlated, are there particular
-implantation locations that, if present in a patient's brain, yield
-especially high reconstruction accuracies throughout the rest of the
-brain?  For example, one might hypothesize that brain structures that
-are heavily interconnected with many other structures could be more
-informative about full-brain activity patterns than comparatively
-isolated structures.  To test this hypothesis, we computed the average reconstruction
-accuracy across all of each patient's electrodes (using our
-across-patients cross validation test; black histograms in
-Fig.~\ref{fig:corrmap}A and B).  We first labeled each patient's electrodes,
-in each dataset, with the average reconstruction accuracy for that
-patient.  In other words, we assigned every electrode from each
-patient the same value, reflecting how well the activity patterns for that patient were reconstructed.  Next, for each voxel
-in the 4~mm$^3$ MNI brain, we computed the average value across any
-electrode (from any patient) that came within 20 MNI units of that
-voxel's center.  This yielded an \textit{information
-  score} for each voxel, reflecting the average reconstruction
-accuracy across any patients with electrodes near each voxel-- where
-the averages were weighted to reflect patients who had more electrodes
-implanted near that location. We created a single map of these information scores for each
-dataset, highlighting regions that are especially informative about activity in \textit{other} brain areas
-(Fig.~\ref{fig:informap}A and B).  Despite task
-and patient differences across the two datasets, we nonetheless found
-that the maps of the most promising implantation targets derived from
-both datasets were similar (voxelwise correlation between information
-scores across the two datasets: $r = 0.18, p < 10^{-10}$).  While the
-correspondence between the two maps was imperfect, our finding that
-there were some commonalities between the two maps lends support to
-the notion that different brain areas are differently informative
-about full-brain activity patterns.  We also examined the intersection
-between the top 10\% most informative voxels across the two datasets
-(gray areas in Fig.~\ref{fig:informap}C, networks shown in
-Fig.~\ref{fig:networks}A (All)).
-Supporting the notion that structures that are highly interconnected
-with the rest of the brain might be especially good targets for
-implantation, this intersecting set of voxels with the highest
-information scores included major portions of the dorsal attention
-network (e.g., inferior parietal lobule, precuneus, inferior temporal
-gyrus, thalamus, and striatum) as well as some portions of the default
-mode network (e.g., angular gyrus) that are highly interconnected with
-a large proportion of the brain's gray matter~\citep[e.g., ][]{TomaVolk11}.
+A basic assumption of our approach (and of most prior ECoG work) is that
+electrode recordings are most informative about the neural activity near the
+recording surface of the electrode.  But if we consider that activity patterns
+throughout the brain are meaningfully correlated, are there particular
+implantation locations that, if present in a patient's brain, yield especially
+high reconstruction accuracies throughout the rest of the brain?  For example,
+one might hypothesize that brain structures that are heavily interconnected with
+many other structures could be more informative about full-brain activity
+patterns than comparatively isolated structures.  To test this hypothesis, we
+computed the average reconstruction accuracy across all of each patient's
+electrodes (using our across-patients cross validation test; black histograms in
+Fig.~\ref{fig:corrmap}A and B).  We first labeled each patient's electrodes, in
+each dataset, with the average reconstruction accuracy for that patient.  In
+other words, we assigned every electrode from each patient the same value,
+reflecting how well the activity patterns for that patient were reconstructed.
+Next, for each voxel in the 4~mm$^3$ MNI brain, we computed the average value
+across any electrode (from any patient) that came within 20 MNI units of that
+voxel's center.  This yielded an \textit{information score} for each voxel,
+reflecting the average reconstruction accuracy across any patients with
+electrodes near each voxel-- where the averages were weighted to reflect
+patients who had more electrodes implanted near that location. We created a
+single map of these information scores for each dataset, highlighting regions
+that are especially informative about activity in \textit{other} brain areas
+(Fig.~\ref{fig:informap}A and B).  Despite task and patient differences across
+the two datasets, we nonetheless found that the maps of the most promising
+implantation targets derived from both datasets were similar (voxelwise
+correlation between information scores across the two datasets: $r = 0.18, p <
+10^{-10}$).  While the correspondence between the two maps was imperfect, our
+finding that there were some commonalities between the two maps lends support to
+the notion that different brain areas are differently informative about
+full-brain activity patterns.  We also examined the intersection between the top
+10\% most informative voxels across the two datasets (gray areas in
+Fig.~\ref{fig:informap}C, networks shown in Fig.~\ref{fig:networks}A (All)).
+Supporting the notion that structures that are highly interconnected with the
+rest of the brain might be especially good targets for implantation, this
+intersecting set of voxels with the highest information scores included major
+portions of the dorsal attention network (e.g., inferior parietal lobule,
+precuneus, inferior temporal gyrus, thalamus, and striatum) as well as some
+portions of the default mode network (e.g., angular gyrus) that are highly
+interconnected with a large proportion of the brain's gray matter~\citep[e.g.,
+][]{TomaVolk11}.
 
@@
 
-We also wondered whether the map of information scores might vary as a function of the spectral
-components of the activity patterns under consideration.  For example, low frequency $\delta$ activity in the thalamus has been implicated in
-supporting connectivity with cortex~\citep[e.g.,][]{Jone09}; $\theta$ activity
-in frontal regions have been implicated in memory consolidation~\citep{NishEtal09} and integration~\citep{BackEtal16}; parietal and occipital $\alpha activity has been
-implicated in attention modulation~\citep[e.g., see][]{Klim12}; $\beta$ activity in motor cortex have been implicated in motor control and processing~\citep{BrovEtal04, KoelEtal08, RubiEtal06};
-and occipital $\gamma$ activity has been implicated in visual attention and visual processing~\citep{ZhouEtal16, TallEtal05, FrieEtal07}.
-We computed analogous maps of information scores for each individual frequency band.
-Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed reliable positive correlations
-between the voxel-by-voxel maps of information scores ($\delta$: $r = 0.09, p < 10^{-57}$;
-$\theta$: $r = 0.24, p < 10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$,
-$\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$: $r = 0.1, p < 10^{-67}$;
-$\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r = 0.21, p < 10^{-297}).
+We also wondered whether the map of information scores might vary as a function
+of the spectral components of the activity patterns under consideration.  For
+example, low frequency $\delta$ activity in the thalamus has been implicated in
+supporting connectivity with cortex~\citep[e.g.,][]{Jone09}. We computed
+analogous maps of information scores for each individual frequency band. Across
+Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed
+reliable positive correlations between the voxel-by-voxel maps of information
+scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$;
+$\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$:
+$r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r =
+0.21, p < 10^{-297})$.
 
 To gain additional insight into which regions were most informative about
-full-brain activity patterns at different frequency ranges, we next computed (for each frequency range)
-the intersection of the top 10\% highest information scores across the maps for
-Datasets 1 and 2 (analogous to our approach in Fig.~\ref{fig:informap}C).
-This yielded a single map of the (reliably) most informative locations for each frequency range we examined.
-We then carried out two \textit{post hoc} analyses on each of these maps to better characterize
-the underlying structural and functional properties of each set of regions we identified
-as being particularly informative about one or more neural patterns.
+full-brain activity patterns at different frequency ranges, we next computed
+(for each frequency range) the intersection of the top 10\% highest information
+scores across the maps for Datasets 1 and 2 (analogous to our approach in
+Fig.~\ref{fig:informap}C). This yielded a single map of the (reliably) most
+informative locations for each frequency range we examined. We then carried out
+two \textit{post hoc} analyses on each of these maps to better characterize the
+underlying structural and functional properties of each set of regions we
+identified as being particularly informative about one or more neural patterns.
 
-A growing body of neuroscientific research is concerned with characterizing the \textit{parcellations}
-of anatomical and functional brain networks~\citep[for review see][]{ZaleEtal10, ArslEtal18}.
-The dominant approaches entail obtaining a full-brain connectivity matrix using either diffusion tensor imaging to identify the brain's network of
-white matter connections, or functional connectivity (typically applied to resting state data) to
-correlate the patterns of activity exhibited by different brain structures.  One can then apply graph theoretic approaches
-to assign each brain structure (typically a single fMRI voxel) to one or more networks~\citep[for review see][]{BullSpor09}.
-The result is a set of distinct (or partially overlapping) brain ``networks'' that may be
-further examined to elucidate their potential functional role.  We overlaid a well-cited seven-network
-parcellation map identified by \cite{YeoEtal11} onto the maps of brain locations that were most informative
-about each neural pattern.  For each of these information maps, we computed the proportion of voxels in the most informative
-brain regions that belonged to each of the seven networks identified by \cite{YeoEtal11}.
-We found that the regions we identified as being most informative about different neural patterns varied
-markedly with respect to which functional networks they belonged to (Fig.~\ref{fig:networks}A, B).  This is consistent with
-the notion that there is no ``universal'' brain region that consistently reflects activity in the rest of the brain.  Rather,
-each region's activity patterns appear to be characterized by different spectral profiles, and the ability to
-infer activity patterns at a particular frequency range depends on the structural and functional
-connectome specific to that frequency range.
+A growing body of neuroscientific research is concerned with characterizing the
+\textit{parcellations} of anatomical and functional brain networks~\citep[for
+review see][]{ZaleEtal10, ArslEtal18}. The dominant approaches entail obtaining
+a full-brain connectivity matrix using either diffusion tensor imaging to
+identify the brain's network of white matter connections, or functional
+connectivity (typically applied to resting state data) to correlate the patterns
+of activity exhibited by different brain structures.  One can then apply graph
+theoretic approaches to assign each brain structure (typically a single fMRI
+voxel) to one or more networks~\citep[for review see][]{BullSpor09}. The result
+is a set of distinct (or partially overlapping) brain ``networks'' that may be
+further examined to elucidate their potential functional role.  We overlaid a
+well-cited seven-network parcellation map identified by \cite{YeoEtal11} onto
+the maps of brain locations that were most informative about each neural
+pattern.  For each of these information maps, we computed the proportion of
+voxels in the most informative brain regions that belonged to each of the seven
+networks identified by \cite{YeoEtal11}; Figure~\ref{fig:networks}D. We found
+that the regions we identified as being most informative about different neural
+patterns varied markedly with respect to which functional networks they belonged
+to (Fig.~\ref{fig:networks}A, B).
 
-%next: neurosynth
+The frequency-specific information score maps we observed were consistent with
+the notion that there is no ``universal'' brain region that  reflects all
+activity patterns throughout the rest of the brain.  Rather, each region's
+activity patterns appear to be characterized by different spectral profiles, and
+the ability to infer full-brain activity patterns at a particular frequency
+range depends on the structural and functional connectome specific to that
+frequency range (Fig.~\ref{fig:networks}E).  We wondered how the maps we found
+might fit in with prior work.  To this end, in addition to examining the
+anatomical profiles of each map, we used Neurosynth~\citep{RubiEtal17} to
+identify (using meta analyses of the neuroimaging literature) the top five most
+common terms associated with each frequency-specific map
+(Fig.~\ref{fig:networks}C).  We found that $\delta$ patterns across the brain
+were best predicted by regions of ventromedial prefrontal cortex, striatum, and
+thalamus (yellow).  These regions are also implicated in modulating $\delta$
+oscillations during sleep, and are heavily interconnected with
+cortex~\citep[e.g.,][]{AmziSter98}.  The brain areas most predictive of
+full-brain $\theta$ patterns were occipital and parietal regions traditionally
+linked with visual processing and visual attention (light green). Prior work has
+implicated $\theta$ oscillations in these areas in periodic sampling of visual
+attention~\citep[e.g.,][]{BuscVanR10}.  We found that full-brain $\alpha$
+patterns were best predicted by motor areas (dark green), which also exhibit
+$\alpha$ band changes during voluntary movements~\citep[e.g.,][]{JurkEtal06}.
+Striatum and thalamus (teal) were most informative about full-brain $\beta$
+patterns.  Prior work has implicated striatal $\beta$ activity in sensory and
+motor processing~\citep{FeinEtal15} and thalamic $\beta$ activity has been
+implicated in modulating widespread $\beta$ patterns across
+neocortex~\citep{SherEtal16}. Somatosensory areas (dark blue) were most
+informative about full-brain $\gamma_L$ patterns. Prior work has implicated
+somatosensory $\gamma_L$ in somatosensory processing and motor
+planning~\citep{AyaEtal03}.  Occipital cortex (purple) was most informative
+about full-brain $\gamma_H$ patterns.  Occipital $\gamma_H$ has also been linked
+with visual processing and reading~\citep{WuEtal11} and the transmission of
+visual representations from low-order to higher-order visual
+areas~\citep{MatsEtal13}.  Full-brain broadband patterns were best predicted by
+inferior parietal cortex precuneus (maroon).  Functional neuroimaging BOLD
+responses~\citep{SimoEtal16} and broadband ECoG patterns~\citep{HoneEtal12} in
+these default-mode hubs have been implicated in processing context-dependent
+representations that unfold over long timescales.
 
-%%%%STOPPED HERE
-
-as $\delta$, $\theta$, and $\alpha$, have
-been implicated in processing modes which span large swaths of
-cortical regions and are thought to serve the purpose of integration
-across many cortical sites ~\citep{Knya12}. Higher frequency
-oscillations such as $\beta$ and $\gamma$, are more limited to topographic
-areas ~\citep{Nune95}, and are modulated by slow oscillations
-hierarchically ~\citep{EngeEtal10}. Using the frequency-specific reconstruction accuracies, we
-followed the process outlined in Fig.~\ref{fig:informap}C, to obtain
-the most informative locations for each frequency.  When we examined the intersection
-between the top 10\% most informative voxels across the two datasets
-for each bandpassed frequency, we found a somewhat consistent hierarchical
-structure (see Fig.~\ref{fig:networks}E).
-
-We then wondered which
-networks were involved in each of
-these frequency-specific intersecting regions.  To better understand the networks involved
-we colored the regions (Fig.~\ref{fig:networks}A) based on the
-network parcellation ~\citep[using $k$=7;][]{YeoEtal11}} (Fig.~\ref{fig:networks}D) and calculated the proportion of each
-of those networks (Fig.~\ref{fig:networks}B).  Consistent with the idea outlined
-above, we found networks most involved in the lowest frequency band,
-$\delta$, were networks involved integration and global processing
-(specifically the dorsal attention ~\citep{MarzEtal13}, default mode,
-and frontoparietal networks).  Although these networks are also seen
-in the $\theta$ intersection, they are less proportionally to the
-visual network.  Alpha power is consistently modulated in EEG studies
-of attention and visuo-motor ~\citep{MantEtal07, MarzEtal13}, and we
-similarly found a high proportion of visual, somatomotor, and dorsal attention networks
-within this band.  We found $\beta$ intersections to predominantly
-consist of somatomotor network, in line with~\citep{RittEtal09, VaneEtal11}.  Also accordant with heavily cited
-literature~\citep{FrieEtal07}, the network most predominant in the
-$\gamma$ intersection was the visual network.  Lastly, broadband power
-was found predominantly in frontoparietal and default mode networks,
-consistent with ~\citep{OssaEtal11}.
+Taken together, the frequency-specific information maps suggest potential new
+interpretation of many of the above previously reported findings.  Prior work
+has largely treated region-specific narrowband and broadband activity as an
+indictor that activity at those frequency ranges reflect that the given region
+is representing or supporting a particular function.  Our work suggests the
+alternative interpretation that when we observe a particular neural pattern in a
+particular brain region, it may instead reflect how that region is is transmitting
+information to the rest of the brain via patterns at the given frequency range.
 
@@
 \section*{Discussion}
-Are our brain's networks static or dynamic?  And to what extent are
-the network properties of our brains stable across people and tasks?
-One body of work suggests that our brain's \textit{functional}
-networks are dynamic~\citep[e.g., ][]{MannEtal18},
-person-specific~\citep[e.g., ][]{FinnEtal15}, and
-task-specific~\citep[e.g., ][]{Turk13}.  In contrast, although the
-gross anatomical structure of our brains changes meaningfully over the
-course of years as our brains develop, on the timescales of typical
-neuroimaging experiments (i.e., hours to days) our anatomical networks
-are largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many
-aspects of brain anatomy, including white matter structure, are largely
-preserved across people~\citep[e.g., ][]{TalaTour88, JahaEtal13,
-  MoriEtal08}. There are several possible means of reconciling this
-apparent inconsistency between dynamic person- and task-specific
-functional networks versus stable anatomical networks.  For example,
-relatively small magnitude anatomical differences across people may be
-reflected in reliable functional connectivity differences.  Along
-these lines, one recent study found that diffusion tensor imaging
-(DTI) structural data is similar across people, but may be used to
-predict person-specific resting state functional connectivity
-data~\citep{BeckEtal18}.  Similarly, other work indicates that
-task-specific functional connectivity may be predicted by resting
-state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.  Another
-(potentially complementary) possibility is that our functional
-networks are constrained by anatomy, but nevertheless exhibit
-(potentially rapid) task-dependent changes~\citep[e.g.,
-][]{SporBetz16}.
+Are our brain's networks static or dynamic?  And to what
+extent are the network properties of our brains stable across people and tasks?
+One body of work suggests that our brain's \textit{functional} networks are
+dynamic~\citep[e.g., ][]{MannEtal18}, person-specific~\citep[e.g.,
+][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.  In contrast,
+although the gross anatomical structure of our brains changes meaningfully over
+the course of years as our brains develop, on the timescales of typical
+neuroimaging experiments (i.e., hours to days) our anatomical networks are
+largely stable~\citep[e.g., ][]{CaseEtal00}.  Further, many aspects of brain
+anatomy, including white matter structure, are largely preserved across
+people~\citep[e.g., ][]{TalaTour88, JahaEtal13, MoriEtal08}. There are several
+possible means of reconciling this apparent inconsistency between dynamic
+person- and task-specific functional networks versus stable anatomical networks.
+For example, relatively small magnitude anatomical differences across people may
+be reflected in reliable functional connectivity differences.  Along these
+lines, one recent study found that diffusion tensor imaging (DTI) structural
+data is similar across people, but may be used to predict person-specific
+resting state functional connectivity data~\citep{BeckEtal18}.  Similarly, other
+work indicates that task-specific functional connectivity may be predicted by
+resting state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.
+Another (potentially complementary) possibility is that our functional networks
+are constrained by anatomy, but nevertheless exhibit (potentially rapid)
+task-dependent changes~\citep[e.g., ][]{SporBetz16}.
 
 Here we have taken a model-based approach to studying whether high
-spatiotemporal resolution activity patterns throughout the human brain
-may be explained by a static connectome model that is shared across
-people and tasks.  Specifically, we trained a model to take in
-recordings from a subset of brain locations, and then predicted
-activity patterns during the same interval, but at \textit{other}
-locations that were held out from the model.  Our model, based on
-Gaussian process regression, was built on three general hypotheses
-about the nature of the correlational structure of neural activity
-(each of which we tested).  First, we hypothesized that functional
-correlations are stable over time and across tasks.  We found that,
-although aspects of the patients' functional correlations were
-stable across tasks, we achieved better reconstruction accuracy when
-we trained the model on within-task data~\citep[we acknowledge that
-our general approach could potentially be extended to better model
-across-task changes, following][and others]{ColeEtal16, TavoEtal16}.
-Second, we hypothesized that some of the correlational structure of
-people's brain activity is similar across individuals.  Consistent
-with this hypothesis, our model explained the data best when we
-trained the correlation model using data from \textit{other}
-patients-- even when compared to a correlation model trained on the
-same patient's data.  Third, we resolved ambiguities in the data by
-hypothesizing that neural activity from nearby sources will tend to be
-similar, all else being equal.  This hypothesis was supported through
-our finding that all of the models we trained that incorporated this
-spatial smoothness assumption predicted held-out data well above chance.
+spatiotemporal resolution activity patterns throughout the human brain may be
+explained by a static connectome model that is shared across people and tasks.
+Specifically, we trained a model to take in recordings from a subset of brain
+locations, and then predicted activity patterns during the same interval, but at
+\textit{other} locations that were held out from the model.  Our model, based on
+Gaussian process regression, was built on three general hypotheses about the
+nature of the correlational structure of neural activity (each of which we
+tested).  First, we hypothesized that functional correlations are stable over
+time and across tasks.  We found that, although aspects of the patients'
+functional correlations were stable across tasks, we achieved better
+reconstruction accuracy when we trained the model on within-task data~\citep[we
+acknowledge that our general approach could potentially be extended to better
+model across-task changes, following][and others]{ColeEtal16, TavoEtal16}.
+Second, we hypothesized that some of the correlational structure of people's
+brain activity is similar across individuals.  Consistent with this hypothesis,
+our model explained the data best when we trained the correlation model using
+data from \textit{other} patients-- even when compared to a correlation model
+trained on the same patient's data.  Third, we resolved ambiguities in the data
+by hypothesizing that neural activity from nearby sources will tend to be
+similar, all else being equal.  This hypothesis was supported through our
+finding that all of the models we trained that incorporated this spatial
+smoothness assumption predicted held-out data well above chance.
 
-One potential limitation of our approach is that it does not provide a
-natural means of estimating the precise timing of single-neuron action
-potentials.  Prior work has shown that gamma band and broadband
-activity in the LFP may be used to estimate the firing rates of
-neurons that underly the population contributing to the
-LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.  Because
-SuperEEG reconstructs LFPs throughout the brain, one could in
-principle use broadband power in the reconstructed signals to
-estimate the corresponding firing rates (though not the timings of
-individual action potentials). Interestingly, our frequency-specific
-analysis yielded the best reconstruction accuracies using broadband
-power.
+One potential limitation of our approach is that it does not provide a natural
+means of estimating the precise timing of single-neuron action potentials.
+Prior work has shown that gamma band and broadband activity in the LFP may be
+used to estimate the firing rates of neurons that underly the population
+contributing to the LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.
+Because SuperEEG reconstructs LFPs throughout the brain, one could in principle
+use broadband power in the reconstructed signals to estimate the corresponding
+firing rates (though not the timings of individual action potentials).
+Interestingly, our frequency-specific analysis yielded the best reconstruction
+accuracies using broadband power.
 
-Beyond providing a means of estimating ongoing activity throughout the
-brain using already implanted electrodes, our work also has
-implications for where to place the electrodes in the first place.
-Electrodes are typically implanted to maximize coverage of suspected
-epileptogenic tissue.  However, our findings suggest that this
-approach could be further optimized.  Specifically, one could leverage
-not only the non-invasive recordings taken during an initial
-monitoring period (as is currently done routinely), but also
-recordings collected from other patients.  We could then ask: given
-what we learn from other patients' data (and potentially from the
-scalp EEG recordings of this new patient), where should we place a
-fixed number of electrodes to maximize our ability to map seizure
-foci?  As shown in Figures~\ref{fig:informap} and~\intersectmap, recordings from
-different locations are differently informative in terms of
-reconstructing the spatiotemporal activity patterns throughout the
-brain.  This property might be leveraged in decisions about where to
-surgically implant electrodes in future patients.
+Beyond providing a means of estimating ongoing activity throughout the brain
+using already implanted electrodes, our work also has implications for where to
+place the electrodes in the first place. Electrodes are typically implanted to
+maximize coverage of suspected epileptogenic tissue.  However, our findings
+suggest that this approach could be further optimized.  Specifically, one could
+leverage not only the non-invasive recordings taken during an initial monitoring
+period (as is currently done routinely), but also recordings collected from
+other patients.  We could then ask: given what we learn from other patients'
+data (and potentially from the scalp EEG recordings of this new patient), where
+should we place a fixed number of electrodes to maximize our ability to map
+seizure foci?  As shown in Figures~\ref{fig:informap} and~\intersectmap,
+recordings from different locations are differently informative in terms of
+reconstructing the spatiotemporal activity patterns throughout the brain.  This
+property might be leveraged in decisions about where to surgically implant
+electrodes in future patients.
 
 \section*{Concluding remarks}
-Over the past several decades, neuroscientists have begun to leverage
-the strikingly profound mathematical structure underlying the brain's
-complexity to infer how our brains carry out computations to support
-our thoughts, actions, and physiological processes.  Whereas
-traditional beamforming techniques rely on geometric
-source-localization of signals measured at the scalp, here we propose
-an alternative approach that leverages the rich correlational
-structure of two large datasets of human intracranial recordings.  In
-doing so, we are one step closer to observing, and perhaps
-someday understanding, the full spatiotemporal structure of human
-neural activity.
+Over the past several decades, neuroscientists
+have begun to leverage the strikingly profound mathematical structure underlying
+the brain's complexity to infer how our brains carry out computations to support
+our thoughts, actions, and physiological processes.  Whereas traditional
+beamforming techniques rely on geometric source-localization of signals measured
+at the scalp, here we propose an alternative approach that leverages the rich
+correlational structure of two large datasets of human intracranial recordings.
+In doing so, we are one step closer to observing, and perhaps someday
+understanding, the full spatiotemporal structure of human neural activity.
 
 \section*{Code availability}
-We have published an open-source toolbox implementing the SuperEEG
-algorithm.  It may be downloaded
-\href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}. Additionally,
-we have provided code for all analyses and figures reported in the
+We have published an open-source toolbox
+implementing the SuperEEG algorithm.  It may be downloaded
+\href{https://supereeg.readthedocs.io/en/latest/}{\underline{here}}.
+Additionally, we have provided code for all analyses and figures reported in the
 current manuscript, available
@@
 \section*{Acknowledgements}
-We are grateful for useful discussions with Luke J. Chang, Uri Hasson,
-Josh Jacobs, Michael J. Kahana, and Matthijs van der Meer.  We are
-also grateful to Michael J. Kahana for generously sharing the ECoG
-data we analyzed in our paper, which was collected under NIMH grant
-MH55687 and DARPA RAM Cooperative Agreement N66001-14-2-4-032, both to
-M.J.K.  Our work was also supported in part by NSF EPSCoR Award Number
-1632738 and by a sub-award of DARPA RAM Cooperative Agreement
-N66001-14-2-4-032 to J.R.M.  The content is solely the responsibility
-of the authors and does not necessarily represent the official views
-of our supporting organizations.
+We are grateful for useful discussions with Luke J.
+Chang, Uri Hasson, Josh Jacobs, Michael J. Kahana, and Matthijs van der Meer.
+We are also grateful to Michael J. Kahana for generously sharing the ECoG data
+we analyzed in our paper, which was collected under NIMH grant MH55687 and DARPA
+RAM Cooperative Agreement N66001-14-2-4-032, both to M.J.K.  Our work was also
+supported in part by NSF EPSCoR Award Number 1632738 and by a sub-award of DARPA
+RAM Cooperative Agreement N66001-14-2-4-032 to J.R.M.  The content is solely the
+responsibility of the authors and does not necessarily represent the official
+views of our supporting organizations.
 
 \section*{Author Contributions}
-J.R.M conceived and initiated the project. L.L.W.O., T.A.M, and
-A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote the
-manuscript.
+J.R.M conceived and initiated the project.
+L.L.W.O., T.A.M, and A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote
+the manuscript.
 
 \section*{Author Information}
-Reprints and permissions information is available at www.nature.com/reprints.
-The authors declare no competing financial interests.
-Readers are welcome to comment on the online version of the paper.
-Publisher's note: Springer Nature remains neutral with regard to jurisdictional claims in published maps and institutional affiliations.
-Correspondence and requests for materials should be addressed to J.R.M.
+Reprints and permissions information is available
+at www.nature.com/reprints.  The authors declare no competing financial
+interests.  Readers are welcome to comment on the online version of the paper.
+Publisher's note: Springer Nature remains neutral with regard to jurisdictional
+claims in published maps and institutional affiliations.  Correspondence and
+requests for materials should be addressed to J.R.M.
 (jeremy.r.manning@dartmouth.edu).

### 2020-02-20 paper/main.tex
did a pass through the discussion

@@
 functional correlations were stable across tasks, we achieved better
-reconstruction accuracy when we trained the model on within-task data~\citep[we
-acknowledge that our general approach could potentially be extended to better
-model across-task changes, following][and others]{ColeEtal16, TavoEtal16}.
+reconstruction accuracy when we trained the model on within-task data.
+This suggests that our general approach could be extended to better
+model across-task changes, following \cite{ColeEtal16, TavoEtal16} and others.
 Second, we hypothesized that some of the correlational structure of people's
@@
 use broadband power in the reconstructed signals to estimate the corresponding
-firing rates (though not the timings of individual action potentials).
-Interestingly, our frequency-specific analysis yielded the best reconstruction
-accuracies using broadband power.
+firing rates (though not the timings of individual action potentials).  We found
+that we were able to reconstruct full-brain patterns of broadband power well (Fig.~\ref{fig:frequency}).
 
 Beyond providing a means of estimating ongoing activity throughout the brain
-using already implanted electrodes, our work also has implications for where to
-place the electrodes in the first place. Electrodes are typically implanted to
-maximize coverage of suspected epileptogenic tissue.  However, our findings
-suggest that this approach could be further optimized.  Specifically, one could
-leverage not only the non-invasive recordings taken during an initial monitoring
-period (as is currently done routinely), but also recordings collected from
-other patients.  We could then ask: given what we learn from other patients'
-data (and potentially from the scalp EEG recordings of this new patient), where
-should we place a fixed number of electrodes to maximize our ability to map
-seizure foci?  As shown in Figures~\ref{fig:informap} and~\intersectmap,
-recordings from different locations are differently informative in terms of
-reconstructing the spatiotemporal activity patterns throughout the brain.  This
-property might be leveraged in decisions about where to surgically implant
-electrodes in future patients.
+using already implanted electrodes, our work also has implications how to
+optimize electrode placements in neurosurgical evaluations. Electrodes are
+typically implanted to maximize coverage of suspected epileptogenic tissue.
+However, our findings suggest that this approach might be improved.
+Specifically, one could leverage not only the non-invasive recordings taken
+during an initial monitoring period (as is currently done routinely), but also
+recordings collected from \textit{other} patients.  We could then ask: given
+what we learn from other patients' data (and potentially from the scalp EEG
+recordings of this new patient), where should we place a fixed number of
+electrodes to maximize our ability to map seizure foci?  As shown in
+Figures~\ref{fig:informap}, \ref{fig:networks}, and~\intersectmap, recordings
+from different regions vary in their ability to predict different narrowband and
+broadband full-brain activity patterns.
+
+By providing a means of reconstructing full-brain activity patterns, the
+SuperEEG approach maps ECoG recordings from different patients into a common
+neural space, despite that different patients' electrodes were implanted in
+different locations. This feature of our approach enables across-patient ECoG
+studies, analogous to across-patient fMRI studies~\citep[e.g.,][]{HaxbEtal01,
+NormEtal06, HaxbEtal11}. Whereas the focus of this manuscript is to specifically
+evaluate which aspects of neural activity patterns SuperEEG recovers well (or
+poorly), in parallel work we are training across-patient classifiers by
+leveraging the common neural spaces obtained by applying SuperEEG to
+multi-patient data.  For example, we have shown that SuperEEG-derived activity
+patterns may be used to accurately predict psychiatric conditions such as
+depression~\citep{ScanEtal20}.  Analogous approaches could in principle be used
+to develop improved brain-computer interfaces and/or to carry out other analyses
+that would benefit from high spatiotemporal resolution full-brain data in
+individuals.
 

### 2020-02-21 paper/main.tex

@@
 across-subject cross-validated reconstruction accuracy tests (analogous to
-Fig.~\ref{fig:corrmaps}) separately for each frequency band
+Fig.~\ref{fig:corrmap}) separately for each frequency band
 (Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis on the
@@
 We also wondered whether the map of information scores might vary as a function
-of the spectral components of the activity patterns under consideration.  For
-example, low frequency $\delta$ activity in the thalamus has been implicated in
-supporting connectivity with cortex~\citep[e.g.,][]{Jone09}. We computed
-analogous maps of information scores for each individual frequency band. Across
-Datasets 1 and 2 (with the exception of $\alpha$ band activity), we observed
-reliable positive correlations between the voxel-by-voxel maps of information
-scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p < 10^{-60}$;
-$\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$; $\gamma_L$:
-$r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$; broadband: $r =
-0.21, p < 10^{-297})$.
+of the spectral components of the activity patterns under consideration.  We
+computed analogous maps of information scores for each individual frequency
+band. Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we
+observed reliable positive correlations between the voxel-by-voxel maps of
+information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p <
+10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$;
+$\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$;
+broadband: $r = 0.21, p < 10^{-297})$.
 
@@
 somatosensory $\gamma_L$ in somatosensory processing and motor
-planning~\citep{AyaEtal03}.  Occipital cortex (purple) was most informative
+planning~\citep{IharEtal03}.  Occipital cortex (purple) was most informative
 about full-brain $\gamma_H$ patterns.  Occipital $\gamma_H$ has also been linked
@@
 inferior parietal cortex precuneus (maroon).  Functional neuroimaging BOLD
-responses~\citep{SimoEtal16} and broadband ECoG patterns~\citep{HoneEtal12} in
+responses~\citep{SimoEtal16} and broadband ECoG patterns~\citep{HoneEtal12a} in
 these default-mode hubs have been implicated in processing context-dependent

### 2020-02-24 paper/main.tex
completed next pass through, updated stats from TM and LLWO

@@
 task-general predictions.  Dataset 2 comprised multi-session recordings from
-4436 electrodes implanted in the brains of 40 epilepsy
+14860 electrodes implanted in the brains of 131 epilepsy
 patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17,
@@
 
-We first applied fourth order Butterworth notch filter to remove 60 Hz ($\pm$ .5
-Hz) line noise from every recording (from every electrode). Next, we downsampled
-the recordings (regardless of the original sample rate) to 250 Hz.  (This
-downsampling step served to both normalize for differences in sampling rates
-across patients and to ease the computational burden of our subsequent
-analyses.)  We then excluded any electrodes that showed putative epileptiform
+We first applied fourth order Butterworth notch filters to remove 60 Hz ($\pm$
+.5 Hz) line noise from every recording (from every electrode). Next, we
+downsampled the recordings (regardless of the original sample rate) to 250 Hz.
+This downsampling step served to both normalize for differences in sampling
+rates across patients and to ease the computational burden of our subsequent
+analyses.  We then excluded any electrodes that showed putative epileptiform
 activity. Specifically, we excluded from further analysis any electrode that
@@
 can become computationally intractable when $T$ is very large (e.g., an example
-patient in Dataset 1, $T = 12,786,750$; also see Fig.~\suppstats, Panels E and
+patient in Dataset 1, $T = 51147$; also see Fig.~\suppstats, Panels E and
 K). However, because Equation~\ref{eqn:reconstruction} is time invariant, we may
@@
 \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/corrmap}
-  \caption{\textbf{Reconstruction quality across all electrodes in two
-      ECoG datasets.}  \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Dataset 1.}  The across-patient distribution (black) reflects
-    reconstruction accuracy (correlation) using a correlation model
-    learned from all but one patient's data, and then applied to that
-    held-out patient's data.  The within-patient distribution (gray)
-    reflects performance using a correlation model learned from the same
-    patient who contributed the to-be-reconstructed electrode.
-    \textbf{B. Distributions of correlations for Dataset 2.}  This
-    panel is in the same format as Panel A, but reflects results
-    obtained from Dataset 2.  The histograms aggregate data across
-    both Dataset 2 experiments; for results broken down by experiment
-    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
-      performance by location.} The colors denote the average across-session
-    correlation, using the across-patient correlation model, between
-    the observed and reconstructed activity at the given electrode
-    location projected to the cortical surface~\citep{CombEtal19}.}
-  \label{fig:corrmap}
+  \centering \includegraphics[width=\textwidth]{figs/corrmap}
+  \caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
+  datasets.}  \textbf{A. Distributions of correlations between observed versus
+  reconstructed activity by electrode, for Dataset 1.}  The across-patient
+  distribution (black) reflects reconstruction accuracy (correlation) using a
+  correlation model learned from all but one patient's data, and then applied to
+  that held-out patient's data.  The within-patient distribution (gray) reflects
+  performance using a correlation model learned from the same patient who
+  contributed the to-be-reconstructed electrode. \textbf{B. Distributions of
+  correlations for Dataset 2.}  This panel is in the same format as Panel A, but
+  reflects results obtained from Dataset 2.  The histograms aggregate data
+  across both Dataset 2 experiments; for results broken down by experiment see
+  Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction accuracy by
+  location.} The colors denote the average across-session correlations, using
+  the across-patient correlation model, between the observed and reconstructed
+  activity at the given electrode location projected to the cortical
+  surface~\citep{CombEtal19}.  Panel C displays the map for Dataset 1 and Panel
+  D displays the map for Dataset 2.} \label{fig:corrmap}
 \end{figure}
@@
 Although both datasets we examined provide good full-brain coverage (when
-considering data from every patient; e.g.\ Fig.~\ref{fig:corrmap}C, D),
-electrodes were not sampled uniformly throughout the brain.  For example,
-electrodes are more likely to be implanted in regions like the medial temporal
-lobe (MTL), and are rarely implanted in occipital cortex
-(Fig.~\ref{fig:density}A, B). Separately for each dataset, for each voxel in the
-4~mm$^3$ voxel MNI152 brain, we computed the proportion of electrodes in the
-dataset that were contained within a 20 MNI unit radius sphere centered on that
-voxel.  We defined the \textit{density} at that location as this proportion.
-Across Datasets 1 and 2, the electrode placement densities were similar
-(correlation by voxel: $r = 0.6, p < 10^{-10}$).  We wondered whether regions
-with good covererage might be associated with better reconstruction accuracy.
-For example, Figures~\ref{fig:corrmap}C and D indicate that many electrodes in
-the MTL (which tends to be relatively densely sampled) have relatively high
-reconstruction accuracy, and occipital electrodes (which tends to be relatively
-sparsely sampled) tend to have relatively low reconstruction accuracy.  To test
-whether this held more generally across the entire brain, for each dataset we
-computed the electrode placement density for each electrode from each patient
-(using the proportion of \textit{other} patients' electrodes within 20 MNI units
-of the given electrode).  We then correlated these density values with the
-across-patient reconstruction accuracies for eachg electrode.  We found a
-statistically reliable negative correlation between reconstruction accuracy and
-density for Dataset 1, but no reliable correlation for Dataset 2 (Dataset 1: $r
-= -0.21, p = 0.05$; Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
-reconstruction accuracies we observed are \textit{not} driven solely by sampling
-density, but rather may also reflect higher order properties of neural dynamics
-such as functional correlations between distant voxels~\citep{BetzEtal17b}.
+considering data from every patient), electrodes were not sampled uniformly
+throughout the brain.  For example, electrodes are more likely to be implanted
+in regions like the medial temporal lobe (MTL), and are rarely implanted in
+occipital cortex (Fig.~\ref{fig:density}A, B). Separately for each dataset, for
+each voxel in the 4~mm$^3$ voxel MNI152 brain, we computed the proportion of
+electrodes in the dataset that were contained within a 20 MNI unit radius sphere
+centered on that voxel.  We defined the \textit{density} at that location as
+this proportion. Across Datasets 1 and 2, the electrode placement densities were
+similar (correlation by voxel: $r = 0.6, p < 10^{-10}$).  We wondered whether
+regions with good covererage might be associated with better reconstruction
+accuracy. For example, Figures~\ref{fig:density}A and B indicate that many
+electrodes in the MTL (which tends to be relatively densely sampled) have
+relatively high reconstruction accuracy, and occipital electrodes (which tends
+to be relatively sparsely sampled) tend to have relatively low reconstruction
+accuracy.  To test whether this held more generally across the entire brain, for
+each dataset we computed the electrode placement density for each electrode from
+each patient (using the proportion of \textit{other} patients' electrodes within
+20 MNI units of the given electrode).  We then correlated these density values
+with the across-patient reconstruction accuracies for each electrode.  We found
+no reliable correlation between reconstruction accuracy and density for Dataset
+1 ($r = 0.05, p = 0.70$) and a reliable negative correlation for Dataset 2 ($r =
+-0.21, p = 0.05$).  This indicates that the reconstruction accuracies we
+observed are \textit{not} driven solely by sampling density, but rather may also
+reflect higher order properties of neural dynamics such as functional
+correlations between distant voxels~\citep{BetzEtal17b}.
 
@@
 $\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of
-broadband power~\citep[defined as the mean height of a linear robust regression
-fit in log-log space to the order 4 Morelet wavelet-computed power spectrum at
-50 log-spaced frequencies from from 2--100 Hz;][]{MannEtal09}.  We used
-second-order Butterworth bandpass filters to compute the activity patterns
-within each narrow frequency band.  We then repeated our within-subject and
-across-subject cross-validated reconstruction accuracy tests (analogous to
-Fig.~\ref{fig:corrmap}) separately for each frequency band
-(Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis on the
-Hilbert transform-computed spectral power within each narrow band; see
-Fig.~\freqpower.)  Across both datasets, we found that our approach is best at
-reconstructing patterns of broadband activity (right-most bars in
+broadband power.  We defined broadband power as the mean height of a linear
+robust regression fit in log-log space to the order 4 Morelet wavelet-computed
+power spectrum at 50 log-spaced frequencies from from 2--100
+Hz~\citep{MannEtal09}. We used second-order Butterworth bandpass filters to
+compute the activity patterns within each narrow frequency band.  We then
+repeated our within-subject and across-subject cross-validated reconstruction
+accuracy tests (analogous to Fig.~\ref{fig:corrmap}) separately for each
+frequency band (Fig.~\ref{fig:frequency}).  (We also carried out a similar
+analysis on the Hilbert transform-computed spectral power within each narrow
+band; see Fig.~\freqpower.)  Across both datasets, we found that our approach is
+best at reconstructing patterns of broadband activity (right-most bars in
 Figs.~\ref{fig:frequency}A and D), a correlate of population firing
@@
 \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/frequency}
-  \caption{\textbf{Reconstruction quality across all electrodes in two
-      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      each frequency band in Dataset 1.}  The across-patient
-    distribution (left jitter barplot) reflects
-    reconstruction accuracy (correlation) using a correlation model
-    learned from all but one patient's data, and then applied to that
-    held-out patient's data.  The within-patient distribution (right
-    jitter barplot in lighter color)
-    reflects performance using a correlation model learned from the same
-    patient who contributed the to-be-reconstructed electrode, colored
-    by frequency and includes the raw voltages displayed in
-    Fig.~\ref{fig:corrmap}A in gray.
-    \textbf{B.~Statistical summary of across-patient reconstruction
-      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
-    map, warmer colors (positive t-values) indicate that the
-    distribution of
-    reconstruction accuracy for the frequency band in a given row
-    yielded was greater than the frequency band in the given
-    column. Cooler colors (negative t-values) indicate that the
-    frequency band in the given row yielded lower reconstruction
-    accuracy than the frequency band in the given column. The lower
-    triangles of each map denote the corresponding p-values for the
-    t-tests. The diagonal entries display the average
-    reconstruction accuracy given to each frequency
-    band. \textbf{C.~Statistical summary of within-patient reconstruction
-      quality by electrode for each frequency band in Dataset 1.}
-    This panel displays the within-patient statistical summary,
-    in the same format as Panel B.  \textbf{D.~Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      each frequency band in Dataset 2.}  This panel displays
-    reconstruction accuracy distributions for each frequency band for
-    Dataset 2. \textbf{E.~Statistical summary of
-      across-patient reconstruction quality by electrode for each
-      frequency band in Dataset 2.} This is the same format as Panel
-    B for Dataset 2. \textbf{F.~Statistical summary of
-      within-patient reconstruction quality by electrode for each
-      frequency band in Dataset 2.}This is the same format as Panel
-    C for Dataset 2.}
-  \label{fig:frequency}
+  \centering \includegraphics[width=\textwidth]{figs/frequency}
+  \caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
+  datasets for each frequency triangles.} \textbf{A. Distributions of
+  correlations between observed versus reconstructed activity by electrode, for
+  each frequency band in Dataset 1.}  Each color denotes a different frequency
+  range. Within each color group, the darker dots and bar on the left display
+  the distribution (and mean) across-patient reconstruction accuracies
+  (analogous to the black histograms in Fig.~\ref{fig:corrmap}).  The lighter
+  dots and bar on the right display the distribution (and mean) within-patient
+  reconstruction accuracies (analogous to the gray histograms in
+  Fig.~\ref{fig:corrmap}). To facilitate visual comparison with the
+  frequency-specific results, the leftmost bars (gray) re-plot the histograms in
+  Fig.~\ref{fig:corrmap}A. \textbf{B.~Statistical summary of across-patient
+  reconstruction accuracy by electrode for each frequency band in Dataset 1.} In
+  the upper triangles of each map, warmer colors (positive $t$-values) indicate
+  that the distribution of reconstruction accuracy for the frequency band in a
+  given row yielded was greater than the frequency band in the given column.
+  Cooler colors (negative $t$-values) indicate that the frequency band in the
+  given row yielded lower reconstruction accuracy than the frequency band in the
+  given column. The lower triangles of each map denote the corresponding
+  $p$-values for the $t$-tests. The diagonal entries display the average
+  reconstruction accuracy within each frequency band. \textbf{C.~Statistical
+  summary of within-patient reconstruction accuracy by electrode for each
+  frequency band in Dataset 1.} This panel displays the within-patient
+  statistical summary, in the same format as Panel B.  \textbf{D.~Distributions
+  of correlations between observed versus reconstructed activity by electrode,
+  for each frequency band in Dataset 2.}  This panel displays reconstruction
+  accuracy distributions for each frequency range for Dataset 2.
+  \textbf{E.--F.~Statistical summaries of across-patient and within-patient
+  reconstruction accuracy by electrode for each frequency band in Dataset 2.}
+  These panels are in the same as Panels B and C, but display results from
+  Dataset 2.} \label{fig:frequency}
 \end{figure}
@@
 \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/density}
-  \caption{\textbf{Electrode sampling density by location.}
-    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
-    voxel is colored by the proportion of total electrodes in the
-    dataset that are
-    located within a 20~MNI unit radius sphere centered on the given
-    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
-      2.}  This panel displays the sampling density map for Dataset 2,
-    in the same format as Panel A.  \textbf{C.~Correspondence in
-      sampling density by voxel across Datasets 1 and 2.}  The
-    two-dimensional histogram displays the by-voxel densities in the
-    two Datasets, and the one-dimensional histograms display the
-    proportions of voxels in each dataset with the given density
-    value.  The correlation reported in the panel is across voxels in
-    the 4~mm$^3$ MNI brain.}
-  \label{fig:density}
+  \centering \includegraphics[width=\textwidth]{figs/density}
+  \caption{\textbf{Electrode sampling density by location.} \textbf{A.~Electrode
+  sampling density by voxel location in Dataset 1.} Each voxel is colored by the
+  proportion of total electrodes in the dataset that are located within a 20~MNI
+  unit radius sphere centered on the given voxel.  \textbf{B.~Electrode sampling
+  density by voxel location in Dataset 2.}  This panel displays the sampling
+  density map for Dataset 2, in the same format as Panel A.
+  \textbf{C.~Correspondence in sampling density by voxel location across
+  Datasets 1 and 2.}  The two-dimensional histogram displays the per-voxel
+  sampling densities in the two Datasets, and the one-dimensional histograms
+  display the proportions of voxels in each dataset with the given density
+  value.  The correlation reported in the panel is across voxels in the 4~mm$^3$
+  MNI152 brain.} \label{fig:density}
 \end{figure}
@@
 throughout the brain are meaningfully correlated, are there particular
-implantation locations that, if present in a patient's brain, yield especially
-high reconstruction accuracies throughout the rest of the brain?  For example,
-one might hypothesize that brain structures that are heavily interconnected with
-many other structures could be more informative about full-brain activity
-patterns than comparatively isolated structures.  To test this hypothesis, we
-computed the average reconstruction accuracy across all of each patient's
-electrodes (using our across-patients cross validation test; black histograms in
-Fig.~\ref{fig:corrmap}A and B).  We first labeled each patient's electrodes, in
-each dataset, with the average reconstruction accuracy for that patient.  In
-other words, we assigned every electrode from each patient the same value,
-reflecting how well the activity patterns for that patient were reconstructed.
-Next, for each voxel in the 4~mm$^3$ MNI brain, we computed the average value
-across any electrode (from any patient) that came within 20 MNI units of that
-voxel's center.  This yielded an \textit{information score} for each voxel,
-reflecting the average reconstruction accuracy across any patients with
-electrodes near each voxel-- where the averages were weighted to reflect
+implantation locations that, recorded from in a given patient's brain, yield
+especially high reconstruction accuracies throughout the rest of their brain?
+For example, one might hypothesize that brain structures that are heavily
+interconnected with many other structures could be more informative about
+full-brain activity patterns than comparatively isolated structures.  To test
+this hypothesis, we computed the average reconstruction accuracy across all of
+each patient's electrodes (using our across-patients cross validation test;
+black histograms in Fig.~\ref{fig:corrmap}A and B).  We first labeled each
+patient's electrodes, in each dataset, with the average reconstruction accuracy
+for that patient.  In other words, we assigned every electrode from each patient
+the same value, reflecting how well the activity patterns for that patient were
+reconstructed. Next, for each voxel in the 4~mm$^3$ MNI brain, we computed the
+average value across any electrode (from any patient) that came within 20 MNI
+units of that voxel's center.  This yielded an \textit{information score} for
+each voxel, reflecting the average reconstruction accuracy across any patients
+with electrodes near each voxel-- where the averages were weighted to reflect
 patients who had more electrodes implanted near that location. We created a
@@
 the two datasets, we nonetheless found that the maps of the most promising
-implantation targets derived from both datasets were similar (voxelwise
+implantation targets derived from both datasets were correlated (voxel-wise
 correlation between information scores across the two datasets: $r = 0.18, p <
-10^{-10}$).  While the correspondence between the two maps was imperfect, our
-finding that there were some commonalities between the two maps lends support to
-the notion that different brain areas are differently informative about
-full-brain activity patterns.  We also examined the intersection between the top
-10\% most informative voxels across the two datasets (gray areas in
-Fig.~\ref{fig:informap}C, networks shown in Fig.~\ref{fig:networks}A (All)).
-Supporting the notion that structures that are highly interconnected with the
-rest of the brain might be especially good targets for implantation, this
-intersecting set of voxels with the highest information scores included major
-portions of the dorsal attention network (e.g., inferior parietal lobule,
-precuneus, inferior temporal gyrus, thalamus, and striatum) as well as some
-portions of the default mode network (e.g., angular gyrus) that are highly
-interconnected with a large proportion of the brain's gray matter~\citep[e.g.,
-][]{TomaVolk11}.
+10^{-10}$).  Our finding that there were some commonalities between the two
+datasets' maps lends support to the notion that different brain areas are
+(reliably) differently informative about full-brain activity patterns.  We also
+examined the intersection between the top 10\% most informative voxels across
+the two datasets (gray areas in Fig.~\ref{fig:informap}C, networks shown in
+Fig.~\ref{fig:networks}A, top row). Supporting the notion that structures that
+are highly interconnected with the rest of the brain are most informative about
+full-brain activity patterns, the intersecting set of voxels with the highest
+information scores included major portions of the dorsal attention network
+(e.g., inferior parietal lobule, precuneus, inferior temporal gyrus, thalamus,
+and striatum) as well as some portions of the default mode network (e.g.,
+angular gyrus) that are highly interconnected with a large proportion of the
+brain's gray matter~\citep[e.g.,][]{TomaVolk11}.
 
 \begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/informap}
-  \caption{\textbf{Most informative electrode locations.}
-    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
-    reflect the weighted average reconstruction accuracy across all
-    electrodes from any patients with at least one electrode within 20
-    MNI units of the given voxel.  \textbf{B. Dataset 2 information
-      score by voxel.}  This panel is in the same format as Panel A.
-    In both panels the contours indicate the intersections between the
-    top 10\% most informative voxels in each map (also see
-    Fig.~\networks Panels A.-C. All for networks within this region).  \textbf{C. Intersection.}
-    Gray areas indicate the intersections between the
-    top 10\% most informative voxels in each map and projected onto the cortical surface~\citep{CombEtal19}. \textbf{D. Correspondence in information
-      scores by voxel across Datasets 1 and 2.}  Same format as
-    Figure~\ref{fig:density}C.}
+  \centering \includegraphics[width=\textwidth]{figs/informap}
+  \caption{\textbf{Most informative recording locations.} \textbf{A. Dataset 1
+  information scores by voxel.} The voxel colors reflect the weighted average
+  reconstruction accuracy across all electrodes from any patients with at least
+  one electrode within 20 MNI units of the given voxel.  \textbf{B. Dataset 2
+  information scores by voxel.}  This panel is in the same format as Panel A.
+  \textbf{C. Intersection.} Gray areas indicate the intersections between the
+  top 10\% most informative voxels in each map and projected onto the cortical
+  surface~\citep{CombEtal19}. \textbf{D. Correspondence in information scores by
+  voxel across Datasets 1 and 2.}  The correlation reported in the Panel is
+  between the per-voxel information scores across Datasets 1 and 2.}
   \label{fig:informap}
@@
 computed analogous maps of information scores for each individual frequency
-band. Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we
-observed reliable positive correlations between the voxel-by-voxel maps of
+range. Across Datasets 1 and 2 (with the exception of $\alpha$ band activity),
+we observed reliable positive correlations between the voxel-by-voxel maps of
 information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p <
@@
 Fig.~\ref{fig:informap}C). This yielded a single map of the (reliably) most
-informative locations for each frequency range we examined. We then carried out
-two \textit{post hoc} analyses on each of these maps to better characterize the
+informative locations, for each frequency range we examined. We then carried out
+\textit{post hoc} analyses on each of these maps to better characterize the
 underlying structural and functional properties of each set of regions we
@@
 well-cited seven-network parcellation map identified by \cite{YeoEtal11} onto
-the maps of brain locations that were most informative about each neural
+the maps of brain locations that were most informative about each type of neural
 pattern.  For each of these information maps, we computed the proportion of
@@
 to (Fig.~\ref{fig:networks}A, B).
+
+\begin{figure}
+  \centering \includegraphics[width=\textwidth]{figs/networks}
+  \caption{\textbf{Most informative recording locations by frequency range.}
+  \textbf{A.~Intersections between information score maps by frequency range.}
+  The regions indicated in each row depict the intersection between the top 10\%
+  most informative locations across Datasets 1 and 2.  \textbf{B.~Network
+  memberships of the most informative brain regions.}  The pie charts display
+  the proportions of voxels in each region that belong to the seven networks
+  identified by \cite{YeoEtal11}.  The relative sizes of the charts for each
+  frequency range reflct the average across-subject reconstruction accuracies
+  (Fig.~\ref{fig:corrmap}A, D).  The voxels in Panel A are colored according to
+  the same network memberships.  \textbf{C.~Neurosynth terms associated with the
+  most informative brain regions, by frequency range.}  The lists in each row
+  display the top five neurosynth terms~\citep{RubiEtal17} decoded for each
+  region.  \textbf{D.~Network parcellation map and legend.}  The parcellation
+  defined by \cite{YeoEtal11} is displayed on the inflated brain maps.  The
+  colors and network labels serve as a legend for Panels A and B.
+  \textbf{E.~Combined map of the most informative brain regions.}  The map
+  displays the union of the most informative maps in Panel A, colored by
+  frequency range.  The labels also serve as a legend for Panel C.}
+  \label{fig:networks}
+\end{figure}
 
@@
 cortex~\citep[e.g.,][]{AmziSter98}.  The brain areas most predictive of
-full-brain $\theta$ patterns were occipital and parietal regions traditionally
-linked with visual processing and visual attention (light green). Prior work has
-implicated $\theta$ oscillations in these areas in periodic sampling of visual
+full-brain $\theta$ patterns were occipital and parietal regions associated with
+visual processing and visual attention (light green). Prior work has implicated
+$\theta$ oscillations in these areas in periodic sampling of visual
 attention~\citep[e.g.,][]{BuscVanR10}.  We found that full-brain $\alpha$
@@
 
-Taken together, the frequency-specific information maps suggest potential new
+Taken together, the frequency-specific information maps suggest a potential new
 interpretation of many of the above previously reported findings.  Prior work
 has largely treated region-specific narrowband and broadband activity as an
-indictor that activity at those frequency ranges reflect that the given region
+indictor that activity at those frequency ranges reflects that the given region
 is representing or supporting a particular function.  Our work suggests the
 alternative interpretation that when we observe a particular neural pattern in a
-particular brain region, it may instead reflect how that region is is transmitting
-information to the rest of the brain via patterns at the given frequency range.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{figs/networks}
-  \caption{\textbf{Most informative electrode locations by frequency
-      and the networks involved.}
-    \textbf{A.~Intersections across datasets for each frequency.} The
-    inflated brain plots display the intersections between the
-    top 10\% most informative voxels were calculated as described in Fig.~\ref{fig:informap}
-    for each frequency and projected onto the cortical surface~\citep{CombEtal19}. Intersecting voxels are colored according to the 7 networks
-    from~\citep{YeoEtal11}.
-    \textbf{B.~Proportion of networks in most informative electrode locations by
-    frequency.}  Pie graphs display the proportion of the 7 networks
-  ~\citep{YeoEtal11} in the most informative locations by
-  frequency, and are sized relative to the average reconstruction
-  accuracy for each frequency. \textbf{C.~Terms associated with most informative
-    electrode locations.}  The
-    lists of terms display the top five Neurosynth
-    terms~\citep{RubiEtal17} decoded from the corresponding brain
-    maps, and colored according the frequency (see Panel
-    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
-    Seven network parcellation as described
-    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
-      frequency.} The inflated brain plot displays the locations of
-    the most informative locations (Panel A), colored by frequency,
-    and projected onto the cortical surface~\citep{CombEtal19}.}
-  \label{fig:networks}
-\end{figure}
+particular brain region, it may instead reflect how that region is is
+transmitting information to the rest of the brain via signalling at the given
+frequency range.
 
@@
 functional correlations were stable across tasks, we achieved better
-reconstruction accuracy when we trained the model on within-task data.
-This suggests that our general approach could be extended to better
-model across-task changes, following \cite{ColeEtal16, TavoEtal16} and others.
-Second, we hypothesized that some of the correlational structure of people's
-brain activity is similar across individuals.  Consistent with this hypothesis,
-our model explained the data best when we trained the correlation model using
-data from \textit{other} patients-- even when compared to a correlation model
-trained on the same patient's data.  Third, we resolved ambiguities in the data
-by hypothesizing that neural activity from nearby sources will tend to be
-similar, all else being equal.  This hypothesis was supported through our
-finding that all of the models we trained that incorporated this spatial
-smoothness assumption predicted held-out data well above chance.
+reconstruction accuracy when we trained the model on within-task data. This
+suggests that our general approach could be extended to better model across-task
+changes, e.g., following \cite{ColeEtal16, TavoEtal16}; and others. Second, we
+hypothesized that some of the correlational structure of people's brain activity
+is similar across individuals.  Consistent with this hypothesis, our model
+explained the data best when we trained the correlation model using data from
+\textit{other} patients-- even when compared to a correlation model trained on
+the same patient's data.  Third, we resolved ambiguities in the data by
+hypothesizing that neural activity from nearby sources will tend to be similar,
+all else being equal.  This hypothesis was supported through our finding that
+all of the models we trained that incorporated this spatial smoothness
+assumption predicted held-out data well above chance.
 
 One potential limitation of our approach is that it does not provide a natural
-means of estimating the precise timing of single-neuron action potentials.
-Prior work has shown that gamma band and broadband activity in the LFP may be
-used to estimate the firing rates of neurons that underly the population
-contributing to the LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}.
-Because SuperEEG reconstructs LFPs throughout the brain, one could in principle
-use broadband power in the reconstructed signals to estimate the corresponding
+means of estimating the precise timing of single-neuron action potentials. Prior
+work has shown that gamma band and broadband activity in the LFP may be used to
+estimate the firing rates of neurons that underly the population contributing to
+the LFP~\citep{MillEtal08, MannEtal09, JacoEtal10b, CronEtal11}. Because
+SuperEEG reconstructs LFPs throughout the brain, one could in principle use
+broadband power in the reconstructed signals to estimate the corresponding
 firing rates (though not the timings of individual action potentials).  We found
-that we were able to reconstruct full-brain patterns of broadband power well (Fig.~\ref{fig:frequency}).
+that we were able to reconstruct full-brain patterns of broadband power well
+(Fig.~\ref{fig:frequency}).
 
@@
 typically implanted to maximize coverage of suspected epileptogenic tissue.
-However, our findings suggest that this approach might be improved.
+However, our findings suggest that this approach might be improved upon.
 Specifically, one could leverage not only the non-invasive recordings taken
@@
 electrodes to maximize our ability to map seizure foci?  As shown in
-Figures~\ref{fig:informap}, \ref{fig:networks}, and~\intersectmap, recordings
-from different regions vary in their ability to predict different narrowband and
-broadband full-brain activity patterns.
+Figures~\ref{fig:informap}, \ref{fig:networks}, and~\networkpower, recordings
+from different regions vary with respect to how informative they are about
+different narrowband and broadband full-brain activity patterns.
 
@@
 leveraging the common neural spaces obtained by applying SuperEEG to
-multi-patient data.  For example, we have shown that SuperEEG-derived activity
-patterns may be used to accurately predict psychiatric conditions such as
-depression~\citep{ScanEtal20}.  Analogous approaches could in principle be used
-to develop improved brain-computer interfaces and/or to carry out other analyses
-that would benefit from high spatiotemporal resolution full-brain data in
-individuals.
+multi-patient ECoG data.  For example, we have shown that SuperEEG-derived
+activity patterns may be used to accurately predict psychiatric conditions such
+as depression~\citep{ScanEtal20}.  Analogous approaches could in principle be
+used to develop improved brain-computer interfaces and/or to carry out other
+analyses that would benefit from high spatiotemporal resolution full-brain data
+in individuals.
 
@@
 \section*{Data availability}
-The dataset analyzed in this study was generously shared by Michael
+The datasets analyzed in this study were generously shared by Michael
 J. Kahana.  A portion of Dataset 1 may be downloaded
@@
 
-\section*{Author Contributions}
-J.R.M conceived and initiated the project.
-L.L.W.O., T.A.M, and A.C.H. performed the analyses. J.R.M. and L.L.W.O. wrote
-the manuscript.
+\section*{Author Contributions} J.R.M conceived and initiated the project.
+L.L.W.O., T.A.M, and A.C.H. performed the analyses using software packages that
+all authors contributed to. J.R.M. and L.L.W.O. wrote the manuscript with input
+from all other authors.
 

### 2020-03-09 paper/main.tex
next round of JRM edits

@@
 
-\title{A Gaussian process model of human electrocorticographic data}
+\title{A Gaussian process model of human e\-lect\-ro\-cort\-i\-co\-graph\-ic data}
 \author{
@@
 two obstacles.  First, the inverse problem beamforming seeks to solve
-has infinitely many solutions.  Researchers have made traction towards
+has infinitely many solutions.  Researchers have made progress towards
 constraining the solution space by assuming that signal-generating
@@
 in his popular science fiction novel \textit{The Terminal
-Experiment}~\cite{Sawy95}.  SuperEEG is a fictional technology that measures
-ongoing neural activity throughout the entire living human brain with perfect
-precision and at arbitrarily high spatiotemporal resolution.}, based on Gaussian
-process regression~\citep{Rasm06}.  SuperEEG entails using data from multiple
-people to estimate activity patterns at arbitrary locations in each person's
-brain (i.e., independent of their electrode placements).  We test our SuperEEG
-approach using two large datasets of intracranial recordings~\citep{SedeEtal03,
-SedeEtal07a, SedeEtal07b, MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17,
-KragEtal17, KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18,
-KuceEtal18}.  We show that the SuperEEG algorithm recovers signals well from
-electrodes that were held out of the training dataset.  We also examine the
-factors that influence how accurately activity may be estimated (recovered),
-which may have implications for electrode design and placement in neurosurgical
-applications.
+Experiment}~\citep{Sawy95}.  SuperEEG is a fictional technology that measures
+ongoing neural activity throughout the entire living human brain at arbitrarily
+high spatiotemporal resolution.}, based on Gaussian process
+regression~\citep{Rasm06}.  SuperEEG entails using data from multiple people to
+estimate activity patterns at arbitrary locations in each person's brain (i.e.,
+independent of their electrode placements).  We test our SuperEEG approach using
+two large datasets of intracranial recordings~\citep{SedeEtal03, SedeEtal07a,
+SedeEtal07b, MannEtal11, MannEtal12, EzzyEtal17, HoraEtal17, KragEtal17,
+KuceEtal17, LinEtal17, SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  We show
+that the SuperEEG algorithm recovers signals well from electrodes that were held
+out of the training dataset.  We also examine the factors that influence how
+accurately activity may be estimated (recovered), which may have implications
+for electrode design and placement in neurosurgical applications.
 
-\section*{Approach} The SuperEEG approach to inferring high temporal resolution
-full-brain activity patterns is outlined and summarized in
-Figure~\ref{fig:methods}. We describe (in this section) and evaluate (in
-\textit{Results}) our approach using a two large previously collected datasets
-comprising multi-session intracranial recordings. Dataset 1 comprises
-multi-session recordings taken from 6876 electrodes implanted in the brains of
-88 epilepsy patients~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
-MannEtal12}.  Each recording session lasted from 0.2--3~h (total recording time:
-0.3--14.2~h; Fig.~\suppstats E).  During each recording session, the patients
-participated in a free recall list learning task, which lasted for up to
-approximately 1~h.  In addition, the recordings included ``buffer'' time (the
-length varied by patient) before and after each experimental session, during
-which the patients went about their regular hospital activities (confined to
-their hospital room, and primarily in bed).  These additional activities
-included interactions with medical staff and family, watching television,
-reading, and other similar activities.  For the purposes of the Dataset 1
-analyses presented here, we aggregated all data across each recording session,
-including recordings taken during the main experimental task as well as during
-non-experimental time.  We used Dataset 1 to develop our main SuperEEG approach,
-and to examine the extent to which SuperEEG might be able to generate
-task-general predictions.  Dataset 2 comprised multi-session recordings from
-14860 electrodes implanted in the brains of 131 epilepsy
+\section*{Approach}
+
+The SuperEEG approach to inferring high temporal resolution full-brain activity
+patterns is outlined and summarized in Figure~\ref{fig:methods}. We describe (in
+this section) and evaluate (in \textit{Results}) our approach using two large
+previously collected datasets comprising multi-session intracranial recordings.
+Dataset 1 comprises multi-session recordings taken from 6876 electrodes
+implanted in the brains of 88 epilepsy patients~\citep{SedeEtal03, SedeEtal07a,
+SedeEtal07b, MannEtal11, MannEtal12}.  Each recording session lasted from
+0.2--3~h (total recording time: 0.3--14.2~h; Fig.~\suppstats E).  During each
+recording session, the patients participated in a free recall list learning
+task, which lasted for up to approximately 1~h.  In addition, the recordings
+included ``buffer'' time (the length varied by patient) before and after each
+experimental session, during which the patients went about their regular
+hospital activities (confined to their hospital room, and primarily in bed).
+These additional activities included interactions with medical staff and family,
+watching television, reading, and other similar activities.  For the purposes of
+the Dataset 1 analyses presented here, we aggregated all data across each
+recording session, including recordings taken during the main experimental task
+as well as during non-experimental time.  We used Dataset 1 to develop our main
+SuperEEG approach, and to examine the extent to which SuperEEG might be able to
+generate task-general predictions.  Dataset 2 comprised multi-session recordings
+from 14860 electrodes implanted in the brains of 131 epilepsy
 patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17,
@@
   dots in Panel A, defined as $\bar{R}$ in the text).  The weights fall off with
-  positional distance (in MNI space) according to an RBF. \textbf{C.~Per-patient
+  positional distance~\citep[in MNI152 space;][]{LyttEtal07} according to an RBF. \textbf{C.~Per-patient
   correlation matrices.}  After computing the pairwise correlations between the
@@
 .5 Hz) line noise from every recording (from every electrode). Next, we
-downsampled the recordings (regardless of the original sample rate) to 250 Hz.
+downsampled the recordings (regardless of the original samplerate) to 250 Hz.
 This downsampling step served to both normalize for differences in sampling
@@
 Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$ matrix, which
-can become computationally intractable when $T$ is very large (e.g., an example
-patient in Dataset 1, $T = 51147$; also see Fig.~\suppstats, Panels E and
-K). However, because Equation~\ref{eqn:reconstruction} is time invariant, we may
-compute $Y_{s,k,\beta_s}$ in a piecewise manner by filling in $Y_{s,k,\beta_s}$
-one row at a time (using the corresponding samples from $Y_{s, k, \alpha_s}$).
+can become computationally expensive when $T$ is very large (e.g., for the
+Dataset 1 patient with the longest recording time, $T = 12,786,750$; also see
+Fig.~\suppstats, Panels E and K). However, because
+Equation~\ref{eqn:reconstruction} is time invariant, we may compute
+$Y_{s,k,\beta_s}$ in a piecewise manner by filling in $Y_{s,k,\beta_s}$ one row
+at a time (using the corresponding samples from $Y_{s, k, \alpha_s}$).
 
@@
 Fig.~\ref{fig:corrmap}C).  The observed distribution of correlations was
-centered well above zero (mean: 0.51; $t$-test comparing mean of distribution of
+centered well above zero (mean: $r = 0.51$; $t$-test comparing mean of distribution of
 $z$-transformed average patient correlation coefficients to 0: $t(66) = 23.55, p
@@
 Figure~\ref{fig:corrmap}A (gray histogram), the distribution of within-patient
-correlations was centered well above zero (mean: 0.32; $t$-test comparing mean
-of distribution of $z$-transformed average patient correlation coefficients to
-0: $t(66) = 15.16, p < 10^{-10}$). However, the across-patient correlations were
-substantially higher ($t$-test comparing average $z$-transformed within versus
-across patient electrode correlations: $t(66) = 9.17, p < 10^{-10}$).  This is
-an especially conservative test, given that the across-patient SuperEEG
+correlations was centered well above zero (mean: $r = 0.32$; $t$-test comparing
+mean of distribution of $z$-transformed average patient correlation coefficients
+to 0: $t(66) = 15.16, p < 10^{-10}$). However, the across-patient correlations
+were substantially higher ($t$-test comparing average $z$-transformed within
+versus across patient electrode correlations: $t(66) = 9.17, p < 10^{-10}$).
+This is an especially conservative test, given that the across-patient SuperEEG
 reconstructions exclude (from the correlation matrix estimates) all data from
@@
 provide additional predictive power to the data reconstructions beyond the
-information contained solely in nearby electrodes.  (This follows from the fact
+information contained solely in nearby electrodes.  This follows from the fact
 that each patient's grid, strip, and depth electrodes are implanted in a unique
 set of locations, so for any given electrode the closest electrodes in the full
-dataset tend to come from the same patient.)  Second, it implies that the
+dataset tend to come from the same patient.  Second, it implies that the
 spatial correlations learned using the SuperEEG algorithm are, to some extent,
@@
 patients performed a variety of (largely idiosyncratic) tasks throughout each
-day's recording session.  That we observed reliable reconstruction accuracy
-across patients suggests that the spatial correlations derived from the SuperEEG
+day's recording session.  That we observed reliable reconstructions  across
+patients suggests that the spatial correlations derived from the SuperEEG
 algorithm are, to some extent, similar across tasks.  We tested this finding
@@
 reconstruction accuracy was highest for the across-patient models limited to
-data from the same experiment (mean accuracy: $0.68$); next-highest for the
-models that combined data across both experiments (mean accuracy: $0.61$); and
-lowest for models trained across tasks (mean accuracy: $0.47$).  This pattern of
+data from the same experiment (mean accuracy: $r = 0.68$); next-highest for the
+models that combined data across both experiments (mean accuracy: $r = 0.61$); and
+lowest for models trained across tasks (mean accuracy: $r = 0.47$).  This pattern of
 results also held for each of the Dataset 2 experiments individually
@@
 
+\begin{figure}
+  \centering \includegraphics[width=\textwidth]{figs/density}
+  \caption{\textbf{Electrode sampling density by location.} \textbf{A.~Electrode
+  sampling density by voxel location in Dataset 1.} Each voxel is colored by the
+  proportion of total electrodes in the dataset that are located within 20~MNI
+  units of the given voxel.  \textbf{B.~Electrode sampling density by voxel
+  location in Dataset 2.}  This panel displays the sampling density map for
+  Dataset 2, in the same format as Panel A. \textbf{C.~Correspondence in
+  sampling density by voxel location across Datasets 1 and 2.}  The
+  two-dimensional histogram displays the per-voxel sampling densities in the two
+  Datasets, and the one-dimensional histograms display the proportions of voxels
+  in each dataset with the given density value.  The correlation reported in the
+  panel is across voxels in the 4~mm$^3$ MNI152 brain.} \label{fig:density}
+\end{figure}
+
 Although both datasets we examined provide good full-brain coverage (when
 considering data from every patient), electrodes were not sampled uniformly
-throughout the brain.  For example, electrodes are more likely to be implanted
-in regions like the medial temporal lobe (MTL), and are rarely implanted in
-occipital cortex (Fig.~\ref{fig:density}A, B). Separately for each dataset, for
-each voxel in the 4~mm$^3$ voxel MNI152 brain, we computed the proportion of
-electrodes in the dataset that were contained within a 20 MNI unit radius sphere
-centered on that voxel.  We defined the \textit{density} at that location as
-this proportion. Across Datasets 1 and 2, the electrode placement densities were
-similar (correlation by voxel: $r = 0.6, p < 10^{-10}$).  We wondered whether
-regions with good covererage might be associated with better reconstruction
-accuracy. For example, Figures~\ref{fig:density}A and B indicate that many
-electrodes in the MTL (which tends to be relatively densely sampled) have
-relatively high reconstruction accuracy, and occipital electrodes (which tends
-to be relatively sparsely sampled) tend to have relatively low reconstruction
-accuracy.  To test whether this held more generally across the entire brain, for
-each dataset we computed the electrode placement density for each electrode from
-each patient (using the proportion of \textit{other} patients' electrodes within
-20 MNI units of the given electrode).  We then correlated these density values
-with the across-patient reconstruction accuracies for each electrode.  We found
-no reliable correlation between reconstruction accuracy and density for Dataset
-1 ($r = 0.05, p = 0.70$) and a reliable negative correlation for Dataset 2 ($r =
+throughout the brain.  For example, in our patient population, electrodes are
+more likely to be implanted in regions like the medial temporal lobe (MTL), and
+are rarely implanted in occipital cortex (Fig.~\ref{fig:density}A, B).
+Separately for each dataset, for each voxel in the 4~mm$^3$ voxel MNI152 brain,
+we computed the proportion of electrodes in the dataset that were contained
+within a 20 MNI unit radius sphere centered on that voxel.  We defined the
+\textit{density} at that location as this proportion. Across Datasets 1 and 2,
+the electrode placement densities were similar (correlation by voxel: $r = 0.6,
+p < 10^{-10}$).  We wondered whether regions with good covererage might be
+associated with better reconstruction accuracy. For example,
+Figures~\ref{fig:corrmap}A and B indicate that many electrodes in the MTL (which
+tends to be relatively densely sampled) have relatively high reconstruction
+accuracy, and occipital electrodes (which tends to be relatively sparsely
+sampled) tend to have relatively low reconstruction accuracy.  To test whether
+this held more generally across the entire brain, for each dataset we computed
+the electrode placement density for each electrode from each patient (using the
+proportion of \textit{other} patients' electrodes within 20 MNI units of the
+given electrode).  We then correlated these density values with the
+across-patient reconstruction accuracies for each electrode.  We found no
+reliable correlation between reconstruction accuracy and density for Dataset 1
+($r = 0.05, p = 0.70$) and a reliable negative correlation for Dataset 2 ($r =
 -0.21, p = 0.05$).  This indicates that the reconstruction accuracies we
@@
 further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
-MannEtal09}.  We therefore wondered whether the reconstructions we observed
-might be differently weighting or considering the contributions of activity at
-different frequency bands.  We therefore examined a range of frequency bands
-($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz;
-$\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of
-broadband power.  We defined broadband power as the mean height of a linear
-robust regression fit in log-log space to the order 4 Morelet wavelet-computed
-power spectrum at 50 log-spaced frequencies from from 2--100
-Hz~\citep{MannEtal09}. We used second-order Butterworth bandpass filters to
-compute the activity patterns within each narrow frequency band.  We then
-repeated our within-subject and across-subject cross-validated reconstruction
-accuracy tests (analogous to Fig.~\ref{fig:corrmap}) separately for each
-frequency band (Fig.~\ref{fig:frequency}).  (We also carried out a similar
-analysis on the Hilbert transform-computed spectral power within each narrow
-band; see Fig.~\freqpower.)  Across both datasets, we found that our approach is
-best at reconstructing patterns of broadband activity (right-most bars in
+MannEtal09}.  We wondered whether the reconstructions we observed might be
+differently weighting or considering the contributions of activity at different
+frequency bands.  We therefore examined a range of frequency bands ($\delta$:
+2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz; $\gamma_L$:
+30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of broadband power.
+We used second-order Butterworth bandpass filters to compute the activity
+patterns within each narrow frequency band.  We defined broadband power as the
+mean height of a linear robust regression fit in log-log space to the order 4
+Morelet wavelet-computed power spectrum at 50 log-spaced frequencies from from
+2--100 Hz~\citep{MannEtal09}. We then repeated our within-subject and
+across-subject cross-validated reconstruction accuracy tests (analogous to
+Fig.~\ref{fig:corrmap}) separately for each frequency band
+(Fig.~\ref{fig:frequency}). (We also carried out a similar analysis on the
+Hilbert transform-computed spectral power within each narrow band; see
+Fig.~\freqpower.) Across both datasets, we found that our approach is best at
+reconstructing patterns of broadband activity (right-most bars in
 Figs.~\ref{fig:frequency}A and D), a correlate of population firing
@@
 results indicate that our approach is able to accurately recover information
-within the 2--100 Hz range, although those reconstructions are most accurate for
-low-frequency or broadband patterns.
+within the 2--100 Hz range.
 
@@
   \caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
-  datasets for each frequency triangles.} \textbf{A. Distributions of
-  correlations between observed versus reconstructed activity by electrode, for
-  each frequency band in Dataset 1.}  Each color denotes a different frequency
-  range. Within each color group, the darker dots and bar on the left display
-  the distribution (and mean) across-patient reconstruction accuracies
-  (analogous to the black histograms in Fig.~\ref{fig:corrmap}).  The lighter
-  dots and bar on the right display the distribution (and mean) within-patient
-  reconstruction accuracies (analogous to the gray histograms in
-  Fig.~\ref{fig:corrmap}). To facilitate visual comparison with the
-  frequency-specific results, the leftmost bars (gray) re-plot the histograms in
-  Fig.~\ref{fig:corrmap}A. \textbf{B.~Statistical summary of across-patient
-  reconstruction accuracy by electrode for each frequency band in Dataset 1.} In
-  the upper triangles of each map, warmer colors (positive $t$-values) indicate
-  that the distribution of reconstruction accuracy for the frequency band in a
-  given row yielded was greater than the frequency band in the given column.
-  Cooler colors (negative $t$-values) indicate that the frequency band in the
-  given row yielded lower reconstruction accuracy than the frequency band in the
-  given column. The lower triangles of each map denote the corresponding
+  datasets for each frequency band.} \textbf{A. Distributions of correlations
+  between observed versus reconstructed activity by electrode for each frequency
+  band in Dataset 1.}  Each color denotes a different frequency band. Within
+  each color group, the darker dots and bar on the left display the distribution
+  (and mean) across-patient reconstruction accuracies (analogous to the black
+  histograms in Fig.~\ref{fig:corrmap}).  The lighter dots and bar on the right
+  display the distribution (and mean) within-patient reconstruction accuracies
+  (analogous to the gray histograms in Fig.~\ref{fig:corrmap}). Each dot
+  indicates the reconstruction accuracy for one electrode in the dataset. To
+  facilitate visual comparison with the frequency-specific results, the leftmost
+  bars (gray) re-plot the histograms in Figure~\ref{fig:corrmap}A.
+  \textbf{B.~Statistical summary of across-patient reconstruction accuracy by
+  electrode for each frequency band in Dataset 1.} In the upper triangles of
+  each map, warmer colors (positive $t$-values) indicate that the reconstruction
+  accuracy for the frequency band in the given row was greater (via a two-tailed
+  paired-sample $t$-test) than for the frequency band in the given column.
+  Cooler colors (negative $t$-values) indicate that reconstruction accuracy for
+  the frequency band in the given row was lower than for the frequency band in
+  the given column. The lower triangles of each map denote the corresponding
   $p$-values for the $t$-tests. The diagonal entries display the average
@@
   for each frequency band in Dataset 2.} This panel displays reconstruction
-  accuracy distributions for each frequency range for Dataset 2.
+  accuracy distributions for each frequency band for Dataset 2.
   \textbf{E.--F.~Statistical summaries of across-patient and within-patient
@@
 
-\begin{figure}
-  \centering \includegraphics[width=\textwidth]{figs/density}
-  \caption{\textbf{Electrode sampling density by location.} \textbf{A.~Electrode
-  sampling density by voxel location in Dataset 1.} Each voxel is colored by the
-  proportion of total electrodes in the dataset that are located within a 20~MNI
-  unit radius sphere centered on the given voxel.  \textbf{B.~Electrode sampling
-  density by voxel location in Dataset 2.}  This panel displays the sampling
-  density map for Dataset 2, in the same format as Panel A.
-  \textbf{C.~Correspondence in sampling density by voxel location across
-  Datasets 1 and 2.}  The two-dimensional histogram displays the per-voxel
-  sampling densities in the two Datasets, and the one-dimensional histograms
-  display the proportions of voxels in each dataset with the given density
-  value.  The correlation reported in the panel is across voxels in the 4~mm$^3$
-  MNI152 brain.} \label{fig:density}
-\end{figure}
-
 A basic assumption of our approach (and of most prior ECoG work) is that
@@
 throughout the brain are meaningfully correlated, are there particular
-implantation locations that, recorded from in a given patient's brain, yield
+implantation locations that, if recorded from a given patient's brain, yield
 especially high reconstruction accuracies throughout the rest of their brain?
@@
 units of that voxel's center.  This yielded an \textit{information score} for
-each voxel, reflecting the average reconstruction accuracy across any patients
-with electrodes near each voxel-- where the averages were weighted to reflect
-patients who had more electrodes implanted near that location. We created a
-single map of these information scores for each dataset, highlighting regions
-that are especially informative about activity in \textit{other} brain areas
-(Fig.~\ref{fig:informap}A and B).  Despite task and patient differences across
-the two datasets, we nonetheless found that the maps of the most promising
-implantation targets derived from both datasets were correlated (voxel-wise
-correlation between information scores across the two datasets: $r = 0.18, p <
-10^{-10}$).  Our finding that there were some commonalities between the two
-datasets' maps lends support to the notion that different brain areas are
-(reliably) differently informative about full-brain activity patterns.  We also
-examined the intersection between the top 10\% most informative voxels across
-the two datasets (gray areas in Fig.~\ref{fig:informap}C, networks shown in
+each voxel, reflecting the (weighted) average reconstruction accuracy across any
+patients with electrodes near each voxel, where the averages were weighted to
+reflect patients who had more electrodes implanted near that location. We
+created a single map of these information scores for each dataset, highlighting
+regions that are especially informative about activity in \textit{other} brain
+areas (Figs.~\ref{fig:informap}A and B).  Despite task and patient differences
+across the two datasets, we nonetheless found that the information score maps
+from both datasets were correlated (voxelwise correlation between information
+scores across the two datasets: $r = 0.18, p < 10^{-10}$).  Our finding that
+there were some commonalities between the two datasets' information score maps
+lends support to the notion that different brain areas are (reliably)
+differently informative about full-brain activity patterns.  We also examined
+the intersection between the top 10\% most informative voxels across the two
+datasets (gray areas in Fig.~\ref{fig:informap}C, networks shown in
 Fig.~\ref{fig:networks}A, top row). Supporting the notion that structures that
@@
 computed analogous maps of information scores for each individual frequency
-range. Across Datasets 1 and 2 (with the exception of $\alpha$ band activity),
-we observed reliable positive correlations between the voxel-by-voxel maps of
+band. Across Datasets 1 and 2 (with the exception of $\alpha$-band activity),
+we observed reliable positive correlations between the voxelwise maps of
 information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p <
-10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$;
+10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$; $\beta$: $r = 0.02, p = 0.0011$;
 $\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$;
@@
 To gain additional insight into which regions were most informative about
-full-brain activity patterns at different frequency ranges, we next computed
-(for each frequency range) the intersection of the top 10\% highest information
-scores across the maps for Datasets 1 and 2 (analogous to our approach in
+full-brain activity patterns at different frequency bands, we next computed (for
+each frequency band) the intersection of the top 10\% highest information scores
+across the maps for Datasets 1 and 2 (analogous to our approach in
 Fig.~\ref{fig:informap}C). This yielded a single map of the (reliably) most
-informative locations, for each frequency range we examined. We then carried out
-\textit{post hoc} analyses on each of these maps to better characterize the
-underlying structural and functional properties of each set of regions we
-identified as being particularly informative about one or more neural patterns.
+informative locations, for each frequency band we examined. We then carried out
+\textit{post hoc} analyses on each of these maps to characterize the underlying
+structural and functional properties of each set of regions we identified as
+being particularly informative about one or more types of neural pattern.
 
@@
   \centering \includegraphics[width=\textwidth]{figs/networks}
-  \caption{\textbf{Most informative recording locations by frequency range.}
-  \textbf{A.~Intersections between information score maps by frequency range.}
+  \caption{\textbf{Most informative recording locations by frequency band.}
+  \textbf{A.~Intersections between information score maps by frequency band.}
   The regions indicated in each row depict the intersection between the top 10\%
@@
   identified by \cite{YeoEtal11}.  The relative sizes of the charts for each
-  frequency range reflct the average across-subject reconstruction accuracies
-  (Fig.~\ref{fig:corrmap}A, D).  The voxels in Panel A are colored according to
+  frequency band reflct the average across-subject reconstruction accuracies
+  (Figs.~\ref{fig:corrmap}A, D).  The voxels in Panel A are colored according to
   the same network memberships.  \textbf{C.~Neurosynth terms associated with the
-  most informative brain regions, by frequency range.}  The lists in each row
+  most informative brain regions, by frequency band.}  The lists in each row
   display the top five neurosynth terms~\citep{RubiEtal17} decoded for each
@@
   displays the union of the most informative maps in Panel A, colored by
-  frequency range.  The labels also serve as a legend for Panel C.}
+  frequency band.  The labels also serve as a legend for Panel C.}
   \label{fig:networks}
@@
 
-The frequency-specific information score maps we observed were consistent with
-the notion that there is no ``universal'' brain region that  reflects all
-activity patterns throughout the rest of the brain.  Rather, each region's
-activity patterns appear to be characterized by different spectral profiles, and
-the ability to infer full-brain activity patterns at a particular frequency
-range depends on the structural and functional connectome specific to that
-frequency range (Fig.~\ref{fig:networks}E).  We wondered how the maps we found
-might fit in with prior work.  To this end, in addition to examining the
-anatomical profiles of each map, we used Neurosynth~\citep{RubiEtal17} to
-identify (using meta analyses of the neuroimaging literature) the top five most
-common terms associated with each frequency-specific map
-(Fig.~\ref{fig:networks}C).  We found that $\delta$ patterns across the brain
-were best predicted by regions of ventromedial prefrontal cortex, striatum, and
-thalamus (yellow).  These regions are also implicated in modulating $\delta$
-oscillations during sleep, and are heavily interconnected with
-cortex~\citep[e.g.,][]{AmziSter98}.  The brain areas most predictive of
-full-brain $\theta$ patterns were occipital and parietal regions associated with
-visual processing and visual attention (light green). Prior work has implicated
-$\theta$ oscillations in these areas in periodic sampling of visual
-attention~\citep[e.g.,][]{BuscVanR10}.  We found that full-brain $\alpha$
+The variability we observed in the frequency-specific information score maps is
+consistent with the notion that there is no ``universal'' brain region that
+reflects all types of activity patterns throughout the rest of the brain.
+Rather, each region's activity patterns appear to be characterized by different
+spectral profiles, and the ability to infer full-brain activity patterns at a
+particular frequency band depends on the structural and functional connectome
+specific to that frequency band (Fig.~\ref{fig:networks}E).  We wondered how the
+maps we found might fit in with prior work.  To this end, in addition to
+examining the anatomical profiles of each map, we used
+Neurosynth~\citep{RubiEtal17} to identify (using meta analyses of the
+neuroimaging literature) the top five most common terms associated with each
+frequency-specific map (Fig.~\ref{fig:networks}C).  We found that $\delta$
+patterns across the brain were best predicted by regions of ventromedial
+prefrontal cortex, striatum, and thalamus (yellow).  These regions are also
+implicated in modulating $\delta$ oscillations during sleep, and are heavily
+interconnected with cortex~\citep[e.g.,][]{AmziSter98}.  The brain areas most
+informative about full-brain $\theta$ patterns were occipital and parietal regions
+associated with visual processing and visual attention (light green). Prior work
+has implicated $\theta$ oscillations in these areas in periodic sampling of
+visual attention~\citep[e.g.,][]{BuscVanR10}.  We found that full-brain $\alpha$
 patterns were best predicted by motor areas (dark green), which also exhibit
@@
 indictor that activity at those frequency ranges reflects that the given region
-is representing or supporting a particular function.  Our work suggests the
+is representing or supporting a particular function.  Our work suggests an
 alternative interpretation that when we observe a particular neural pattern in a
@@
 One body of work suggests that our brain's \textit{functional} networks are
-dynamic~\citep[e.g., ][]{MannEtal18}, person-specific~\citep[e.g.,
+dynamic~\citep[e.g., ][]{MannEtal18, OwenEtal19}, person-specific~\citep[e.g.,
 ][]{FinnEtal15}, and task-specific~\citep[e.g., ][]{Turk13}.  In contrast,
@@
 is similar across individuals.  Consistent with this hypothesis, our model
-explained the data best when we trained the correlation model using data from
-\textit{other} patients-- even when compared to a correlation model trained on
-the same patient's data.  Third, we resolved ambiguities in the data by
-hypothesizing that neural activity from nearby sources will tend to be similar,
-all else being equal.  This hypothesis was supported through our finding that
-all of the models we trained that incorporated this spatial smoothness
-assumption predicted held-out data well above chance.
+explained each patient's data best when trained using data from \textit{other}
+patients-- even when compared models trained within-patient. Third, we
+resolved ambiguities in the data by hypothesizing that neural activity from
+nearby sources tends to be similar, all else being equal.  This hypothesis
+was supported through our finding that all of the models we trained that
+incorporated this spatial smoothness assumption predicted held-out data well
+above chance.
 
@@
 Beyond providing a means of estimating ongoing activity throughout the brain
-using already implanted electrodes, our work also has implications how to
+using already-implanted electrodes, our work also has implications how to
 optimize electrode placements in neurosurgical evaluations. Electrodes are
@@
 analyses that would benefit from high spatiotemporal resolution full-brain data
-in individuals.
+in individuals, projected into a common ECoG space across people.
 

### 2020-03-09 paper/supporting_information.tex
editing supplement [WIP, does not compile]

@@
 
+\newcommand{\methods}{1}
+\newcommand{\corrmaps}{2}
+\newcommand{\freqs}{3}
+\newcommand{\density}{4}
+\newcommand{\infomap}{5}
+\newcommand{\infomapfreqs}{6}
+
 \begin{titlepage}
@@
 
-\begin{figure}[b!]
+\begin{figure}[p]
 \centering
 \includegraphics[width=\textwidth]{figs/supplemental_1}
-\caption{\textbf{Reconstruction quality for Datasets 1 and 2.}
+\caption{\textbf{Reconstruction quality across all electrodes in two
+    ECoG datasets, broken down by experiment.}
   \textbf{A. Distributions of correlations between observed versus
-    reconstructed activity by electrode, for Dataset 1.} The split
-  violin plot reflects the same data as Figure~3A, presented here for
-  comparison.  \textbf{B. Distributions of correlation between
-    observed versus reconstructed activity by electrode, for Dataset
-    2.}  The left-most split violin plot (``Within'') reflects the
-  same data as Figure~3B, presented here for comparison.  The
-  ``Across'' plot reflects the same analyses, but limited to models
-  that were trained and tested on \textit{different} Dataset 2
-  experiments.  The ``All'' plot reflects the same analyses, but
-  including models that were trained and tested on both of the Dataset
-  2 experiments.  All plots: the dark gray distributions denote
-  across-subject correlations (model trained on all but one patient
-  and tested on the held-out patient), and the medium gray
-  distributions denote within-subject correlations (model trained on
-  all but one electrode from one patient, and tested on the held-out
-  electrode).  The horizontal bars denote $t$-tests between the
-  corresponding distributions (after $z$-transforming the
-  correlations), and the white numbers reflect the distribution means.
-  The symbols denote the corresponding $p$-values of those statistical
-  tests.}
+    reconstructed activity by electrode, for Dataset 1.}  The
+  across-patient distribution (black) reflects reconstruction accuracy
+  (correlation) using a correlation model learned from all but one
+  patient's data, and then applied to that held-out patient's data.
+  The within-patient distribution (gray) reflects performance using a
+  correlation model learned from the same patient who contributed the
+  to-be-reconstructed electrode.  The split violin plot displays the
+  same distributions shown in Figure~\corrmaps A.
+  \textbf{B. Distributions of correlations for Dataset 2.}  The split
+  violin plots are in the same format as those in Panel A.  The
+  leftmost plot (``Within'') displays the same distributions shown in
+  Figure~\corrmaps B.  All reconstructions reflected in the
+  distribution were carried out using a model trained and tested using
+  data from the same experiment.  The middle plots (``Across'')
+  reflect reconstructions trained and tested using data from different
+  experiments.  The rightmost plot (``All'') reflect reconstructions
+  obtained using models trained and tested on data from both
+  experiments.  The black distributions reflect models trained and
+  tested across patients (analogous to the black histograms in
+  Figure~\corrmaps) and the gray distributions reflect models trained
+  and tested within patient (analogous to the gray histograms in
+  Figure~\corrmaps).  The dark gray significance bars reflect
+  paired-sample $t$-tests comparing the ($z$-transformed)
+  reconstruction accuracy for each electrode obtained within versus
+  across patients.  The black significance bars reflect paired-sample
+  $t$-tests comparing the across-patient reconstruction accuracies
+  across datasets.  The light gray significance bars reflect
+  paired-sample $t$-tests comparing the within-patient reconstruction
+  accuracies across datasets.  The symbols denote the corresponding
+  $p$-values of those statistical tests.}
 \label{fig:supplemental_1}
@@
 \includegraphics[width=\textwidth]{figs/supplemental_2}
-\caption{\textbf{Reconstruction quality for Dataset 2,
-    Experiments 1 and 2.} \textbf{A. Distributions of correlations
-    between observed versus reconstructed activity by electrode, for
-    Experiment 1.}  Each split violin plot and horizontal bar is in
-  the same format as the plots in Figure~\ref{fig:supplemental_1}.
-  ``Within'' denotes within-subject correlations (model trained on all
-  but one electrode from one patient, and tested on the held-out
-  electrode); ``Across'' denotes across-subject correlations (model
-  trained an all but one patient and tested on the held-out patient);
-  ``All'' denotes a model trained on all data from all patients,
-  except for one held-out electrode (and tested on the held-out
-  electrode).  \textbf{B. Distributions of correlations between
-    observed versus reconstructed activity by electrode, for
-    Experiment 2.}  All of the plots and bars are in the same format
-  as those in Panel A.}
+\caption{\textbf{Reconstruction quality for Dataset 2, Experiments 1
+    and 2.}  \textbf{A. Distributions of correlations between observed
+    versus reconstructed activity by electrode, for Dataset 2
+    (Experiment 1).}  The plots are in the same format as
+  Figure~\ref{fig:supplemental_1}B, but reflect data only from
+  Experiment 1 in Dataset 2.  \textbf{A. Distributions of correlations between observed
+    versus reconstructed activity by electrode, for Dataset 2
+    (Experiment 2).  The plots are in the same format as Panel A, but
+    reflect data only from Experiment 2 in Dataset 2.}} 
 \label{fig:supplemental_2}
@@
 
+%JRM STOPPED HERE
 \begin{figure}[p]
@@
 \includegraphics[width=\textwidth]{figs/supplemental_3}
+\caption{\textbf{Reconstruction quality across all electrodes, broken
+    down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
+      between observed versus reconstructed activity by electrode, for
+      Dataset 1.}  The across-patient distribution (black) reflects
+    reconstruction accuracy (correlation) using a correlation model
+    learned from all but one patient's data, and then applied to that
+    held-out patient's data.  The within-patient distribution (gray)
+    reflects performance using a correlation model learned from the same
+    patient who contributed the to-be-reconstructed electrode.
+    \textbf{B. Distributions of correlations for Dataset 2.}  This
+    panel is in the same format as Panel A, but reflects results
+    obtained from Dataset 2.  The histograms aggregate data across
+    both Dataset 2 experiments; for results broken down by experiment
+    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
+      performance by location.} The colors denote the average across-session
+    correlation, using the across-patient correlation model, between
+    the observed and reconstructed activity at the given electrode
+    location projected to the cortical surface~\citep{CombEtal19}.}
+
 \caption{\textbf{Reconstruction quality across all electrodes in two
@@
 
-\begin{figure}[ptb]
+\begin{figure}[p]
 \centering
@@
 
+\clearpage
+\newpage
 \renewcommand{\bibnumfmt}[1]{[S#1]}

### 2020-03-09 paper/main.tex

@@
   dots in Panel A, defined as $\bar{R}$ in the text).  The weights fall off with
-  positional distance~\citep[in MNI152 space;][]{LyttEtal07} according to an RBF. \textbf{C.~Per-patient
+  positional distance (in MNI152 space) according to an RBF. \textbf{C.~Per-patient
   correlation matrices.}  After computing the pairwise correlations between the
@@
 We first applied fourth order Butterworth notch filters to remove 60 Hz ($\pm$
-.5 Hz) line noise from every recording (from every electrode). Next, we
+0.5 Hz) line noise from every recording (from every electrode). Next, we
 downsampled the recordings (regardless of the original samplerate) to 250 Hz.
@@
 associated with better reconstruction accuracy. For example,
-Figures~\ref{fig:corrmap}A and B indicate that many electrodes in the MTL (which
+Figures~\ref{fig:corrmap}C and D indicate that some electrodes in the MTL (which
 tends to be relatively densely sampled) have relatively high reconstruction
@@
 ($r = 0.05, p = 0.70$) and a reliable negative correlation for Dataset 2 ($r =
--0.21, p = 0.05$).  This indicates that the reconstruction accuracies we
+-0.21, p = 0.05$).  This suggests that the reconstruction accuracies we
 observed are \textit{not} driven solely by sampling density, but rather may also
@@
 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz; $\gamma_L$:
-30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of broadband power.
-We used second-order Butterworth bandpass filters to compute the activity
+30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of broadband (BB)
+power. We used second-order Butterworth bandpass filters to compute the activity
 patterns within each narrow frequency band.  We defined broadband power as the
@@
   identified by \cite{YeoEtal11}.  The relative sizes of the charts for each
-  frequency band reflct the average across-subject reconstruction accuracies
-  (Figs.~\ref{fig:corrmap}A, D).  The voxels in Panel A are colored according to
+  frequency band reflect the average across-subject reconstruction accuracies
+  (Figs.~\ref{fig:frequency}A, D).  The voxels in Panel A are colored according to
   the same network memberships.  \textbf{C.~Neurosynth terms associated with the

### 2020-03-11 paper/supporting_information.tex
editing supplement [WIP, does not compile]
backing up progress [WIP]

@@
     reflect data only from Experiment 2 in Dataset 2.}}
-\label{fig:supplemental_2}
-\end{figure}
-
-%JRM STOPPED HERE
-\begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_3}
-\caption{\textbf{Reconstruction quality across all electrodes, broken
-    down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Dataset 1.}  The across-patient distribution (black) reflects
-    reconstruction accuracy (correlation) using a correlation model
-    learned from all but one patient's data, and then applied to that
-    held-out patient's data.  The within-patient distribution (gray)
-    reflects performance using a correlation model learned from the same
-    patient who contributed the to-be-reconstructed electrode.
-    \textbf{B. Distributions of correlations for Dataset 2.}  This
-    panel is in the same format as Panel A, but reflects results
-    obtained from Dataset 2.  The histograms aggregate data across
-    both Dataset 2 experiments; for results broken down by experiment
-    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
-      performance by location.} The colors denote the average across-session
-    correlation, using the across-patient correlation model, between
-    the observed and reconstructed activity at the given electrode
-    location projected to the cortical surface~\citep{CombEtal19}.}
-
-\caption{\textbf{Reconstruction quality across all electrodes in two
-      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
-    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
- \textbf{B. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Experiment 2.}  Same format as Figure~3A and B, but reflects
-    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
-    plot).  \textbf{C.--D.  Reconstruction
-      performance by location.} Each dot reflects the location of a
-    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
-    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
-    average within-experiment (across-session)
-    correlation, using the across-patient correlation model, between
-    the observed and reconstructed activity at the given electrode
-    location projected to the cortical surface~\citep{CombEtal19}.}
+% \label{fig:supplemental_2}
+% \end{figure}
+%
+% %JRM STOPPED HERE
+% \begin{figure}[p]
+% \centering
+% \includegraphics[width=\textwidth]{figs/supplemental_3}
+% \caption{\textbf{Reconstruction quality across all electrodes, broken
+%     down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
+%       between observed versus reconstructed activity by electrode, for
+%       Dataset 1.}  The across-patient distribution (black) reflects
+%     reconstruction accuracy (correlation) using a correlation model
+%     learned from all but one patient's data, and then applied to that
+%     held-out patient's data.  The within-patient distribution (gray)
+%     reflects performance using a correlation model learned from the same
+%     patient who contributed the to-be-reconstructed electrode.
+%     \textbf{B. Distributions of correlations for Dataset 2.}  This
+%     panel is in the same format as Panel A, but reflects results
+%     obtained from Dataset 2.  The histograms aggregate data across
+%     both Dataset 2 experiments; for results broken down by experiment
+%     see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
+%       performance by location.} The colors denote the average across-session
+%     correlation, using the across-patient correlation model, between
+%     the observed and reconstructed activity at the given electrode
+%     location projected to the cortical surface~\citep{CombEtal19}.}
+%
+%
+% \caption{\textbf{Reconstruction quality across all electrodes in two
+%       Dataset 2 experiments.}  \textbf{A. Distributions of correlations
+%       between observed versus reconstructed activity by electrode, for
+%       Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
+%     in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
+%  \textbf{B. Distributions of correlations
+%       between observed versus reconstructed activity by electrode, for
+%       Experiment 2.}  Same format as Figure~3A and B, but reflects
+%     data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
+%     plot).  \textbf{C.--D.  Reconstruction
+%       performance by location.} Each dot reflects the location of a
+%     single implanted electrode from Dataset 2, Experiment 1 (Panel C)
+%     or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
+%     average within-experiment (across-session)
+%     correlation, using the across-patient correlation model, between
+%     the observed and reconstructed activity at the given electrode
+%     location projected to the cortical surface~\citep{CombEtal19}.}
 \label{fig:supplemental_3}

### 2020-03-11 paper/supporting_information.tex
working on suplement

--- 2020-03-09 paper/supporting_information.tex
@@
 \includegraphics[width=\textwidth]{figs/supplemental_1}
-\caption{\textbf{Reconstruction quality across all electrodes in two
+\caption{\textbf{Reconstruction accuracy across all electrodes in two
     ECoG datasets, broken down by experiment.}
@@
 \includegraphics[width=\textwidth]{figs/supplemental_2}
-\caption{\textbf{Reconstruction quality for Dataset 2, Experiments 1
+\caption{\textbf{Reconstruction accuracy for Dataset 2, Experiments 1
     and 2.}  \textbf{A. Distributions of correlations between observed
@@
     versus reconstructed activity by electrode, for Dataset 2
-    (Experiment 2).  The plots are in the same format as Panel A, but
-    reflect data only from Experiment 2 in Dataset 2.}} 
+    (Experiment 2).}  The plots are in the same format as Panel A, but
+    reflect data only from Experiment 2 in Dataset 2.}
 \label{fig:supplemental_2}
@@
 
-%JRM STOPPED HERE
 \begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_3}
-\caption{\textbf{Reconstruction quality across all electrodes, broken
-    down by Dataset 2 experiment.}  \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Dataset 1.}  The across-patient distribution (black) reflects
-    reconstruction accuracy (correlation) using a correlation model
-    learned from all but one patient's data, and then applied to that
-    held-out patient's data.  The within-patient distribution (gray)
-    reflects performance using a correlation model learned from the same
-    patient who contributed the to-be-reconstructed electrode.
-    \textbf{B. Distributions of correlations for Dataset 2.}  This
-    panel is in the same format as Panel A, but reflects results
-    obtained from Dataset 2.  The histograms aggregate data across
-    both Dataset 2 experiments; for results broken down by experiment
-    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
-      performance by location.} The colors denote the average across-session
-    correlation, using the across-patient correlation model, between
-    the observed and reconstructed activity at the given electrode
-    location projected to the cortical surface~\citep{CombEtal19}.}
-
-\caption{\textbf{Reconstruction quality across all electrodes in two
-      Dataset 2 experiments.}  \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Experiment 1.}  Same format as Figure~3A and B, but reflects data shown
-    in Figure~\ref{fig:supplemental_2}A (leftmost violin plot).
- \textbf{B. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      Experiment 2.}  Same format as Figure~3A and B, but reflects
-    data shown in Figure~\ref{fig:supplemental_2}B (leftmost violin
-    plot).  \textbf{C.--D.  Reconstruction
-      performance by location.} Each dot reflects the location of a
-    single implanted electrode from Dataset 2, Experiment 1 (Panel C)
-    or Dataset 2, Experiment 2 (Panel D).  The dot colors denote the
-    average within-experiment (across-session)
-    correlation, using the across-patient correlation model, between
-    the observed and reconstructed activity at the given electrode
-    location projected to the cortical surface~\citep{CombEtal19}.}
+\centering \includegraphics[width=\textwidth]{figs/supplemental_3}
+\caption{\textbf{Reconstruction accuracy across all electrodes in Dataset 2.}
+This figure is analogous to Figure~\corrmaps in the main text, but displays data
+for Dataset 2 broken down by experiment. \textbf{A. Distributions of
+correlations between observed versus reconstructed activity by electrode for
+Experiment 1.}  The across-patient distribution (black) reflects reconstruction
+accuracy (correlation) using a correlation model learned from all but one
+patient's data, and then applied to that held-out patient's data.  The
+within-patient distribution (gray) reflects performance using a correlation
+model learned from the same patient who contributed the to-be-reconstructed
+electrode. \textbf{B. Distributions of correlations for Experiment 2.}  This
+panel is in the same format as Panel A, but reflects results obtained from
+Experiment 2. \textbf{C.--D. Reconstruction accuracy by location.} The colors
+denote the average across-session correlations, using the across-patient
+correlation model, between the observed and reconstructed activity at the given
+electrode location projected to the cortical surface~\citep{CombEtal19}.  Panel
+C displays the map for Experiment 1 and Panel D displays the map for Experiment 2.}
 \label{fig:supplemental_3}
@@
 \includegraphics[width=\textwidth]{figs/supplemental_4}
-\caption{\textbf{Reconstruction quality across all electrodes in two
-      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      each frequency band in Dataset 1.} Same format as Figure~5A, but
-    using power at each frequency.
-    \textbf{B.~Statistical summary of across-patient reconstruction
-      quality by electrode for each frequency band in Dataset 1.} Same format as Figure~5B, but
-    using power at each frequency.\textbf{C.~Statistical summary of within-patient reconstruction
-      quality by electrode for each frequency band in Dataset 1.}
-    This panel displays the within-patient statistical summary,
-    in the same format as Panel B.  \textbf{D.~Distributions of correlations
-      between observed versus reconstructed activity by electrode, for
-      each frequency band in Dataset 2.}  This panel displays
-    reconstruction accuracy distributions for each frequency band for
-    Dataset 2. \textbf{E.~Statistical summary of
-      across-patient reconstruction quality by electrode for each
-      frequency band in Dataset 2.} This is the same format as Panel
-    B for Dataset 2. \textbf{F.~Statistical summary of
-      within-patient reconstruction quality by electrode for each
-      frequency band in Dataset 2.}This is the same format as Panel
-    C for Dataset 2.}
+\caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
+datasets for power in each frequency band.} This figure is analogous to
+Figure~\freqs in the main text, but displays the reconstruction accuracies of
+the \textit{power} in each frequency band, rather than the bandpass-filtered
+voltages, as in Figure~\freqs. \textbf{A. Distributions of correlations between
+observed versus reconstructed power by electrode for each frequency band in
+Dataset 1.}  Each color denotes a different frequency band. Within each color
+group, the darker dots and bar on the left display the distribution (and mean)
+across-patient reconstruction accuracies (analogous to the black histograms in
+Fig.~\corrmaps).  The lighter dots and bar on the right display the distribution
+(and mean) within-patient reconstruction accuracies (analogous to the gray
+histograms in Fig.~\corrmaps). Each dot indicates the reconstruction accuracy
+for one electrode in the dataset. \textbf{B.~Statistical summary of
+across-patient reconstruction accuracy by electrode for each frequency band in
+Dataset 1.} In the upper triangles of each map, warmer colors (positive
+$t$-values) indicate that the reconstruction accuracy for the frequency band in
+the given row was greater (via a two-tailed paired-sample $t$-test) than for the
+frequency band in the given column. Cooler colors (negative $t$-values) indicate
+that reconstruction accuracy for the frequency band in the given row was lower
+than for the frequency band in the given column. The lower triangles of each map
+denote the corresponding $p$-values for the $t$-tests. The diagonal entries
+display the average reconstruction accuracy within each frequency band.
+\textbf{C.~Statistical summary of within-patient reconstruction accuracy by
+electrode for each frequency band in Dataset 1.} This panel displays the
+within-patient statistical summary, in the same format as Panel B.
+\textbf{D.~Distributions of correlations between observed versus reconstructed
+activity by electrode, for each frequency band in Dataset 2.} This panel
+displays reconstruction accuracy distributions for each frequency band for
+Dataset 2. \textbf{E.--F.~Statistical summaries of across-patient and
+within-patient reconstruction accuracy by electrode for each frequency band in
+Dataset 2.} These panels are in the same as Panels B and C, but display results
+from Dataset 2.}
 \label{fig:supplemental_4}
@@
 \begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_5}
-\caption{\textbf{Most informative electrode locations by frequency
-      and the networks involved.}
-    \textbf{A.~Intersections across datasets for each frequency.}  Same format as Figure~6A, but
-    using power at each frequency.
-    \textbf{B.~Proportion of networks in most informative electrode locations by
-    frequency.}  Pie graphs display the proportion of the 7 networks
-  ~\citep{YeoEtal11} in the most informative locations by
-  frequency, and are sized relative to the average reconstruction
-  accuracy for each frequency. \textbf{C.~Terms associated with most informative
-    electrode locations.}  The
-    lists of terms display the top five Neurosynth
-    terms~\citep{RubiEtal17} decoded from the corresponding brain
-    maps, and colored according the frequency (see Panel
-    E legend). \textbf{D.~Network parcellation from~\citep{YeoEtal11}.}
-    Seven network parcellation as described
-    in~\citep{YeoEtal11}. \textbf{E.~Most informative locations by
-      frequency.} The inflated brain plot displays the locations of
-    the most informative locations (Panel A), colored by frequency,
-    and projected onto the cortical surface~\citep{CombEtal19}.}
+\centering \includegraphics[width=\textwidth]{figs/supplemental_5}
+\caption{\textbf{Most informative recording locations by frequency band.} This
+figure is analogous to Figure~\infomapfreqs in the main text, but displays the
+brain regions that were most informative about the \textit{power} in each
+frequency band (whereas Fig.~\infomapfreqs displays the regions that were most
+informative about the bandpass-filtered voltages within each band).
+\textbf{A.~Intersections between information score maps by frequency band.} The
+regions indicated in each row depict the intersection between the top 10\% most
+informative locations across Datasets 1 and 2.  \textbf{B.~Network memberships
+of the most informative brain regions.}  The pie charts display the proportions
+of voxels in each region that belong to the seven networks identified by
+\cite{YeoEtal11}.  The relative sizes of the charts for each frequency band
+reflect the average across-subject reconstruction accuracies
+(Figs.~\ref{fig:frequency}A, D).  The voxels in Panel A are colored according to
+the same network memberships.  \textbf{C.~Neurosynth terms associated with the
+most informative brain regions, by frequency band.}  The lists in each row
+display the top five neurosynth terms~\citep{RubiEtal17} decoded for each
+region.  \textbf{D.~Network parcellation map and legend.}  The parcellation
+defined by \cite{YeoEtal11} is displayed on the inflated brain maps.  The colors
+and network labels serve as a legend for Panels A and B. \textbf{E.~Combined map
+of the most informative brain regions.}  The map displays the union of the most
+informative maps in Panel A, colored by frequency band.  The labels also serve
+as a legend for Panel C.}
 \label{fig:supplemental_5}
@@
 \begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_6}
-\caption{\textbf{Reconstruction accuracy versus within-subject data
-    features for two ECoG datasets.} \textbf{A.--F.  Features from
-    Dataset 1.}  Features include: (\textbf{A.}) total number of
-  electrodes implanted in each patient's brain, (\textbf{B.})
-  per-patient number of electrodes that were filtered out due to
-  having an maximum kurtosis greater than 10 across all recording
-  sessions, (\textbf{C.})  per-patient proportion of electrodes that
-  were filtered out due to having an average kurtosis greater than 10,
-  (\textbf{D.})  per-patient number of recording sessions,
-  (\textbf{E.}) per-patient total recording time (h), and
-  (\textbf{F.}) per-patient average session length (h).
-  \textbf{G.--L. Features from Dataset 2.}  Analogous format to Panels
-  A--F.}
+\centering \includegraphics[width=\textwidth]{figs/supplemental_6}
+\caption{\textbf{Reconstruction accuracy versus within-subject data features for
+two ECoG datasets.} The individual dots in each panel  reflect data from one
+patient.  The least-squares linear regression lines (with shaded 95\% confidence
+intervals) and the correlations reported in each panel are between the data
+shown on the $x$- and $y$-axes of the panel.  The $y$-axis in each panel
+denotes the average $z$-transformed correlation between the observed and
+predicted voltage timeseries at each electrode (across all of the patient's
+electrodes). The cross-validated predictions were obtained using the
+across-patient model (Fig.~\corrmaps A and B, black histograms).  \textbf{A.--F.
+Dataset 1.}  \textbf{A. Total electrodes.}  The $x$-coordinates of each dot
+display the total number of electrodes implanted in each patient's brain.
+\textbf{B. Number thresholded.}  The $x$-coordinates of each dot display the
+number of implanted electrodes that survived the kurtosis-based filtering
+procedure (see \textit{Approach}).  \textbf{C. Proportion thresholded.} The
+$x$-coordinates of each dot display the \textit{proportion} of each patient's
+implanted electrodes (relative to the total number) that survived the
+kurtosis-based filtering procedure.  \textbf{D. Sessions.}  The $x$-coordinates of each dot display the
+number of distinct recording sessions contributed by each patient.  \textbf{E. Total time.} The $x$-coordinates of each dot display the
+total duration (in hours) of each patient's recordings, across all of their recording sessions.
+\textbf{F.
+Average session length.} The $x$-coordinates of each dot display average duration (in hours) of the patient's recording sessions.
+  \textbf{G.--L. Features from Dataset 2.}  These panels display analogous information to Panels A--F, but for Dataset 2 patients.}
 \label{fig:supplemental_6}

### 2020-03-11 paper/supporting_information.tex
updated supplemental fig captions, pending final info from lucy

@@
 \begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_1}
-\caption{\textbf{Reconstruction accuracy across all electrodes in two
-    ECoG datasets, broken down by experiment.}
-  \textbf{A. Distributions of correlations between observed versus
-    reconstructed activity by electrode, for Dataset 1.}  The
-  across-patient distribution (black) reflects reconstruction accuracy
-  (correlation) using a correlation model learned from all but one
-  patient's data, and then applied to that held-out patient's data.
-  The within-patient distribution (gray) reflects performance using a
-  correlation model learned from the same patient who contributed the
-  to-be-reconstructed electrode.  The split violin plot displays the
-  same distributions shown in Figure~\corrmaps A.
-  \textbf{B. Distributions of correlations for Dataset 2.}  The split
-  violin plots are in the same format as those in Panel A.  The
-  leftmost plot (``Within'') displays the same distributions shown in
-  Figure~\corrmaps B.  All reconstructions reflected in the
-  distribution were carried out using a model trained and tested using
-  data from the same experiment.  The middle plots (``Across'')
-  reflect reconstructions trained and tested using data from different
-  experiments.  The rightmost plot (``All'') reflect reconstructions
-  obtained using models trained and tested on data from both
-  experiments.  The black distributions reflect models trained and
-  tested across patients (analogous to the black histograms in
-  Figure~\corrmaps) and the gray distributions reflect models trained
-  and tested within patient (analogous to the gray histograms in
-  Figure~\corrmaps).  The dark gray significance bars reflect
-  paired-sample $t$-tests comparing the ($z$-transformed)
-  reconstruction accuracy for each electrode obtained within versus
-  across patients.  The black significance bars reflect paired-sample
-  $t$-tests comparing the across-patient reconstruction accuracies
-  across datasets.  The light gray significance bars reflect
-  paired-sample $t$-tests comparing the within-patient reconstruction
-  accuracies across datasets.  The symbols denote the corresponding
-  $p$-values of those statistical tests.}
+\centering \includegraphics[width=\textwidth]{figs/supplemental_1}
+\caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
+datasets, broken down by experiment.} \textbf{A. Distributions of correlations
+between observed versus reconstructed activity by electrode, for Dataset 1.}
+The across-patient distribution (black) reflects reconstruction accuracy
+(correlation) using a correlation model learned from all but one patient's data,
+and then applied to that held-out patient's data. The within-patient
+distribution (gray) reflects performance using a correlation model learned from
+the same patient who contributed the to-be-reconstructed electrode.  The split
+violin plot displays the same distributions shown in Figure~\corrmaps A.  The
+white numbers within each half denote the means of each distribution. \textbf{B.
+Distributions of correlations for Dataset 2.}  The split violin plots are in the
+same format as those in Panel A.  The leftmost plot (``Within'') displays the
+same distributions shown in Figure~\corrmaps B.  All reconstructions reflected
+in the distribution were carried out using a model trained and tested using data
+from the same experiment.  The middle plots (``Across'') reflect reconstructions
+trained and tested using data from different experiments.  The rightmost plot
+(``All'') reflect reconstructions obtained using models trained and tested on
+data from both experiments.  The black distributions reflect models trained and
+tested across patients (analogous to the black histograms in Figure~\corrmaps)
+and the gray distributions reflect models trained and tested within patient
+(analogous to the gray histograms in Figure~\corrmaps).  The dark gray
+significance bars reflect paired-sample $t$-tests comparing the
+($z$-transformed) reconstruction accuracy for each electrode obtained within
+versus across patients.  The black significance bars reflect paired-sample
+$t$-tests comparing the across-patient reconstruction accuracies across
+datasets.  The light gray significance bars reflect paired-sample $t$-tests
+comparing the within-patient reconstruction accuracies across datasets.  The
+symbols denote the corresponding $p$-values of those statistical tests.}
 \label{fig:supplemental_1}
@@
 \caption{\textbf{Reconstruction accuracy across all electrodes in Dataset 2.}
-This figure is analogous to Figure~\corrmaps in the main text, but displays data
+This figure is analogous to Figure~\corrmaps~in the main text, but displays data
 for Dataset 2 broken down by experiment. \textbf{A. Distributions of
@@
 datasets for power in each frequency band.} This figure is analogous to
-Figure~\freqs in the main text, but displays the reconstruction accuracies of
+Figure~\freqs~in the main text, but displays the reconstruction accuracies of
 the \textit{power} in each frequency band, rather than the bandpass-filtered
@@
 \caption{\textbf{Most informative recording locations by frequency band.} This
-figure is analogous to Figure~\infomapfreqs in the main text, but displays the
+figure is analogous to Figure~\infomapfreqs~in the main text, but displays the
 brain regions that were most informative about the \textit{power} in each
-frequency band (whereas Fig.~\infomapfreqs displays the regions that were most
+frequency band (whereas Fig.~\infomapfreqs~displays the regions that were most
 informative about the bandpass-filtered voltages within each band).
@@
 reflect the average across-subject reconstruction accuracies
-(Figs.~\ref{fig:frequency}A, D).  The voxels in Panel A are colored according to
+(Figs.~\freqs A, D).  The voxels in Panel A are colored according to
 the same network memberships.  \textbf{C.~Neurosynth terms associated with the
@@
 \begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_7}
-\caption{\textbf{Stability of correlation matrix across time.} \textbf{A.--B.  Features from
-    Dataset 1.}  Features include: (\textbf{A. Correlation of split
-  halves by the percent samples included.})  For each patient, we
-  split the timeseries data in
-  half and created a correlation matrix with one half.  With the
-  remaining data, we created the second correlation matrix with more
-  and more time samples (in 1000 sample increments).  These time
-  samples were either drawn randomly (``Random'') , or were drawn sequentially from
-  either the closest timepoint (``Close'' ) or the furthest timepoint
-  (``Apart'' ). The two correlation matrices were then correlated, and the
-  coefficient plotted relative to the percentage of data included.  (\textbf{B. Correlation of split
-  halves by the number of time samples included.})
-Same analysis as Panel A, but the
-  coefficient plotted relative to the total number of samples included.
-  \textbf{C.--D. Features from Dataset 2.}  Analogous format to Panels
-  A--B.}
+\centering \includegraphics[width=\textwidth]{figs/supplemental_7}
+\caption{\textbf{Temporal stability of estimated patient-specific correlation
+matrices.}  For each patient $s$, we computed their patient-specific correlation
+matrix ($C_s$) using two different subsets of their recorded data.  We
+correlated the upper triangles of these estimates of $C_s$ to obtain a single
+correlation for each participant, reflecting how stable (in time) the estimates
+were.  We computed this stability measure, for each patient, as a function of
+how much data was used to estimate each $C_s$ (expressed as a proportion of the
+patient's total dataset, as in Panels \textbf{A} and \textbf{C}; or as the total duration of the
+patient's recordings, as in Panels \textbf{B} and \textbf{D}).  We also varied how the timepoints
+that went into each estimate were related. Specifically, we first concatenated the data from each patient's recording sessions to
+construct a single data timeseries (ignoring session boundaries) for each patient.  We then constructed two
+estimates of $C_s$ by drawing each patient's data from two equally sized sets of timepoints chosen from their multi-session data matrix.
+The timepoints were drawn either at \textit{random} without replacement (teal lines); from equally sized timespans at the start and end of the multi-session data matrix (\textit{apart}, blue lines); or from two equally sized timespans just prior to and just after the data midpoint (\textit{close}, purple lines).
+Panels A and B display the resulting correlations for Dataset 1, and panels C and D display the correlations for Dataset 2.
+Error ribbons in all panels denote 95\% confidence intervals (computed across patients).}
 \label{fig:supplemental_7}
@@
 \begin{figure}[p]
-\centering
-\includegraphics[width=\textwidth]{figs/supplemental_8}
-\caption{\textbf{Stability of correlation matrix across patients.} \textbf{A.--B.  Features from
-    Dataset 1.}  Features include: (\textbf{A. Correlation of split
-  halves by number of patients included.})  For 500 iterations, we randomly split the
-patient-specific correlations in half, then created one correlation
-matrix with the first half and created the second correlation matrix
-using more and more patients. The two correlation matrices were then correlated, and the
-  coefficient plotted relative to the number of patients included.
-  (\textbf{B. Standard error of the mean across iterations by the
-    number of patients included.})
-To measure the variability across the iterations, we plot the standard
-error of the mean as a function of the number of patients included in
-the second correlation matix.
-  \textbf{C.--D. Features from Dataset 2.}  Analogous format to Panels
-  A--B.}
+\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
+\caption{\textbf{Stability of full-brain correlation matrices across patients.}
+We estimated full-brain correlation matrices ($\bar{K}$) using different subsets
+of patients from each dataset. We explored how stable these estimates were as a
+function of how many patients were used to compute $\bar{K}$. For each sample
+size $n$ (number of patients), we drew two non-overlapping sets of $n$ patients
+(without replacement) from the full set of patients in each dataset.
+We then estimated $\bar{K}$ using the two sets of $n$ patients.
+We computed the correlation between the upper triangles of these matrices as a measure of how similar the matrices were.
+We repeated this procedure 500 times for each value of $n$ (ranging from 1 up to $\frac{1}{2}$ of the total number of patients in the given dataset); this yielded a distribution of correlation coefficients for each value of $n$.
+Panels \textbf{A} and \textbf{C} diplay the mean correlations as a function of $n$ for Datasets 1 and 2, respectively.
+The error ribbons denote 95\% confidence intervals (computed across iterations).
+Panels \textbf{B} and \textbf{D} display
+the standard error of the mean (SEM) of these distributions of correlations as a function of $n$, for Datasets 1 and 2, respectively.  The error ribbons
+denote bootstrap-derived 95\% confidence intervals.}
 \label{fig:supplemental_8}

### 2020-03-11 paper/main.tex
minor spellchecking and formatting

@@
 1 is a random-word list free recall task; Experiment 2 is a categorized list
-free recall task (24 patients particpated in both).  We wondered whether a
+free recall task (24 patients participated in both).  We wondered whether a
 correlation model learned from data from one experiment might yield good
@@
 
-\section*{Author Information}
-Reprints and permissions information is available
-at www.nature.com/reprints.  The authors declare no competing financial
-interests.  Readers are welcome to comment on the online version of the paper.
-Publisher's note: Springer Nature remains neutral with regard to jurisdictional
-claims in published maps and institutional affiliations.  Correspondence and
-requests for materials should be addressed to J.R.M.
-(jeremy.r.manning@dartmouth.edu).
-
+%\clearpage
 \bibliography{CDL-bibliography/memlab}
@@
 
-\clearpage
-
 \end{document}

### 2020-03-11 paper/main.tex
updated description of random analysis

@@
 reconstructed better than high-frequency patterns ($\gamma_L$ and $\gamma_H$),
-with reconstruction accuracy peaking in the $\alpha$ band.  Overall, these
+with reconstruction accuracy peaking in the $\theta$ band.  Overall, these
 results indicate that our approach is able to accurately recover information

### 2020-03-11 paper/supporting_information.tex
minor spellchecking and formatting
updated description of random analysis

@@
-\documentclass[10pt]{article}
+\documentclass[11pt]{article}
 \usepackage[utf8]{inputenc}
@@
 \centering \includegraphics[width=\textwidth]{figs/supplemental_7}
-\caption{\textbf{Temporal stability of estimated patient-specific correlation
-matrices.}  For each patient $s$, we computed their patient-specific correlation
-matrix ($C_s$) using two different subsets of their recorded data.  We
-correlated the upper triangles of these estimates of $C_s$ to obtain a single
-correlation for each participant, reflecting how stable (in time) the estimates
-were.  We computed this stability measure, for each patient, as a function of
-how much data was used to estimate each $C_s$ (expressed as a proportion of the
-patient's total dataset, as in Panels \textbf{A} and \textbf{C}; or as the total duration of the
-patient's recordings, as in Panels \textbf{B} and \textbf{D}).  We also varied how the timepoints
-that went into each estimate were related. Specifically, we first concatenated the data from each patient's recording sessions to
-construct a single data timeseries (ignoring session boundaries) for each patient.  We then constructed two
-estimates of $C_s$ by drawing each patient's data from two equally sized sets of timepoints chosen from their multi-session data matrix.
-The timepoints were drawn either at \textit{random} without replacement (teal lines); from equally sized timespans at the start and end of the multi-session data matrix (\textit{apart}, blue lines); or from two equally sized timespans just prior to and just after the data midpoint (\textit{close}, purple lines).
-Panels A and B display the resulting correlations for Dataset 1, and panels C and D display the correlations for Dataset 2.
-Error ribbons in all panels denote 95\% confidence intervals (computed across patients).}
+\caption{\textbf{Temporal stability of estimated patient-specific
+    correlation matrices.}  For each patient $s$, we computed their
+  patient-specific correlation matrix ($C_s$) using two different
+  subsets of their recorded data.  We correlated the upper triangles
+  of these estimates of $C_s$ to obtain a single correlation for each
+  participant, reflecting how stable (in time) the estimates were.  We
+  computed this stability measure, for each patient, as a function of
+  how much data was used to estimate each $C_s$ (expressed as a
+  proportion of the patient's total dataset, as in Panels \textbf{A}
+  and \textbf{C}; or as the total duration of the patient's
+  recordings, as in Panels \textbf{B} and \textbf{D}).  We also varied
+  how the timepoints that went into each estimate were
+  related. Specifically, we first concatenated the data from each
+  patient's recording sessions to construct a single data timeseries
+  (ignoring session boundaries) for each patient.  We then constructed
+  two estimates of $C_s$ by drawing each patient's data from two
+  equally sized sets of $t$ timepoints chosen from their multi-session
+  data matrix.  These timepoints were drawn either at \textit{random}
+  without replacement (teal lines); from equally sized timespans at
+  the start and end of the multi-session data matrix (\textit{apart},
+  blue lines); or from two equally sized timespans just prior to and
+  just after the data midpoint (\textit{close}, purple lines).  For
+  the random condition of this analysis, as we increased $t$, we
+  ensured that all of the timepoints included in the analysis for
+  smaller values of $t$ were also included in the analyses for larger
+  values of $t$.  For example, the randomly drawn timepoints for
+  $t = 2000$ included the same timepoints drawn for $t = 1000$, plus
+  an additional 1000 new timepoints.  Panels A and B display the
+  resulting correlations for Dataset 1, and panels C and D display the
+  correlations for Dataset 2.  Error ribbons in all panels denote 95\%
+  confidence intervals (computed across patients).}
 \label{fig:supplemental_7}
@@
 \centering \includegraphics[width=\textwidth]{figs/supplemental_8}
-\caption{\textbf{Stability of full-brain correlation matrices across patients.}
-We estimated full-brain correlation matrices ($\bar{K}$) using different subsets
-of patients from each dataset. We explored how stable these estimates were as a
-function of how many patients were used to compute $\bar{K}$. For each sample
-size $n$ (number of patients), we drew two non-overlapping sets of $n$ patients
-(without replacement) from the full set of patients in each dataset.
-We then estimated $\bar{K}$ using the two sets of $n$ patients.
-We computed the correlation between the upper triangles of these matrices as a measure of how similar the matrices were.
-We repeated this procedure 500 times for each value of $n$ (ranging from 1 up to $\frac{1}{2}$ of the total number of patients in the given dataset); this yielded a distribution of correlation coefficients for each value of $n$.
-Panels \textbf{A} and \textbf{C} diplay the mean correlations as a function of $n$ for Datasets 1 and 2, respectively.
-The error ribbons denote 95\% confidence intervals (computed across iterations).
-Panels \textbf{B} and \textbf{D} display
-the standard error of the mean (SEM) of these distributions of correlations as a function of $n$, for Datasets 1 and 2, respectively.  The error ribbons
-denote bootstrap-derived 95\% confidence intervals.}
+\caption{\textbf{Stability of full-brain correlation matrices across
+    patients.}  We estimated full-brain correlation matrices
+  ($\bar{K}$) using different subsets of patients from each
+  dataset. We explored how stable these estimates were as a function
+  of how many patients were used to compute $\bar{K}$. For each sample
+  size $n$ (number of patients), we drew two non-overlapping sets of
+  $n$ patients (without replacement) from the full set of patients in
+  each dataset. We then estimated $\bar{K}$ using the two sets of $n$
+  patients.  We computed the correlation between the upper triangles
+  of these matrices as a measure of how similar the matrices were.  We
+  repeated this procedure 500 times for each value of $n$ (ranging
+  from 1 up to $\frac{1}{2}$ of the total number of patients in the
+  given dataset); this yielded a distribution of correlation
+  coefficients for each value of $n$.  Panels \textbf{A} and
+  \textbf{C} display the mean correlations as a function of $n$ for
+  Datasets 1 and 2, respectively.  The error ribbons denote 95\%
+  confidence intervals (computed across iterations).  Panels
+  \textbf{B} and \textbf{D} display the standard error of the mean
+  (SEM) of these distributions of correlations as a function of $n$,
+  for Datasets 1 and 2, respectively.  The error ribbons denote
+  bootstrap-derived 95\% confidence intervals.}
 \label{fig:supplemental_8}
@@
 \newpage
+\renewcommand{\refname}{Supplemental references}
 \renewcommand{\bibnumfmt}[1]{[S#1]}
@@
 % \newpage
-% \renewcommand{\refname}{Supplemental references}
+
 % \bibliography{memlab}

### 2020-03-11 paper/main.tex
implemented overline suggestion from tudor

@@
   patient (black) weights on the full set of locations under consideration (all
-  dots in Panel A, defined as $\bar{R}$ in the text).  The weights fall off with
+  dots in Panel A, defined as $\overline{R}$ in the text).  The weights fall off with
   positional distance (in MNI152 space) according to an RBF. \textbf{C.~Per-patient
@@
   recordings from each patient's electrodes, we use RBF-weighted averages to
-  estimate correlations between all locations in $\bar{R}$.  We obtain an
+  estimate correlations between all locations in $\overline{R}$.  We obtain an
   estimated full-brain correlation matrix using each patient's data.
@@
 correlations in the data to estimate these anatomical
-connections~\citep{BeckEtal18}.  Let $\bar{R}$ be the set of locations at which
-we wish to estimate local field potentials, and let $R_{s} \subseteq \bar{R}$ be
+connections~\citep{BeckEtal18}.  Let $\overline{R}$ be the set of locations at which
+we wish to estimate local field potentials, and let $R_{s} \subseteq \overline{R}$ be
 set of locations at which we observe local field potentials from patient $s$
 (excluding the electrodes that did not pass the kurtosis test described above).
-In the analyses below we define $\bar{R} = \cup_{s=1}^S R_s$.  We can calculate
+In the analyses below we define $\overline{R} = \cup_{s=1}^S R_s$.  We can calculate
 the expected inter-electrode correlation matrix for patient $s$, where
@@
 \begin{align}
-  \bar{C}_{s} &=
+  \overline{C}_{s} &=
   \mathrm{r}\left(\frac{1}{n}\left(\sum_{k=1}^{n}\mathrm{z}(C_{s,k})\right)\right),\label{eqn:inter_corr}~\mathrm{where}\\
@@
   $W_s$ approximates how informative the recordings at each location in $R_s$
-  are in reconstructing activity at each location in $\bar{R}$, where the
+  are in reconstructing activity at each location in $\overline{R}$, where the
   contributions fall off with an RBF according to the distances between the
@@
 Given this weight matrix, $W_s$, and the observed inter-electrode correlation
-matrix for patient $s$, $\bar{C}_{s}$, we can estimate the correlation matrix
-for all locations in $\bar{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:
+matrix for patient $s$, $\overline{C}_{s}$, we can estimate the correlation matrix
+for all locations in $\overline{R}$ ($\hat{C}_s$; Fig.~\ref{fig:methods}C) using:
 
 \begin{align}
-\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\bar{C}_{s}(i,j))}\label{eqn:subj_corrmat_num}\\
+\hat{N}_{s}(x,y) & = { \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i) \cdot W(y,j)\cdot \mathrm{z}(\overline{C}_{s}(i,j))}\label{eqn:subj_corrmat_num}\\
  \hat{D}_{s}(x,y) & = \sum_{i = 1}^{| R_{s}|}\sum_{j=1}^{i-1} W(x,i)
@@
 Having used the multi-patient data to estimate a full-brain correlation matrix
-at the set of locations in $\bar{R}$ that we wish to know about, we next use
-$\hat{K}$ to estimate activity patterns everywhere in $\bar{R}$, given
-observations at only a subset of locations in $\bar{R}$
+at the set of locations in $\overline{R}$ that we wish to know about, we next use
+$\hat{K}$ to estimate activity patterns everywhere in $\overline{R}$, given
+observations at only a subset of locations in $\overline{R}$
 (Fig.~\ref{fig:methods}E).
@@
 Let $\alpha_s$ be the set of indices of patient $s$'s electrode locations in
-$\bar{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of
-indices of all other locations in $\bar{R}$. In other words, $\beta_s$ reflects
-the locations in $\bar{R}$ where we did not observe a recording for patient $s$
+$\overline{R}$ (i.e., the locations in $R_s$), and let $\beta_s$ be the set of
+indices of all other locations in $\overline{R}$. In other words, $\beta_s$ reflects
+the locations in $\overline{R}$ where we did not observe a recording for patient $s$
 (these are the recording locations we will want to fill in using SuperEEG). We
@@
 estimates of the time-varying voltages at \textit{every} location in
-$\bar{R}$, provided that we define $\bar{R}$ in advance to include the
+$\overline{R}$, provided that we define $\overline{R}$ in advance to include the
 union of all of the locations in $R_s$ and all of the locations
@@
 to estimate, up to a constant scaling factor, local field potentials (LFPs) for
-each patient at all arbitrarily chosen locations in the set $\bar{R}$,
+each patient at all arbitrarily chosen locations in the set $\overline{R}$,
 \textit{even if we did not record that patient's brain at all of those
@@
 SuperEEG-reconstructed voltage traces and the observed voltage traces from that
-electrode.  For this analysis we set $\bar{R}$ to be the union of all electrode
+electrode.  For this analysis we set $\overline{R}$ to be the union of all electrode
 locations across all patients.  This yielded a single correlation coefficient
-for each electrode location in $\bar{R}$, reflecting how well the SuperEEG
+for each electrode location in $\overline{R}$, reflecting how well the SuperEEG
 algorithm was able to recover the recording at that location by incorporating

### 2020-03-11 paper/supporting_information.tex
implemented overline suggestion from tudor

@@
     patients.}  We estimated full-brain correlation matrices
-  ($\bar{K}$) using different subsets of patients from each
+  ($\overline{K}$) using different subsets of patients from each
   dataset. We explored how stable these estimates were as a function
-  of how many patients were used to compute $\bar{K}$. For each sample
+  of how many patients were used to compute $\overline{K}$. For each sample
   size $n$ (number of patients), we drew two non-overlapping sets of
   $n$ patients (without replacement) from the full set of patients in
-  each dataset. We then estimated $\bar{K}$ using the two sets of $n$
+  each dataset. We then estimated $\overline{K}$ using the two sets of $n$
   patients.  We computed the correlation between the upper triangles

### 2020-03-11 paper/main.tex
updated supplemental figure references in main text, added references to S7 and S8

@@
 
-\newcommand{\perexpcorrmaps}{S1}
-\newcommand{\perexptaskrecon}{S2}
-\newcommand{\perexptaskreconseparated}{S3}
+\newcommand{\combinedexpviolins}{S1}
+\newcommand{\splitexpviolins}{S2}
+\newcommand{\splitexpcorrmaps}{S3}
 \newcommand{\freqpower}{S4}
@@
 \newcommand{\suppstats}{S6}
+\newcommand{\temporalstability}{S7}
+\newcommand{\patientstability}{S8}
 
@@
 \section*{Results}
-We used a cross-validation approach to test the accuracy with
-which the SuperEEG algorithm reconstructs activity throughout the brain. For
+We used a cross-validation approach to test the accuracy with which
+the SuperEEG algorithm reconstructs activity throughout the brain. For
 each patient in turn, we estimated full-brain correlation matrices
-(Eqn.~\ref{eqn:corrmat}) using data from all of the \textit{other} patients.
-This step ensured that the data we were reconstructing could not also be used to
-estimate the between-location correlations that drove the reconstructions via
-Equation~\ref{eqn:reconstruction} (otherwise the analysis would be circular).
-For that held-out patient, we held out each electrode in turn.  We used
-Equation~\ref{eqn:reconstruction} to reconstruct activity at the held-out
-electrode location, using the correlation matrix learned from all other
-patients' data as $\hat{K}$, and using activity recorded from the other
-electrodes from the held-out patient as $Y_{s, k, \alpha_s}$.  We then asked:
-how closely did each of the SuperEEG-estimated recordings at those electrodes
-match the observed recordings from those electrodes (i.e., how closely did the
-estimated $\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$)?
+(Eqn.~\ref{eqn:corrmat}) using data from all of the \textit{other}
+patients.  This step ensured that the data we were reconstructing
+could not also be used to estimate the between-location correlations
+that drove the reconstructions via Equation~\ref{eqn:reconstruction}
+(otherwise the analysis would be circular).  For that held-out
+patient, we held out each electrode in turn.  We used
+Equation~\ref{eqn:reconstruction} to reconstruct activity at the
+held-out electrode location, using the correlation matrix learned from
+all other patients' data as $\hat{K}$, and using activity recorded
+from the other electrodes from the held-out patient as
+$Y_{s, k, \alpha_s}$.  (For analyses examining the stability of our
+estimates of $\hat{K}$ across time and patients, see
+Figs.~\temporalstability~and \patientstability, respectively).  We then asked: how closely did each of the
+SuperEEG-estimated recordings at those electrodes match the observed
+recordings from those electrodes (i.e., how closely did the estimated
+$\hat{Y}_{s, k, \beta_s}$ match the observed $Y_{s, k, \beta_s}$)?
 
@@
 $t(77) = 11.25, p < 10^{-10}$). We also replicated this result separately for
-each of the two experiments from Dataset 2 (Fig.~\perexpcorrmaps).  This overall
+each of the two experiments from Dataset 2 (Fig.~\splitexpcorrmaps).  This overall
 finding, that reconstructions of held-out data using correlation models learned
@@
   across both Dataset 2 experiments; for results broken down by experiment see
-  Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction accuracy by
+  Figures~\splitexpviolins~and~\splitexpcorrmaps. \textbf{C.--D.  Reconstruction accuracy by
   location.} The colors denote the average across-session correlations, using
@@
 trained within versus across the two experiments, or combining across both
-experiments (Fig.~\perexptaskrecon).  In every case we found that across-patient
+experiments (Fig.~\combinedexpviolins).  In every case we found that across-patient
 models trained using data from all other patients out-performed within-patient
@@
 results also held for each of the Dataset 2 experiments individually
-(Fig.~\perexptaskreconseparated).  Taken together, these results indicate that
+(Fig.~\splitexpviolins).  Taken together, these results indicate that
 there are reliable commonalities in the spatial correlations of full-brain
@@
 structural and functional properties of each set of regions we identified as
-being particularly informative about one or more types of neural pattern.
+being particularly informative about one or more types of neural
+pattern (Figs.~\ref{fig:networks} and~\networkpower).
 

### 2020-03-12 code/notebooks/plot.py
update to stability figure size

@@ -835,8 +835,8 @@ def plot_split_barplot_colors(df, X, Y, H, x_order, hue_order, left_colors, righ
         axes[e].spines['bottom'].set_visible(False)
 
         z_df = df_temp.copy(deep=True)
-        z_df[Y] = r2z(z_df[Y])
-        yposlist = z2r(z_df.groupby([X, H])[Y].mean())
+        z_df[Y] = r2z(z_df[Y] + offset)
+        yposlist = z2r(z_df.groupby([X, H])[Y].mean()) - offset
         xposlist = range(1)
 
         locs,labels = plt.yticks()

### 2020-03-13 paper/supporting_information.tex

--- 2020-03-11 paper/supporting_information.tex
@@
     patients.}  We estimated full-brain correlation matrices
-  ($\bar{K}$) using different subsets of patients from each
+  ($\hat{K}$) using different subsets of patients from each
   dataset. We explored how stable these estimates were as a function
-  of how many patients were used to compute $\bar{K}$. For each sample
+  of how many patients were used to compute $\hat{K}$. For each sample
   size $n$ (number of patients), we drew two non-overlapping sets of
   $n$ patients (without replacement) from the full set of patients in
-  each dataset. We then estimated $\bar{K}$ using the two sets of $n$
+  each dataset. We then estimated $\hat{K}$ using the two sets of $n$
   patients.  We computed the correlation between the upper triangles

### 2020-04-15 paper/main.tex
fixed typo
proposed modifications to address reviewer concerns

@@
   millisecond-scale temporal resolutions using standard human
-  intracranial recordings.  Our approach assumes that different
-  people's brains exhibit similar correlational structure, and that
-  activity and correlation patterns vary smoothly over space.  One can
-  then ask, for an arbitrary individual's brain: given recordings from
-  a limited set of locations in that individual's brain, along with
-  the observed spatial correlations learned from other people's
-  recordings, how much can be inferred about ongoing activity at
-  \textit{other} locations throughout that
-  individual's brain?  We show that our approach generalizes across
-  people and tasks, thereby providing a person- and task-general means
-  of inferring high spatiotemporal resolution full-brain neural
-  dynamics from standard low-density intracranial recordings.
+  intracranial recordings.  Our approach makes the simplifying
+  assumptions that different people's brains exhibit similar
+  correlational structure, and that activity and correlation patterns
+  vary smoothly over space.  One can then ask, for an arbitrary
+  individual's brain: given recordings from a limited set of locations
+  in that individual's brain, along with the observed spatial
+  correlations learned from other people's recordings, how much can be
+  inferred about ongoing activity at \textit{other} locations
+  throughout that individual's brain?  We show that our approach
+  generalizes across people and tasks, thereby providing a person- and
+  task-general means of inferring high spatiotemporal resolution
+  full-brain neural dynamics from standard low-density intracranial
+  recordings.
   \\\\
@@
 the electrode placement densities were similar (correlation by voxel: $r = 0.6,
-p < 10^{-10}$).  We wondered whether regions with good covererage might be
+p < 10^{-10}$).  We wondered whether regions with good coverage might be
 associated with better reconstruction accuracy. For example,
@@
 components of the local field potential tend to have higher power and extend
-further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
+further in space than high-frequency components~\citep[e.g., ][]{MillEtal07a,
 MannEtal09}.  We wondered whether the reconstructions we observed might be
@@
 
-Taken together, the frequency-specific information maps suggest a potential new
-interpretation of many of the above previously reported findings.  Prior work
-has largely treated region-specific narrowband and broadband activity as an
-indictor that activity at those frequency ranges reflects that the given region
-is representing or supporting a particular function.  Our work suggests an
-alternative interpretation that when we observe a particular neural pattern in a
-particular brain region, it may instead reflect how that region is is
-transmitting information to the rest of the brain via signalling at the given
-frequency range.
-
-\section*{Discussion}
-Are our brain's networks static or dynamic?  And to what
+\section*{Discussion} Are our brain's networks static or dynamic?  And to what
 extent are the network properties of our brains stable across people and tasks?
@@
 resting state functional connectivity data~\citep{BeckEtal18}.  Similarly, other
-work indicates that task-specific functional connectivity may be predicted by
+work indicates that task-specific functional activations may be predicted by
 resting state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.
@@
 are constrained by anatomy, but nevertheless exhibit (potentially rapid)
-task-dependent changes~\citep[e.g., ][]{SporBetz16}.
+task-dependent changes~\citep[e.g., ][]{SporBetz16}.  This prior work differs
+from ours in a number of ways.  For example, fMRI data has substantially higher
+spatial resolution than (raw) ECoG data, and fMRI data have nearly complete
+spatial overlap across participants whereas ECoG data have minimal spatial
+overlap across participants.  Nevertheless, our work draws inspiration from
+those studies in that we also attempt to estimate held-out activity patterns
+across people and tasks.
 
@@
 
+Another important finding is that SuperEEG-based reconstructions accurately
+recover activity patterns at a broad range of frequencies (as well as broadband
+patterns).  However, brain networks differed in how informative they were about
+activity within each frequency band.  Prior work has largely treated
+region-specific narrowband and broadband activity as an indicator that activity
+at those frequency ranges reflects that the given region is representing or
+supporting a particular function.  Our work suggests a complementary
+interpretation that when we observe a particular neural pattern in a particular
+brain region, it may instead (or in addition) reflect how that region is
+transmitting information to the rest of the brain via signalling at the given
+frequency range.
+
 One potential limitation of our approach is that it does not provide a natural
@@
 (Fig.~\ref{fig:frequency}).
+
+A second potential limitation of our approach is that it relies on
+ECoG data from epilepsy patients.  Recent work comparing functional
+correlations in epilepsy patients (measured using ECoG) and healthy
+individuals (measured using fMRI) suggests that there are gross
+similarities between these populations~\citep[e.g.,][]{ReddEtal18,
+  KucyEtal18}.  Nevertheless, because all of the patients we examined
+have drug-resistant epilepsy, it remains uncertain how generally the
+findings reported here might apply more broadly to the population at
+large (e.g., non-clinical populations).
 
@@
 different locations. This feature of our approach enables across-patient ECoG
-studies, analogous to across-patient fMRI studies~\citep[e.g.,][]{HaxbEtal01,
+studies, analogous to across-subject fMRI studies~\citep[e.g.,][]{HaxbEtal01,
 NormEtal06, HaxbEtal11}. Whereas the focus of this manuscript is to specifically

### 2020-04-15 code/notebooks/plot.py
square r values

@@ -357,6 +357,106 @@ def plot_2_histograms(df, X, Y, xticks=True, legend=True, outfile=None):
     print('t test: ')
     print(t_stat_group)
 
+
+def plot_2r_histograms(df, X, Y, xticks=True, legend=True, outfile=None):
+
+    grouped_results = df.groupby('Subject')[Y, X].mean()
+    one_sided_t_across = stats.ttest_1samp(grouped_results[Y],  0)
+    one_sided_t_within = stats.ttest_1samp(grouped_results[X],  0)
+
+    print('one sided t test for across: ')
+    print(one_sided_t_across)
+
+
+    print('one sided t test for within: ')
+    print(one_sided_t_within)
+
+    t_stat_group = stats.ttest_rel(grouped_results[Y],grouped_results[X])
+
+    fig = plt.gcf()
+    fig.set_size_inches(18.5, 8.5)
+    fig.subplots_adjust(left=0.2, bottom=.2)
+    bin_values = np.arange(start=-1, stop=1, step=.01)
+
+
+    ax = sns.distplot(z2r(df[X]), hist=True, kde=True,
+             bins=bin_values, color = 'k',
+             hist_kws={'edgecolor':'lightgray', 'alpha':.3},
+             kde_kws={'linewidth': 4, 'alpha':1, 'color':'lightgray'})
+
+
+    ax = sns.distplot(z2r(df[Y]), hist=True, kde=True,
+             bins=bin_values, color = 'k',
+             hist_kws={'edgecolor':'k', 'alpha':.7},
+             kde_kws={'linewidth': 4, 'alpha':1, 'color':'k'})
+
+    ax.spines['right'].set_visible(False)
+    ax.spines['top'].set_visible(False)
+    left, width = .05, .5
+    bottom, height = .25, .5
+    n_count = len(df[Y].values)
+
+    ax.set_xlim(0, 1)
+
+    #ax.get_yaxis().set_major_formatter(mtick.FormatStrFormatter('%.1e'))
+
+    vals = ax.get_yticks()
+    ax.set_yticklabels([np.round(x/n_count*10000,2) for x in vals])
+    f = mtick.ScalarFormatter(useOffset=False, useMathText=True)
+    g = lambda x,pos : "${}$".format(f._formatSciNotation('%1.10e' % x))
+    fmt = mtick.FuncFormatter(g)
+
+    t_left, t_width = 0, .5
[…]

### 2020-04-18 paper/rev1.tex

--- 2020-04-15 paper/main.tex
@@
 
-\section*{Discussion} Are our brain's networks static or dynamic?  And to what
+Taken together, the frequency-specific information maps suggest a potential new
+interpretation of many of the above previously reported findings.  Prior work
+has largely treated region-specific narrowband and broadband activity as an
+indicator that activity at those frequency ranges reflects that the given region
+is representing or supporting a particular function.  Our work suggests an
+alternative interpretation that when we observe a particular neural pattern in a
+particular brain region, it may instead reflect how that region is 
+transmitting information to the rest of the brain via signalling at the given
+frequency range.
+
+\section*{Discussion}
+Are our brain's networks static or dynamic?  And to what
 extent are the network properties of our brains stable across people and tasks?
@@
 resting state functional connectivity data~\citep{BeckEtal18}.  Similarly, other
-work indicates that task-specific functional activations may be predicted by
+work indicates that task-specific functional connectivity may be predicted by
 resting state functional connectivity data~\citep{ColeEtal16, TavoEtal16}.
@@
 are constrained by anatomy, but nevertheless exhibit (potentially rapid)
-task-dependent changes~\citep[e.g., ][]{SporBetz16}.  This prior work differs
-from ours in a number of ways.  For example, fMRI data has substantially higher
-spatial resolution than (raw) ECoG data, and fMRI data have nearly complete
-spatial overlap across participants whereas ECoG data have minimal spatial
-overlap across participants.  Nevertheless, our work draws inspiration from
-those studies in that we also attempt to estimate held-out activity patterns
-across people and tasks.
+task-dependent changes~\citep[e.g., ][]{SporBetz16}.
 
@@
 above chance.
-
-Another important finding is that SuperEEG-based reconstructions accurately
-recover activity patterns at a broad range of frequencies (as well as broadband
-patterns).  However, brain networks differed in how informative they were about
-activity within each frequency band.  Prior work has largely treated
-region-specific narrowband and broadband activity as an indicator that activity
-at those frequency ranges reflects that the given region is representing or
-supporting a particular function.  Our work suggests a complementary
-interpretation that when we observe a particular neural pattern in a particular
-brain region, it may instead (or in addition) reflect how that region is
-transmitting information to the rest of the brain via signalling at the given
-frequency range.
 
